### 2018-11-02 draft.tex
Init

\documentclass{llncs}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{color}
\usepackage{alltt}
\usepackage{xspace}
\usepackage{multirow}
\pagestyle{plain}
\usepackage{xcolor}
\usepackage{algorithm2e}
\usepackage{tikz}
\usepackage{etoolbox}
\usepackage{mathtools}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{listings}
%\usepackage{adjustbox}
%\usetikzlibrary{arrows,calc}
\captionsetup{compatibility=false}
%\usepackage{a4wide}
%\usepackage[margin=40mm, top=35mm]{geometry}

%\usepackage{latexsym}
\usepackage{setspace}
\usepackage{cancel}
\usepackage{graphicx}
\usepackage{appendix}
\usepackage{amssymb}
\usepackage{dsfont}
%\usepackage{cancel}
%\usepackage{verbatim}
%\usepackage{chngpage}
%\usepackage{xcolor}
%\usepackage{mathrsfs}

\lstset{language=Java,
	basicstyle=\ttfamily\footnotesize,
	showspaces=false,
	showtabs=false,
	breaklines=true,
	showstringspaces=false,
	breakatwhitespace=true,
	commentstyle=\color{pgreen},
	keywordstyle=\color{blue},
	stringstyle=\color{red},
	basicstyle=\ttfamily
}

\newcommand{\Var}{\mathtt{Var}}
\newcommand{\Exp}{\mathtt{Exp}}
\newcommand{\Cmd}{\mathtt{Cmd}}
\newcommand{\Grd}{\mathtt{Grd}}
\newcommand{\Prg}{\mathtt{Prg}}
\DontPrintSemicolon
\SetKwRepeat{Loop}{Loop\{}{\}}%

\newcommand{\true}{\mathsf{true}}
\newcommand{\false}{\mathsf{false}}

\newcommand{\hide}[1]{}
\newcommand{\defn}{\overset{\triangle}{=}}
\newcommand{\maxi}{m}
\newcommand{\cur}{cur()}
\newcommand{\dom}[1]{\mathsf{dom}(#1)}
\newcommand{\ite}[3]{
	 \ifmmode 
	 \mathbf{if}\ #1 \ \mathbf{then}\ #2\  \mathbf{else}\ #3 
	 \else
	 \textbf{if}\ #1 \ \textbf{then}\ #2\  \textbf{else}\ #3
	 \fi}
\newcommand{\rloop}{
	\ifmmode 
	\mathbf{Loop}
	\else
	\textbf{Loop}
	\fi}

\newcommand{\Z}{\mathbb{Z}}

\title{J-ReCoVer: Java Reducer Commutativity Verifier}

\author{
Yu-Fang Chen\inst{1}\inst{2}
\and
Chang-Yi Chiang\inst{2}
\and
Hung-Wei Hsu\inst{1}
\and
Wei-Tsung Kao\inst{1}
\and
Yen-Fu Wen\inst{2}
\and
Wei-Cheng Wu\inst{1}
}
\institute
{
Institute of Information Science, Academia Sinica, Taiwan
\and
Graduate Institute of Information Management, National Taipei University, Taiwan
}

\begin{document}

\maketitle

\begin{abstract}

MapReduce framework for data-parallel computation was first proposed by Google~\cite{dean04} and later implemented in the Apache Hadoop project~\cite{hadoop}.
Under the MapReduce framework, the reducer component computes output values from a sequence of input values transmitted over the network.  Due to the non-determinism in data transmission, the order of input values arrived at the reducer component is not fixed.
The \emph{commutativity problem} of reducers asks if the output of a reducer is independent of the order of its inputs. There are several advantages for a reducer being commutative, e.g., the verification problem of a MapReduce program can be reduced to the problem of verifying a sequential program. 
In this paper, we propose effective heuristics for reducer commutative analysis and implement them as a tool J-ReCoVer (Java Reducer Commutativity Verifier), which is the first tool that is specialized in checking reducer commutativity. Experimental results over 128 benchmark examples collected from literatures and open repositories are very positive; J-ReCoVer correctly handles over 97\% of them.

\end{abstract}

\section{Introduction}
\label{section:introduction}

MapReduce is one of the most popular framework for data parallel computation.
A MapReduce~\cite{dean04,hadoop} program consists of several pairs of \emph{mappers} and \emph{reducers} running on a machine cluster for handling big data in parallel. Usually mappers and reducers are the only components in a MapReduce program that involves concurrency. Mappers read data from a distributed database and output a sequence of \emph{key-value} pairs. The sequence elements (key-value pairs) with the same key will be sent to the same reducer for further processing. Due to scheduling polices and network latency, the same list of values may arrive a reducer in different order in different executions, which results in the so-called \emph{commutativity problem} of reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}, that is, if the outputs of a reducer is independent of the order of its inputs. 
If all reducers are commutative, then they will have the same external behavior under all possible schedules. In such a case, by fixing a schedule, the verification problem of a MapReduce program can be reduced to the verification problem of a sequential program, which is known to be much easier then concurrent verification.

\hide{More concretely, for the verification of a MapReduce program, we propose to do it in two phases. First, ensuring if all reducers are commutative. If some reducers are non-commutative, modifying them to commutative ones. Usually, the modification is not a difficult task~\cite{xiao14mr}, and can be done without affecting their functionality and performance. For example, assume that the task of a reducer is to find the name of the person with highest score. Such a reducer is non-commutative when the input include two people with the same highest score. This reducer can be made commutative, by also comparing the ID number of people with the same score. Once all reducers are made commutative, we reduce the verification problem to sequential verification by fixing a scheduler. In this two-phase approach, the key enabling technique is an efficient procedure for checking reducer commutativity.}

On the other hand, in many cases, the non-commutative behavior of a reducer can be the source of very tricky bugs. A study conducted by Microsoft investigated the commutativity problem of $508$ reducers running on their MapReduce server~\cite{xiao14mr}. The reducer programs have been checked carefully using all traditional means such as code review, testing, and experiments with real data for months. Still, among them, five programs contain very subtle bugs caused by non-commutativity (confirmed by the programmers).

However, checking reducer commutativity is a difficult problem on its own right~\cite{ChenHSW15,ChenSW16,ChenLTW17}. Even for a simple case that all values are mathematical integers, it is proved undecidable in~\cite{ChenHSW15}. For the case that all values are machine integer (e.g, 64-bits integer), the problem is decidable, but the only available algorithm that was proposed in the same paper is of very high complexity and hence is only of theoretical interests.

In this paper, we propose heuristics for the commutativity problem that works very efficiently on a large set of practical integer reducer programs. We reduce the commutativity problem to a SMT problem in a sounds but incomplete manner; it  reports commutative only when it holds for all possible initial valuations, even if some of them are in fact unreachable. We also propose optimizations to enable the approach working on real world examples. For the case that the reducer is not proven commutative, we complement the approach by using testing to find concrete counterexamples. We implement those heuristics as a tool called J-ReCoVer (Java Reducer Commutativity Verifier), which is available at~\verb|http://jrecover.iis.sinica.edu.tw|.

We use 2 sets of integer reducer benchmarks to evaluate J-ReCoVer. The first set is collected from open repositories such as Github, Bitbuckect, and GoogleCode. With the help of a search engine~\cite{searchcode} over those repositories, we collected 118 examples. J-ReCoVer is able to correctly analyze all but 3 of them. We also tried all 10 Integer reducers descried in verification literatures~\cite{ChenHSW15,ChenSW16} and J-ReCoVer can handle all of them in almost no time.

\subsection*{Related Works}
Reducer commutativity problem can be reduced to program equivalence problem. One creates a variant $R'$ of the original reducer program $R$ such that $R'$ non-deterministically swaps two consecutive input elements and then executes the code of $R$. If $R'$ and $R$ are equivalent, using the fact that all permutation of a list can be obtained by swapping consecutive list elements finitely many times, $R$ can be proved to be commutative.

There are a series of research results on program equivalence checking (a.k.a regression verification)~\cite{symdiff,fedyukovich2015automated,sharma2013data,godlin2009regression,fedyukovich2016property,felsing2014automating,KieferKlebanovUlbrich2017,lahiri2013differential,grossman2017verifying,barthe2011relational,KlebanovRuemmerUlbrich2017}. At a high level, checking equivalence of two programs $P$ and $P'$ can be reduced to a sequential verification problem by executing $P'$ after $P$ and at the end asserting they have the same outputs. It can be made more efficient by finding the right~\emph{synchronization points} and combining the code of $P$ and $P'$ in a interleaved manner. A lot of the research effort in this research direction is in finding good synchronization points. For the case of commutativity analysis, good synchronization points are already given; one can simply use the beginning of the loop as the synchronization point. However, in our experience, if we naively reduce the commutativity problem to equivalence problem and check it in a precise manner, many examples cannot be solved. In this paper, we propose a good over-approximation (c.f. Section~\ref{sec:prover}) of the reducer's behavior. The approximation allows a much more efficient yet precise enough commutativity analysis.

One main motivation of commutativity analysis is to reduce verification problem of a concurrent program to a sequential one. There are several researches sharing the similar motivation. For instance, the concept of \emph{robustness} of event-driven asynchronous programs~\cite{ahmed2017:robustness}  and program running under relaxed memory model~\cite{ahmed2013:robustness,AbdullaACLR13,AbdullaACLR12}, \emph{synchronizability} of communicating finite state machines~\cite{FinkelL17,basu2012synchronizability,basu2011choreography}. However, their computation models are quite different to that of reducers and hence the result cannot be directly applied. Besides verification, another interesting research direction is the synthesis of MapReduce programs~\cite{SmithA16}. Commutativity analysis is used as a component under this framework.

\section{Notations and Definitions}
\label{section:integer-reducers}
For the presentation purpose, we will describe a highly simplified model to characterize the essence of reducers. The model allows to describe the computation of reducers and investigate their commutativity.

\begin{equation*}
\begin{array}{rclcl}
\multicolumn{3}{l}{v\in \Var\mbox{, and }c \in \Z}&&\textmd{Variable and Constant}\\
e \in \Exp    &\ \ \  {\triangleq}\ \ \   & v \mid c \mid \cur \mid e + e \mid e - e \mid e \times e \mid *\mid\ldots & &\textmd{Integer Expression}\\
g\in \Grd  & {\triangleq}  & e < e \mid not\ e \mid g \wedge g  \mid \ldots& & \textmd{Guard}\\
s\in \Cmd  & {\triangleq}  & v:= e \mid out(v) \mid \ite{g}{s}{s} \mid s;s && \textmd{Command}\\
p\in \Prg  & {\triangleq}  & s.\rloop\{s\}.s&& \textmd{Reducer Program}\\
\end{array}
\end{equation*}

Here $v\in \Var$ and $c \in \Z$ are variables and constant integer values, respectively. An \emph{integer expression} in $\Exp$ can be either a variable, constant value, a call to the $\cur$ function that reads and consumes an input value of the reducer, their combinations over basic arithmetic operations, or a non-deterministically chosen integer value $*$.
A \emph{guard} in $\Grd$ can be a comparison between two expressions or boolean combinations of several guards A \emph{command} in $\Cmd$ can be an assignment, a branch statement, concatenation of several commands, or $out(v)$ that outputs that value of $v$.
A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$, and $s_2$ is assumed to have at most one $\cur$ expression in each branch~\footnote{We define a \emph{branch} of a command $s$ as a sequence obtained by replacing all if statement $\ite{g}{s_1}{s_2}$ in $s$ with either $(g)\wedge s_1$ or $(not\ g) \wedge s_2$.} . According to our observation over thousands reducer programs in open repositories, reducer programs are almost always in this form. The $\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ when the next input value exists and does it repeatedly until all input values are consumed. A few examples of reducer programs in this model can be found in Fig.~\ref{fig:reducer_example}. Some reducer uses two loops to compute the output. For example, for standard derivation, one need to first compute the average of the list values (Fig.~\ref{fig:reducer_example}(b)) and use the computed average (set it as a non-deterministic value) to compute the standard derivation (Fig.~\ref{fig:reducer_example}(c)). In that case, we can still partition the reducer into two in the way similar to the one in Fig.~\ref{fig:reducer_example} and verify them separately.

\begin{figure}
	\begin{minipage}{0.32\textwidth}
		\begin{algorithm}[H]
			$m := \cur$; \;
			\Loop{}{
				\uIf{ $\cur > m$}{
					$m := \cur$ 
				}
			};
			$out(m)$\;
		\end{algorithm}
		\caption*{(a) max}
	\end{minipage}	
	\begin{minipage}{0.3\textwidth}
		\begin{algorithm}[H]
			$s := 0;c:=0$; \;
			\Loop{}{
				$s := s+\cur$;\;
				$c := c+1$ 
			};
			$out(s/c)$\;\;
		\end{algorithm}
		\caption*{(b) average}
	\end{minipage}	
	\begin{minipage}{0.36\textwidth}
		\begin{algorithm}[H]
			$a:=*;s := 0; c:=0$;\;
			\Loop{}{
				$s := s+(\cur-a)^2$; \;
				$c := c+1$ 
			};
			$out(s/c)$
		\end{algorithm}
		\caption*{(c) standard derivation}
	\end{minipage}	
	\caption{Example of reducer programs}
	\label{fig:reducer_example}
\end{figure}

\section{Overview of the J-ReCoVer tool}
\label{sec:overview}
%Hadoop, Java;
The input of J-ReCoVer is a Hadoop~\cite{hadoop} reducer program written in Java, which is the most popular programming language used in this framework. 
The J-ReCoVer tool has three main components, the \emph{Preprocessor}, the \emph{Prover}, and the \emph{BugFinder}. As the name suggests, the Preprocessor reads the input reducer and performs the required preprocessing.  The goal of Prover is to show that a given reducer is commutative and the goal of BugFinder is the opposite. The architecture of J-ReCoVer can be found in Fig.~\ref{fig:overview-jrecover}. The user can input a reducer program to J-ReCoVer either though our web-interface or binary installed in their own machine.

\begin{figure}[h]

	\scalebox{0.9}{
		\begin{tikzpicture}

		%J-ReCoVer
		\node[draw=red!30, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=9cm,fill=red!10,minimum height=8cm] (jrecover) at (5.5,0.8) {};		
		\node at (5.5,0.4) {\textbf{J-ReCoVer}};

		%JAVA reducer
		\node[draw=yellow!80, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=1cm,fill=yellow!20,minimum height=4cm] (reducer) at (0,-1.6) {};
		\node[rotate=270, align = center] at (0,-3.6) {Java Reducer};

		%JPreprocessor
		\node[draw=blue!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=3cm,fill=blue!20,minimum height=6.cm] (preprocessor) at (3,-.8) {};
		\node[] at (3,-1.2) {Preprocessor};

		%JPreprocessor->Interface
		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=0.3cm,fill=green!10,minimum height=1.5cm] (interface1) at (1.8,-1.6) {};
		\node[rotate=270, align = center] at (1.8,-2.4) {Web};

		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=0.3cm,fill=green!10,minimum height=3cm] (interace2) at (1.8,-3.6) {};
		\node[rotate=270, align = center] at (1.8,-5) {Installed app.};

		%JPreprocessor->Technologies
		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1cm] (soot) at (3.2,-2) {};
		\node at (3.2,-2.6) {Soot~\cite{soot}};

		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.4cm] (symex) at (3.2,-3.3) {};
		\node at (3.2,-4) {
			\begin{minipage}[t]{0.222\textwidth}
			\centering
			Dummy\\ 
			Hadoop\\
			Enviorment
			\end{minipage}						
			};

			\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (prog_trans) at (3.2,-5) {};
			\node at (3.2,-5.6) {
				\begin{minipage}[t]{0.222\textwidth}
				\centering
				Program\\ 
				Transform
				\end{minipage}						
			};

		%JProver
		\node[draw=blue!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=3cm,fill=blue!20,minimum height=5.5cm] (prover) at (7,0) {};
		\node[] at (7,-0.4) {Prover};

		%JProver->Technologies
		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (7,-1) {};

		\node at (7,-1.6) {
			\begin{minipage}[t]{0.222\textwidth}
			\centering
			Z3 SMT \\
			Solver~\cite{z3}
			\end{minipage}						
		};

		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (7,-2.5) {};

		\node at (7,-3.1) {
			\begin{minipage}[t]{0.222\textwidth}
			\centering
			Symbolic \\
			Execution
			\end{minipage}						
		};

		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (7,-4.) {};

		\node at (7,-4.6) {
			\begin{minipage}[t]{0.222\textwidth}
			\centering
			Data Flow \\
			Analysis
			\end{minipage}						
		};

		%JBugFinder
		\node[draw=blue!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=3cm,fill=blue!20,minimum height=1cm] (learner) at (7,-6) {};
		\node[] at (7,-6.5) {BugFinder};

		%JResults

		\node at (12,-1) {
			Commutative				
		};

		\node at (12,-3.5) {
			Unknown					
		};

		\node at (12,-6.5) {
			\begin{minipage}[t]{0.25\textwidth}
			\centering
			Non-Commutative	 \\
			+\\
			Counterexample
			\end{minipage}

		};

		\draw [->] (8.5,-6.8) -- (10.5,-6.8) ;	
		\draw [->] (8.5,-1) -- (10.5,-1) ;	
		\draw [-] (8.5,-6.2) -- (9.5,-6.2) --(9.5,-3.5);	
		\draw [->] (8.5,-3.5) -- (10.5,-3.5) ;

		\draw [->] (4.5,-3) -- (5.5,-3) ;	
		\draw [->] (4.5,-6.5) -- (5.5,-6.5) ;

		\draw [->] (0.5,-4) -- (1.5,-4) ;

		\end{tikzpicture}
	}
	\caption{Overview of the J-ReCoVer Tool. }\label{fig:overview-jrecover}
\end{figure}

The Preprocessor component first compiles a reducer program to bytecode and use the tool Soot~\cite{soot} to convert it to the so called Jimple format, which is an intermediate language that is designed to make the analysis of Java program easier. Under the Hadoop MapReduce framework, the permutation of the input is caused by the scheduler/shuffler component and is affected by things like network latency, which is not controllable by the user. In order to handle this issue, we wrote our own dummy Hadoop interface for the reducer as a part of the Preprocessor component . So that the input/output of the reducer is now controlled by J-ReCoVer. Finally, we perform in the Preprocessor some simple program transformations that make the analysis easier. For example, we convert all output commands $out(e)$ inside loops to an special assignment $v_{out}:=e$.

In the Prover component, we reduce the commutativity problem to a SMT formula satisfiability problem, using the fact that all permutations of a list can be obtained by swapping consecutive elements finitely many times. At a high level, we check equivalence between a reducer program and its variant that have two consecutive inputs swapped. We show that this can be reduced to a simple SMT problem and give it to Z3~\cite{z3} for solving. In case that Z3 proved the formula unsatisfiable, J-ReCoVer stops and reports the reducer is commutative. 
If we run the approach in a naive manner, it does not scale to large programs and is very imprecise.  We will introduce two critical optimizations that makes the proposed approach works for real examples in Section~\ref{section:optimizations}: an improved symbolic execution algorithm to generate Z3 formulae and a data flow analysis to extract critical variables. More details of the algorithms used in the Preprocessor and the Prover components will be explained in Section~\ref{sec:preprocessor_prover} and the optimizations will be introduced in~\ref{section:optimizations}.

The BugFinder component randomly generated 1500 pairs of list and its permutation for testing. A concrete counterexample is reported if inputting any pair of lists from the 1500 generated ones to the reducer generates different results.
Our procedure for generating random pairs is quite naive. We use five different input list of lengths 5, 7, 9 ,11, and 13. For each length, we generates 300 lists. For each list, we pick uniformly at random one of its permutations. Although the approach is simple, in practice it finds counterexamples in all of our non-commutative benchmarks.

\section{The Preprocessor and the Prover}
\label{sec:preprocessor_prover}

As mentioned, before entering the Prover components, the Preprocessor first performs a few program transformation to simplify the verification task. 
We assume the reducer $s_1;\rloop\{s_2\};s_3$ is given. We begin the section with our first program transformation task that handles the case when $s_2$ contains $out$ commands. The output of the first transformation task is a commutativity-equivalent reducer program where $out$ does not occur in $s_1$. Then we explain the algorithm of the Prover that works only in a special case where no read from input occurs in $s_1$. For general reducer programs, we introduce the second program transformation task whose output is a reducer program that contains all input/output behaviors of the original reducer (may contain behaviors not in the original reducer) and does not have $\cur$ in $s_1$, which can be analyzed by the algorithm of Prover.

\subsection{The First Program Transformation Task in the Preprocessor}
\label{sec:program_trans1}
J-ReCoVer  first generates a new variable $v_{out_n}$ for the $n$-th output command $out(e)$ inside $s_2$ and replace the $out(e)$ command with an assignment $v_{out_n}:=e$. 
Notice that the value of $v_{out_n}$ stays the same from the point it has been assigned a value. 
If the values of $v_{out_n}$ are the same for all permutations of input lists at the end of $s_2$, we know that the a reducer that is commutative w.r.t. to all output commands inside the loop.

\subsection{The Prover: Reducing Commutativity to SMT Solving}
\label{sec:prover}
Below we begin with a simple version where $s_1$ never calls the $\cur$ function. Later we will explain how to handle the general case using program transformation. The command $s_2$ can be viewed as a function $F$ that reads the values of all variables and the current input before executing $s_2$ and outputs values of all variables after $s_2$. Formally, the function $F(n,x_1,x_2,\ldots,x_n): \Z^{n+1} \rightarrow \Z^n$ returns a tuple of values $x_1',x_2',\ldots,x_n'$, where $n$ is the current input value of the reducer, $x_i$ and $x_i'$ are the values of variables before and after the execution of $s_2$, respectively. The construction of $F$ from $s_2$ can be done in the standard way. We will introduce a more efficient data structure for the construction in Section~\ref{section:optimizations}.

We check if the formula is valid for all possible values of $n_1,n_2, x_1,x_2,\ldots,x_n$.
\begin{equation}
 F(n_1, F(n_2,x_1,x_2,\ldots,x_n) = F(n_2, F(n_1,x_1,x_2,\ldots,x_n) 
\label{eq:commu}
\end{equation}
The validity of formula~(\ref{eq:commu}) implies that swapping any two consecutive input values does not change the final variable valuation. Informally, it says that the values of all program variables stay the same when we execute the loop body twice (from any initial valuations of variables), one with the inputs $n_1$ and $n_2$ and the other with their reverse. That is, swapping any two consecutive input values does not change the output. 
Since any permutation of a sequence can be obtained by swapping consecutive values finitely many times~\cite{algebra}, this further implies that starting from the same variable valuation, the loop ends with the same valuation for any permutation of input values and produce the same sequence of output.

We show that this is sufficient to prove the commutativity of the reducer. Notice that $s_1$ does not read from the input and at $s_3$ all input has been read (this is the exit condition of the loop), both of them behave deterministically in the sense that from the same initial valuation, they output the same sequence of values and ends at the same valuation. From the validity of formula~(\ref{eq:commu}), any permutation of input values leads the reducer to the same valuation. Hence we know that any permutation of input values will produce the same sequence of output.

\subsection{The Second Program Transformation Task in the Preprocessor}
\label{sec:program_trans2}

\begin{figure}[t]
	\begin{minipage}{0.4\textwidth}
		\begin{algorithm}[H]
			$m := \cur + 10$; \;
			\Loop{}{
				\uIf{ $\cur > m$}{
					$m := \cur$ \;
				}
			};
			$out(m)$
		\end{algorithm}
		\caption*{(a)Reducer max$^+$}
	\end{minipage}
		\begin{minipage}{0.6\textwidth}
			\begin{algorithm}[H]
				$s:=*;$\;
				\Loop{}{
					\uIf{$s=1$}{$m := \cur + 10; s:= 2$}
					\uElseIf{ $\cur > m$}{
						$m := \cur$ \;
					}
				};
				$out(m)$
			\end{algorithm}
			\caption*{(b) Reducer max$^{+\mathtt{fix}}$}
		\end{minipage}
	\caption{Reducer examples}
	\label{fig:reducer_max}
\end{figure}

\begin{wrapfigure}{r}{0.56\textwidth} 
%		\vspace{-1.8cm}
		\begin{algorithm}[H]
			$s'_0;s:=*;$\;
			\Loop{}{
				\uIf{$s=1$}{ $x_{i_1} := \cur; s'_1; s:=2$}
				\uElseIf{ $s =2$}{ $x_{i_2} := \cur; s'_2; s:=3$}
				\uElseIf{ $s = 3$}{$\ldots$}
				\uElseIf{ $s = m$}{$x_{i_m} := \cur; s'_m; s:=m+1$}
				\uElse{ $s_2$}
			};$s_3$\;
		\end{algorithm}
		\caption{The second program transformation}
		\label{fig:general_program_transformation}
\end{wrapfigure} 
However, in reality, it is often that the $s_1$ part also reads from the input. See the example in Fig.~\ref{fig:reducer_max} (a), in this example, the program remembers the first input value in the variable $m$, increases its value by 10, and then updates its value to bigger ones if any occurs in the loop. The corresponding formula~(\ref{eq:commu}) is valid in this case, however, the reducer is not commutative. For example, the two lists $[1,2,3,4,5]$ and $[5,4,3,2,1]$ are permutations of each other, but the reducer respectively outputs $11$ and $15$ with them as the inputs.

We handle the problem again by program transformation. For the example in Fig.~\ref{fig:reducer_max} (a), we move the prefix $s_1$ into the loop body and use a new variable $s$ to force that $s_1$ is always executed before the original loop body. The result after the transformation can be found in Fig.~\ref{fig:reducer_max} (b). Observe that the new reducer program over-approximates all possible inputs/outputs of the original one.
It also satisfies all assumptions required for the Prover: (I) $s'_0$ does not have any $\cur$ expression and (II) each branch (recall that this is defined in Section~\ref{section:integer-reducers}) of the loop body has at most one $\cur$. So we can apply equation~(\ref{eq:commu}) to prove its commutativity.
Since the new reducer has all the possible output of the original one, the new reducer is commutative implying that the original one is also commutative.

For the general case, we first rewrite the $s_1$ part of the reducer $s_1;\rloop\{s_2\};s_3$ to the form 
$$s'_0;x_{i_1}{:=} \cur;s'_1.\ldots x_{i_{m}}{:=}\cur;s'_m, $$ where $\cur$ never occur in $s'_0,s'_1,\ldots, s'_m$. The reducer in Fig.~\ref{fig:general_program_transformation} is an over-approximation of the original reducer that satisfies all assumptions required for the Prover. Hence the equation~(\ref{eq:commu}) can then be applied to prove its commutativity.

\subsection{Limitations and assumptions}
At the back-end, we use SMT theory of integer arithmetics as the reasoning tool. In this implementation, we do not handle more advanced data-types such as string and floating point. 
The problem of variable overflow is not handled by this tool. In fact, if we consider all possible inputs of a reducer, almost all reducer programs will run into the problem of overflow. Even the basic example that computes the sum of all input values, overflow can occur when a list contains two maximal 64-bit integer values is used as the input. Nevertheless, such example might not be of the interests of MapReduce programmers, who usually care only about the data set they want to analyze. We are building another tool that estimates a safe bound of data size such that overflow will not occur. The programmer can than check if their data set fits the computed bound and use lager data type in the program when needed.

\section{Optimizations}
\label{section:optimizations}
In this section we explain how data flow analysis are used in our case to improve the precision of commutativity checking and the algorithm we used to construct the $F$ function in formula~(\ref{eq:commu}).

\subsection{Improving the precision of commutativity verification using data flow analysis}

We find that in many cases, formula~\ref{eq:commu} is a condition that is too strong for the reducer to be commutative. For instance, consider the example in Fig.~\ref{fig:reducer_opt}, in the loop body, the input is first stored in a variable $t$ and then added to $s$. In this case, the $F$ function returns the updated values of both $s$ and $t$ after the execution of loop body. Observe that 
$F(c_1, F(c_2,s,t) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t) = (c_1+c_2, c_2)$, which follows that the corresponding equation~\ref{eq:commu} is invalid. The second component of the returned tuple, which corresponds to the value of $temp$ after executing the loop body twice, are $c_1$ and $c_2$, respectively. However, in this case, the value of $t$ is not important to the output of this reducer.

\begin{figure}[t]
	\begin{minipage}{0.4\textwidth}
		\begin{algorithm}[H]
			$s:= 0$; \;
			\Loop{}{
				$t:=\cur$;
				$s:= s + t$\;
			};
			$out(s)$\;
		\end{algorithm}
		\caption{A commutative reducer with an invalid equation~(\ref{eq:commu}).}
		\label{fig:reducer_opt}
	\end{minipage}
	\begin{minipage}{0.5\textwidth}
		\begin{algorithm}[H]
			$c_1;c_2;\ldots;c_i$\;
			\lIf{$g_1$}{$\ldots$}
			\lElseIf{ $g_2$}{$\ldots$}
			\lElseIf{ $g_3$}{$\ldots$}
			\lElseIf{ $g_m$}{$c_{i+1};\ldots ;c_n; out(v);\ldots$}
			\lElse{ $\ldots$}
		\end{algorithm}
		\caption{$out(v)$ in nested branches of $s_3$.}
		\label{fig:nested_out}
	\end{minipage}
\end{figure}

To handle such situation, we perform a simple data flow analysis to collect all variables whose value may propagate to the output after the loop. We do it in a backward manner.  With out loss of generality, we assume there is only one output command after the loop. Then the code after the loop (i.e., the $s_3$ part of the reducer) can only be in the form of Fig.~\ref{fig:nested_out}.
The commands $c_1\ldots c_n$ are either assignment commands $w:=e$ or branch command $\ite{g}{c'_1}{c'_2}$, and the only output command stays in the $m$-th layer of the branch command after $c_i$.

The data flow analysis algorithm works as follows.
A set $V_3$ whose value is initially a singleton set $\{v\}$ is used to remember important variables that might flow to the output commands in $s_3$.
The commands and guards will be inspected in the following order $c_{n}$,$\ldots$,$c_{i+1}$, $g_m$, $g_{m-1}$, $\ldots$, $g_1$, $s_i$, $\ldots$, $c_2$, $c_1$. For the case that a guard $g_j$ for $j\in [1,m]$ is being processed, we simply add all variables occurred in $g_j$ to $V_3$.

Recall that the commands $c_j$ for $j\in [1,n]$ can only be in the form of $w:=e$ or $\ite{g}{c'_1}{c'_2}$.
For the case that $c_j$ is an assignment $w:=e$ and $w\in V_3$, we add all variables contained in $e$ to $V_3$. For the case that $c_j$ is an branch command $\ite{g}{c'_1}{c'_2}$, we process both $c'_1$ and $c'_2$ in a similar manner. Starting from the same set $V_3$,  after processing $c'_1$ and $c'_2$, we get respectively two sets $V_3^1$ and $V_3^2$, we take their union $V_3^1\cup V_3^2$ as the new value of $V_3$.

Then we modify the equation~(\ref{eq:commu}) to the one below

\begin{equation}
F(n_1, F(n_2,x_1,x_2,\ldots,x_n) =_{V_2\cup V_3} F(n_2, F(n_1,x_1,x_2,\ldots,x_n) 
\label{eq:commu2}
\end{equation}
The special equality operator $=_{V_2\cup V_3}$ is defined (informally) as an equality that only focus on the positions of variables in $V_2\cup V_3$.
The set $V_2$ is defined as the set of variables we used to collect output values in the loop body $s_2$ of the reducer, i.e., $V_2= \{v_{out_k} \mid k \in [1,l]\}$, , where $l$ is the number of output commands occurred in $s_2$.

The use of equation~(\ref{eq:commu2}) is critical to the successful of our approach. In our evaluation, the ratio of examples that our approach can successfully analyze is significantly increased from $14\%$ to $98\%$. The details of the experiments can be found in Section~\ref{section:exp}.

\subsection{Computing the $F$ function using symbolic execution with efficiently data structure}
The computation of $F$ in equation~(\ref{eq:commu2}) can be done in several different ways. For example, one can construct a formula in the style of bounded model checking. Here we apply \emph{symbolic execution} to generate $F$. Our approach is very simple. First, we define the set $\Var_0=\{v_0 \mid v \in \Var \}\cup \{c_0\}$ as the set of initial symbolic values of all variables, where $c_0$ is used to denote the symbolic value from the input of the reducer.
A \emph{symbolic state} is a triple $\langle pc, val, cmds \rangle$, where the \emph{path condition} $pc$ is a guard in $\Grd$ over $\Var_0$, the \emph{symbolic valuation} is a mapping from variables in $\Var$ to an expression in $\Exp$ over $\Var_0$, and $cmds\in \Cmd$ is the remaining commands to be executed. The \emph{initial symbolic state} is $\langle \true, val_0, s_2\rangle$, where $val_0(v) = v_0$ for all $v\in\Var$. 
One can compute the next symbolic state of $\langle pc, val, c;cmds \rangle$ according to the following transition rules. Recall that $c$ is either in the form of $(v:= e_0)$ or $\ite{g}{c_1}{c_2}$:
\begin{enumerate}
	\item If $c$ is $(v:= e_0)$, the next symbolic state is $\langle pc, val[v \rightarrow e_0(val) ], cmds \rangle$.
	\item  If $c$ is $\ite{g}{c_1}{c_2}$, the next symbolic states are $\langle pc\wedge g, val, c_1.cmds \rangle$ and $\langle pc\wedge not\  g, val, c_2.cmds \rangle$. 
\end{enumerate}

Here $e_0(val)$ is a formula obtained by substituting every variable $v$ in $e_0$ with $val(v)$ and $val[v \rightarrow e_0(val) ]$ is obtained by reassigning the value of $v$ in $val$ to $e_0(val)$. The symbolic execution terminates when its path condition is conflict or the commands become empty. So far it is standard.

For the loop body $s_2$, symbolic execution is guaranteed to terminate.
When the execution terminates, we collect all states with empty commands $\langle pc, val, \emptyset \rangle$ as a set $T$ and use them to create the function $F$ in formula~(\ref{eq:commu2}). 
First, we create for each variable $v\in\Var$ a formula $f_v$ whose initial value is $\false$. For each symbolic state $\langle pc, val, \emptyset \rangle \in Ts$, we reassign $f_v$ to $f_v \vee (pc \wedge val(v))$. 
Assuming that the set $P_2\cup P_3$ in equation~(\ref{eq:commu2}) equals $\{v_1,v_2,\ldots,v_n\}$, the function $F$ simply returns tuple $\{f_{v_1},f_{v_2},\ldots, f_{v_n}\}$.

However, doing symbolic execution in a naive way can be extremely inefficient. 
The length of the formula $val(v)$ can grow exponentially w.r.t. the input commands. For example, consider a simple command $u:=x+y;u:=u+u;u:=u+u$, each execution of $u:= u+ u$ will double the length of the expression storing the symbolic value of $u$. More concretely, after the execution of $u:=x+y$, the symbolic value of $u$ is $x_0+y_0$. After the two executions of $u:=u+u$, the value of $u$ changes to $x_0+y_0+x_0+y_0$ and $x_0+y_0+x_0+y_0+x_0+y_0+x_0+y_0$, respectively. One way to alleviate the problem is to apply some formula simplification algorithm, e.g., those build-in Z3~\cite{z3}. 
However, this will require some additional cost in the invocation of Z3. Here we propose in a very simple alternative solution that works quite well in our reducer benchmarks.

We use a more efficient data structure to store symbolic values. At a high level, in a symbolic state, we count the number of occurrences of each variables in $\Var_0$ and just update the count for operations such as $+$ and $-$. For other operations (e.g., $*$), we create the symbolic formula in the original way.
More concretely, we use a map $sv_x:\Exp\rightarrow \mathbb{N}$ (symbolic value of $x$) to remember the number of occurrences of each expression in $x$. Initially, $sv_x(x_0) = 1$ and $sv_x (e) =0$ for all $e\neq x$. Assume that the symbolic value of $x,y$ are $sv_x,sv_y$ in the current symbolic state. The symbolic value $sv'_x$ of $x$ after the assignment $x:=x\circ y$ is defined as follows.

\begin{itemize}
	\item For the case that $\circ \in\{+,-\}$, we have $sv'_x(z) = sv_x(z)\circ  sv_y(z)$. 
	\item For the case that $\circ \notin\{+,-\}$, we compute an expression $e_1= (\Sigma_{z\in \dom{sv_x}} (z\times sv_x(z)) )\circ (\Sigma_{z\in \dom{sv_y}} (z\times sv_x(z)))$, where $\dom{sv}=\{e\mid sv(e)\neq 0\}$. Then we define $sv'_x(e_1) =1$ and $sv'_x(e_2) = 0$ for all $e_2\neq e_1$. 
\end{itemize}

This data structure is efficient for strong symbolic values of reducer programs mainly for reason that the operations $+$ and $-$ are quite heavily used in such programs.

\section{Evaluation}
\label{section:exp}
J-ReCoVer is implemented in JAVA and build on top of the Soot~\cite{soot} framework. In order to properly evaluate the performance of J-ReCoVer, we collect benchmark example from two sources. We run J-Recover on a machine with (RAM, CPU)

First, we use the search engine \url{http://searchcode.com}~\cite{searchcode} to collect java programs contains the key strings ``public void reduce('' or ``protected void reduce(''.  Since there is an upper bound in number of returned results in the search engine, we add different search filters in order to get more data. We tried all $12$ combinations of $6$ code length filters $\{<50$,$ 50\sim 250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim 1250\}$ 
and two filters for data sources $\{\url{github.com}, \url{bitbuckect.com}\}$. In total we get $11346$ Java programs. We then filter out cases that are not Hadoop MapReduce reducer programs (those do not import the Hadoop library, do not extend or implement the reducer interface) and obtain $1273$ examples. We further remove those that cannot be compiled, those that are identical to each other, or those uses non-numerical data types (e.g, string) and obtained $118$ programs as the final benchmark.
The second set of examples are those have been discussed in verification literatures~\cite{ChenHSW15,ChenSW16,SmithA16}. This set is relatively small, we have only $10$ examples. All benchmark examples can be found on the web-site of J-Recover.

\hide{For the third set of benchmarks, we created a program that randomly generate reducer program in order to test the scalability of J-Recover, which we can give as parameter the number of variables $N$, branch statements $B$, assignment statements $A$. All assignments are in them form of $v_1 := v_2\circ v_3$ and all guards are in the form of $v_1 \circ v_2$. The source code of the random generator is available at \url{http://www.github.com/xxxxx}.}

Our evaluation answers the following three questions:
\begin{itemize}
	\item Is J-Recover better than other competing tools?
	%\item How good J-Recover scales?
	\item Are the two optimizations proposed in Section~\ref{section:optimizations} critical and effective?
\end{itemize}

\subsection{Comparison with competing tools}
As already pointed out in~\cite{ChenHSW15}, reducer commutativity problems can be reduced to a reachability problem of programs. 
The examples in~\cite{ChenHSW15}, which includes \textsf{rangesum}\footnote{The sum of the second half of the input list.}, \textsf{avg}, \textsf{max}, \textsf{sep}\footnote{The number of occurrences of even numbers minus that of odd numbers.}, \textsf{sum}, are already included in SV-Comp~\cite{svcomp} (Software Verification Competition) benchmarks.
Although those examples are tiny and simple, none of the software verifiers are able to verify all of them according to the 2018 results, c.f., Table~\ref{tab:svcomp}. The number of the other verifiers are taken directly from the SV-Comp web-site.

\begin{table}
	\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
							   & \small CBMC\cite{cbmc2} 	& \small CPA-Seq\cite{cpachecker} & \small  ESBMC-kind\cite{esbmc} & \small  UAutomizer\cite{uautomizer} &\small  VeriAbs\cite{veriabs} &\small J-Recover\\
\hline
\hline
\small \textsf{rangesum}	& 0.96 	   & 30 		 & 2.2 				 &  10				 & 180       &6.1\\
\hline
\small \textsf{avg}			 &  TO      &  TO		  &  TO				 &  TO				 &  2          &5.2\\
\hline
\small \textsf{max}		    &  TO      &  TO		 &  TO				& TO				 &  7         &5.8\\
\hline
\small \textsf{sep}		     &  TO      &  TO		  &  TO				 & TO				 &  TO        &6.3\\
\hline
\small \textsf{sum}		    &  TO      &  TO		 &  TO				& TO				&  1.7       &5.3\\
\hline
	\end{tabular}
	\caption{SV-Comp 2018 results on reducer commutativity. For space reason, we only list results of tool with better performance in these examples, which includes top three tools in the overall ranking and the reachability safety category.}
	\label{tab:svcomp}
\end{table}

\subsection{The performance of J-Recover with and without optimizations}

\begin{table}
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		& &Equation~(\ref{eq:commu})	& Equation~(\ref{eq:commu2}) \\
		\hline
		\hline
		\multirow{3}{*}{Open repositories}&Commutative& 8&106\\ 
		\cline{2-4}
		&Non-commutative&9&9\\
		\cline{2-4}
		&Unknown&101&3\\
		\hline
		\hline
		\multirow{3}{*}{Literatures}&Commutative& 0&9\\
		\cline{2-4}
		&Non-commutative&1&1\\
		\cline{2-4}
		&Unknown&9&0\\
		\hline
	\end{tabular}
	\caption{The improvement of precision using data flow analysis.}
	\label{tab:opt1}
\end{table}

%Discuss the tool’s practical capabilities with reference to the type and size of problems it can handle

\bibliographystyle{splncs-sorted}
\bibliography{refs}

\end{document}

### 2018-11-02 draft.tex
minor updates

@@
 \label{section:exp}
-J-ReCoVer is implemented in JAVA and build on top of the Soot~\cite{soot} framework.
-In order to properly evaluate the performance of J-ReCoVer, we collect benchmark example from two sources.
-We run J-Recover on a machine with (RAM, CPU)
+J-ReCoVer is implemented in JAVA and build on top of the Soot~\cite{soot} 2.5.0 and Z3~\cite{z3} 4.7.1.
+We run J-Recover on a virtual machine running on a server with AMD Opteron 6376 CPU.
+4GB of memory is allocated to this virtual machine.
+The operation system is Ubuntu 16.04.5 LTS.
 
+ In order to properly evaluate the performance of J-ReCoVer, we collect benchmark example from three different sources. 
 First, we use the search engine \url{http://searchcode.com}~\cite{searchcode} to collect java programs contains the key strings ``public void reduce('' or ``protected void reduce(''.
 Since there is an upper bound in number of returned results in the search engine, we add different search filters in order to get more data.
-We tried all $12$ combinations of $6$ code length filters $\{<50$,$ 50\sim 250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim 1250\}$
+We tried all $12$ combinations of $6$ code length filters $\{<50$, $ 50\sim 250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim 1250\}$
 and two filters for data sources $\{\url{github.com}, \url{bitbuckect.com}\}$.
@@
 All benchmark examples can be found on the web-site of J-Recover.
-
-\hide{For the third set of benchmarks, we created a program that randomly generate reducer program in order to test the scalability of J-Recover, which we can give as parameter the number of variables $N$, branch statements $B$, assignment statements $A$.
-All assignments are in them form of $v_1 := v_2\circ v_3$ and all guards are in the form of $v_1 \circ v_2$.
-The source code of the random generator is available at \url{http://www.github.com/xxxxx}.}
+For the third set of benchmarks, we created a program that randomly generate reducer program in order to test the scalability of J-Recover, which we can give as parameter a tuple $(N,B,A)$, where $N$ is the number of variables, $B$ is the branch statements, and $A$ is the number of assignment statement.
+All assignments are in the form of $v_1 := v_2\circ v_3,\circ\in\{+,-,\times\}$ and all guards are in the form of $v_1 \circ v_2, \circ\in\{\geq, >,=, \neq, <,\leq \}$.
+ The source code of the random generator is available at \url{https://github.com/spencerwuwu/benchmark-generator}.
 
@@
 \begin{itemize}
-	\item Is J-Recover better than other competing tools?
-	%\item How good J-Recover scales?
+	\item Is J-Recover better than other competing tools/techniques?
 	\item Are the two optimizations proposed in Section~\ref{section:optimizations} critical and effective?
+	\item How good J-Recover scales?
 \end{itemize}
@@
 Although those examples are tiny and simple, none of the software verifiers are able to verify all of them according to the 2018 results, c.f., Table~\ref{tab:svcomp}.
-The number of the other verifiers are taken directly from the SV-Comp web-site.
+In this tools, the number of tools other than J-Recover are taken directly from the SV-Comp~\cite{svcomp} web-site.
+Although the machine we used are different, but the results of J-Recover will not be much different if we run it on other machines.
 

### 2018-11-05 draft.tex
Update exp graphes and tables

@@
 \usepackage{algorithm2e}
-\usepackage{tikz}
+\usepackage{tikz,pgfplots}
 \usepackage{etoolbox}
@@
 \hline
-\small \textsf{rangesum}	& 0.96 	   & 30 		 & 2.2 				 &  10				 & 180       &6.1\\
+\small \textsf{rangesum}	& 0.96 	   & 30 		 & 2.2 				 &  10				 & 180       &9.9\\
 \hline
-\small \textsf{avg}			 &  TO      &  TO		  &  TO				 &  TO				 &  2          &5.2\\
+\small \textsf{avg}			 &  TO      &  TO		  &  TO				 &  TO				 &  2          &10.9\\
 \hline
-\small \textsf{max}		    &  TO      &  TO		 &  TO				& TO				 &  7         &5.8\\
+\small \textsf{max}		    &  TO      &  TO		 &  TO				& TO				 &  7         &9.4\\
 \hline
-\small \textsf{sep}		     &  TO      &  TO		  &  TO				 & TO				 &  TO        &6.3\\
+\small \textsf{sep}		     &  TO      &  TO		  &  TO				 & TO				 &  TO        &9.9\\
 \hline
-\small \textsf{sum}		    &  TO      &  TO		 &  TO				& TO				&  1.7       &5.3\\
+\small \textsf{sum}		    &  TO      &  TO		 &  TO				& TO				&  1.7       &9.9\\
 \hline
@@
 
+% Optimization table
+\begin{table}
+	\begin{tabular}{|l|l|l|l|l|l|l|}
+\hline
+		& \multicolumn{3}{c|}{\small w/o Optimization}	& \multicolumn{3}{c|}{\small Optimized} \\
+\hline
+		\small Lines & \small Average & \small Median & \small Timeout & \small Average & \small Median & \small Timeout \\
+\hline
+\hline
+		50	&	11.104	&	10.446	&	0	&	10.284	&	10.193	&	0	\\
+\hline                                                                              
+		100	&	19.766	&	11.239	&	1	&	29.544	&	11.172	&	3	\\
+\hline                                                                             
+		150	&	88.741	&	17.943	&	12	&	63.931	&	13.984	&	7	\\
+\hline                                                                             
+		200	&	88.741	&	169.456	&	26	&	63.931	&	13.984	&	7	\\
+\hline                                                                             
+		250	&	232.348	&	300.000	&	43	&	175.976	&	248.998	&	30	\\
+\hline
+	\end{tabular}
+	\caption{....}
+	\label{tab:opt2}
+\end{table}
+
+% Optimization compare graph
+\begin{tikzpicture}
+	\begin{axis}[%
+			xmin=-5, xmax=320,
+			ymin=-5, ymax=320,
+			xlabel=Optimize,
+			ylabel=w/o Optimization
+			]
+	\addplot[scatter,only marks,%
+		scatter src=explicit symbolic, mark=x]%
+		file {plot_data/optimize.data};
+\draw (-100,-100) -- (400, 400);
+\end{axis}
+\end{tikzpicture}
+
+% BMC table
+\begin{table}
+	\begin{tabular}{|l|l|l|l|l|l|l|l|}
+\hline
+		& \multicolumn{3}{c|}{\small Optimized}	& & \multicolumn{3}{c|}{\small w/o Optimization} \\
+\hline
+		\small Lines/Vars & \small Average & \small Median & \small Timeout & Lines/Vars (jimple)& \small Average & \small Median & \small Timeout \\
+\hline
+\hline
+		50/5	&	0.063	&	0.058	&	0	&	72.85/65.7	&	0.139	&	0.143	&	0	\\
+\hline
+		100/10	&	0.840	&	0.240	&	0	&	129.95/120.85	&	3.052	&	0.374	&	0	\\
+\hline
+		150/15	&	28.459	&	1.752	&	1	&	186.9/175.6	&	36.233	&	2.151	&	1	\\
+\hline
+		200/20	&	76.220	&	14.37	&	2	&	243.75/230.6	&	89.730	&	15.941	&	5	\\
+\hline
+		250/25	&	84.358	&	1.413	&	5	&	300.55/285.85	&	172.482	&	243.845	&	10	\\
+\hline
+	\end{tabular}
+	\caption{....}
+	\label{tab:opt2}
+\end{table}
+
+% BMC compare graph
+\begin{tikzpicture}
+	\begin{axis}[%
+			xmin=-5, xmax=150,
+			ymin=-5, ymax=150,
+			xlabel=J-ReCoVer(s),
+			ylabel=BMC(s)
+			]
+	\addplot[scatter,only marks,%
+		scatter src=explicit symbolic, mark=x]%
+		file {plot_data/bmc.data};
+\draw (-100,-100) -- (400, 400);
+\end{axis}
+\end{tikzpicture}
+
 %Discuss the tool’s practical capabilities with reference to the type and size of problems it can handle

### 2018-11-08 draft.tex
Edit BMC graph axis
Update line number
Correct name
minor

@@
 \label{section:exp}
-J-ReCoVer is implemented in JAVA and build on top of the Soot~\cite{soot} 2.5.0 and Z3~\cite{z3} 4.7.1.
+J-ReCoVer is implemented in JAVA and build on top of Soot~\cite{soot} 2.5.0 and Z3~\cite{z3} 4.7.1.
 We run J-Recover on a virtual machine running on a server with AMD Opteron 6376 CPU.
@@
 We further remove those that cannot be compiled, those that are identical to each other, or those uses non-numerical data types (e.g, string) and obtained $118$ programs as the final benchmark.
-The second set of examples are those have been discussed in verification literatures~\cite{ChenHSW15,ChenSW16,SmithA16}.
-This set is relatively small, we have only $10$ examples.
-All benchmark examples can be found on the web-site of J-Recover.
+The second set of examples are those have been discussed in verification literatures~\cite{ChenHSW15,ChenSW16,SmithA16}. This set is relatively small, we have only $10$ examples. 
 For the third set of benchmarks, we created a program that randomly generate reducer program in order to test the scalability of J-Recover, which we can give as parameter a tuple $(N,B,A)$, where $N$ is the number of variables, $B$ is the branch statements, and $A$ is the number of assignment statement.
@@
  The source code of the random generator is available at \url{https://github.com/spencerwuwu/benchmark-generator}.
+All benchmark examples can be found on the web-site of J-Recover.
 
@@
 The examples in~\cite{ChenHSW15}, which includes \textsf{rangesum}\footnote{The sum of the second half of the input list.}, \textsf{avg}, \textsf{max}, \textsf{sep}\footnote{The number of occurrences of even numbers minus that of odd numbers.}, \textsf{sum}, are already included in SV-Comp~\cite{svcomp} (Software Verification Competition) benchmarks.
-Although those examples are tiny and simple, none of the software verifiers are able to verify all of them according to the 2018 results, c.f., Table~\ref{tab:svcomp}.
-In this tools, the number of tools other than J-Recover are taken directly from the SV-Comp~\cite{svcomp} web-site.
+Although those examples are tiny and simple, none of the software verifiers are able to verify all of them according to the 2018 results. In contrast, J-Recover can verify all them very efficiently.
+
+In Table~\ref{tab:svcomp}, the statistics of tools other than J-Recover are taken directly from the SV-Comp~\cite{svcomp} web-site.
 Although the machine we used are different, but the results of J-Recover will not be much different if we run it on other machines.
-
-\begin{table}
+The other limitation is that in J-Recover, we analysis Java implementation and in SV-Comp they analyze the C implementations.
+Since those functions to be analyzed are relatively simple, the difference between C and Java implementation is very small (even syntactically).
+The main difference in the statistics still comes from the algorithm being used for verification.
+\begin{table}[t]
+\scalebox{0.95}{
 	\begin{tabular}{|l|l|l|l|l|l|l|}
@@
 	\end{tabular}
+}
 	\caption{SV-Comp 2018 results on reducer commutativity.
-For space reason, we only list results of tool with better performance in these examples, which includes top three tools in the overall ranking and the reachability safety category.}
+For space reason, we only list results of competitive tool in this table, which includes top three tools in the overall ranking and the reachability safety category.}
 	\label{tab:svcomp}
@@
 
+In the other experiments (Table~\ref{}), we compare the efficiency using bounded model checking and symbolic execution we described in Section~\ref{section:optimizations}.
+
 \bibliographystyle{splncs-sorted}

### 2018-11-08 draft.tex
evaluation

@@
 \subsection{Improving the precision of commutativity verification using data flow analysis}
-
+\label{section:opt1}
 We find that in many cases, formula~\ref{eq:commu} is a condition that is too strong for the reducer to be commutative.
@@
 \begin{equation}
-F(n_1, F(n_2,x_1,x_2,\ldots,x_n) =_{V_2\cup V_3} F(n_2, F(n_1,x_1,x_2,\ldots,x_n) 
+F(n_1, F(n_2,x_1,x_2,\ldots,x_n) )=_{V_2\cup V_3} F(n_2, F(n_1,x_1,x_2,\ldots,x_n) )
 \label{eq:commu2}
@@
 \subsection{Computing the $F$ function using symbolic execution with efficiently data structure}
+\label{section:opt2}
+
 The computation of $F$ in equation~(\ref{eq:commu2}) can be done in several different ways.
@@
 The second set of examples are those have been discussed in verification literatures~\cite{ChenHSW15,ChenSW16,SmithA16}. This set is relatively small, we have only $10$ examples. 
-For the third set of benchmarks, we created a program that randomly generate reducer program in order to test the scalability of J-Recover, which we can give as parameter a tuple $(N,B,A)$, where $N$ is the number of variables, $B$ is the branch statements, and $A$ is the number of assignment statement.
+For the third set of benchmarks, we created a program that randomly generate reducer program in order to test the scalability of J-Recover, which we can give as parameter a tuple $(N,B,A)$, where $N$ is the number of variables, $B$ is the number of branch statements, and $A$ is the number of assignment statement.
 All assignments are in the form of $v_1 := v_2\circ v_3,\circ\in\{+,-,\times\}$ and all guards are in the form of $v_1 \circ v_2, \circ\in\{\geq, >,=, \neq, <,\leq \}$.
@@
 
-Our evaluation answers the following three questions:
+Our evaluation answers the following two questions:
 \begin{itemize}
-	\item Is J-Recover better than other competing tools/techniques?
+	\item Is J-Recover better than other competing tools?
 	\item Are the two optimizations proposed in Section~\ref{section:optimizations} critical and effective?
-	\item How good J-Recover scales?
 \end{itemize}
@@
 The other limitation is that in J-Recover, we analysis Java implementation and in SV-Comp they analyze the C implementations.
-Since those functions to be analyzed are relatively simple, the difference between C and Java implementation is very small (even syntactically).
-The main difference in the statistics still comes from the algorithm being used for verification.
+Since those functions to be analyzed are relatively simple, the syntactical difference between C and Java implementation is very small.
+The difference in the statistics mainly comes from the verification algorithm being used, not the programing language the reducer is written in.
 \begin{table}[t]
@@
 
-\begin{table}
+For the optimization based on data flow analysis (Section~\ref{section:opt1}), we evaluation them based on real-world benchmark sets collected from open repositories (118 examples) and also literatures (10 examples).
+The difference between the version with and without this optimization is very clear.
+The results are presented in table~\ref{tab:opt1}.
+The first column is the result without optimization, i.e., using Equation~(\ref{eq:commu}) and the second column is the result with optimization, i.e., using Equation~(\ref{eq:commu2}).
+The precision of the analysis is improved from $14.4\%$ to $97.5\%$ for examples from open repositories and
+$10\%$ to $100\%$ for examples from literatures.
+There are only three cases that J-Recover with data flow analysis cannot handle.
+The reason that J-Recover fails is that the three reducer uses more complicated structure than what J-Recover currently supports, i.e., in the form of $s_1;\rloop\{s_2\};s_3$.
+The three reducer programs uses a branch statement before entering the loop, i.e., in the form $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$.
+In theory, such program can be handled by more sophisticated program transformation operations, For example, we can merge the two loops and push the outer branch condition inside the merged loop.
+However, this new program transformation operation is not implemented in J-Recover yet.
+
+\begin{table}[htb]
 	\centering
@@
 		\hline
-		& &Equation~(\ref{eq:commu})	& Equation~(\ref{eq:commu2}) \\
+		& &W/O optimization	& With optimization\\
 		\hline
 		\hline
-		\multirow{3}{*}{Open repositories}&Commutative& 8&106\\ 
+		\multirow{4}{*}{Open repositories}&Commutative& 8&106\\ 
 		\cline{2-4}
@@
 		&Unknown&101&3\\
+		\cline{2-4}
+		&Precision& 14.4\% & 97.5\%\\
 		\hline
 		\hline
-		\multirow{3}{*}{Literatures}&Commutative& 0&9\\
+		\multirow{4}{*}{Literatures}&Commutative& 0&9\\
 		\cline{2-4}
@@
 		&Unknown&9&0\\
+		\cline{2-4}
+		&Precision& 10\% & 100\%\\
 		\hline
 	\end{tabular}
-	\caption{The improvement of precision using data flow analysis.}
+	\caption{The improvement of precision using data flow analysis.
+The row ``Precision'' is calculated as the number of examples that J-Recover returns commutative or non-commutative divided by the total number of example.}
 	\label{tab:opt1}
@@
 
-% Optimization table
-\begin{table}
+For the optimization based on improving the data structure used in symbolic execution (Section~\ref{section:opt2}), the main focus in on the improvement in scalability.
+In fact, even for the version without optimizations, J-Recover can handle most of the real-world benchmarks efficiently.
+So we use randomly generated examples as the target in this evaluation.
+Recall that our random reducer program generator uses three parameters $(N,B,A)$, where $N$ is the number of variables, $B$ is the number of branch statements, and $A$ is the number of assignment statements.
+In the evaluation, we keep the ratio $N:B:A = 5:1:50$ and uses lines numbers from $50$ to $250$.
+The most difficult cases might have $5$ to $6$ nested branches and $25$ integer variables in reducer program.
+Those program will be processed by Soot and translated to the so called Jimple format.
+In our experience, this will increase the number of lines by $20\%$ and variables by $11$ times.
+The results are presented in Fig.~\ref{tab:opt2} in the form of a table and also a scatter plot.
+Form there we can see that the optimization is helpful in improving all the statistics (average, median execution time and the number of cases that cannot be finished within 300 seconds).
+Also from the scatter plot we can see that much more cases are solved with the new optimization.
+
+\begin{figure}[htb]
+
+	\begin{minipage}{0.6\textwidth}
 \begin{tabular}{|l|l|l|l|l|l|l|}
 	\hline
-		& \multicolumn{3}{c|}{\small w/o Optimization}	& \multicolumn{3}{c|}{\small Optimized} \\
+	& \multicolumn{3}{c|}{\small W/O optimization}	& \multicolumn{3}{c|}{\small With optimization} \\
 	\hline
-		\small Lines & \small Average & \small Median & \small Timeout & \small Average & \small Median & \small Timeout \\
+	\small Lines & \small Average & \small Median & \small T/O & \small Average & \small Median & \small T/O \\
 	\hline
@@
 \end{tabular}
-	\caption{....}
-	\label{tab:opt2}
-\end{table}
-
-% Optimization compare graph
+	\end{minipage}	
+	\begin{minipage}{0.4\textwidth}
+\scalebox{0.6}{
 	\begin{tikzpicture}
@@
 	ymin=-5, ymax=320,
-			xlabel=Optimize,
-			ylabel=w/o Optimization
+	xlabel={\Large with optimization},
+	ylabel={\Large w/o optimization}
 	]
@@
 	\end{tikzpicture}
+}		
+	\end{minipage}
 
-% BMC table
-\begin{table}
-	\begin{tabular}{|l|l|l|l|l|l|l|l|}
+	\caption{The improvement in scalability using the better data structure for symbolic execution.
+Each cell in the table is the summary of 60 randomly generated programs.
+In the table T/O stands for timeout and W/O is without.
+}
+	\label{tab:opt2}
+\end{figure}
+
+% Optimization compare graph
+Bounded model checking (BMC) is another approach to create the $F$ function in Equations~\ref{eq:commu} and \ref{eq:commu2}.
+Although we use symbolic execution in J-Recover, it is interesting to see how good BMC works in checking the commutativity of reducer examples.
+In this evaluation, we use the same random reducer program generator.
+One major different difference is that for the BMC part, we directly generate the corresponding $F$ formula in the BMC-style without going through the Soot framework.
+So the number of variables in the formula is much less than the symbolic execution version.
+The results can be found in Table~\ref{tab:bmc}.
+For symbolic execution, we first use J-Recover to generate the formula for evaluation.
+For BMC, the formula is directly generated by the random generator.
+In this evaluation, we see that the performance of using BMC is in general better, less timeout and lower average execution time, so we plan to also include a BMC engine in the next version.
+However, from the scatter plot we can see there are multiple cases that  can be solved using symbolic execution but are slower or even falied using BMC.
+So the best strategy should be keep the both engine and switch to another if one fails.
+
+\begin{table}[htb]
+
+\begin{minipage}{0.7\textwidth}	
+	\begin{tabular}{|l||l|l| l||l|l|}
 \hline
-		& \multicolumn{3}{c|}{\small Optimized}	& & \multicolumn{3}{c|}{\small w/o Optimization} \\
+		Java& \multicolumn{2}{c|}{\small BMC}	& Jimple& \multicolumn{2}{c|}{\small Symbolic Exec.} \\
 \hline
-		\small Lines/Vars & \small Average & \small Median & \small Timeout & Lines/Vars (jimple)& \small Average & \small Median & \small Timeout \\
+		\small Lines/Vars & \small Average & \small  \small T/O & Lines/Vars& \small Average & \small  \small T/O \\
 \hline
 \hline
-		50/5	&	0.063	&	0.058	&	0	&	72.85/65.7	&	0.139	&	0.143	&	0	\\
+		50/5	&	0.063		&	0	&	72.85/65.7	&	0.139	&		0	\\
 \hline
-		100/10	&	0.840	&	0.240	&	0	&	129.95/120.85	&	3.052	&	0.374	&	0	\\
+		100/10	&	0.840	&		0	&	129.95/120.85	&	3.052	&	0	\\
 \hline
-		150/15	&	28.459	&	1.752	&	1	&	186.9/175.6	&	36.233	&	2.151	&	1	\\
+		150/15	&	28.459	&		1	&	186.9/175.6	&	36.233	&		1	\\
 \hline
-		200/20	&	76.220	&	14.37	&	2	&	243.75/230.6	&	89.730	&	15.941	&	5	\\
+		200/20	&	76.220	&		2	&	243.75/230.6	&	89.730	&		5	\\
 \hline
-		250/25	&	84.358	&	1.413	&	5	&	300.55/285.85	&	172.482	&	243.845	&	10	\\
+		250/25	&	84.358	&		5	&	300.55/285.85	&	172.482	&		10	\\
 \hline
 	\end{tabular}
-	\caption{....}
-	\label{tab:opt2}
-\end{table}
-
-% BMC compare graph
+		\end{minipage}		
+	\begin{minipage}{0.29\textwidth}
+\scalebox{0.5}{
 \begin{tikzpicture}
 \begin{axis}[%
-			xmin=-5, xmax=150,
-			ymin=-5, ymax=150,
+xmin=-5, xmax=320,
+ymin=-5, ymax=320,
 xlabel=J-ReCoVer(s),
@@
 \end{tikzpicture}
+}			
+		\end{minipage}		
+	\caption{The performance of using BMC and symbolic execution. Each table cell is the result obtained from 20 randomly generated cases.}
+	\label{tab:bmc}
 
-%Discuss the tool’s practical capabilities with reference to the type and size of problems it can handle
+\end{table}
 
-In the other experiments (Table~\ref{}), we compare the efficiency using bounded model checking and symbolic execution we described in Section~\ref{section:optimizations}.
+\section{Concluding Remarks}
 

### 2018-11-09 draft.tex
Update graph data
Update table data
polish sections 1-4

@@
 
+\newcommand{\todo}[1]{{\color{blue}TODO:#1}}
 \newcommand{\hide}[1]{}
@@
 MapReduce framework for data-parallel computation was first proposed by Google~\cite{dean04} and later implemented in the Apache Hadoop project~\cite{hadoop}.
-Under the MapReduce framework, the reducer component computes output values from a sequence of input values transmitted over the network.
-Due to the non-determinism in data transmission, the order of input values arrived at the reducer component is not fixed.
+Under the MapReduce framework, the reducer computes output values from a sequence of input values transmitted over the network.
+Due to the non-determinism in data transmission, the order of input values arrived at the reducer is not fixed.
 The \emph{commutativity problem} of reducers asks if the output of a reducer is independent of the order of its inputs.
@@
 The sequence elements (key-value pairs) with the same key will be sent to the same reducer for further processing.
-Due to scheduling polices and network latency, the same list of values may arrive a reducer in different order in different executions, which results in the so-called \emph{commutativity problem} of reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}, that is, if the outputs of a reducer is independent of the order of its inputs.
-If all reducers are commutative, then they will have the same external behavior under all possible schedules.
+Due to scheduling polices and network latency, the same inputs may arrive a reducer in different order in different executions, which results in the so-called \emph{commutativity problem} of reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}, that is, if the outputs of a reducer is independent of the order of its inputs.
+If all reducers are commutative, they will have the same external behavior under all possible schedules.
 In such a case, by fixing a schedule, the verification problem of a MapReduce program can be reduced to the verification problem of a sequential program, which is known to be much easier then concurrent verification.
+One needs to consider only a particular interleaving of input values instead of all of them.
 
@@
 
-We use 2 sets of integer reducer benchmarks to evaluate J-ReCoVer.
-The first set is collected from open repositories such as Github, Bitbuckect, and GoogleCode.
+We use two sets of integer reducer benchmarks to evaluate J-ReCoVer.
+The first set is collected from open repositories such as Github and Bitbuckect.
 With the help of a search engine~\cite{searchcode} over those repositories, we collected 118 examples.
 J-ReCoVer is able to correctly analyze all but 3 of them.
-We also tried all 10 Integer reducers descried in verification literatures~\cite{ChenHSW15,ChenSW16} and J-ReCoVer can handle all of them in almost no time.
+We also tried all 10 integer reducers descried in verification literatures~\cite{ChenHSW15,ChenSW16} and J-ReCoVer can handle all of them.
 
@@
 Reducer commutativity problem can be reduced to program equivalence problem.
-One creates a variant $R'$ of the original reducer program $R$ such that $R'$ non-deterministically swaps two consecutive input elements and then executes the code of $R$.
-If $R'$ and $R$ are equivalent, using the fact that all permutation of a list can be obtained by swapping consecutive list elements finitely many times, $R$ can be proved to be commutative.
-
-There are a series of research results on program equivalence checking (a.k.a regression verification)~\cite{symdiff,fedyukovich2015automated,sharma2013data,godlin2009regression,fedyukovich2016property,felsing2014automating,KieferKlebanovUlbrich2017,lahiri2013differential,grossman2017verifying,barthe2011relational,KlebanovRuemmerUlbrich2017}.
-At a high level, checking equivalence of two programs $P$ and $P'$ can be reduced to a sequential verification problem by executing $P'$ after $P$ and at the end asserting they have the same outputs.
-It can be made more efficient by finding the right~\emph{synchronization points} and combining the code of $P$ and $P'$ in a interleaved manner.
+One creates another program $R'$ that first non-deterministically swaps two consecutive input values and then executes the code of $R$.
+If $R'$ and $R$ are equivalent, using the fact that all permutations of a list can be obtained by swapping consecutive list elements finitely many times\footnote{Here is an example to produce [2;3;5;1;4] from [1;2;3;4;5] by swapping consecutive elements: [\textbf{1};\textbf{2};3;4;5] $\rightarrow$ [2;\textbf{1};\textbf{3};4;5] $\rightarrow$ [2;3;1;\textbf{4};\textbf{5}]$\rightarrow$ [2;3;\textbf{1};\textbf{5};4]$\rightarrow$ [\textbf{2};\textbf{3};5;1;4]$\rightarrow$ [2;3;5;1;4].}, $R$ can be proved to be commutative.
+There are a series of research results on program equivalence checking (or closely related topics such as regression verification)~\cite{symdiff,fedyukovich2015automated,sharma2013data,godlin2009regression,fedyukovich2016property,felsing2014automating,KieferKlebanovUlbrich2017,lahiri2013differential,grossman2017verifying,barthe2011relational,KlebanovRuemmerUlbrich2017}.
+At a high level, checking equivalence of two programs $P$ and $P'$ can be reduced to a sequential verification problem by executing $P'$ after $P$ and at the end checking if they always have the same outputs.
+It can be made more efficient by finding the right~\emph{synchronization points} and combining the code of $P$ and $P'$ in an interleaved manner.
 A lot of the research effort in this research direction is in finding good synchronization points.
@@
 Besides verification, another interesting research direction is the synthesis of MapReduce programs~\cite{SmithA16}.
-Commutativity analysis is used as a component under this framework.
+Commutativity analysis is used as a component under the synthesis framework.
 
@@
 \label{section:integer-reducers}
-For the presentation purpose, we will describe a highly simplified model to characterize the essence of reducers.
+For the presentation purpose, we describe a highly simplified model to characterize the essence of reducers.
 The model allows to describe the computation of reducers and investigate their commutativity.
@@
 An \emph{integer expression} in $\Exp$ can be either a variable, constant value, a call to the $\cur$ function that reads and consumes an input value of the reducer, their combinations over basic arithmetic operations, or a non-deterministically chosen integer value $*$.
-A \emph{guard} in $\Grd$ can be a comparison between two expressions or boolean combinations of several guards A \emph{command} in $\Cmd$ can be an assignment, a branch statement, concatenation of several commands, or $out(v)$ that outputs that value of $v$.
-A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$, and $s_2$ is assumed to have at most one $\cur$ expression in each branch~\footnote{We define a \emph{branch} of a command $s$ as a sequence obtained by replacing all if statement $\ite{g}{s_1}{s_2}$ in $s$ with either $(g)\wedge s_1$ or $(not\ g) \wedge s_2$.} .
-According to our observation over thousands reducer programs in open repositories, reducer programs are almost always in this form.
-The $\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ when the next input value exists and does it repeatedly until all input values are consumed.
-A few examples of reducer programs in this model can be found in Fig.~\ref{fig:reducer_example}.
+A \emph{guard} in $\Grd$ can be a comparison between two expressions or boolean combinations of several guards.
+A \emph{command} in $\Cmd$ can be an assignment, a branch statement, concatenation of several commands, or $out(v)$ that outputs that value of $v$.
+A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$, and $s_2$ is assumed to have at most one $\cur$ expression in each branch\footnote{We define a \emph{branch} of a command $s$ as a sequence obtained by replacing all if statement $\ite{g}{s_1}{s_2}$ in $s$ with either $(g)\wedge s_1$ or $(not\ g) \wedge s_2$.} .
+According to our observation over hundreds  of reducer programs in open repositories, reducer programs are almost always in this form.
+The $\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly until the entire input list is consumed.
+A few examples of reducer programs in this model can be found in Figure~\ref{fig:reducer_example}.
+
 Some reducer uses two loops to compute the output.
-For example, for standard derivation, one need to first compute the average of the list values (Fig.~\ref{fig:reducer_example}(b)) and use the computed average (set it as a non-deterministic value) to compute the standard derivation (Fig.~\ref{fig:reducer_example}(c)).
-In that case, we can still partition the reducer into two in the way similar to the one in Fig.~\ref{fig:reducer_example} and verify them separately.
+For example, for standard derivation, one first computes the average of inputs and then uses it to compute the standard derivation.
+In that case, we can still verify the reducer by first partitioning it into two reducers and then verifying them separately.
+One reducer computes the average (Figure~\ref{fig:reducer_example}(b)) and the other reducer uses a non-deterministic value to over-approximate the computed average ($a := *$) and and use it in the computation of standard derivation (Figure~\ref{fig:reducer_example}(c)).
+The reducer in Figure~\ref{fig:reducer_example}(c) ``over-approximates''  all possible output of the standard derivation computation; it computes an output even if $a$ is not the average of inputs.
+However, the reducer is still commutative and the commutativity verification can still be done.
 
@@
 	\end{minipage}	
+	\hspace{-0.5cm}
 	\begin{minipage}{0.3\textwidth}
@@
 			};
-			$out(s/c)$\;\;
+			$o := s/c$;\;
+			$out(o)$\;
 		\end{algorithm}
@@
 	\end{minipage}	
-	\begin{minipage}{0.36\textwidth}
+	\begin{minipage}{0.4\textwidth}
 		\begin{algorithm}[H]
@@
 			};
-			$out(s/c)$
+			$o := s/c$;\;
+			$out(o)$
 		\end{algorithm}
@@
 
+In the next section, we give a brief overview of J-Recover,  our tool for reducer commutativity verification.
+
 \section{Overview of the J-ReCoVer tool}
@@
 %Hadoop, Java;
-The input of J-ReCoVer is a Hadoop~\cite{hadoop} reducer program written in Java, which is the most popular programming language used in this framework. 
+The input of J-ReCoVer is a reducer program written in Java, which is the most popular programming language used in the Hadoop~\cite{hadoop} MapReduce framework. 
 The J-ReCoVer tool has three main components, the \emph{Preprocessor}, the \emph{Prover}, and the \emph{BugFinder}.
-As the name suggests, the Preprocessor reads the input reducer and performs the required preprocessing.
+As the name suggests, the Preprocessor reads as input a reducer program and performs the required preprocessing.
 The goal of Prover is to show that a given reducer is commutative and the goal of BugFinder is the opposite.
-The architecture of J-ReCoVer can be found in Fig.~\ref{fig:overview-jrecover}.
+The architecture of J-ReCoVer can be found in Figure~\ref{fig:overview-jrecover}.
 The user can input a reducer program to J-ReCoVer either though our web-interface or binary installed in their own machine.
@@
 
-The Preprocessor component first compiles a reducer program to bytecode and use the tool Soot~\cite{soot} to convert it to the so called Jimple format, which is an intermediate language that is designed to make the analysis of Java program easier.
-Under the Hadoop MapReduce framework, the permutation of the input is caused by the scheduler/shuffler component and is affected by things like network latency, which is not controllable by the user.
-In order to handle this issue, we wrote our own dummy Hadoop interface for the reducer as a part of the Preprocessor component .
-So that the input/output of the reducer is now controlled by J-ReCoVer.
-Finally, we perform in the Preprocessor some simple program transformations that make the analysis easier.
-For example, we convert all output commands $out(e)$ inside loops to an special assignment $v_{out}:=e$.
+\textbf{The Preprocessor component} first compiles a reducer program to bytecode and use the tool Soot~\cite{soot} to further convert it to the so called ``Jimple'' format, which is an intermediate language that is designed to make the analysis of Java program easier.
+Under the Hadoop MapReduce framework, the permutation of the input is handled by the scheduler/shuffler component and is affected by things like network latency, which is not controllable by the user.
+In order to deal with this issue, we wrote our own dummy Hadoop interface for the reducer as a part of the Preprocessor component.
+So that the input order of the reducer is now controlled by J-ReCoVer.
+Finally, we perform in the Preprocessor some simple program transformations tasks to simplify the analysis.
+For example, we convert all output commands $out(e)$ inside loops to an special assignment.
 
-In the Prover component, we reduce the commutativity problem to a SMT formula satisfiability problem, using the fact that all permutations of a list can be obtained by swapping consecutive elements finitely many times.
-At a high level, we check equivalence between a reducer program and its variant that have two consecutive inputs swapped.
-We show that this can be reduced to a simple SMT problem and give it to Z3~\cite{z3} for solving.
-In case that Z3 proved the formula unsatisfiable, J-ReCoVer stops and reports the reducer is commutative.
-If we run the approach in a naive manner, it does not scale to large programs and is very imprecise.
-We will introduce two critical optimizations that makes the proposed approach works for real examples in Section~\ref{section:optimizations}: an improved symbolic execution algorithm to generate Z3 formulae and a data flow analysis to extract critical variables.
-More details of the algorithms used in the Preprocessor and the Prover components will be explained in Section~\ref{sec:preprocessor_prover} and the optimizations will be introduced in~\ref{section:optimizations}.
-
-The BugFinder component randomly generated 1500 pairs of list and its permutation for testing.
+\textbf{The BugFinder component} randomly generated 1500 pairs of lists.
+The lists in a pair are permutations of each other.
 A concrete counterexample is reported if inputting any pair of lists from the 1500 generated ones to the reducer generates different results.
@@
 
+\textbf{The Prover component} reduces the commutativity problem to a SMT formula satisfiability problem, using the fact that all permutations of a list can be obtained by swapping consecutive elements finitely many times.
+At a high level, we check equivalence between a reducer program and its variant that have two consecutive inputs swapped.
+We show that this can be reduced to a SMT problem and give it to SMT solver Z3~\cite{z3} for solving.
+In case that Z3 proved the formula unsatisfiable, J-ReCoVer stops and reports that the reducer is commutative.
+If we run the approach in a naive manner, it does not scale to large programs and is very imprecise.
+We will introduce two critical optimizations that enables the proposed approach working for real-world examples in Section~\ref{section:optimizations}: a data flow analysis to extract critical variables and an improved symbolic execution algorithm to generate Z3 formulae.
+More details of the algorithms used in the Preprocessor and the Prover components will be explained in Section~\ref{sec:preprocessor_prover} and the optimizations will be introduced in~\ref{section:optimizations}.
+
 \section{The Preprocessor and the Prover}
@@
 
-As mentioned, before entering the Prover components, the Preprocessor first performs a few program transformation to simplify the verification task. 
+Before entering the Prover component, the Preprocessor first performs a few program transformation tasks to simplify the verification task. 
 We assume the reducer $s_1;\rloop\{s_2\};s_3$ is given.
-We begin the section with our first program transformation task that handles the case when $s_2$ contains $out$ commands.
-The output of the first transformation task is a commutativity-equivalent reducer program where $out$ does not occur in $s_1$.
-Then we explain the algorithm of the Prover that works only in a special case where no read from input occurs in $s_1$.
-For general reducer programs, we introduce the second program transformation task whose output is a reducer program that contains all input/output behaviors of the original reducer (may contain behaviors not in the original reducer) and does not have $\cur$ in $s_1$, which can be analyzed by the algorithm of Prover.
+We begin the section with our first program transformation task (Section~\ref{sec:program_trans1}) that handles the case when $s_2$ contains $out$ commands.
+The output of the first transformation task is a commutativity-equivalent reducer program where $out$ does not occur in $s_2$.
+Then we explain the algorithm of the Prover (Section~\ref{sec:prover}) that works only in a special case where no read from input occurs in $s_1$.
+For general reducer programs, we introduce the second program transformation task (Section~\ref{sec:program_trans2}) whose output is a reducer program that contains all input/output behaviors of the original reducer (may contain behaviors that are not in the original reducer) and there is no read from input (i,e., does not have the $\cur$ expression) in $s_1$, which can be analyzed by the algorithm of Prover.
 
@@
 Notice that the value of $v_{out_n}$ stays the same from the point it has been assigned a value. 
-If the values of $v_{out_n}$ are the same for all permutations of input lists at the end of $s_2$, we know that the a reducer that is commutative w.r.t. to all output commands inside the loop.
+If the values of $v_{out_n}$ are the same for all permutations of input lists at the end of $s_2$, we know that the reducer is commutative w.r.t. to all output commands inside the loop body $s_2$.
 
@@
 \begin{equation}
- F(n_1, F(n_2,x_1,x_2,\ldots,x_n) = F(n_2, F(n_1,x_1,x_2,\ldots,x_n) 
+ F(n_1, F(n_2,x_1,x_2,\ldots,x_n)) = F(n_2, F(n_1,x_1,x_2,\ldots,x_n) )
 \label{eq:commu}
 \end{equation}
-The validity of formula~(\ref{eq:commu}) implies that swapping any two consecutive input values does not change the final variable valuation.
-Informally, it says that the values of all program variables stay the same when we execute the loop body twice (from any initial valuations of variables), one with the inputs $n_1$ and $n_2$ and the other with their reverse.
-That is, swapping any two consecutive input values does not change the output.
-Since any permutation of a sequence can be obtained by swapping consecutive values finitely many times~\cite{algebra}, this further implies that starting from the same variable valuation, the loop ends with the same valuation for any permutation of input values and produce the same sequence of output.
 
-We show that this is sufficient to prove the commutativity of the reducer.
-Notice that $s_1$ does not read from the input and at $s_3$ all input has been read (this is the exit condition of the loop), both of them behave deterministically in the sense that from the same initial valuation, they output the same sequence of values and ends at the same valuation.
-From the validity of formula~(\ref{eq:commu}), any permutation of input values leads the reducer to the same valuation.
-Hence we know that any permutation of input values will produce the same sequence of output.
+Using the reducer that computes average (Figure~\ref{fig:reducer_example} (b)) as an example.
+It has two variables $s$ and $c$.
+It is not difficult to compute that $F_{average}(n,s,c)=(s+n, c+1)$.
+In this case, the corresponding Equation~(\ref{eq:commu}) is valid because $F_{average}(n_1, F_{average}(n_2,s,c)) =F_{average}(n_1, s+n_2, c+1)= (s+n_1+n_2,c+2)=F_{average}(n_2, s+n_1, c+1)=F_{average}(n_2, F_{average}(n_1,s,c))$.
+
+The validity of Equation~(\ref{eq:commu}) implies that swapping any two consecutive input values does not change the final variable valuation.
+Informally, it says that starting from the same initial valuations of variables and with two different input orders, the values of all program variables are the same after we execute the loop body twice.
+The first execution reads $n_1$ and then reads $n_2$.
+The other execution reads the two inputs in the reverse order.
+
+In the example of ``average'', the values of $s$ and $c$ are the same no matter the reducer first reads $n_1$ and then $n_2$ or reads the two values in the swapped order.
+So it computes the same value for the input [1;2;3;4;5] and any other input with two consecutive values swaps, e.g., [1;2;\textbf{4};\textbf{3};5].
+Since any permutation of a sequence can be obtained by swapping consecutive values finitely many times~\cite{algebra}, this further implies that starting from the same variable valuation, the loop ends with the same valuation for any permutation of input values.
+Recall that the first program transformation task remembers all output values in variables that will stay unchanged until the end of the loop.
+The validity of Equation~(\ref{eq:commu}) also implies that the execution of the loop produces the same sequence of outputs.
+
+We explain why that the validity of Equation~(\ref{eq:commu}) is sufficient to prove the commutativity of the reducer.
+Notice that $s_1$ (the commands before entering the loop) does not read from the input (the assumption in this subsection).
+The execution of $s_1$ is deterministic in the sense that from the same initial valuation, it outputs the same sequence of values and ends at the same valuation.
+From the validity of Equation~(\ref{eq:commu}), any permutation of input values leads the reducer to the same final valuation and the same sequence of outputs.
+Before executing $s_3$ (the commands before after the execution of the loop), all inputs have been read (this is the exit condition of the loop) already, similar the the case of $s_1$, it behaves deterministically for all permutations of inputs and outputs the same sequence of values.
+
+In the next subsection, we explain how to generalize our approach to support general reducer programs using program transformation.
 
@@
 		\begin{algorithm}[H]
-			$m := \cur + 10$; \;
+			\;\;$m := \cur + 10$; \;
 			\Loop{}{
-				\uIf{ $\cur > m$}{
-					$m := \cur$ \;
+				$t:=\cur$\;
+				\uIf{ $t> m$}{
+					$m := t$ \;
 				}
 			};
-			$out(m)$
+			$out(m)$\;\;
 		\end{algorithm}
-		\caption*{(a)Reducer max$^+$}
+		\caption*{(a) Reducer max$^+$}
 	\end{minipage}
@@
 					\uIf{$s=1$}{$m := \cur + 10; s:= 2$}
-					\uElseIf{ $\cur > m$}{
-						$m := \cur$ \;
+					\uElse{
+						$t:=\cur$\;
+						\uIf{ $t > m$}{
+							$m := t$ \;
+						}
 					}
@@
 
+In real-world examples, it is often that the $s_1$ part of the reducer also reads from the input.
+In the example in Figure~\ref{fig:reducer_max} (a), the reducer program remembers the first input value in the variable $m$, increases its value by 10, and then updates its value to bigger ones if any occurs in the loop.
+The corresponding Equation~(\ref{eq:commu}) is valid in this case, however, the reducer is not commutative.
+For example, the two lists $[1,2,3,4,5]$ and $[5,4,3,2,1]$ are permutations of each other, but the reducer respectively outputs $11$ and $15$ with them as the inputs.
+
+We handle the problem again by program transformation.
+To handle the example in Figure~\ref{fig:reducer_max} (a), we move the prefix $s_1$ into the loop body and use a new variable $s$ to force that $s_1$ is always executed before the original loop body.
+The result after the transformation can be found in Figure~\ref{fig:reducer_max} (b).
+Observe that the new reducer program over-approximates all possible inputs/outputs of the original one.
+It also satisfies all assumptions required for the Prover component: (a) The commands before entering the loop does not have any $\cur$ expression and (II) each branch (recall that ``branch'' is formally defined in Section~\ref{section:integer-reducers}) of the loop body has at most one $\cur$.
+So we can apply Equation~(\ref{eq:commu}) to prove its commutativity.
+Since the new reducer has all the possible outputs of the original one, the new reducer is commutative implying that the original one is also commutative.
+
 \begin{wrapfigure}{r}{0.56\textwidth} 
-%		\vspace{-1.8cm}
+		\vspace{-1.2cm}
 	\begin{algorithm}[H]
@@
 	\end{algorithm}
-		\caption{The second program transformation}
+	\caption{The second transformation task}
 	\label{fig:general_program_transformation}
+		\vspace{-1.2cm}
 \end{wrapfigure}
-However, in reality, it is often that the $s_1$ part also reads from the input.
-See the example in Fig.~\ref{fig:reducer_max} (a), in this example, the program remembers the first input value in the variable $m$, increases its value by 10, and then updates its value to bigger ones if any occurs in the loop.
-The corresponding formula~(\ref{eq:commu}) is valid in this case, however, the reducer is not commutative.
-For example, the two lists $[1,2,3,4,5]$ and $[5,4,3,2,1]$ are permutations of each other, but the reducer respectively outputs $11$ and $15$ with them as the inputs.
-
-We handle the problem again by program transformation.
-For the example in Fig.~\ref{fig:reducer_max} (a), we move the prefix $s_1$ into the loop body and use a new variable $s$ to force that $s_1$ is always executed before the original loop body.
-The result after the transformation can be found in Fig.~\ref{fig:reducer_max} (b).
-Observe that the new reducer program over-approximates all possible inputs/outputs of the original one.
-It also satisfies all assumptions required for the Prover: (I) $s'_0$ does not have any $\cur$ expression and (II) each branch (recall that this is defined in Section~\ref{section:integer-reducers}) of the loop body has at most one $\cur$.
-So we can apply equation~(\ref{eq:commu}) to prove its commutativity.
-Since the new reducer has all the possible output of the original one, the new reducer is commutative implying that the original one is also commutative.
 
@@
 $$s'_0;x_{i_1}{:=} \cur;s'_1.\ldots x_{i_{m}}{:=}\cur;s'_m, $$ where $\cur$ never occur in $s'_0,s'_1,\ldots, s'_m$.
-The reducer in Fig.~\ref{fig:general_program_transformation} is an over-approximation of the original reducer that satisfies all assumptions required for the Prover.
-Hence the equation~(\ref{eq:commu}) can then be applied to prove its commutativity.
+Then we produce the reducer in Figure~\ref{fig:general_program_transformation}, which is an over-approximation of the original reducer satisfying all assumptions required for the Prover.
+Hence the Equation~(\ref{eq:commu}) can then be applied to prove its commutativity.
 
@@
 Nevertheless, such example might not be of the interests of MapReduce programmers, who usually care only about the data set they want to analyze.
-We are building another tool that estimates a safe bound of data size such that overflow will not occur.
+We are planing to build another tool that estimates a safe bound of data size such that overflow will not occur.
 The programmer can than check if their data set fits the computed bound and use lager data type in the program when needed.
+So overflow will not occurs in the data set of interests.
 
@@
 \label{section:optimizations}
-In this section we explain how data flow analysis are used in our case to improve the precision of commutativity checking and the algorithm we used to construct the $F$ function in formula~(\ref{eq:commu}).
+In this section we explain how data flow analysis are used in our case to improve the precision of commutativity checking and the algorithm we used to construct the $F$ function in Equation~(\ref{eq:commu}).
 
@@
 \label{section:opt1}
-We find that in many cases, formula~\ref{eq:commu} is a condition that is too strong for the reducer to be commutative.
-For instance, consider the example in Fig.~\ref{fig:reducer_opt}, in the loop body, the input is first stored in a variable $t$ and then added to $s$.
+We find that in many cases, Equation~(\ref{eq:commu}) is a condition that is too strong for the reducer to be commutative.
+For instance, consider the example in Figure~\ref{fig:reducer_opt}, in the loop body, the input is first stored in a variable $t$ and then added to $s$.
 In this case, the $F$ function returns the updated values of both $s$ and $t$ after the execution of loop body.
@@
 $F(c_1, F(c_2,s,t) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t) = (c_1+c_2, c_2)$, which follows that the corresponding equation~\ref{eq:commu} is invalid.
-The second component of the returned tuple, which corresponds to the value of $temp$ after executing the loop body twice, are $c_1$ and $c_2$, respectively.
+The second component of the returned tuple, which corresponds to the value of $t$ after executing the loop body twice, are $c_1$ and $c_2$, respectively.
 However, in this case, the value of $t$ is not important to the output of this reducer.
+The situation happens in all Jimple code produced by Soot.
 
-\begin{figure}[t]
+\begin{figure}[hbt]
 	\begin{minipage}{0.4\textwidth}
@@
 			};
-			$out(s)$\;
+			$out(s)$\;\;
 		\end{algorithm}
-		\caption{A commutative reducer with an invalid equation~(\ref{eq:commu}).}
+		\caption{A commutative reducer with an invalid Equation~(\ref{eq:commu}).}
 		\label{fig:reducer_opt}
 	\end{minipage}
-	\begin{minipage}{0.5\textwidth}
+	\begin{minipage}{0.55\textwidth}
+		\centering
+		\begin{minipage}{0.75\textwidth}
 		\begin{algorithm}[H]
@@
 		\end{algorithm}
+	\end{minipage}
 		\caption{$out(v)$ in nested branches of $s_3$.}
@@
 
-To handle such situation, we perform a simple data flow analysis to collect all variables whose value may propagate to the output after the loop.
+To handle such a situation, we perform a simple data flow analysis to collect all variables whose value may propagate to the output command after the loop execution.
 We do it in a backward manner.
 With out loss of generality, we assume there is only one output command after the loop.
-Then the code after the loop (i.e., the $s_3$ part of the reducer) can only be in the form of Fig.~\ref{fig:nested_out}.
+Then the code after the loop (i.e., the $s_3$ part of the reducer) can only be in the form of Figure~\ref{fig:nested_out}.
 The commands $c_1\ldots c_n$ are either assignment commands $w:=e$ or branch command $\ite{g}{c'_1}{c'_2}$, and the only output command stays in the $m$-th layer of the branch command after $c_i$.
@@
 The data flow analysis algorithm works as follows.
-A set $V_3$ whose value is initially a singleton set $\{v\}$ is used to remember important variables that might flow to the output commands in $s_3$.
-The commands and guards will be inspected in the following order $c_{n}$,$\ldots$,$c_{i+1}$, $g_m$, $g_{m-1}$, $\ldots$, $g_1$, $s_i$, $\ldots$, $c_2$, $c_1$.
+A set $V_3$ whose value is initially a singleton set $\{v\}$ is used to remember important variables that might flow to the output command in $s_3$.
+The commands and guards will be inspected in the following order $c_{n}$,$\ldots$,$c_{i+1}$, $g_m$, $g_{m-1}$, $\ldots$, $g_1$, $c_i$, $\ldots$, $c_2$, $c_1$.
 For the case that a guard $g_j$ for $j\in [1,m]$ is being processed, we simply add all variables occurred in $g_j$ to $V_3$.
-
-Recall that the commands $c_j$ for $j\in [1,n]$ can only be in the form of $w:=e$ or $\ite{g}{c'_1}{c'_2}$.
+For the case that a command $c_j$ for $j\in [1,n]$ is being processed, 
+recall that $c_j$ can only be in the form of an assignment $w:=e$ or a branch $\ite{g}{c'_1}{c'_2}$.
 For the case that $c_j$ is an assignment $w:=e$ and $w\in V_3$, we add all variables contained in $e$ to $V_3$.
-For the case that $c_j$ is an branch command $\ite{g}{c'_1}{c'_2}$, we process both $c'_1$ and $c'_2$ in a similar manner.
+For the case that $c_j$ is a branch command $\ite{g}{c'_1}{c'_2}$, we process both $c'_1$ and $c'_2$ in a similar manner.
 Starting from the same set $V_3$,  after processing $c'_1$ and $c'_2$, we get respectively two sets $V_3^1$ and $V_3^2$, we take their union $V_3^1\cup V_3^2$ as the new value of $V_3$.
 
-Then we modify the equation~(\ref{eq:commu}) to the one below
+Then we modify the Equation~(\ref{eq:commu}) to the one below
 
@@
 The use of equation~(\ref{eq:commu2}) is critical to the successful of our approach.
-In our evaluation, the ratio of examples that our approach can successfully analyze is significantly increased from $14\%$ to $98\%$.
-The details of the experiments can be found in Section~\ref{section:exp}.
+In our evaluation, the ratio of examples that our approach can successfully analyze is significantly increased from $6.8\%$ to $97.5\%$.
+The details of the evaluation can be found in Section~\ref{section:exp}.
 
@@
 In our experience, this will increase the number of lines by $20\%$ and variables by $11$ times.
-The results are presented in Fig.~\ref{tab:opt2} in the form of a table and also a scatter plot.
+The results are presented in Figure~\ref{tab:opt2} in the form of a table and also a scatter plot.
 Form there we can see that the optimization is helpful in improving all the statistics (average, median execution time and the number of cases that cannot be finished within 300 seconds).
@@
 In this evaluation, we see that the performance of using BMC is in general better, less timeout and lower average execution time, so we plan to also include a BMC engine in the next version.
-However, from the scatter plot we can see there are multiple cases that  can be solved using symbolic execution but are slower or even falied using BMC.
+However, from the scatter plot we can see there are multiple cases that  can be solved using symbolic execution but are slower or even failed using BMC.
 So the best strategy should be keep the both engine and switch to another if one fails.

### 2018-11-11 draft.tex
polish sections 1-4
conclusion

@@
 			\Loop{}{
-				\uIf{ $\cur > m$}{
-					$m := \cur$ 
+				$t:=\cur$;\;
+				\uIf{ $t > m$}{
+					$m := t$ 
 				}
@@
 
-\subsection{Limitations and assumptions}
-At the back-end, we use SMT theory of integer arithmetics as the reasoning tool. In this implementation, we do not handle more advanced data-types such as string and floating point. 
-The problem of variable overflow is not handled by this tool.
-In fact, if we consider all possible inputs of a reducer, almost all reducer programs will run into the problem of overflow.
-Even the basic example that computes the sum of all input values, overflow can occur when a list contains two maximal 64-bit integer values is used as the input.
-Nevertheless, such example might not be of the interests of MapReduce programmers, who usually care only about the data set they want to analyze.
-We are planing to build another tool that estimates a safe bound of data size such that overflow will not occur.
-The programmer can than check if their data set fits the computed bound and use lager data type in the program when needed.
-So overflow will not occurs in the data set of interests.
-
 \section{Optimizations}
@@
 		\hline
-		\multirow{4}{*}{Open repositories}&Commutative& 8&106\\ 
+		\multirow{4}{*}{Open repositories}&Commutative& 0&106\\ 
 		\cline{2-4}
-		&Non-commutative&9&9\\
+		&Non-commutative&8&9\\
 		\cline{2-4}
-		&Unknown&101&3\\
+		&Unknown&110&3\\
 		\cline{2-4}
-		&Precision& 14.4\% & 97.5\%\\
+		&Precision& 6.8\% & 97.5\%\\
 		\hline
@@
 	\hline
-	50	&	11.104	&	10.446	&	0	&	10.284	&	10.193	&	0	\\
+	50	&	4.3	    &   3.7	&	0	&	4.7	&	3.6	&	0	\\
 	\hline                                                                      
-	100	&	19.766	&	11.239	&	1	&	29.544	&	11.172	&	3	\\
+	100	&	35.8	&	5.1&	4	&	37.2	&	4.5	&	6	\\
 	\hline                                                                     
-	150	&	88.741	&	17.943	&	12	&	63.931	&	13.984	&	7	\\
+	150	&	92.3	&	12.3&	13	&	74.0	&	7.5	&	9	\\
 	\hline                                                                     
-	200	&	88.741	&	169.456	&	26	&	63.931	&	13.984	&	7	\\
+	200	&	156.6	&	179.7&	25	&	138.1	&	48.2	&	25	\\
 	\hline                                                                     
-	250	&	232.348	&	300.000	&	43	&	175.976	&	248.998	&	30	\\
+	250	&	196.8	&	300.0&	35	&	175.9	&	274.9	&	30	\\
 	\hline
@@
 
+\hide{
 % Optimization compare graph
@@
 \hline
-		50/5	&	0.063		&	0	&	72.85/65.7	&	0.139	&		0	\\
+		50/5	&	0.1		&	0	&	72.9/65.7	&	0.1	&		0	\\
 \hline
-		100/10	&	0.840	&		0	&	129.95/120.85	&	3.052	&	0	\\
+		100/10	&	0.8	&		0	&	130.0/120.9	&	3.1	&	0	\\
 \hline
-		150/15	&	28.459	&		1	&	186.9/175.6	&	36.233	&		1	\\
+		150/15	&	28.5	&		1	&	186.9/175.6	&	36.2	&		1	\\
 \hline
-		200/20	&	76.220	&		2	&	243.75/230.6	&	89.730	&		5	\\
+		200/20	&	76.2	&		2	&	243.8/230.6	&	89.7	&		5	\\
 \hline
-		250/25	&	84.358	&		5	&	300.55/285.85	&	172.482	&		10	\\
+		250/25	&	84.4	&		5	&	300.6/285.9	&	172.5	&		10	\\
 \hline
@@
 ymin=-5, ymax=320,
-xlabel=J-ReCoVer(s),
+xlabel=Symbolic Exec.(s),
 ylabel=BMC(s)
@@
 \end{table}
+}
+\section{Concluding Remarks}
+We believe that simpler but more restricted language/framework will be the trend for parallel program development.
+It lowers the barrier for writing parallel program.
+So experts in other domains such as data science and machine learning can use the power of parallel data processing with much less efforts.
+Many of their applications do not need the full power of message passing programming so they do not need to those build their programs on top of traditional means such as MPI or socket programming.
+MapReduce framework is a pioneer in this kind of frameworks for data parallel computation.
+Its successors such as Spark, Flink, Beam, and Google Cloud Dataflow, still share many features of its design.
+We believe the design of J-Recover will lead to significant impact to the verification/testing of programs under such frameworks.
 
-\section{Concluding Remarks}
+The current version of J-Recover shares similar limitation with SMT-based software verification tools.
+We use SMT theory of integer and real number arithmetics as the reasoning tool.
+In this implementation.
+We do not handle more advanced data-types such as string and floating point.
+The problem of variable overflow is not handled by this tool.
+In fact, if we consider all possible inputs of a reducer, almost all reducer programs will run into the problem of overflow.
+Even the basic example that computes the sum of all input values, overflow can occur when a list contains two maximal 64-bit integer values is used as the input.
+Nevertheless, such example might not be of the interests of MapReduce programmers, who usually care only about the data set they want to analyze.
+We are planing to build another tool that estimates a safe bound of data size such that overflow will not occur.
+The programmer can than check if their data set fits the computed bound and use lager data type in the program when needed.
+So overflow will not occurs in the data set of interests.
 
-\bibliographystyle{splncs-sorted}
+%\bibliographystyle{splncs-sorted}
 \bibliography{refs}

### 2018-11-11 draft.tex
conclusion

@@
 Nevertheless, such example might not be of the interests of MapReduce programmers, who usually care only about the data set they want to analyze.
-We are planing to build another tool that estimates a safe bound of data size such that overflow will not occur.
-The programmer can than check if their data set fits the computed bound and use lager data type in the program when needed.
+We are planing to build another tool that estimates a safe bound of data size such that overflow will not occur if data size is within bound.
+The programmer can then check if their data set fits in the computed bound and switch to use lager data type in the program when needed.
 So overflow will not occurs in the data set of interests.

### 2018-11-13 draft.tex
Trim trailing spaces in `draft.tex`
polish

@@
 In this paper, we propose effective heuristics for reducer commutative analysis and implement them as a tool J-ReCoVer (Java Reducer Commutativity Verifier), which is the first tool that is specialized in checking reducer commutativity.
-Experimental results over 128 benchmark examples collected from literatures and open repositories are very positive; J-ReCoVer correctly handles over 97\% of them.
+Experimental results over 128 benchmark examples collected from literature and open repositories are very positive; J-ReCoVer correctly handles over 97\% of them.
 
@@
 The sequence elements (key-value pairs) with the same key will be sent to the same reducer for further processing.
-Due to scheduling polices and network latency, the same inputs may arrive a reducer in different order in different executions, which results in the so-called \emph{commutativity problem} of reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}, that is, if the outputs of a reducer is independent of the order of its inputs.
+Due to scheduling polices and network latency, the same inputs may arrive at a reducer in different order in different executions, which results in the so-called \emph{commutativity problem} of reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}, that is, if the outputs of a reducer is independent of the order of its inputs.
 If all reducers are commutative, they will have the same external behavior under all possible schedules.
-In such a case, by fixing a schedule, the verification problem of a MapReduce program can be reduced to the verification problem of a sequential program, which is known to be much easier then concurrent verification.
+In such a case, by fixing a schedule, the verification problem of a MapReduce program can be reduced to the verification problem of a sequential program, which is known to be much easier then the verification problem of concurrent programs.
 One needs to consider only a particular interleaving of input values instead of all of them.
@@
 J-ReCoVer is able to correctly analyze all but 3 of them.
-We also tried all 10 integer reducers descried in verification literatures~\cite{ChenHSW15,ChenSW16} and J-ReCoVer can handle all of them.
+We also tried all 10 integer reducers descried in verification literature~\cite{ChenHSW15,ChenSW16} and J-ReCoVer can handle all of them.
 
@@
 One creates another program $R'$ that first non-deterministically swaps two consecutive input values and then executes the code of $R$.
-If $R'$ and $R$ are equivalent, using the fact that all permutations of a list can be obtained by swapping consecutive list elements finitely many times\footnote{Here is an example to produce [2;3;5;1;4] from [1;2;3;4;5] by swapping consecutive elements: [\textbf{1};\textbf{2};3;4;5] $\rightarrow$ [2;\textbf{1};\textbf{3};4;5] $\rightarrow$ [2;3;1;\textbf{4};\textbf{5}]$\rightarrow$ [2;3;\textbf{1};\textbf{5};4]$\rightarrow$ [\textbf{2};\textbf{3};5;1;4]$\rightarrow$ [2;3;5;1;4].}, $R$ can be proved to be commutative.
+If $R'$ and $R$ are equivalent, using the fact that all permutations of a list can be obtained by swapping consecutive list elements finitely many times\footnote{Here is an example to produce [3;2;5;1;4] from [1;2;3;4;5] by swapping consecutive elements: [\textbf{1};\textbf{2};3;4;5] $\rightarrow$ [2;\textbf{1};\textbf{3};4;5] $\rightarrow$ [2;3;1;\textbf{4};\textbf{5}]$\rightarrow$ [2;3;\textbf{1};\textbf{5};4]$\rightarrow$ [\textbf{2};\textbf{3};5;1;4]$\rightarrow$ [3;2;5;1;4].}, $R$ can be proved to be commutative.
 There are a series of research results on program equivalence checking (or closely related topics such as regression verification)~\cite{symdiff,fedyukovich2015automated,sharma2013data,godlin2009regression,fedyukovich2016property,felsing2014automating,KieferKlebanovUlbrich2017,lahiri2013differential,grossman2017verifying,barthe2011relational,KlebanovRuemmerUlbrich2017}.
@@
 \label{section:integer-reducers}
-For the presentation purpose, we describe a highly simplified model to characterize the essence of reducers.
-The model allows to describe the computation of reducers and investigate their commutativity.
+We use $\Z$ to denote the set of integers and $[n,m]$ to denote the set of integers $\{k\mid n \leq k\leq m\}$. 
+We lift the equality $=$ operation to tuples in the standard way.
+Let $S\subseteq [1,k]$, the equality $\{v_1,\ldots,v_k\}=_{S} \{v'_1,\ldots,v'_k\}$ between tuples holds if and only if $\bigwedge_{i\in S} v_i=v'_i$.
+For presentation purpose, we describe a highly simplified model to characterize the essence of reducers. The model allows to describe the computation of reducers and investigate their commutativity.
 
@@
 e \in \Exp    &\ \ \  {\triangleq}\ \ \   & v \mid c \mid \cur \mid e + e \mid e - e \mid e \times e \mid *\mid\ldots & &\textmd{Integer Expression}\\
-g\in \Grd  & {\triangleq}  & e < e \mid not\ e \mid g \wedge g  \mid \ldots& & \textmd{Guard}\\
+g\in \Grd  & {\triangleq}  & e < e \mid not\ g \mid g \wedge g  \mid \ldots& & \textmd{Guard}\\
 s\in \Cmd  & {\triangleq}  & v:= e \mid out(v) \mid \ite{g}{s}{s} \mid s;s && \textmd{Command}\\
@@
 A \emph{guard} in $\Grd$ can be a comparison between two expressions or boolean combinations of several guards.
-A \emph{command} in $\Cmd$ can be an assignment, a branch statement, concatenation of several commands, or $out(v)$ that outputs that value of $v$.
-A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$, and $s_2$ is assumed to have at most one $\cur$ expression in each branch\footnote{We define a \emph{branch} of a command $s$ as a sequence obtained by replacing all if statement $\ite{g}{s_1}{s_2}$ in $s$ with either $(g)\wedge s_1$ or $(not\ g) \wedge s_2$.} .
+A \emph{command} in $\Cmd$ can be an assignment, a branch statement, concatenation of a sequence of commands, or $out(v)$ that outputs the value of $v$.
+A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$, and $s_2$ is assumed to have at most one $\cur$ expression in each branch\footnote{We define a \emph{branch} of a command $s$ as a sequence obtained by replacing every branch statement $\ite{g}{s_1}{s_2}$ in $s$ with either $(g)\wedge s_1$ or $(not\ g) \wedge s_2$.} .
 According to our observation over hundreds  of reducer programs in open repositories, reducer programs are almost always in this form.
@@
 Some reducer uses two loops to compute the output.
-For example, for standard derivation, one first computes the average of inputs and then uses it to compute the standard derivation.
+For example, for calculating standard deviation, one first computes the average of inputs and then uses it to compute the standard deviation.
 In that case, we can still verify the reducer by first partitioning it into two reducers and then verifying them separately.
-One reducer computes the average (Figure~\ref{fig:reducer_example}(b)) and the other reducer uses a non-deterministic value to over-approximate the computed average ($a := *$) and and use it in the computation of standard derivation (Figure~\ref{fig:reducer_example}(c)).
-The reducer in Figure~\ref{fig:reducer_example}(c) ``over-approximates''  all possible output of the standard derivation computation; it computes an output even if $a$ is not the average of inputs.
-However, the reducer is still commutative and the commutativity verification can still be done.
+One reducer computes the average (Figure~\ref{fig:reducer_example}(b)) and the other reducer uses a non-deterministic value to over-approximate the computed average ($a := *$) and then use it in the computation of standard deviation (Figure~\ref{fig:reducer_example}(c)).
+The reducer in Figure~\ref{fig:reducer_example}(c) ``over-approximates''  all possible output of the standard deviation computation; it computes an output even if $a$ is not the average of inputs.
+However, the reducer is still commutative and its commutativity verification can still be done.
 
@@
 		\end{algorithm}
-		\caption*{(c) standard derivation}
+		\caption*{(c) standard deviation}
 	\end{minipage}	
@@
 The architecture of J-ReCoVer can be found in Figure~\ref{fig:overview-jrecover}.
-The user can input a reducer program to J-ReCoVer either though our web-interface or binary installed in their own machine.
+The user can input a reducer program to J-ReCoVer either through our web-interface or binary installed on their own machine.
 
@@
 
-\textbf{The Preprocessor component} first compiles a reducer program to bytecode and use the tool Soot~\cite{soot} to further convert it to the so called ``Jimple'' format, which is an intermediate language that is designed to make the analysis of Java program easier.
-Under the Hadoop MapReduce framework, the permutation of the input is handled by the scheduler/shuffler component and is affected by things like network latency, which is not controllable by the user.
-In order to deal with this issue, we wrote our own dummy Hadoop interface for the reducer as a part of the Preprocessor component.
+\textbf{The Preprocessor component} first compiles a reducer program to bytecode and use the tool Soot~\cite{soot} to further convert it to the so called ``Jimple'' format, which is an intermediate language that is designed to simplift the analysis of Java programs.
+Under the Hadoop MapReduce framework, the permutation of the input is handled by the scheduler/shuffler component and is affected by things like network latency, which is not controllable by programmers.
+In order to deal with this issue, we wrote our own dummy Hadoop environment for the reducer as a part of the Preprocessor component.
 So that the input order of the reducer is now controlled by J-ReCoVer.
 Finally, we perform in the Preprocessor some simple program transformations tasks to simplify the analysis.
-For example, we convert all output commands $out(e)$ inside loops to an special assignment.
+For example, we convert all output commands $out(e)$ inside loops to an special assignment (Section~\ref{sec:program_trans1} and~\ref{sec:program_trans2}).
 
@@
 We use five different input list of lengths 5, 7, 9 ,11, and 13.
-For each length, we generates 300 lists.
-For each list, we pick uniformly at random one of its permutations.
+For each length, we generate 300 lists and pick uniformly at random one of its permutations.
 Although the approach is simple, in practice it finds counterexamples in all of our non-commutative benchmarks.
 
-\textbf{The Prover component} reduces the commutativity problem to a SMT formula satisfiability problem, using the fact that all permutations of a list can be obtained by swapping consecutive elements finitely many times.
+\textbf{The Prover component} reduces the commutativity problem to a SMT formula satisfiability problem.
 At a high level, we check equivalence between a reducer program and its variant that have two consecutive inputs swapped.
 We show that this can be reduced to a SMT problem and give it to SMT solver Z3~\cite{z3} for solving.
-In case that Z3 proved the formula unsatisfiable, J-ReCoVer stops and reports that the reducer is commutative.
+Recall that all permutations of a list can be obtained by swapping consecutive elements finitely many times.
+In case that Z3 proved the formula unsatisfiable, we know that swapping any two consecutive inputs of the reducer will not change its output.
+It follows that the reducer outputs the same value for all permutations of the same list of input.
+In this case,  J-ReCoVer stops and reports that the reducer is commutative.
+
 If we run the approach in a naive manner, it does not scale to large programs and is very imprecise.
@@
 \label{sec:program_trans1}
-J-ReCoVer  first generates a new variable $v_{out_n}$ for the $n$-th output command $out(e)$ inside $s_2$ and replace the $out(e)$ command with an assignment $v_{out_n}:=e$. 
-Notice that the value of $v_{out_n}$ stays the same from the point it has been assigned a value. 
-If the values of $v_{out_n}$ are the same for all permutations of input lists at the end of $s_2$, we know that the reducer is commutative w.r.t. to all output commands inside the loop body $s_2$.
+J-ReCoVer  first generates a new variable $v_{out_k}$ for the $k$-th output command $out(e)$ inside $s_2$ and replace the $out(e)$ command with an assignment $v_{out_k}:=e$. 
+Notice that the value of $v_{out_k}$ stays the same from the point it has been assigned a value. 
+If the values of $v_{out_k}$ are the same for all permutations of input lists at the end of $s_2$, we know that the reducer is commutative w.r.t.
+to all output values produced inside the loop body $s_2$.
 
@@
 The command $s_2$ can be viewed as a function $F$ that reads the values of all variables and the current input before executing $s_2$ and outputs values of all variables after $s_2$.
-Formally, the function $F(n,x_1,x_2,\ldots,x_n): \Z^{n+1} \rightarrow \Z^n$ returns a tuple of values $x_1',x_2',\ldots,x_n'$, where $n$ is the current input value of the reducer, $x_i$ and $x_i'$ are the values of variables before and after the execution of $s_2$, respectively.
+Formally, the function $F(n,x_1,x_2,\ldots,x_k): \Z^{k+1} \rightarrow \Z^k$ returns a tuple of values $x_1',x_2',\ldots,x_k'$, where $k$ is the current input value of the reducer, $x_i$ and $x_i'$ are the values of variables before and after the execution of $s_2$, respectively.
 The construction of $F$ from $s_2$ can be done in the standard way.
@@
 
-We check if the formula is valid for all possible values of $n_1,n_2, x_1,x_2,\ldots,x_n$.
+We check if the formula below is valid for all possible values of $n_1,n_2, x_1,x_2,\ldots,x_k$. 
 \begin{equation}
- F(n_1, F(n_2,x_1,x_2,\ldots,x_n)) = F(n_2, F(n_1,x_1,x_2,\ldots,x_n) )
+ F(n_1, F(n_2,x_1,x_2,\ldots,x_k)) = F(n_2, F(n_1,x_1,x_2,\ldots,x_k) )
 \label{eq:commu}
@@
 So it computes the same value for the input [1;2;3;4;5] and any other input with two consecutive values swaps, e.g., [1;2;\textbf{4};\textbf{3};5].
-Since any permutation of a sequence can be obtained by swapping consecutive values finitely many times~\cite{algebra}, this further implies that starting from the same variable valuation, the loop ends with the same valuation for any permutation of input values.
+Since any permutation of a sequence can be obtained by swapping consecutive values finitely many times~\cite{algebra}, this further implies that starting from the same variable valuation, the loop ends with the same valuation for any permutation of input values, e.g., the reducer will output the same value for [1;2;\textbf{3};\textbf{4};5], [1;\textbf{2};\textbf{4};3;5], [\textbf{1};\textbf{4};2;3;5], [4;1;2;3;5], etc.
 Recall that the first program transformation task remembers all output values in variables that will stay unchanged until the end of the loop.
@@
 
-We explain why that the validity of Equation~(\ref{eq:commu}) is sufficient to prove the commutativity of the reducer.
-Notice that $s_1$ (the commands before entering the loop) does not read from the input (the assumption in this subsection).
+We explain why that the validity of Equation~(\ref{eq:commu}) is sufficient to prove the commutativity of the reducer $s_1;\rloop\{s_2\};s_3$.
+Notice that $s_1$ does not read from the input (assumed at the beginning of this subsection).
 The execution of $s_1$ is deterministic in the sense that from the same initial valuation, it outputs the same sequence of values and ends at the same valuation.
-From the validity of Equation~(\ref{eq:commu}), any permutation of input values leads the reducer to the same final valuation and the same sequence of outputs.
-Before executing $s_3$ (the commands before after the execution of the loop), all inputs have been read (this is the exit condition of the loop) already, similar the the case of $s_1$, it behaves deterministically for all permutations of inputs and outputs the same sequence of values.
+For the execution of $\rloop\{s_2\}$, from the validity of Equation~(\ref{eq:commu}), any permutation of input values leads the reducer to the same final valuation and the same sequence of outputs at the end of the loop.
+Before executing the commands after the loop $s_3$, all inputs have been read (the loop exit condition) already, similar the case of $s_1$, the execution of $s_3$ is deterministic for all permutations of inputs and outputs the same sequence of values.
 
@@
 In the example in Figure~\ref{fig:reducer_max} (a), the reducer program remembers the first input value in the variable $m$, increases its value by 10, and then updates its value to bigger ones if any occurs in the loop.
-The corresponding Equation~(\ref{eq:commu}) is valid in this case, however, the reducer is not commutative.
-For example, the two lists $[1,2,3,4,5]$ and $[5,4,3,2,1]$ are permutations of each other, but the reducer respectively outputs $11$ and $15$ with them as the inputs.
+The corresponding Equation~(\ref{eq:commu}) is valid in this case.
+However, the reducer is not commutative.
+A counterexample can be easily found.
+With the list $[1,2,3,4,5]$ and its permutation $[5,4,3,2,1]$ as the inputs, the reducer respectively outputs $11$ and $15$.
 
@@
 To handle the example in Figure~\ref{fig:reducer_max} (a), we move the prefix $s_1$ into the loop body and use a new variable $s$ to force that $s_1$ is always executed before the original loop body.
-The result after the transformation can be found in Figure~\ref{fig:reducer_max} (b).
+The result after the transformation is demonstrated in Figure~\ref{fig:reducer_max} (b).
 Observe that the new reducer program over-approximates all possible inputs/outputs of the original one.
@@
 So we can apply Equation~(\ref{eq:commu}) to prove its commutativity.
-Since the new reducer has all the possible outputs of the original one, the new reducer is commutative implying that the original one is also commutative.
+Since the new reducer has all the possible outputs of the original one, the new reducer being commutative implies that the original one is also commutative.
 
-\begin{wrapfigure}{r}{0.56\textwidth} 
-		\vspace{-1.2cm}
+\begin{figure}[htb]
+	\centering
+	\begin{minipage}{0.8\textwidth}
 	\begin{algorithm}[H]
@@
 		\Loop{}{
-			\uIf{$s=1$}{ $x_{i_1} := \cur; s'_1; s:=2$}
-			\uElseIf{ $s =2$}{ $x_{i_2} := \cur; s'_2; s:=3$}
-			\uElseIf{ $s = 3$}{$\ldots$}
-			\uElseIf{ $s = m$}{$x_{i_m} := \cur; s'_m; s:=m+1$}
-			\uElse{ $s_2$}
+			\lIf{$s=1$}{ $x_{i_1} := \cur; s'_1; s:=2$}
+			\lElseIf{ $s =2$}{ $x_{i_2} := \cur; s'_2; s:=3$}
+			\lElseIf{ $s = 3$}{$\ldots$}
+			\lElseIf{ $s = m$}{$x_{i_m} := \cur; s'_m; s:=m+1$}
+			\lElse{ $s_2$}
 		};$s_3$\;
 	\end{algorithm}
+	\end{minipage}
 	\caption{The second transformation task}
 	\label{fig:general_program_transformation}
-		\vspace{-1.2cm}
-\end{wrapfigure}
+\end{figure}
 
@@
 $$s'_0;x_{i_1}{:=} \cur;s'_1.\ldots x_{i_{m}}{:=}\cur;s'_m, $$ where $\cur$ never occur in $s'_0,s'_1,\ldots, s'_m$.
-Then we produce the reducer in Figure~\ref{fig:general_program_transformation}, which is an over-approximation of the original reducer satisfying all assumptions required for the Prover.
+Then we produce the reducer in Figure~\ref{fig:general_program_transformation}, which is an over-approximation of the original reducer.
+For the case that $s=1$ at the beginning, its output sequence is the same as the original reducer.
+When $s\neq 1$, it may produce outputs that are not possible by the original reducer.
+Observe that the reducer in Figure~\ref{fig:general_program_transformation} satisfies all assumptions required for the Prover: each branch has at most one $\cur$.
 Hence the Equation~(\ref{eq:commu}) can then be applied to prove its commutativity.
@@
 \label{section:optimizations}
-In this section we explain how data flow analysis are used in our case to improve the precision of commutativity checking and the algorithm we used to construct the $F$ function in Equation~(\ref{eq:commu}).
+In this section we explain how data flow analysis are used in J-Recover to improve the precision of commutativity checking and the algorithm we used to construct the $F$ function in Equation~(\ref{eq:commu}).
 
@@
 Observe that
-$F(c_1, F(c_2,s,t) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t) = (c_1+c_2, c_2)$, which follows that the corresponding equation~\ref{eq:commu} is invalid.
+$F(c_1, F(c_2,s,t) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t) = (c_1+c_2, c_2)$.
+It follows that the corresponding Equation~(\ref{eq:commu}) is invalid.
 The second component of the returned tuple, which corresponds to the value of $t$ after executing the loop body twice, are $c_1$ and $c_2$, respectively.
 However, in this case, the value of $t$ is not important to the output of this reducer.
-The situation happens in all Jimple code produced by Soot.
 
@@
 	\begin{minipage}{0.55\textwidth}
+		\LinesNumbered
 		\centering
@@
 
-To handle such a situation, we perform a simple data flow analysis to collect all variables whose value may propagate to the output command after the loop execution.
-We do it in a backward manner.
+To handle such a situation, we perform a simple backward data flow analysis to collect all variables whose value may propagate to the output command after the loop execution.
 With out loss of generality, we assume there is only one output command after the loop.
 Then the code after the loop (i.e., the $s_3$ part of the reducer) can only be in the form of Figure~\ref{fig:nested_out}.
-The commands $c_1\ldots c_n$ are either assignment commands $w:=e$ or branch command $\ite{g}{c'_1}{c'_2}$, and the only output command stays in the $m$-th layer of the branch command after $c_i$.
+We unfold all concatenation of commands, so now the commands $c_1\ldots c_n$ are either assignment commands $w:=e$ or branch command $\ite{g}{c'_1}{c'_2}$, and the only output command stays in the $m$-th layer of the branch command after $c_i$.
+For the case that $m=0$, the entire branch command in Lines 2-6 of Figure~\ref{fig:nested_out} is replaced with $out(v)$.
 
-The data flow analysis algorithm works as follows.
-A set $V_3$ whose value is initially a singleton set $\{v\}$ is used to remember important variables that might flow to the output command in $s_3$.
+The data flow analysis algorithm works as follows. Recall that $s_3$ can only be in from of Figure~\ref{fig:nested_out}.
+A set $V_3$ whose value is initially a singleton set $\{v\}$ is used to remember important variables that might flow to the output command $out(v)$ in $s_3$.
 The commands and guards will be inspected in the following order $c_{n}$,$\ldots$,$c_{i+1}$, $g_m$, $g_{m-1}$, $\ldots$, $g_1$, $c_i$, $\ldots$, $c_2$, $c_1$.
@@
 Starting from the same set $V_3$,  after processing $c'_1$ and $c'_2$, we get respectively two sets $V_3^1$ and $V_3^2$, we take their union $V_3^1\cup V_3^2$ as the new value of $V_3$.
+After the entire $s_3$ is being processed we get the set of important variables that might affect the outputs.
+We define the set $V_2$ as the set of variables that the first program transformation task used to collect output values in the loop body $s_2$, i.e., $V_2= \{v_{out_k} \mid k \in [1,l]\}$, where $l$ is the number of output commands occurred in $s_2$.
 
 Then we modify the Equation~(\ref{eq:commu}) to the one below
-
 \begin{equation}
-F(n_1, F(n_2,x_1,x_2,\ldots,x_n) )=_{V_2\cup V_3} F(n_2, F(n_1,x_1,x_2,\ldots,x_n) )
+F(n_1, F(n_2,x_1,x_2,\ldots,x_k) )=_{PosF(V_2\cup V_3)} F(n_2, F(n_1,x_1,x_2,\ldots,x_k) )
 \label{eq:commu2}
 \end{equation}
-The special equality operator $=_{V_2\cup V_3}$ is defined (informally) as an equality that only focus on the positions of variables in $V_2\cup V_3$.
-The set $V_2$ is defined as the set of variables we used to collect output values in the loop body $s_2$ of the reducer, i.e., $V_2= \{v_{out_k} \mid k \in [1,l]\}$, , where $l$ is the number of output commands occurred in $s_2$.
-
-The use of equation~(\ref{eq:commu2}) is critical to the successful of our approach.
+The function $PosF(X)$ returns the corresponding positions of variables in $X$ in the output of $F$. E.g., if $X = \{x_1,x_4,y\}$, where $y\notin \{x_1,x_2,\ldots,x_n\}$, then $PosF(X)=\{1,4\}$.
+The use of equation~(\ref{eq:commu2}) is critical to the success of our approach.
 In our evaluation, the ratio of examples that our approach can successfully analyze is significantly increased from $6.8\%$ to $97.5\%$.
@@
 
-\subsection{Computing the $F$ function using symbolic execution with efficiently data structure}
+\subsection{Computing the $F$ function using symbolic execution with efficient data structure}
 \label{section:opt2}
@@
 Here we apply \emph{symbolic execution} to generate $F$.
-Our approach is very simple.
+Below we first review the standard symbolic execution algorithm and then explain how we use it to construct the formula $F$.
+
 First, we define the set $\Var_0=\{v_0 \mid v \in \Var \}\cup \{c_0\}$ as the set of initial symbolic values of all variables, where $c_0$ is used to denote the symbolic value from the input of the reducer.
 A \emph{symbolic state} is a triple $\langle pc, val, cmds \rangle$, where the \emph{path condition} $pc$ is a guard in $\Grd$ over $\Var_0$, the \emph{symbolic valuation} is a mapping from variables in $\Var$ to an expression in $\Exp$ over $\Var_0$, and $cmds\in \Cmd$ is the remaining commands to be executed.
-The \emph{initial symbolic state} is $\langle \true, val_0, s_2\rangle$, where $val_0(v) = v_0$ for all $v\in\Var$.
-One can compute the next symbolic state of $\langle pc, val, c;cmds \rangle$ according to the following transition rules. Recall that $c$ is either in the form of $(v:= e_0)$ or $\ite{g}{c_1}{c_2}$:
+The \emph{initial symbolic state} is $\langle \true, val_0, s_2\rangle$, where $val_0(v) = v_0$ for all $v\in\Var$ and $s_2$ is the loop body of the reducer.
+One can compute the next symbolic state of $\langle pc, val, c;cmds \rangle$ according to the following transition rules.
+Recall that $c$ is either in the form of $(v:= e_0)$ or $\ite{g}{c_1}{c_2}$ after the program transformation tasks are performed:
 \begin{enumerate}
-	\item If $c$ is $(v:= e_0)$, the next symbolic state is $\langle pc, val[v \rightarrow e_0(val) ], cmds \rangle$.
+	\item If $c$ is $(v:= e_0)$, the next symbolic state is $\langle pc, val[v \rightarrow val(e_0) ], cmds \rangle$.
 	\item If $c$ is $\ite{g}{c_1}{c_2}$, the next symbolic states are $\langle pc\wedge g, val, c_1.cmds \rangle$ and $\langle pc\wedge not\  g, val, c_2.cmds \rangle$. 
@@
 
-Here $e_0(val)$ is a formula obtained by substituting every variable $v$ in $e_0$ with $val(v)$ and $val[v \rightarrow e_0(val) ]$ is obtained by reassigning the value of $v$ in $val$ to $e_0(val)$.
-The symbolic execution terminates when its path condition is conflict or the commands become empty.
+Here we lift the $val$ function from variables to expressions in the standard way and $val[v \rightarrow val(e_0) ]$ is obtained by reassigning the value of $v$ in $val$ to $val(e_0)$.
+The symbolic execution terminates when its path condition is conflict or the commands become empty, i.e., all commands have been processed.
 So far it is standard.
 
-For the loop body $s_2$, symbolic execution is guaranteed to terminate.
-When the execution terminates, we collect all states with empty commands $\langle pc, val, \emptyset \rangle$ as a set $T$ and use them to create the function $F$ in formula~(\ref{eq:commu2}). 
-First, we create for each variable $v\in\Var$ a formula $f_v$ whose initial value is $\false$.
-For each symbolic state $\langle pc, val, \emptyset \rangle \in Ts$, we reassign $f_v$ to $f_v \vee (pc \wedge val(v))$.
-Assuming that the set $P_2\cup P_3$ in equation~(\ref{eq:commu2}) equals $\{v_1,v_2,\ldots,v_n\}$, the function $F$ simply returns tuple $\{f_{v_1},f_{v_2},\ldots, f_{v_n}\}$.
+For the loop body $s_2$, symbolic execution is guaranteed to terminate because there is no commands in $s_2$ that may lead to infinite computations.
+When the execution terminates, we collect all states with empty commands $\langle pc, val, \emptyset \rangle$ as a set $T$ and use them to create the function $F$ in Equation~(\ref{eq:commu2}). 
+First, we create for each variable $x\in\Var$ a formula $f_x$ whose value is $\bigvee_{\langle pc, val, \emptyset \rangle \in T} (pc \wedge val(x))$.
+The function $F(n,x_1,x_2,\ldots,x_k)$ simply returns the tuple $\{f_{x_1},f_{x_2},\ldots, f_{x_k}\}$.
 
@@
 After the two executions of $u:=u+u$, the value of $u$ changes to $x_0+y_0+x_0+y_0$ and $x_0+y_0+x_0+y_0+x_0+y_0+x_0+y_0$, respectively.
-One way to alleviate the problem is to apply some formula simplification algorithm, e.g., those build-in Z3~\cite{z3}.
-However, this will require some additional cost in the invocation of Z3. Here we propose in a very simple alternative solution that works quite well in our reducer benchmarks.
+One way to alleviate the problem is to apply formula simplification algorithms, e.g., those implemented in Z3~\cite{z3}.
+Here we propose in a very simple alternative solution that works quite well in our reducer benchmarks.
 
@@
 \end{itemize}
-
+To make the definition complete for our simple reducer program commands, we further define (1) $sv_{\cur}(c_0) =1$ and $sv_{\cur}(e)=0$ for $e\neq \cur$, (2) $sv_{n}(1) =n$ and $sv_{n}(e)=0$ for $e\neq 1 \wedge n\in \Z$.
 This data structure is efficient for strong symbolic values of reducer programs mainly for reason that the operations $+$ and $-$ are quite heavily used in such programs.
@@
 \label{section:exp}
-J-ReCoVer is implemented in JAVA and build on top of Soot~\cite{soot} 2.5.0 and Z3~\cite{z3} 4.7.1.
+J-ReCoVer is implemented in Java and built on top of Soot~\cite{soot} 2.5.0 and Z3~\cite{z3} 4.7.1.
 We run J-Recover on a virtual machine running on a server with AMD Opteron 6376 CPU.
@@
 In total we get $11346$ Java programs.
-We then filter out cases that are not Hadoop MapReduce reducer programs (those do not import the Hadoop library, do not extend or implement the reducer interface) and obtain $1273$ examples.
+We exclude cases that are not Hadoop MapReduce reducer programs (those do not import the Hadoop library, do not extend or implement the reducer interface) and obtain $1273$ examples.
 We further remove those that cannot be compiled, those that are identical to each other, or those uses non-numerical data types (e.g, string) and obtained $118$ programs as the final benchmark.
-The second set of examples are those have been discussed in verification literatures~\cite{ChenHSW15,ChenSW16,SmithA16}. This set is relatively small, we have only $10$ examples. 
+The second set of examples are those have been discussed in verification literature~\cite{ChenHSW15,ChenSW16,SmithA16}. This set is relatively small, we have only $10$ examples. 
 For the third set of benchmarks, we created a program that randomly generate reducer program in order to test the scalability of J-Recover, which we can give as parameter a tuple $(N,B,A)$, where $N$ is the number of variables, $B$ is the number of branch statements, and $A$ is the number of assignment statement.
@@
 \subsection{Comparison with competing tools}
-As already pointed out in~\cite{ChenHSW15}, reducer commutativity problems can be reduced to a reachability problem of programs. 
+As already pointed out in~\cite{ChenHSW15}, a reducer commutativity problem can be reduced to a reachability problem of a program. 
 The examples in~\cite{ChenHSW15}, which includes \textsf{rangesum}\footnote{The sum of the second half of the input list.}, \textsf{avg}, \textsf{max}, \textsf{sep}\footnote{The number of occurrences of even numbers minus that of odd numbers.}, \textsf{sum}, are already included in SV-Comp~\cite{svcomp} (Software Verification Competition) benchmarks.
@@
 
-For the optimization based on data flow analysis (Section~\ref{section:opt1}), we evaluation them based on real-world benchmark sets collected from open repositories (118 examples) and also literatures (10 examples).
+%The situation happens in all Jimple code produced by Soot.
+
+For the optimization based on data flow analysis (Section~\ref{section:opt1}), we evaluation them based on real-world benchmark sets collected from open repositories (118 examples) and also literature (10 examples).
 The difference between the version with and without this optimization is very clear.
@@
 The precision of the analysis is improved from $14.4\%$ to $97.5\%$ for examples from open repositories and
-$10\%$ to $100\%$ for examples from literatures.
+$10\%$ to $100\%$ for examples from literature.
 There are only three cases that J-Recover with data flow analysis cannot handle.
-The reason that J-Recover fails is that the three reducer uses more complicated structure than what J-Recover currently supports, i.e., in the form of $s_1;\rloop\{s_2\};s_3$.
+The reason that J-Recover fails is that the three reducers use more complicated structure than what J-Recover currently supports, i.e., in the form of $s_1;\rloop\{s_2\};s_3$.
 The three reducer programs uses a branch statement before entering the loop, i.e., in the form $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$.
-In theory, such program can be handled by more sophisticated program transformation operations, For example, we can merge the two loops and push the outer branch condition inside the merged loop.
-However, this new program transformation operation is not implemented in J-Recover yet.
+In theory, such program can be handled by more sophisticated program transformation operations.
+For example, we can merge the two loops and push the outer branch condition inside the merged loop.
+However, this new program transformation task is not implemented in J-Recover yet.
 

### 2018-11-14 draft.tex
polish

@@
 
-\title{J-ReCoVer: Java Reducer Commutativity Verifier}
+\title{\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier}
 
@@
 In this paper, we propose heuristics for the commutativity problem that works very efficiently on a large set of practical integer reducer programs.
-We reduce the commutativity problem to a SMT problem in a sounds but incomplete manner; it  reports commutative only when it holds for all possible initial valuations, even if some of them are in fact unreachable.
+We reduce the commutativity problem to a SMT problem in a sound but incomplete manner.
 We also propose optimizations to enable the approach working on real world examples.
@@
 If $R'$ and $R$ are equivalent, using the fact that all permutations of a list can be obtained by swapping consecutive list elements finitely many times\footnote{Here is an example to produce [3;2;5;1;4] from [1;2;3;4;5] by swapping consecutive elements: [\textbf{1};\textbf{2};3;4;5] $\rightarrow$ [2;\textbf{1};\textbf{3};4;5] $\rightarrow$ [2;3;1;\textbf{4};\textbf{5}]$\rightarrow$ [2;3;\textbf{1};\textbf{5};4]$\rightarrow$ [\textbf{2};\textbf{3};5;1;4]$\rightarrow$ [3;2;5;1;4].}, $R$ can be proved to be commutative.
-There are a series of research results on program equivalence checking (or closely related topics such as regression verification)~\cite{symdiff,fedyukovich2015automated,sharma2013data,godlin2009regression,fedyukovich2016property,felsing2014automating,KieferKlebanovUlbrich2017,lahiri2013differential,grossman2017verifying,barthe2011relational,KlebanovRuemmerUlbrich2017}.
+There is a series of research results on program equivalence checking (or closely related topics such as regression verification and translation validation)~\cite{Pnueli:1998:TV,symdiff,fedyukovich2015automated,sharma2013data,godlin2009regression,fedyukovich2016property,felsing2014automating,KieferKlebanovUlbrich2017,lahiri2013differential,grossman2017verifying,barthe2011relational,KlebanovRuemmerUlbrich2017}.
 At a high level, checking equivalence of two programs $P$ and $P'$ can be reduced to a sequential verification problem by executing $P'$ after $P$ and at the end checking if they always have the same outputs.
 It can be made more efficient by finding the right~\emph{synchronization points} and combining the code of $P$ and $P'$ in an interleaved manner.
-A lot of the research effort in this research direction is in finding good synchronization points.
-For the case of commutativity analysis, good synchronization points are already given; one can simply use the beginning of the loop as the synchronization point.
+A lot of research effort in this direction is in finding good synchronization points.
+For the case of commutativity analysis, one can simply use the beginning of the loop as the synchronization point.
 However, in our experience, if we naively reduce the commutativity problem to equivalence problem and check it in a precise manner, many examples cannot be solved.
@@
 
-One main motivation of commutativity analysis is to reduce verification problem of a concurrent program to a sequential one.
+One main motivation of commutativity analysis is to reduce the verification problem of a concurrent program to a sequential one.
 There are several researches sharing the similar motivation.
@@
 \label{section:integer-reducers}
-We use $\Z$ to denote the set of integers and $[n,m]$ to denote the set of integers $\{k\mid n \leq k\leq m\}$. 
+We use $\Z$ to denote the set of all integers and $[n,m]$ to denote the set of integers $\{k\mid n \leq k\leq m\}$. 
 We lift the equality $=$ operation to tuples in the standard way.
@@
 A \emph{command} in $\Cmd$ can be an assignment, a branch statement, concatenation of a sequence of commands, or $out(v)$ that outputs the value of $v$.
-A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$, and $s_2$ is assumed to have at most one $\cur$ expression in each branch\footnote{We define a \emph{branch} of a command $s$ as a sequence obtained by replacing every branch statement $\ite{g}{s_1}{s_2}$ in $s$ with either $(g)\wedge s_1$ or $(not\ g) \wedge s_2$.} .
+A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$, and $s_2$ is assumed to have at most one $\cur$ expression in each branch\footnote{We define a \emph{branch} of a command $s$ as a sequence obtained by replacing every branch statement $\ite{g}{s_1}{s_2}$ in $s$ with either $(g)\wedge s_1$ or $(not\ g) \wedge s_2$.}.
 According to our observation over hundreds  of reducer programs in open repositories, reducer programs are almost always in this form.
@@
 One reducer computes the average (Figure~\ref{fig:reducer_example}(b)) and the other reducer uses a non-deterministic value to over-approximate the computed average ($a := *$) and then use it in the computation of standard deviation (Figure~\ref{fig:reducer_example}(c)).
-The reducer in Figure~\ref{fig:reducer_example}(c) ``over-approximates''  all possible output of the standard deviation computation; it computes an output even if $a$ is not the average of inputs.
+The reducer in Figure~\ref{fig:reducer_example}(c) ``over-approximates''  all possible outputs of the standard deviation computation; it computes an output even if $a$ is not the average of inputs.
 However, the reducer is still commutative and its commutativity verification can still be done.
@@
 
-\textbf{The Preprocessor component} first compiles a reducer program to bytecode and use the tool Soot~\cite{soot} to further convert it to the so called ``Jimple'' format, which is an intermediate language that is designed to simplift the analysis of Java programs.
+\textbf{The Preprocessor component} first compiles a reducer program to bytecode and use the tool Soot~\cite{soot} to further convert it to the so called ``Jimple'' format, which is an intermediate language that is designed to simplify the analysis of Java programs.
 Under the Hadoop MapReduce framework, the permutation of the input is handled by the scheduler/shuffler component and is affected by things like network latency, which is not controllable by programmers.
@@
 So that the input order of the reducer is now controlled by J-ReCoVer.
-Finally, we perform in the Preprocessor some simple program transformations tasks to simplify the analysis.
+Finally, we perform in the Preprocessor some program transformations tasks to simplify the analysis.
 For example, we convert all output commands $out(e)$ inside loops to an special assignment (Section~\ref{sec:program_trans1} and~\ref{sec:program_trans2}).
@@
 \textbf{The Prover component} reduces the commutativity problem to a SMT formula satisfiability problem.
-At a high level, we check equivalence between a reducer program and its variant that have two consecutive inputs swapped.
-We show that this can be reduced to a SMT problem and give it to SMT solver Z3~\cite{z3} for solving.
-Recall that all permutations of a list can be obtained by swapping consecutive elements finitely many times.
+At a high level, we check equivalence between a reducer program and its variant that has two consecutive inputs swapped.
+We show that this can be reduced to a SMT problem and give it to the SMT solver Z3~\cite{z3} for solving.
 In case that Z3 proved the formula unsatisfiable, we know that swapping any two consecutive inputs of the reducer will not change its output.
-It follows that the reducer outputs the same value for all permutations of the same list of input.
+Because all permutations of a list can be obtained by swapping consecutive elements finitely many times, it follows that the reducer outputs the same value for all permutations of the same list of inputs.
 In this case,  J-ReCoVer stops and reports that the reducer is commutative. 
-
 If we run the approach in a naive manner, it does not scale to large programs and is very imprecise.
-We will introduce two critical optimizations that enables the proposed approach working for real-world examples in Section~\ref{section:optimizations}: a data flow analysis to extract critical variables and an improved symbolic execution algorithm to generate Z3 formulae.
+We will introduce two critical optimizations that enables the proposed approach working for real-world examples in Section~\ref{section:optimizations}: a data flow analysis to extract critical variables and an improved symbolic execution algorithm to generate SMT formulae.
 More details of the algorithms used in the Preprocessor and the Prover components will be explained in Section~\ref{sec:preprocessor_prover} and the optimizations will be introduced in~\ref{section:optimizations}.
@@
 We assume the reducer $s_1;\rloop\{s_2\};s_3$ is given.
-We begin the section with our first program transformation task (Section~\ref{sec:program_trans1}) that handles the case when $s_2$ contains $out$ commands.
+The section begins with an introduction to the first program transformation task (Section~\ref{sec:program_trans1}) that handles the case when $s_2$ contains $out$ commands.
 The output of the first transformation task is a commutativity-equivalent reducer program where $out$ does not occur in $s_2$.
-Then we explain the algorithm of the Prover (Section~\ref{sec:prover}) that works only in a special case where no read from input occurs in $s_1$.
-For general reducer programs, we introduce the second program transformation task (Section~\ref{sec:program_trans2}) whose output is a reducer program that contains all input/output behaviors of the original reducer (may contain behaviors that are not in the original reducer) and there is no read from input (i,e., does not have the $\cur$ expression) in $s_1$, which can be analyzed by the algorithm of Prover.
+Then the algorithm of the Prover is introduced in Section~\ref{sec:prover}.
+This algorithm works only in a special case where no read from input occurs in $s_1$.
+For general reducer programs, we introduce the second program transformation task (Section~\ref{sec:program_trans2}) whose output is a reducer program that falls in the special case required by the Prover and ``over-approximates'' all input/output behaviors of the original reducer.
+The commutative of the produced reducer implies the commutative of the original one, but not vice verse.
 
@@
 The command $s_2$ can be viewed as a function $F$ that reads the values of all variables and the current input before executing $s_2$ and outputs values of all variables after $s_2$.
-Formally, the function $F(n,x_1,x_2,\ldots,x_k): \Z^{k+1} \rightarrow \Z^k$ returns a tuple of values $x_1',x_2',\ldots,x_k'$, where $k$ is the current input value of the reducer, $x_i$ and $x_i'$ are the values of variables before and after the execution of $s_2$, respectively.
+Formally, the function $F(n,x_1,x_2,\ldots,x_k): \Z^{k+1} \rightarrow \Z^k$ returns a tuple of values $x_1',x_2',\ldots,x_k'$, where $n$ is the current input value of the reducer, $x_i$ and $x_i'$ are the values of variables before and after the execution of $s_2$, respectively.
 The construction of $F$ from $s_2$ can be done in the standard way.
 We will introduce a more efficient data structure for the construction in Section~\ref{section:optimizations}.
-
 We check if the formula below is valid for all possible values of $n_1,n_2, x_1,x_2,\ldots,x_k$. 
@@
 The validity of Equation~(\ref{eq:commu}) implies that swapping any two consecutive input values does not change the final variable valuation.
-Informally, it says that starting from the same initial valuations of variables and with two different input orders, the values of all program variables are the same after we execute the loop body twice.
+Informally, it says that starting from the same initial valuations of variables and with two different input orders, $[n_1;n_2]$ and $[n_2;n_1]$, the values of all program variables are the same after we execute the loop body twice.
 The first execution reads $n_1$ and then reads $n_2$.
@@
 For the execution of $\rloop\{s_2\}$, from the validity of Equation~(\ref{eq:commu}), any permutation of input values leads the reducer to the same final valuation and the same sequence of outputs at the end of the loop.
-Before executing the commands after the loop $s_3$, all inputs have been read (the loop exit condition) already, similar the case of $s_1$, the execution of $s_3$ is deterministic for all permutations of inputs and outputs the same sequence of values.
+Before executing the commands $s_3$, all inputs have been read (the loop exit condition) already.
+Similar the case of $s_1$, $s_3$ does not read from the input and hence the execution of $s_3$ is deterministic.
+It follows that for all permutations of inputs, the reducer outputs the same sequence of values.
 
@@
 The result after the transformation is demonstrated in Figure~\ref{fig:reducer_max} (b).
-Observe that the new reducer program over-approximates all possible inputs/outputs of the original one.
-It also satisfies all assumptions required for the Prover component: (a) The commands before entering the loop does not have any $\cur$ expression and (II) each branch (recall that ``branch'' is formally defined in Section~\ref{section:integer-reducers}) of the loop body has at most one $\cur$.
+The new reducer program over-approximates all possible inputs/outputs of the original one.
+For the case that $s=1$ at the beginning, its output sequence is the same as the original reducer.
+When $s\neq 1$, it may produce outputs that are not possible by the original reducer.
+It also satisfies all assumptions required for the Prover component: 
+(I) the commands before entering the loop does not have any $\cur$ expression, 
+(II) each branch (recall that ``branch'' is formally defined in Section~\ref{section:integer-reducers}) of the loop body has at most one $\cur$, and 
+(III) $out(v)$ command does not occur inside the loop body\footnote{We need to apply the first program transformation again to fulfill this assumption.}.
 So we can apply Equation~(\ref{eq:commu}) to prove its commutativity.
@@
 	\begin{minipage}{0.8\textwidth}
+
 	\begin{algorithm}[H]
@@
 $$s'_0;x_{i_1}{:=} \cur;s'_1.\ldots x_{i_{m}}{:=}\cur;s'_m, $$ where $\cur$ never occur in $s'_0,s'_1,\ldots, s'_m$.
-Then we produce the reducer in Figure~\ref{fig:general_program_transformation}, which is an over-approximation of the original reducer.
-For the case that $s=1$ at the beginning, its output sequence is the same as the original reducer.
-When $s\neq 1$, it may produce outputs that are not possible by the original reducer.
-Observe that the reducer in Figure~\ref{fig:general_program_transformation} satisfies all assumptions required for the Prover: each branch has at most one $\cur$.
+Then we produce the reducer in Figure~\ref{fig:general_program_transformation}, which is an over-approximation of the original reducer for the same reason: the case that $s=1$ has the same output sequence to the original reducer and when $s\neq 1$, it may produce additional behavior.
+Observe that the reducer in Figure~\ref{fig:general_program_transformation} satisfies all assumptions required for the Prover.
 Hence the Equation~(\ref{eq:commu}) can then be applied to prove its commutativity.
@@
 \label{section:optimizations}
-In this section we explain how data flow analysis are used in J-Recover to improve the precision of commutativity checking and the algorithm we used to construct the $F$ function in Equation~(\ref{eq:commu}).
+In this section we explain how data flow analysis is used in J-Recover to improve the precision of commutativity checking and the algorithm we used to construct the $F$ function in Equation~(\ref{eq:commu}).
 
@@
 We find that in many cases, Equation~(\ref{eq:commu}) is a condition that is too strong for the reducer to be commutative.
-For instance, consider the example in Figure~\ref{fig:reducer_opt}, in the loop body, the input is first stored in a variable $t$ and then added to $s$.
+For instance, consider the example in Figure~\ref{fig:reducer_opt}.
+In the loop body, the input is first stored in a variable $t$ and then added to $s$.
 In this case, the $F$ function returns the updated values of both $s$ and $t$ after the execution of loop body.
 Observe that
-$F(c_1, F(c_2,s,t) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t) = (c_1+c_2, c_2)$.
+$F(c_1, F(c_2,s,t)) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t)) = (c_1+c_2, c_2)$.
 It follows that the corresponding Equation~(\ref{eq:commu}) is invalid.
-The second component of the returned tuple, which corresponds to the value of $t$ after executing the loop body twice, are $c_1$ and $c_2$, respectively.
-However, in this case, the value of $t$ is not important to the output of this reducer.
+The second component of the returned tuples corresponds to the value of $t$ after executing the loop body twice.
+Their values are $c_1$ and $c_2$, respectively, in $F(c_1, F(c_2,s,t))$ and $F(c_2, F(c_1,s,t))$.
+However, in this case, the value of $t$ will not affect the output of this reducer.
 
@@
 
-To handle such a situation, we perform a simple backward data flow analysis to collect all variables whose value may propagate to the output command after the loop execution.
+To handle such a situation, we need an algorithm to collect a set of variables whose value may affect the output. 
+Recall that the first program transformation task uses a set of variables $V_2=\{v_{out_k} \mid k \in [1,l]\}$, where $l$ is the number of output commands occurred in $s_2$, to collect output values occurred in the loop body $s_2$.
+The set $V_2$ is exactly the set of variables that will affect the output inside the loop.
+
+We perform a simple backward data flow analysis to collect all variables whose value may propagate to the output command after the loop execution.
 With out loss of generality, we assume there is only one output command after the loop.
@@
 
-The data flow analysis algorithm works as follows. Recall that $s_3$ can only be in from of Figure~\ref{fig:nested_out}.
-A set $V_3$ whose value is initially a singleton set $\{v\}$ is used to remember important variables that might flow to the output command $out(v)$ in $s_3$.
+The data flow analysis algorithm works as follows.
+A set $V_3$ whose value is initially a singleton set $\{v\}$ is used to remember important variables that might flow to the output command $out(v)$ in $s_3$ (Figure~\ref{fig:nested_out}).
 The commands and guards will be inspected in the following order $c_{n}$,$\ldots$,$c_{i+1}$, $g_m$, $g_{m-1}$, $\ldots$, $g_1$, $c_i$, $\ldots$, $c_2$, $c_1$.
@@
 For the case that $c_j$ is a branch command $\ite{g}{c'_1}{c'_2}$, we process both $c'_1$ and $c'_2$ in a similar manner.
-Starting from the same set $V_3$,  after processing $c'_1$ and $c'_2$, we get respectively two sets $V_3^1$ and $V_3^2$, we take their union $V_3^1\cup V_3^2$ as the new value of $V_3$.
+Starting from the same set $V_3$,  after processing $c'_1$ and $c'_2$, we get two sets $V_3^1$ and $V_3^2$.
+We take their union $V_3^1\cup V_3^2$ as the new value of $V_3$.
 After the entire $s_3$ is being processed we get the set of important variables that might affect the outputs.
-We define the set $V_2$ as the set of variables that the first program transformation task used to collect output values in the loop body $s_2$, i.e., $V_2= \{v_{out_k} \mid k \in [1,l]\}$, where $l$ is the number of output commands occurred in $s_2$.
 
@@
 \end{equation}
-The function $PosF(X)$ returns the corresponding positions of variables in $X$ in the output of $F$. E.g., if $X = \{x_1,x_4,y\}$, where $y\notin \{x_1,x_2,\ldots,x_n\}$, then $PosF(X)=\{1,4\}$.
+The function $PosF(X)$ returns the corresponding positions of variables in $X$ in the output of $F(n,x_1,\ldots,x_k) $.
+E.g., if $X = \{x_1,x_4,y\}$, where $y\notin \{x_1,\ldots,x_k\}$, then $PosF(X)=\{1,4\}$.
 The use of equation~(\ref{eq:commu2}) is critical to the success of our approach.
@@
 
-First, we define the set $\Var_0=\{v_0 \mid v \in \Var \}\cup \{c_0\}$ as the set of initial symbolic values of all variables, where $c_0$ is used to denote the symbolic value from the input of the reducer.
+First, we define the set $\Var_0=\{v_0 \mid v \in \Var \}\cup \{c_0\}$ as the set of initial symbolic values of all variables, where $c_0$ is used to denote the symbolic value from the input.
 A \emph{symbolic state} is a triple $\langle pc, val, cmds \rangle$, where the \emph{path condition} $pc$ is a guard in $\Grd$ over $\Var_0$, the \emph{symbolic valuation} is a mapping from variables in $\Var$ to an expression in $\Exp$ over $\Var_0$, and $cmds\in \Cmd$ is the remaining commands to be executed.
@@
 Here we lift the $val$ function from variables to expressions in the standard way and $val[v \rightarrow val(e_0) ]$ is obtained by reassigning the value of $v$ in $val$ to $val(e_0)$.
-The symbolic execution terminates when its path condition is conflict or the commands become empty, i.e., all commands have been processed.
+The execution from a symbolic state terminates when its path condition is conflict or the commands to be executed become empty, i.e., all commands have been processed.
 So far it is standard.
@@
 the input commands.
-For example, consider a simple command $u:=x+y;u:=u+u;u:=u+u$, each execution of $u:= u+ u$ will double the length of the expression storing the symbolic value of $u$.
+For example, consider a simple command $u:=x+y;u:=u+u;u:=u+u$, each execution of $u:= u+ u$ will double the length of the expression representing the symbolic value of $u$.
 More concretely, after the execution of $u:=x+y$, the symbolic value of $u$ is $x_0+y_0$.
@@
 We use a more efficient data structure to store symbolic values.
-At a high level, in a symbolic state, we count the number of occurrences of each variables in $\Var_0$ and just update the count for operations such as $+$ and $-$.
-For other operations (e.g., $*$), we create the symbolic formula in the original way.
+At a high level, in a symbolic state, we count the number of occurrences of each symbolic values in $\Var_0$ and update the count when operations such as $+$ and $-$ is applied.
+For other operations $x\odot y$, we create a new symbolic expression $val(x) \odot val(y)$ and count its number of occurrence as one.
 More concretely, we use a map $sv_x:\Exp\rightarrow \mathbb{N}$ (symbolic value of $x$) to remember the number of occurrences of each expression in $x$.
+We have $val(x)= (\Sigma_{z\in \dom{sv_x}} (z\times sv_x(z)) )$, where $\dom{sv}=\{e\mid sv(e)\neq 0\}$.
 Initially, $sv_x(x_0) = 1$ and $sv_x (e) =0$ for all $e\neq x$.
@@
 	\item For the case that $\circ \in\{+,-\}$, we have $sv'_x(z) = sv_x(z)\circ  sv_y(z)$.
-	\item For the case that $\circ \notin\{+,-\}$, we compute an expression $e_1= (\Sigma_{z\in \dom{sv_x}} (z\times sv_x(z)) )\circ (\Sigma_{z\in \dom{sv_y}} (z\times sv_x(z)))$, where $\dom{sv}=\{e\mid sv(e)\neq 0\}$.
-Then we define $sv'_x(e_1) =1$ and $sv'_x(e_2) = 0$ for all $e_2\neq e_1$.
+	\item For the case that $\circ \notin\{+,-\}$, we define $sv'_x(val(x)) =1$ and $sv'_x(e) = 0$ for all $e\neq val(x)$.
 \end{itemize}
@@
 
-In order to properly evaluate the performance of J-ReCoVer, we collect benchmark example from three different sources. 
-First, we use the search engine \url{http://searchcode.com}~\cite{searchcode} to collect java programs contains the key strings ``public void reduce('' or ``protected void reduce(''.
-Since there is an upper bound in number of returned results in the search engine, we add different search filters in order to get more data.
-We tried all $12$ combinations of $6$ code length filters $\{<50$, $ 50\sim 250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim 1250\}$
+In order to properly evaluate the performance of J-ReCoVer, we collect benchmark example from two different sources. 
+First, we use the search engine \url{http://searchcode.com}~\cite{searchcode} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''.
+Since there is an upper bound on number of results returned from the search engine, we add different search filters in order to get more data.
+We tried all $12$ combinations of six filters on code length $\{<50$, $ 50\sim 250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim 1250\}$
 and two filters for data sources $\{\url{github.com}, \url{bitbuckect.com}\}$.
@@
 We further remove those that cannot be compiled, those that are identical to each other, or those uses non-numerical data types (e.g, string) and obtained $118$ programs as the final benchmark.
-The second set of examples are those have been discussed in verification literature~\cite{ChenHSW15,ChenSW16,SmithA16}. This set is relatively small, we have only $10$ examples. 
-For the third set of benchmarks, we created a program that randomly generate reducer program in order to test the scalability of J-Recover, which we can give as parameter a tuple $(N,B,A)$, where $N$ is the number of variables, $B$ is the number of branch statements, and $A$ is the number of assignment statement.
-All assignments are in the form of $v_1 := v_2\circ v_3,\circ\in\{+,-,\times\}$ and all guards are in the form of $v_1 \circ v_2, \circ\in\{\geq, >,=, \neq, <,\leq \}$.
- The source code of the random generator is available at \url{https://github.com/spencerwuwu/benchmark-generator}.
+The second set of examples are those have been discussed in verification literature~\cite{ChenHSW15,ChenSW16}. This set is relatively small, we have only $10$ examples. 
+We also created a program that randomly generate reducer program in order to test the scalability of J-Recover.
 All benchmark examples can be found on the web-site of J-Recover.
@@
 The examples in~\cite{ChenHSW15}, which includes \textsf{rangesum}\footnote{The sum of the second half of the input list.}, \textsf{avg}, \textsf{max}, \textsf{sep}\footnote{The number of occurrences of even numbers minus that of odd numbers.}, \textsf{sum}, are already included in SV-Comp~\cite{svcomp} (Software Verification Competition) benchmarks.
-Although those examples are tiny and simple, none of the software verifiers are able to verify all of them according to the 2018 results. In contrast, J-Recover can verify all them very efficiently.
+Although those examples are tiny and simple, none of the software verifiers can verify all of those examples according to the 2018 results. In contrast, J-Recover can verify all them very efficiently.
 
 In Table~\ref{tab:svcomp}, the statistics of tools other than J-Recover are taken directly from the SV-Comp~\cite{svcomp} web-site.
-Although the machine we used are different, but the results of J-Recover will not be much different if we run it on other machines.
-The other limitation is that in J-Recover, we analysis Java implementation and in SV-Comp they analyze the C implementations.
+Although the machine we used are different, the results of J-Recover will not be much different if we run it on other machines.
+The other limitation is that in J-Recover, we analyze Java implementations and in SV-Comp they analyze the C implementations of the same functions.
 Since those functions to be analyzed are relatively simple, the syntactical difference between C and Java implementation is very small.
@@
 
-%The situation happens in all Jimple code produced by Soot.
-
 For the optimization based on data flow analysis (Section~\ref{section:opt1}), we evaluation them based on real-world benchmark sets collected from open repositories (118 examples) and also literature (10 examples).
@@
 The first column is the result without optimization, i.e., using Equation~(\ref{eq:commu}) and the second column is the result with optimization, i.e., using Equation~(\ref{eq:commu2}).
-The precision of the analysis is improved from $14.4\%$ to $97.5\%$ for examples from open repositories and
+The precision of the analysis is improved from $6.8\%$ to $97.5\%$ for examples from open repositories and
 $10\%$ to $100\%$ for examples from literature.
 There are only three cases that J-Recover with data flow analysis cannot handle.
-The reason that J-Recover fails is that the three reducers use more complicated structure than what J-Recover currently supports, i.e., in the form of $s_1;\rloop\{s_2\};s_3$.
-The three reducer programs uses a branch statement before entering the loop, i.e., in the form $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$.
+The reason that J-Recover fails is that the three reducers use more complicated structure than what J-Recover currently supports; they use a branch statement before entering the loop, i.e., in the form $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$.
 In theory, such program can be handled by more sophisticated program transformation operations.
@@
 
+If we look into scrutiny, we failed to verify any example using Equation~(\ref{eq:commu}).
+The reason is that when Soot convert a Java program to the Jimple format, it always uses a temporary variable to store the value of $\cur$ in the loop body (similar to the example in Figure~\ref{fig:reducer_opt}).
+We tried a simpler heuristics approach that only ignores the temporary variables and the results is not as good as using data flow analysis, because the value of the temporary variable often also propagates to other variables.
 \begin{table}[htb]
@@
 
-For the optimization based on improving the data structure used in symbolic execution (Section~\ref{section:opt2}), the main focus in on the improvement in scalability.
-In fact, even for the version without optimizations, J-Recover can handle most of the real-world benchmarks efficiently.
-So we use randomly generated examples as the target in this evaluation.
-Recall that our random reducer program generator uses three parameters $(N,B,A)$, where $N$ is the number of variables, $B$ is the number of branch statements, and $A$ is the number of assignment statements.
+For the optimization based on improving the data structure used in symbolic execution (Section~\ref{section:opt2}), the main focus is on the improvement in scalability.
+So we use a random reducer program generator to produce examples of different sizes for this evaluation.
+For the generator, we can give as parameter a tuple $(N,B,A)$, where $N$ is the number of variables, $B$ is the number of branch statements, and $A$ is the number of assignment statement.
+All assignments are in the form of $v_1 := v_2\odot v_3,\odot\in\{+,-,\times\}$ and all guards are in the form of $v_1 \circ v_2, \circ\in\{\geq, >,=, \neq, <,\leq \}$.
+The source code of the random generator is available at \url{https://github.com/spencerwuwu/benchmark-generator}.
 In the evaluation, we keep the ratio $N:B:A = 5:1:50$ and uses lines numbers from $50$ to $250$.
-The most difficult cases might have $5$ to $6$ nested branches and $25$ integer variables in reducer program.
-Those program will be processed by Soot and translated to the so called Jimple format.
+The most difficult cases might have $5$ to $6$ nested branches and $25$ integer variables in a reducer program.
+Those programs will be processed by Soot and translated to the Jimple format.
 In our experience, this will increase the number of lines by $20\%$ and variables by $11$ times.
@@
 \section{Concluding Remarks}
-We believe that simpler but more restricted language/framework will be the trend for parallel program development.
-It lowers the barrier for writing parallel program.
-So experts in other domains such as data science and machine learning can use the power of parallel data processing with much less efforts.
-Many of their applications do not need the full power of message passing programming so they do not need to those build their programs on top of traditional means such as MPI or socket programming.
-MapReduce framework is a pioneer in this kind of frameworks for data parallel computation.
+We believe that simpler but more restricted domain specific language/frameworks will be the trend for the development of parallel programs.
+It lowers the barrier for writing correct yet efficient parallel program.
+Complicated issues such as fault torrence, load balancing, and security are handled by the frameworks automatically.
+Programmers only need to focus on their program logic.
+So experts in other domains such as data science and machine learning can enjoy the power of parallel data processing with much less efforts.
+Many of their applications do not need the full power of message passing programming.
+So they do not need to build their programs on top of traditional means such as MPI or socket programming.
+MapReduce framework is a pioneer in this kind of domain specific language/frameworks for data parallel computation.
 Its successors such as Spark, Flink, Beam, and Google Cloud Dataflow, still share many features of its design.
@@
 We do not handle more advanced data-types such as string and floating point.
-The problem of variable overflow is not handled by this tool.
+The problem of variable overflow is also not handled by this tool.
 In fact, if we consider all possible inputs of a reducer, almost all reducer programs will run into the problem of overflow.
-Even the basic example that computes the sum of all input values, overflow can occur when a list contains two maximal 64-bit integer values is used as the input.
+Even the basic example that computes the sum of all input values, overflow can occur when a list [\textsf{MaxInt};\textsf{MaxInt}] is used as the input.
 Nevertheless, such example might not be of the interests of MapReduce programmers, who usually care only about the data set they want to analyze.
-We are planing to build another tool that estimates a safe bound of data size such that overflow will not occur if data size is within bound.
-The programmer can then check if their data set fits in the computed bound and switch to use lager data type in the program when needed.
+We are planing to build another tool to estimate a safe bound of data size such that overflow will not occur if data size is within bound.
+The programmer can then check if their data set fits in the computed bound and switch to use larger data type in the program when needed.
 So overflow will not occurs in the data set of interests.
 
-%\bibliographystyle{splncs-sorted}
+\bibliographystyle{splncs-sorted}
 \bibliography{refs}

### 2018-11-14 draft.tex
polish

@@
 MapReduce framework for data-parallel computation was first proposed by Google~\cite{dean04} and later implemented in the Apache Hadoop project~\cite{hadoop}.
-Under the MapReduce framework, the reducer computes output values from a sequence of input values transmitted over the network.
-Due to the non-determinism in data transmission, the order of input values arrived at the reducer is not fixed.
+Under the MapReduce framework, a reducer computes output values from a sequence of input values transmitted over the network.
+Due to the non-determinism in data transmission, the order of input values arrives at the reducer is not fixed.
 The \emph{commutativity problem} of reducers asks if the output of a reducer is independent of the order of its inputs.
 There are several advantages for a reducer being commutative, e.g., the verification problem of a MapReduce program can be reduced to the problem of verifying a sequential program.
-In this paper, we propose effective heuristics for reducer commutative analysis and implement them as a tool J-ReCoVer (Java Reducer Commutativity Verifier), which is the first tool that is specialized in checking reducer commutativity.
+In this paper, we propose effective heuristics for reducer commutativity analysis and implement them as a tool J-ReCoVer (Java Reducer Commutativity Verifier), which is the first tool that is specialized in checking reducer commutativity.
 Experimental results over 128 benchmark examples collected from literature and open repositories are very positive; J-ReCoVer correctly handles over 97\% of them.
@@
 
-On the other hand, in many cases, the non-commutative behavior of a reducer can be the source of very tricky bugs.
+On the other hand, in many cases, the non-commutative behavior of a reducer can be the source of some very tricky bugs.
 A study conducted by Microsoft investigated the commutativity problem of $508$ reducers running on their MapReduce server~\cite{xiao14mr}.
@@
 For the case that the reducer is not proven commutative, we complement the approach by using testing to find concrete counterexamples.
-We implement those heuristics as a tool called J-ReCoVer (Java Reducer Commutativity Verifier), which is available at~\verb|http://jrecover.iis.sinica.edu.tw|.
+We implement all these heuristics as a tool called J-ReCoVer (Java Reducer Commutativity Verifier), which is available at~\verb|http://jrecover.iis.sinica.edu.tw|.
 
@@
 One main motivation of commutativity analysis is to reduce the verification problem of a concurrent program to a sequential one.
-There are several researches sharing the similar motivation.
-For instance, the concept of \emph{robustness} of event-driven asynchronous programs~\cite{ahmed2017:robustness}  and program running under relaxed memory model~\cite{ahmed2013:robustness,AbdullaACLR13,AbdullaACLR12}, \emph{synchronizability} of communicating finite state machines~\cite{FinkelL17,basu2012synchronizability,basu2011choreography}.
+There are several researches sharing the similar motivation, e.g., the concept of \emph{robustness} of event-driven asynchronous programs~\cite{ahmed2017:robustness}, \emph{robustness} of program running under relaxed memory model~\cite{ahmed2013:robustness,AbdullaACLR13,AbdullaACLR12}, and \emph{synchronizability} of communicating finite state machines~\cite{FinkelL17,basu2012synchronizability,basu2011choreography}.
 However, their computation models are quite different to that of reducers and hence the result cannot be directly applied.
@@
 We lift the equality $=$ operation to tuples in the standard way.
-Let $S\subseteq [1,k]$, the equality $\{v_1,\ldots,v_k\}=_{S} \{v'_1,\ldots,v'_k\}$ between tuples holds if and only if $\bigwedge_{i\in S} v_i=v'_i$.
+Let $S\subseteq [1,k]$, the equality $(v_1,\ldots,v_k)=_{S} (v'_1,\ldots,v'_k)$ between tuples holds if and only if $\bigwedge_{i\in S} v_i=v'_i$.
 For presentation purpose, we describe a highly simplified model to characterize the essence of reducers. The model allows to describe the computation of reducers and investigate their commutativity.
@@
 s\in \Cmd  & {\triangleq}  & v:= e \mid out(v) \mid \ite{g}{s}{s} \mid s;s && \textmd{Command}\\
-p\in \Prg  & {\triangleq}  & s.\rloop\{s\}.s&& \textmd{Reducer Program}\\
+p\in \Prg  & {\triangleq}  & s;\rloop\{s\};s&& \textmd{Reducer Program}\\
 \end{array}
@@
 
-Here $v\in \Var$ and $c \in \Z$ are variables and constant integer values, respectively.
+Here $v\in \Var$ are variables and $c \in \Z$ are constant integer values, respectively.
 An \emph{integer expression} in $\Exp$ can be either a variable, constant value, a call to the $\cur$ function that reads and consumes an input value of the reducer, their combinations over basic arithmetic operations, or a non-deterministically chosen integer value $*$.
@@
 A \emph{command} in $\Cmd$ can be an assignment, a branch statement, concatenation of a sequence of commands, or $out(v)$ that outputs the value of $v$.
-A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$, and $s_2$ is assumed to have at most one $\cur$ expression in each branch\footnote{We define a \emph{branch} of a command $s$ as a sequence obtained by replacing every branch statement $\ite{g}{s_1}{s_2}$ in $s$ with either $(g)\wedge s_1$ or $(not\ g) \wedge s_2$.}.
+A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$, and $s_2$ is assumed to have at most one $\cur$ expression in each \emph{branch}\footnote{We define a \emph{branch} of a command $s$ as a sequence obtained by replacing every branch statement $\ite{g}{s_1}{s_2}$ in $s$ with either $(g); s_1$ or $(not\ g) ;s_2$.
+For example, the loop body of Figure~\ref{fig:reducer_example}(a) has two branches $t:=\cur; (t>0); m:=t$ and $t:=\cur;(not\ t>0)$ }.
 According to our observation over hundreds  of reducer programs in open repositories, reducer programs are almost always in this form.
@@
 
-In the next section, we give a brief overview of J-Recover,  our tool for reducer commutativity verification.
+In the next section, we give a brief overview of J-ReCoVer,  our tool for reducer commutativity verification.
 
@@
 The architecture of J-ReCoVer can be found in Figure~\ref{fig:overview-jrecover}.
-The user can input a reducer program to J-ReCoVer either through our web-interface or binary installed on their own machine.
+The user can input a reducer program to J-ReCoVer either through our web-interface or binary application installed on their own machine.
 
@@
 Under the Hadoop MapReduce framework, the permutation of the input is handled by the scheduler/shuffler component and is affected by things like network latency, which is not controllable by programmers.
-In order to deal with this issue, we wrote our own dummy Hadoop environment for the reducer as a part of the Preprocessor component.
-So that the input order of the reducer is now controlled by J-ReCoVer.
-Finally, we perform in the Preprocessor some program transformations tasks to simplify the analysis.
-For example, we convert all output commands $out(e)$ inside loops to an special assignment (Section~\ref{sec:program_trans1} and~\ref{sec:program_trans2}).
+In order to deal with this issue, we wrote our own dummy Hadoop environment for the reducer as a part of the Preprocessor component so that the input order of the reducer is now controlled by J-ReCoVer.
+Finally, we perform in the Preprocessor some program transformation tasks to simplify the analysis.
+For example, we convert all output commands $out(e)$ inside loops to an special assignment (will be explained in Section~\ref{sec:program_trans1} and~\ref{sec:program_trans2}).
 
@@
 In this case,  J-ReCoVer stops and reports that the reducer is commutative. 
-If we run the approach in a naive manner, it does not scale to large programs and is very imprecise.
+However, if we run the approach in a naive manner, it does not scale to large programs and is very imprecise.
 We will introduce two critical optimizations that enables the proposed approach working for real-world examples in Section~\ref{section:optimizations}: a data flow analysis to extract critical variables and an improved symbolic execution algorithm to generate SMT formulae.
@@
 The output of the first transformation task is a commutativity-equivalent reducer program where $out$ does not occur in $s_2$.
-Then the algorithm of the Prover is introduced in Section~\ref{sec:prover}.
+Then the algorithm of the Prover is explained in Section~\ref{sec:prover}.
 This algorithm works only in a special case where no read from input occurs in $s_1$.
@@
 
-\subsection{The Prover: Reducing Commutativity to SMT Solving}
+\subsection{The Prover: Reduce Commutativity Checking to SMT Solving}
 \label{sec:prover}
-Below we begin with a simple version where $s_1$ never calls the $\cur$ function.
+Below we begin with a simple reducer where $s_1$ never calls the $\cur$ function.
 Later we will explain how to handle the general case using program transformation.
-The command $s_2$ can be viewed as a function $F$ that reads the values of all variables and the current input before executing $s_2$ and outputs values of all variables after $s_2$.
-Formally, the function $F(n,x_1,x_2,\ldots,x_k): \Z^{k+1} \rightarrow \Z^k$ returns a tuple of values $x_1',x_2',\ldots,x_k'$, where $n$ is the current input value of the reducer, $x_i$ and $x_i'$ are the values of variables before and after the execution of $s_2$, respectively.
+The command $s_2$ can be viewed as a function $F$ that reads the values of all variables and the current input before executing $s_2$ and outputs the values of all variables after $s_2$.
+Formally, the function $F(n,x_1,x_2,\ldots,x_k): \Z^{k+1} \rightarrow \Z^k$ returns a tuple of values $x_1',x_2',\ldots,x_k'$, where $n$ is the current input value of the reducer, $x_i$ and $x_i'$ are the values of variables before and after the execution of $s_2$, respectively, for $i\in[1,k]$.
 The construction of $F$ from $s_2$ can be done in the standard way.
@@
 In the example of ``average'', the values of $s$ and $c$ are the same no matter the reducer first reads $n_1$ and then $n_2$ or reads the two values in the swapped order.
-So it computes the same value for the input [1;2;3;4;5] and any other input with two consecutive values swaps, e.g., [1;2;\textbf{4};\textbf{3};5].
-Since any permutation of a sequence can be obtained by swapping consecutive values finitely many times~\cite{algebra}, this further implies that starting from the same variable valuation, the loop ends with the same valuation for any permutation of input values, e.g., the reducer will output the same value for [1;2;\textbf{3};\textbf{4};5], [1;\textbf{2};\textbf{4};3;5], [\textbf{1};\textbf{4};2;3;5], [4;1;2;3;5], etc.
-Recall that the first program transformation task remembers all output values in variables that will stay unchanged until the end of the loop.
+So it computes the same value for the input [1;2;3;4;5] and any other input with two consecutive values being swapped, e.g., [1;2;\textbf{4};\textbf{3};5].
+The swap operation can be applied arbitrarily many times to produce all possible permutations of the input.
+It follows that that starting from the same variable valuation, the loop ends with the same valuation for any permutation of input values, e.g., the reducer will output the same value for [1;2;\textbf{3};\textbf{4};5], [1;\textbf{2};\textbf{4};3;5], [\textbf{1};\textbf{4};2;3;5], [4;1;2;3;5], etc.
+Recall that the first program transformation task stores all output values in variables that will stay unchanged until the end of the loop.
 The validity of Equation~(\ref{eq:commu}) also implies that the execution of the loop produces the same sequence of outputs.
@@
 Before executing the commands $s_3$, all inputs have been read (the loop exit condition) already.
-Similar the case of $s_1$, $s_3$ does not read from the input and hence the execution of $s_3$ is deterministic.
+Similar to the case of $s_1$, $s_3$ does not read from the input and hence the execution of $s_3$ is deterministic.
 It follows that for all permutations of inputs, the reducer outputs the same sequence of values.
 
-In the next subsection, we explain how to generalize our approach to support general reducer programs using program transformation.
+In the next part, we explain how to generalize our approach to support general reducer programs (those without the restriction on $s_1$) using program transformation.
 
@@
 We handle the problem again by program transformation.
-To handle the example in Figure~\ref{fig:reducer_max} (a), we move the prefix $s_1$ into the loop body and use a new variable $s$ to force that $s_1$ is always executed before the original loop body.
+To deal with the example in Figure~\ref{fig:reducer_max} (a), we move the prefix $s_1$ into the loop body and use a new variable $s$ to force that the execution of $s_1$ is always before the original loop body.
 The result after the transformation is demonstrated in Figure~\ref{fig:reducer_max} (b).
@@
 We perform a simple backward data flow analysis to collect all variables whose value may propagate to the output command after the loop execution.
-With out loss of generality, we assume there is only one output command after the loop.
+Without loss of generality, we assume there is only one output command after the loop.
 Then the code after the loop (i.e., the $s_3$ part of the reducer) can only be in the form of Figure~\ref{fig:nested_out}.
@@
 The data flow analysis algorithm works as follows.
-A set $V_3$ whose value is initially a singleton set $\{v\}$ is used to remember important variables that might flow to the output command $out(v)$ in $s_3$ (Figure~\ref{fig:nested_out}).
+A set $V_3$ whose value is initially a singleton set $\{v\}$ is used to remember important variables that might flow to the output command $out(v)$ in $s_3$ (in Figure~\ref{fig:nested_out}).
 The commands and guards will be inspected in the following order $c_{n}$,$\ldots$,$c_{i+1}$, $g_m$, $g_{m-1}$, $\ldots$, $g_1$, $c_i$, $\ldots$, $c_2$, $c_1$.
 For the case that a guard $g_j$ for $j\in [1,m]$ is being processed, we simply add all variables occurred in $g_j$ to $V_3$.
-For the case that a command $c_j$ for $j\in [1,n]$ is being processed, 
-recall that $c_j$ can only be in the form of an assignment $w:=e$ or a branch $\ite{g}{c'_1}{c'_2}$.
-For the case that $c_j$ is an assignment $w:=e$ and $w\in V_3$, we add all variables contained in $e$ to $V_3$.
-For the case that $c_j$ is a branch command $\ite{g}{c'_1}{c'_2}$, we process both $c'_1$ and $c'_2$ in a similar manner.
-Starting from the same set $V_3$,  after processing $c'_1$ and $c'_2$, we get two sets $V_3^1$ and $V_3^2$.
-We take their union $V_3^1\cup V_3^2$ as the new value of $V_3$.
-After the entire $s_3$ is being processed we get the set of important variables that might affect the outputs.
-
+For the case that a command $c_j$ for $j\in [1,n]$ is being processed, we need to handle two different cases:
+\begin{itemize}
+	\item $c_j$ is an assignment $w:=e$ and $w\in V_3$: all variables in $e$ are added to $V_3$. 
+	\item $c_j$ is a branch $\ite{g}{c'_1}{c'_2}$: the algorithm starts from the same set $V_3$ and processes $c'_1$ and $c'_2$ individually and independently (in a similar manner) to obtain $V_3^1$ and $V_3^2$.
+After that, the algorithm takes their union $V_3^1\cup V_3^2$ as the new value of $V_3$.
+\end{itemize}
+After the entire $s_3$ is being processed we get the set of important variables that might affect the outputs that happen in $s_3$.
 Then we modify the Equation~(\ref{eq:commu}) to the one below
@@
 One can compute the next symbolic state of $\langle pc, val, c;cmds \rangle$ according to the following transition rules.
-Recall that $c$ is either in the form of $(v:= e_0)$ or $\ite{g}{c_1}{c_2}$ after the program transformation tasks are performed:
+Recall that $c$ is either in the form of $(v:= e)$ or $\ite{g}{c_1}{c_2}$ after the program transformation tasks are performed:
 \begin{enumerate}
-	\item If $c$ is $(v:= e_0)$, the next symbolic state is $\langle pc, val[v \rightarrow val(e_0) ], cmds \rangle$.
+	\item If $c$ is $(v:= e)$, the next symbolic state is $\langle pc, val[v \rightarrow val(e) ], cmds \rangle$.
 	\item If $c$ is $\ite{g}{c_1}{c_2}$, the next symbolic states are $\langle pc\wedge g, val, c_1.cmds \rangle$ and $\langle pc\wedge not\  g, val, c_2.cmds \rangle$. 
@@
 
-Here we lift the $val$ function from variables to expressions in the standard way and $val[v \rightarrow val(e_0) ]$ is obtained by reassigning the value of $v$ in $val$ to $val(e_0)$.
+Here we lift the $val$ function from variables to expressions in the standard way and $val[v \rightarrow val(e) ]$ is obtained by reassigning the value of $v$ in $val$ to $val(e)$.
 The execution from a symbolic state terminates when its path condition is conflict or the commands to be executed become empty, i.e., all commands have been processed.
@@
 Assume that the symbolic value of $x,y$ are $sv_x,sv_y$ in the current symbolic state.
-The symbolic value $sv'_x$ of $x$ after the assignment $x:=x\circ y$ is defined as follows.
+The symbolic value $sv'_x$ of $x$ after the assignment $x:=p\circ q$ is defined as follows.
 
 \begin{itemize}
-	\item For the case that $\circ \in\{+,-\}$, we have $sv'_x(z) = sv_x(z)\circ  sv_y(z)$.
-	\item For the case that $\circ \notin\{+,-\}$, we define $sv'_x(val(x)) =1$ and $sv'_x(e) = 0$ for all $e\neq val(x)$.
+	\item For the case that $\circ \in\{+,-\}$, we have $sv'_x(z) = sv_p(z)\circ  sv_q(z)$.
+	\item For the case that $\circ \notin\{+,-\}$, we define $sv'_x(val(p) \circ val(q)) =1$ and $sv'_x(e) = 0$ for all $e\neq val(p) \circ val(q)$.
 \end{itemize}

### 2018-11-14 draft.tex
polish

@@
 In that case, we can still verify the reducer by first partitioning it into two reducers and then verifying them separately.
-One reducer computes the average (Figure~\ref{fig:reducer_example}(b)) and the other reducer uses a non-deterministic value to over-approximate the computed average ($a := *$) and then use it in the computation of standard deviation (Figure~\ref{fig:reducer_example}(c)).
+One reducer computes the average (Figure~\ref{fig:reducer_example}(b)) and the other reducer uses a non-deterministic value to over-approximate the computed average ($a := *$) (Figure~\ref{fig:reducer_example}(c)).
 The reducer in Figure~\ref{fig:reducer_example}(c) ``over-approximates''  all possible outputs of the standard deviation computation; it computes an output even if $a$ is not the average of inputs.
@@
 
-Using the reducer that computes average (Figure~\ref{fig:reducer_example} (b)) as an example.
+Using the reducer that computes average (Figure~\ref{fig:reducer_example}(b)) as an example.
 It has two variables $s$ and $c$.
@@
 
-In the next part, we explain how to generalize our approach to support general reducer programs (those without the restriction on $s_1$) using program transformation.
+In the next part, we explain how to generalize our approach to support general reducers (without the restriction on $s_1$) using program transformation.
 
@@
 In real-world examples, it is often that the $s_1$ part of the reducer also reads from the input.
-In the example in Figure~\ref{fig:reducer_max} (a), the reducer program remembers the first input value in the variable $m$, increases its value by 10, and then updates its value to bigger ones if any occurs in the loop.
+In the example in Figure~\ref{fig:reducer_max}(a), the reducer program remembers the first input value in the variable $m$, increases its value by 10, and then updates its value to bigger ones if any occurs in the loop.
 The corresponding Equation~(\ref{eq:commu}) is valid in this case.
@@
 We handle the problem again by program transformation.
-To deal with the example in Figure~\ref{fig:reducer_max} (a), we move the prefix $s_1$ into the loop body and use a new variable $s$ to force that the execution of $s_1$ is always before the original loop body.
-The result after the transformation is demonstrated in Figure~\ref{fig:reducer_max} (b).
+To deal with the example in Figure~\ref{fig:reducer_max}(a), we move the prefix $s_1$ into the loop body and use a new variable $s$ to force that the execution of $s_1$ is always before the original loop body.
+The result after the transformation is demonstrated in Figure~\ref{fig:reducer_max}(b).
 The new reducer program over-approximates all possible inputs/outputs of the original one.
-For the case that $s=1$ at the beginning, its output sequence is the same as the original reducer.
+When $s=1$, its output sequence is the same as the original reducer.
 When $s\neq 1$, it may produce outputs that are not possible by the original reducer.
@@
 So we can apply Equation~(\ref{eq:commu}) to prove its commutativity.
-Since the new reducer has all the possible outputs of the original one, the new reducer being commutative implies that the original one is also commutative.
+Since the new reducer has all behaviors of the original one, the new reducer being commutative implies that the original one is also commutative.
 
@@
 For the general case, we first rewrite the $s_1$ part of the reducer $s_1;\rloop\{s_2\};s_3$ to the form 
-$$s'_0;x_{i_1}{:=} \cur;s'_1.\ldots x_{i_{m}}{:=}\cur;s'_m, $$ where $\cur$ never occur in $s'_0,s'_1,\ldots, s'_m$.
+$s'_0;x_{i_1}{:=} \cur;s'_1.\ldots x_{i_{m}}{:=}\cur;s'_m$, where $\cur$ never occur in $s'_0,s'_1,\ldots, s'_m$.
 Then we produce the reducer in Figure~\ref{fig:general_program_transformation}, which is an over-approximation of the original reducer for the same reason: the case that $s=1$ has the same output sequence to the original reducer and when $s\neq 1$, it may produce additional behavior.
@@
 This data structure is efficient for strong symbolic values of reducer programs mainly for reason that the operations $+$ and $-$ are quite heavily used in such programs. 
+Here we give a tiny example. Initially, $sv_x(x_0)=1$. After the commands $x:=x*x;x:=x+x$, we get $sv_x(x_0*x_0)=1$ and $sv_x(x_0*x_0)=2$, respectively.
 
@@
 Since those functions to be analyzed are relatively simple, the syntactical difference between C and Java implementation is very small.
-The difference in the statistics mainly comes from the verification algorithm being used, not the programing language the reducer is written in.
+The difference in the statistics mainly comes from the verification algorithm being used, not the programming language the reducer is written in.
 \begin{table}[t]
@@
 	\caption{SV-Comp 2018 results on reducer commutativity.
-For space reason, we only list results of competitive tool in this table, which includes top three tools in the overall ranking and the reachability safety category.}
+For space reason, we only list results of competitive tool in this table, which includes top three tools in the overall ranking and the reachability safety category.}\vspace{-1cm}
 	\label{tab:svcomp}

### 2018-11-14 draft.tex
polish

@@
 The sequence elements (key-value pairs) with the same key will be sent to the same reducer for further processing.
-Due to scheduling polices and network latency, the same inputs may arrive at a reducer in different order in different executions, which results in the so-called \emph{commutativity problem} of reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}, that is, if the outputs of a reducer is independent of the order of its inputs.
+Due to scheduling polices and network latency, the same inputs may arrive at a reducer in different order in different executions, which results in the so-called \emph{commutativity problem} of reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}, that is, if the output of a reducer is independent of the order of its inputs.
 If all reducers are commutative, they will have the same external behavior under all possible schedules.
@@
 
-On the other hand, in many cases, the non-commutative behavior of a reducer can be the source of some very tricky bugs.
+On the other hand, in many cases, the non-commutative behavior of a reducer is the source of very tricky bugs.
 A study conducted by Microsoft investigated the commutativity problem of $508$ reducers running on their MapReduce server~\cite{xiao14mr}.
@@
 In this paper, we propose heuristics for the commutativity problem that works very efficiently on a large set of practical integer reducer programs.
-We reduce the commutativity problem to a SMT problem in a sound but incomplete manner.
+We reduce the commutativity problem to an SMT problem in a sound but incomplete manner.
 We also propose optimizations to enable the approach working on real world examples.
@@
 
-\textbf{The Prover component} reduces the commutativity problem to a SMT formula satisfiability problem.
+\textbf{The Prover component} reduces the commutativity problem to an SMT formula satisfiability problem.
 At a high level, we check equivalence between a reducer program and its variant that has two consecutive inputs swapped.
-We show that this can be reduced to a SMT problem and give it to the SMT solver Z3~\cite{z3} for solving.
+We show that this can be reduced to an SMT problem and give it to the SMT solver Z3~\cite{z3} for solving.
 In case that Z3 proved the formula unsatisfiable, we know that swapping any two consecutive inputs of the reducer will not change its output.
@@
 For general reducer programs, we introduce the second program transformation task (Section~\ref{sec:program_trans2}) whose output is a reducer program that falls in the special case required by the Prover and ``over-approximates'' all input/output behaviors of the original reducer.
-The commutative of the produced reducer implies the commutative of the original one, but not vice verse.
+The commutativity of the produced reducer implies the commutativity of the original one, but not vice verse.
 
@@
 In the example of ``average'', the values of $s$ and $c$ are the same no matter the reducer first reads $n_1$ and then $n_2$ or reads the two values in the swapped order.
-So it computes the same value for the input [1;2;3;4;5] and any other input with two consecutive values being swapped, e.g., [1;2;\textbf{4};\textbf{3};5].
+So it computes the same value for the input [1;2;\textbf{3};\textbf{4};5] and any other input with two consecutive values being swapped, e.g., [1;2;4;3;5].
 The swap operation can be applied arbitrarily many times to produce all possible permutations of the input.
-It follows that that starting from the same variable valuation, the loop ends with the same valuation for any permutation of input values, e.g., the reducer will output the same value for [1;2;\textbf{3};\textbf{4};5], [1;\textbf{2};\textbf{4};3;5], [\textbf{1};\textbf{4};2;3;5], [4;1;2;3;5], etc.
+It follows that that starting from the same variable valuation, the loop ends with the same valuation for any permutation of input values, e.g., the reducer will output the same value for [1;2;3;4;5], [1;2;4;3;5], [1;4;2;3;5], [4;1;2;3;5], etc.
 Recall that the first program transformation task stores all output values in variables that will stay unchanged until the end of the loop.
@@
 \label{section:optimizations}
-In this section we explain how data flow analysis is used in J-Recover to improve the precision of commutativity checking and the algorithm we used to construct the $F$ function in Equation~(\ref{eq:commu}).
+In this section we explain how data flow analysis is used in J-ReCoVer to improve the precision of commutativity checking and the algorithm we used to construct the $F$ function in Equation~(\ref{eq:commu}).
 
@@
 			};
-			$out(s)$\;\;
+			$out(s)$\;\;\;
 		\end{algorithm}
@@
 	\end{minipage}
-	\begin{minipage}{0.55\textwidth}
+	\ \ \ \ \ \ \ \ 
+	\begin{minipage}{0.5\textwidth}
 		\LinesNumbered
@@
 	\end{minipage}
-		\caption{$out(v)$ in nested branches of $s_3$.}
+		\caption{The $s_3$ command with an $out(v)$ command in nested branches.}
 		\label{fig:nested_out}
@@
 The data flow analysis algorithm works as follows.
-A set $V_3$ whose value is initially a singleton set $\{v\}$ is used to remember important variables that might flow to the output command $out(v)$ in $s_3$ (in Figure~\ref{fig:nested_out}).
+A set $V_3$ whose value is initially a singleton set $\{v\}$ is used to remember the variables that might flow to the output command $out(v)$ in $s_3$ (in Figure~\ref{fig:nested_out}).
 The commands and guards will be inspected in the following order $c_{n}$,$\ldots$,$c_{i+1}$, $g_m$, $g_{m-1}$, $\ldots$, $g_1$, $c_i$, $\ldots$, $c_2$, $c_1$.
@@
 E.g., if $X = \{x_1,x_4,y\}$, where $y\notin \{x_1,\ldots,x_k\}$, then $PosF(X)=\{1,4\}$.
-The use of equation~(\ref{eq:commu2}) is critical to the success of our approach.
+The use of Equation~(\ref{eq:commu2}) is critical to the success of our approach.
 In our evaluation, the ratio of examples that our approach can successfully analyze is significantly increased from $6.8\%$ to $97.5\%$.
@@
 
-The computation of $F$ in equation~(\ref{eq:commu2}) can be done in several different ways.
+The computation of $F$ in Equation~(\ref{eq:commu2}) can be done in several different ways.
 For example, one can construct a formula in the style of bounded model checking.
@@
 One can compute the next symbolic state of $\langle pc, val, c;cmds \rangle$ according to the following transition rules.
-Recall that $c$ is either in the form of $(v:= e)$ or $\ite{g}{c_1}{c_2}$ after the program transformation tasks are performed:
+Recall that $c$ is either in the form of $v:= e$ or $\ite{g}{c_1}{c_2}$ after the program transformation tasks are performed:
 \begin{enumerate}
-	\item If $c$ is $(v:= e)$, the next symbolic state is $\langle pc, val[v \rightarrow val(e) ], cmds \rangle$.
+	\item If $c$ is $v:= e$, the next symbolic state is $\langle pc, val[v \rightarrow val(e) ], cmds \rangle$.
 	\item If $c$ is $\ite{g}{c_1}{c_2}$, the next symbolic states are $\langle pc\wedge g, val, c_1.cmds \rangle$ and $\langle pc\wedge not\  g, val, c_2.cmds \rangle$. 
@@
 First, we create for each variable $x\in\Var$ a formula $f_x$ whose value is $\bigvee_{\langle pc, val, \emptyset \rangle \in T} (pc \wedge val(x))$.
-The function $F(n,x_1,x_2,\ldots,x_k)$ simply returns the tuple $\{f_{x_1},f_{x_2},\ldots, f_{x_k}\}$.
+The function $F(n,x_1,x_2,\ldots,x_k)$ simply returns the tuple $(f_{x_1},f_{x_2},\ldots, f_{x_k})$.
 
@@
 \end{itemize}
-To make the definition complete for our simple reducer program commands, we further define (1) $sv_{\cur}(c_0) =1$ and $sv_{\cur}(e)=0$ for $e\neq \cur$, (2) $sv_{n}(1) =n$ and $sv_{n}(e)=0$ for $e\neq 1 \wedge n\in \Z$.
+To make the definition complete for our simple reducer program commands, we further define (I) $sv_{\cur}(c_0) =1$ and $sv_{\cur}(e)=0$ for $e\neq \cur$, (II) $sv_{n}(1) =n$ and $sv_{n}(e)=0$ for $e\neq 1 \wedge n\in \Z$.
 This data structure is efficient for strong symbolic values of reducer programs mainly for reason that the operations $+$ and $-$ are quite heavily used in such programs. 
@@
 J-ReCoVer is implemented in Java and built on top of Soot~\cite{soot} 2.5.0 and Z3~\cite{z3} 4.7.1.
-We run J-Recover on a virtual machine running on a server with AMD Opteron 6376 CPU.
+We run J-ReCoVer on a virtual machine running on a server with AMD Opteron 6376 CPU.
 4GB of memory is allocated to this virtual machine.
@@
 In order to properly evaluate the performance of J-ReCoVer, we collect benchmark example from two different sources. 
-First, we use the search engine \url{http://searchcode.com}~\cite{searchcode} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''.
+First, we use the search engine \emph{searchcode.com}~\cite{searchcode} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''.
 Since there is an upper bound on number of results returned from the search engine, we add different search filters in order to get more data.
@@
 We exclude cases that are not Hadoop MapReduce reducer programs (those do not import the Hadoop library, do not extend or implement the reducer interface) and obtain $1273$ examples.
-We further remove those that cannot be compiled, those that are identical to each other, or those uses non-numerical data types (e.g, string) and obtained $118$ programs as the final benchmark.
+We further remove those that cannot be compiled, those that are identical to each other, or those with non-numerical data types (e.g, string) and obtained $118$ programs as the final benchmarks.
 The second set of examples are those have been discussed in verification literature~\cite{ChenHSW15,ChenSW16}. This set is relatively small, we have only $10$ examples. 
-We also created a program that randomly generate reducer program in order to test the scalability of J-Recover.
-All benchmark examples can be found on the web-site of J-Recover.
+We also created a program that randomly generate reducer program in order to test the scalability of J-ReCoVer.
+All benchmark examples can be found on the web-site of J-ReCoVer.
 
@@
 \begin{itemize}
-	\item Is J-Recover better than other competing tools?
+	\item Is J-ReCoVer better than other competing tools?
 	\item Are the two optimizations proposed in Section~\ref{section:optimizations} critical and effective?
@@
 The examples in~\cite{ChenHSW15}, which includes \textsf{rangesum}\footnote{The sum of the second half of the input list.}, \textsf{avg}, \textsf{max}, \textsf{sep}\footnote{The number of occurrences of even numbers minus that of odd numbers.}, \textsf{sum}, are already included in SV-Comp~\cite{svcomp} (Software Verification Competition) benchmarks.
-Although those examples are tiny and simple, none of the software verifiers can verify all of those examples according to the 2018 results. In contrast, J-Recover can verify all them very efficiently.
+Although those examples are tiny and simple, none of the software verifiers can verify all of those examples according to the 2018 results.
+In contrast, J-ReCoVer can verify all of them very efficiently.
 
-In Table~\ref{tab:svcomp}, the statistics of tools other than J-Recover are taken directly from the SV-Comp~\cite{svcomp} web-site.
-Although the machine we used are different, the results of J-Recover will not be much different if we run it on other machines.
-The other limitation is that in J-Recover, we analyze Java implementations and in SV-Comp they analyze the C implementations of the same functions.
+In Table~\ref{tab:svcomp}, the statistics of tools other than J-ReCoVer are taken directly from the SV-Comp~\cite{svcomp} web-site.
+Although the machine we used are different, the results of J-ReCoVer will not be much different if we run it on other machines.
+The other issue of this experiment is that in J-ReCoVer, we analyze the Java implementations and in SV-Comp they analyze the C implementations of the same functions.
 Since those functions to be analyzed are relatively simple, the syntactical difference between C and Java implementation is very small.
@@
 \hline
-		& \small CBMC\cite{cbmc2} 	& \small CPA-Seq\cite{cpachecker} & \small  ESBMC-kind\cite{esbmc} & \small  UAutomizer\cite{uautomizer} &\small  VeriAbs\cite{veriabs} &\small J-Recover\\
+		& \small CBMC\cite{cbmc2} 	& \small CPA-Seq\cite{cpachecker} & \small  ESBMC-kind\cite{esbmc} & \small  UAutomizer\cite{uautomizer} &\small  VeriAbs\cite{veriabs} &\small J-ReCoVer\\
 \hline
@@
 
-\subsection{The performance of J-Recover with and without optimizations}
+\subsection{The performance of J-ReCoVer with and without optimizations}
 
-For the optimization based on data flow analysis (Section~\ref{section:opt1}), we evaluation them based on real-world benchmark sets collected from open repositories (118 examples) and also literature (10 examples).
+For the optimization based on data flow analysis (Section~\ref{section:opt1}), we evaluate them based on real-world benchmark sets collected from open repositories (118 examples) and also literature (10 examples).
 The difference between the version with and without this optimization is very clear.
@@
 $10\%$ to $100\%$ for examples from literature.
-There are only three cases that J-Recover with data flow analysis cannot handle.
-The reason that J-Recover fails is that the three reducers use more complicated structure than what J-Recover currently supports; they use a branch statement before entering the loop, i.e., in the form $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$.
-In theory, such program can be handled by more sophisticated program transformation operations.
-For example, we can merge the two loops and push the outer branch condition inside the merged loop.
-However, this new program transformation task is not implemented in J-Recover yet.
+There are only three cases that J-ReCoVer with data flow analysis cannot handle.
+The reason that J-ReCoVer fails is that the three reducers use more complicated structure than what J-ReCoVer currently supports; they use a branch statement before entering the loop, i.e., in the form $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$.
+In theory, such program can be handled by more sophisticated program transformation tasks.
+For example, we can merge the two loops and push the outer branch condition into the merged loop.
+However, this new program transformation task is not implemented in J-ReCoVer yet.
 
@@
 The reason is that when Soot convert a Java program to the Jimple format, it always uses a temporary variable to store the value of $\cur$ in the loop body (similar to the example in Figure~\ref{fig:reducer_opt}).
-We tried a simpler heuristics approach that only ignores the temporary variables and the results is not as good as using data flow analysis, because the value of the temporary variable often also propagates to other variables.
+We tried a simpler heuristics approach that only ignores the temporary variables and the result is not as good as using data flow analysis, because the values of the temporary variables often also propagate to other variables.
 \begin{table}[htb]
@@
 	\caption{The improvement of precision using data flow analysis.
-The row ``Precision'' is calculated as the number of examples that J-Recover returns commutative or non-commutative divided by the total number of example.}
+The row ``Precision'' is calculated as the number of examples that J-ReCoVer returns commutative or non-commutative divided by the total number of example.}
 	\label{tab:opt1}
@@
 So we use a random reducer program generator to produce examples of different sizes for this evaluation.
-For the generator, we can give as parameter a tuple $(N,B,A)$, where $N$ is the number of variables, $B$ is the number of branch statements, and $A$ is the number of assignment statement.
+For the generator, we can give as parameter a tuple $(N,B,A)$, where $N$ is the number of variables, $B$ is the number of branch statements, and $A$ is the number of assignment statements.
 All assignments are in the form of $v_1 := v_2\odot v_3,\odot\in\{+,-,\times\}$ and all guards are in the form of $v_1 \circ v_2, \circ\in\{\geq, >,=, \neq, <,\leq \}$.
 The source code of the random generator is available at \url{https://github.com/spencerwuwu/benchmark-generator}.
-In the evaluation, we keep the ratio $N:B:A = 5:1:50$ and uses lines numbers from $50$ to $250$.
+In the evaluation, we keep the ratio $N:B:A = 5:1:50$ and produce random reducers from $50$ lines $250$ lines.
 The most difficult cases might have $5$ to $6$ nested branches and $25$ integer variables in a reducer program.
@@
 The results are presented in Figure~\ref{tab:opt2} in the form of a table and also a scatter plot.
-Form there we can see that the optimization is helpful in improving all the statistics (average, median execution time and the number of cases that cannot be finished within 300 seconds).
+From there we can see that the optimization is helpful in improving the statistics in particular for larger programs (average, median execution time and the number of cases that cannot be finished within 300 seconds).
 Also from the scatter plot we can see that much more cases are solved with the new optimization.
@@
 Bounded model checking (BMC) is another approach to create the $F$ function in Equations~\ref{eq:commu} and \ref{eq:commu2}.
-Although we use symbolic execution in J-Recover, it is interesting to see how good BMC works in checking the commutativity of reducer examples.
+Although we use symbolic execution in J-ReCoVer, it is interesting to see how good BMC works in checking the commutativity of reducer examples.
 In this evaluation, we use the same random reducer program generator.
@@
 The results can be found in Table~\ref{tab:bmc}.
-For symbolic execution, we first use J-Recover to generate the formula for evaluation.
+For symbolic execution, we first use J-ReCoVer to generate the formula for evaluation.
 For BMC, the formula is directly generated by the random generator.
@@
 \section{Concluding Remarks}
+
+The current version of J-ReCoVer shares similar limitation with SMT-based software verification tools.
+We use SMT theory of integer and real number arithmetics as the reasoning tool.
+In this implementation, we do not handle more advanced data-types such as string and floating point.
+The problem of variable overflow is also not handled.
+In fact, if we consider all possible inputs of a reducer, almost all reducer programs will run into the problem of overflow.
+Even the basic example that computes the sum of all input values, overflow can occur when a list [\textsf{MaxInt};\textsf{MaxInt}] is used as the input.
+Nevertheless, such example might not be of the interests of MapReduce programmers, who usually care only about the data set they want to analyze.
+We are planing to build another tool to estimate a safe bound of data size such that overflow will not occur if data size is within the bound.
+The programmer can then check if their data set fits in the computed bound and switch to use larger data types in the program when needed.
+So overflow will not occurs in the data set of interests.
+
 We believe that simpler but more restricted domain specific language/frameworks will be the trend for the development of parallel programs.
@@
 Its successors such as Spark, Flink, Beam, and Google Cloud Dataflow, still share many features of its design.
-We believe the design of J-Recover will lead to significant impact to the verification/testing of programs under such frameworks.
-
-The current version of J-Recover shares similar limitation with SMT-based software verification tools.
-We use SMT theory of integer and real number arithmetics as the reasoning tool.
-In this implementation.
-We do not handle more advanced data-types such as string and floating point.
-The problem of variable overflow is also not handled by this tool.
-In fact, if we consider all possible inputs of a reducer, almost all reducer programs will run into the problem of overflow.
-Even the basic example that computes the sum of all input values, overflow can occur when a list [\textsf{MaxInt};\textsf{MaxInt}] is used as the input.
-Nevertheless, such example might not be of the interests of MapReduce programmers, who usually care only about the data set they want to analyze.
-We are planing to build another tool to estimate a safe bound of data size such that overflow will not occur if data size is within bound.
-The programmer can then check if their data set fits in the computed bound and switch to use larger data type in the program when needed.
-So overflow will not occurs in the data set of interests.
+We believe the design of J-ReCoVer will lead to significant impact to the verification/testing of programs under such frameworks.
 

### 2018-11-14 draft.tex
polish

@@
 \label{section:optimizations}
-In this section we explain how data flow analysis is used in J-ReCoVer to improve the precision of commutativity checking and the algorithm we used to construct the $F$ function in Equation~(\ref{eq:commu}).
+In this section, we explain how data flow analysis is used in J-ReCoVer to improve the precision of commutativity checking and the algorithm we used to construct the $F$ function in Equation~(\ref{eq:commu}).
 
@@
 In the loop body, the input is first stored in a variable $t$ and then added to $s$.
-In this case, the $F$ function returns the updated values of both $s$ and $t$ after the execution of loop body.
+In this case, the $F$ function returns the updated values of both $s$ and $t$ after the execution of the loop body.
 Observe that

### 2018-11-14 draft.tex
polish

@@
 
-\subsection{Computing the $F$ function using symbolic execution with efficient data structure}
+\subsection{Computing the $F$ function using symbolic execution with an efficient data structure}
 \label{section:opt2}
@@
 
-For the loop body $s_2$, symbolic execution is guaranteed to terminate because there is no commands in $s_2$ that may lead to infinite computations.
+For the loop body $s_2$, symbolic execution is guaranteed to terminate because there exist no commands in $s_2$ that may lead to infinite computations.
 When the execution terminates, we collect all states with empty commands $\langle pc, val, \emptyset \rangle$ as a set $T$ and use them to create the function $F$ in Equation~(\ref{eq:commu2}).
@@
 First, we use the search engine \emph{searchcode.com}~\cite{searchcode} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''.
-Since there is an upper bound on number of results returned from the search engine, we add different search filters in order to get more data.
+Since there is an upper bound on the number of results returned from the search engine, we add different search filters in order to get more data.
 We tried all $12$ combinations of six filters on code length $\{<50$, $ 50\sim 250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim 1250\}$
 and two filters for data sources $\{\url{github.com}, \url{bitbuckect.com}\}$.
-In total we get $11346$ Java programs.
+In total, we get $11346$ Java programs.
 We exclude cases that are not Hadoop MapReduce reducer programs (those do not import the Hadoop library, do not extend or implement the reducer interface) and obtain $1273$ examples.
@@
 The second set of examples are those have been discussed in verification literature~\cite{ChenHSW15,ChenSW16}. This set is relatively small, we have only $10$ examples.
-We also created a program that randomly generate reducer program in order to test the scalability of J-ReCoVer.
-All benchmark examples can be found on the web-site of J-ReCoVer.
+We also created a program that randomly generates reducer programs in order to test the scalability of J-ReCoVer.
+All benchmark examples can be found on the website of J-ReCoVer.
 
@@
 
-In Table~\ref{tab:svcomp}, the statistics of tools other than J-ReCoVer are taken directly from the SV-Comp~\cite{svcomp} web-site.
-Although the machine we used are different, the results of J-ReCoVer will not be much different if we run it on other machines.
+In Table~\ref{tab:svcomp}, the statistics of tools other than J-ReCoVer are taken directly from the SV-Comp~\cite{svcomp} website.
+Although the machines we used are different, the results of J-ReCoVer will not be much different if we run it on other machines.
 The other issue of this experiment is that in J-ReCoVer, we analyze the Java implementations and in SV-Comp they analyze the C implementations of the same functions.
@@
 	\caption{SV-Comp 2018 results on reducer commutativity.
-For space reason, we only list results of competitive tool in this table, which includes top three tools in the overall ranking and the reachability safety category.}\vspace{-1cm}
+For space reason, we only list the results of competitive tools in this table, which includes top three tools in the overall ranking and the reachability safety category.}\vspace{-1cm}
 	\label{tab:svcomp}
@@
 The reason that J-ReCoVer fails is that the three reducers use more complicated structure than what J-ReCoVer currently supports; they use a branch statement before entering the loop, i.e., in the form $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$.
-In theory, such program can be handled by more sophisticated program transformation tasks.
+In theory, such a program can be handled by more sophisticated program transformation tasks.
 For example, we can merge the two loops and push the outer branch condition into the merged loop.
@@
 If we look into scrutiny, we failed to verify any example using Equation~(\ref{eq:commu}).
-The reason is that when Soot convert a Java program to the Jimple format, it always uses a temporary variable to store the value of $\cur$ in the loop body (similar to the example in Figure~\ref{fig:reducer_opt}).
+The reason is that when Soot converts a Java program to the Jimple format, it always uses a temporary variable to store the value of $\cur$ in the loop body (similar to the example in Figure~\ref{fig:reducer_opt}).
 We tried a simpler heuristics approach that only ignores the temporary variables and the result is not as good as using data flow analysis, because the values of the temporary variables often also propagate to other variables.
@@
 So we use a random reducer program generator to produce examples of different sizes for this evaluation.
-For the generator, we can give as parameter a tuple $(N,B,A)$, where $N$ is the number of variables, $B$ is the number of branch statements, and $A$ is the number of assignment statements.
+For the generator, we can give as a parameter a tuple $(N,B,A)$, where $N$ is the number of variables, $B$ is the number of branch statements, and $A$ is the number of assignment statements.
 All assignments are in the form of $v_1 := v_2\odot v_3,\odot\in\{+,-,\times\}$ and all guards are in the form of $v_1 \circ v_2, \circ\in\{\geq, >,=, \neq, <,\leq \}$.
@@
 
-	\caption{The improvement in scalability using the better data structure for symbolic execution.
+	\caption{The improvement in scalability using a better data structure for symbolic execution.
 Each cell in the table is the summary of 60 randomly generated programs.
@@
 Nevertheless, such example might not be of the interests of MapReduce programmers, who usually care only about the data set they want to analyze.
-We are planing to build another tool to estimate a safe bound of data size such that overflow will not occur if data size is within the bound.
+We are planning to build another tool to estimate a safe bound of data size such that overflow will not occur if the data size is within the bound.
 The programmer can then check if their data set fits in the computed bound and switch to use larger data types in the program when needed.
-So overflow will not occurs in the data set of interests.
+So overflow will not occur in the data set of interests.
 
@@
 It lowers the barrier for writing correct yet efficient parallel program.
-Complicated issues such as fault torrence, load balancing, and security are handled by the frameworks automatically.
+Complicated issues such as fault tolerance, load balancing, and security are handled by the frameworks automatically.
 Programmers only need to focus on their program logic.
@@
 Its successors such as Spark, Flink, Beam, and Google Cloud Dataflow, still share many features of its design.
-We believe the design of J-ReCoVer will lead to significant impact to the verification/testing of programs under such frameworks.
+We believe the design of J-ReCoVer will lead to significant impacts to the verification/testing of programs under such frameworks.
 

### 2018-11-14 draft.tex
polish

@@
 
-MapReduce is one of the most popular framework for data parallel computation.
+MapReduce is one of the most popular frameworks for data parallel computation.
 A MapReduce~\cite{dean04,hadoop} program consists of several pairs of \emph{mappers} and \emph{reducers} running on a machine cluster for handling big data in parallel.
-Usually mappers and reducers are the only components in a MapReduce program that involves concurrency.
+Usually, mappers and reducers are the only components in a MapReduce program that involves concurrency.
 Mappers read data from a distributed database and output a sequence of \emph{key-value} pairs.
 The sequence elements (key-value pairs) with the same key will be sent to the same reducer for further processing.
-Due to scheduling polices and network latency, the same inputs may arrive at a reducer in different order in different executions, which results in the so-called \emph{commutativity problem} of reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}, that is, if the output of a reducer is independent of the order of its inputs.
+Due to scheduling policies and network latency, the same inputs may arrive at a reducer in a different order in different executions, which results in the so-called \emph{commutativity problem} of reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}, that is, if the output of a reducer is independent of the order of its inputs.
 If all reducers are commutative, they will have the same external behavior under all possible schedules.
-In such a case, by fixing a schedule, the verification problem of a MapReduce program can be reduced to the verification problem of a sequential program, which is known to be much easier then the verification problem of concurrent programs.
+In such a case, by fixing a schedule, the verification problem of a MapReduce program can be reduced to the verification problem of a sequential program, which is known to be much easier than the verification problem of concurrent programs.
 One needs to consider only a particular interleaving of input values instead of all of them.
@@
 We reduce the commutativity problem to an SMT problem in a sound but incomplete manner.
-We also propose optimizations to enable the approach working on real world examples.
+We also propose optimizations to enable the approach that works on real-world examples.
 For the case that the reducer is not proven commutative, we complement the approach by using testing to find concrete counterexamples.
@@
 We use two sets of integer reducer benchmarks to evaluate J-ReCoVer.
-The first set is collected from open repositories such as Github and Bitbuckect.
+The first set is collected from open repositories such as Github and Bitbucket.
 With the help of a search engine~\cite{searchcode} over those repositories, we collected 118 examples.
 J-ReCoVer is able to correctly analyze all but 3 of them.
-We also tried all 10 integer reducers descried in verification literature~\cite{ChenHSW15,ChenSW16} and J-ReCoVer can handle all of them.
+We also tried all 10 integer reducers described in verification literature~\cite{ChenHSW15,ChenSW16} and J-ReCoVer can handle all of them.
 
 \subsection*{Related Works}
-Reducer commutativity problem can be reduced to program equivalence problem.
+Reducer commutativity problem can be reduced to a program equivalence problem.
 One creates another program $R'$ that first non-deterministically swaps two consecutive input values and then executes the code of $R$.
@@
 One main motivation of commutativity analysis is to reduce the verification problem of a concurrent program to a sequential one.
-There are several researches sharing the similar motivation, e.g., the concept of \emph{robustness} of event-driven asynchronous programs~\cite{ahmed2017:robustness}, \emph{robustness} of program running under relaxed memory model~\cite{ahmed2013:robustness,AbdullaACLR13,AbdullaACLR12}, and \emph{synchronizability} of communicating finite state machines~\cite{FinkelL17,basu2012synchronizability,basu2011choreography}.
-However, their computation models are quite different to that of reducers and hence the result cannot be directly applied.
+There are several pieces of research sharing the similar motivation, e.g., the concept of \emph{robustness} of event-driven asynchronous programs~\cite{ahmed2017:robustness}, the \emph{robustness} of program running under relaxed memory model~\cite{ahmed2013:robustness,AbdullaACLR13,AbdullaACLR12}, and \emph{synchronizability} of communicating finite state machines~\cite{FinkelL17,basu2012synchronizability,basu2011choreography}.
+However, their computation models are quite different from that of reducers and hence the result cannot be directly applied.
 Besides verification, another interesting research direction is the synthesis of MapReduce programs~\cite{SmithA16}.
@@
 
-Here $v\in \Var$ are variables and $c \in \Z$ are constant integer values, respectively.
+Here any $v\in \Var$ is a variable and any $c \in \Z$ is a constant integer value.
 An \emph{integer expression} in $\Exp$ can be either a variable, constant value, a call to the $\cur$ function that reads and consumes an input value of the reducer, their combinations over basic arithmetic operations, or a non-deterministically chosen integer value $*$.
@@
 
-\textbf{The Preprocessor component} first compiles a reducer program to bytecode and use the tool Soot~\cite{soot} to further convert it to the so called ``Jimple'' format, which is an intermediate language that is designed to simplify the analysis of Java programs.
+\textbf{The Preprocessor component} first compiles a reducer program to bytecode and use the tool Soot~\cite{soot} to further convert it to the so-called ``Jimple'' format, which is an intermediate language that is designed to simplify the analysis of Java programs.
 Under the Hadoop MapReduce framework, the permutation of the input is handled by the scheduler/shuffler component and is affected by things like network latency, which is not controllable by programmers.
@@
 Finally, we perform in the Preprocessor some program transformation tasks to simplify the analysis.
-For example, we convert all output commands $out(e)$ inside loops to an special assignment (will be explained in Section~\ref{sec:program_trans1} and~\ref{sec:program_trans2}).
+For example, we convert all output commands $out(e)$ inside loops to a special assignment (will be explained in Section~\ref{sec:program_trans1} and~\ref{sec:program_trans2}).
 
@@
 Our procedure for generating random pairs is quite naive.
-We use five different input list of lengths 5, 7, 9 ,11, and 13.
+We use five different input list of lengths 5, 7, 9, 11, and 13.
 For each length, we generate 300 lists and pick uniformly at random one of its permutations.
@@
 However, if we run the approach in a naive manner, it does not scale to large programs and is very imprecise.
-We will introduce two critical optimizations that enables the proposed approach working for real-world examples in Section~\ref{section:optimizations}: a data flow analysis to extract critical variables and an improved symbolic execution algorithm to generate SMT formulae.
+We will introduce two critical optimizations that enable the proposed approach working for real-world examples in Section~\ref{section:optimizations}: a data flow analysis to extract critical variables and an improved symbolic execution algorithm to generate SMT formulae.
 More details of the algorithms used in the Preprocessor and the Prover components will be explained in Section~\ref{sec:preprocessor_prover} and the optimizations will be introduced in~\ref{section:optimizations}.
@@
 
-The validity of Equation~(\ref{eq:commu}) implies that swapping any two consecutive input values does not change the final variable valuation.
+The validity of Equation~(\ref{eq:commu}) implies that swapping any two consecutive input values will not change the final variable valuation.
 Informally, it says that starting from the same initial valuations of variables and with two different input orders, $[n_1;n_2]$ and $[n_2;n_1]$, the values of all program variables are the same after we execute the loop body twice.

### 2019-06-18 draft.tex
polish
remove some parts complained by TACAS PCs

@@
 \usepackage{amssymb}
-\usepackage{dsfont}
+\usepackage{times}
 %\usepackage{cancel}
@@
 
+\hide{
 \author{
@@
 \and
-Hung-Wei Hsu\inst{1}
+Hsin-Hung Lin\inst{1}
 \and
@@
 \and
-Yen-Fu Wen\inst{2}
+Yean-Fu Wen\inst{2}
 \and
@@
 Graduate Institute of Information Management, National Taipei University, Taiwan
-}
+}}
 
@@
 
-We use two sets of integer reducer benchmarks to evaluate J-ReCoVer.
-The first set is collected from open repositories such as Github and Bitbucket.
+We collected benchmarks from open repositories such as Github and Bitbucket to evaluate J-ReCoVer.
 With the help of a search engine~\cite{searchcode} over those repositories, we collected 118 examples.
 J-ReCoVer is able to correctly analyze all but 3 of them.
-We also tried all 10 integer reducers described in verification literature~\cite{ChenHSW15,ChenSW16} and J-ReCoVer can handle all of them.
 
@@
 			Hadoop\\
-			Enviorment
+			Environment
 			\end{minipage}
@@
 				Program\\
-				Transform
+				Transform.
 				\end{minipage}
@@
 
-\section{Optimizations}
+\section{Optimization: Live Variable Analysis}
 \label{section:optimizations}
@@
 
-\subsection{Improving the precision of commutativity verification using data flow analysis}
-\label{section:opt1}
 We find that in many cases, Equation~(\ref{eq:commu}) is a condition that is too strong for the reducer to be commutative.
@@
 
-We perform a simple backward data flow analysis to collect all variables whose value may propagate to the output command after the loop execution.
+We perform a simple backward live variable analysis to collect all variables whose value may propagate to the output command after the loop execution.
+In our evaluation, the ratio of examples that our approach can successfully analyze is significantly increased from $6.8\%$ to $97.5\%$.
+The details of the evaluation can be found in Section~\ref{section:exp}.
+
+\hide{
 Without loss of generality, we assume there is only one output command after the loop.
@@
 E.g., if $X = \{x_1,x_4,y\}$, where $y\notin \{x_1,\ldots,x_k\}$, then $PosF(X)=\{1,4\}$.
-The use of Equation~(\ref{eq:commu2}) is critical to the success of our approach.
-In our evaluation, the ratio of examples that our approach can successfully analyze is significantly increased from $6.8\%$ to $97.5\%$.
-The details of the evaluation can be found in Section~\ref{section:exp}.
-
+The use of Equation~(\ref{eq:commu2}) is critical to the success of our approach. }
+\hide{
 \subsection{Computing the $F$ function using symbolic execution with an efficient data structure}
@@
 This data structure is efficient for strong symbolic values of reducer programs mainly for reason that the operations $+$ and $-$ are quite heavily used in such programs.
-Here we give a tiny example. Initially, $sv_x(x_0)=1$. After the commands $x:=x*x;x:=x+x$, we get $sv_x(x_0*x_0)=1$ and $sv_x(x_0*x_0)=2$, respectively.
+Here we give a tiny example. Initially, $sv_x(x_0)=1$. After the commands $x:=x*x;x:=x+x$, we get $sv_x(x_0*x_0)=1$ and $sv_x(x_0*x_0)=2$, respectively.}
 
@@
 We further remove those that cannot be compiled, those that are identical to each other, or those with non-numerical data types (e.g, string) and obtained $118$ programs as the final benchmarks.
-The second set of examples are those have been discussed in verification literature~\cite{ChenHSW15,ChenSW16}. This set is relatively small, we have only $10$ examples.
+
+\hide{The second set of examples are those have been discussed in verification literature~\cite{ChenHSW15,ChenSW16}. This set is relatively small, we have only $10$ examples.
 We also created a program that randomly generates reducer programs in order to test the scalability of J-ReCoVer.
-All benchmark examples can be found on the website of J-ReCoVer.
+All benchmark examples can be found on the website of J-ReCoVer.}
 
-Our evaluation answers the following two questions:
-\begin{itemize}
-	\item Is J-ReCoVer better than other competing tools?
-	\item Are the two optimizations proposed in Section~\ref{section:optimizations} critical and effective?
-\end{itemize}
-
-\subsection{Comparison with competing tools}
-As already pointed out in~\cite{ChenHSW15}, a reducer commutativity problem can be reduced to a reachability problem of a program.
-The examples in~\cite{ChenHSW15}, which includes \textsf{rangesum}\footnote{The sum of the second half of the input list.}, \textsf{avg}, \textsf{max}, \textsf{sep}\footnote{The number of occurrences of even numbers minus that of odd numbers.}, \textsf{sum}, are already included in SV-Comp~\cite{svcomp} (Software Verification Competition) benchmarks.
-Although those examples are tiny and simple, none of the software verifiers can verify all of those examples according to the 2018 results.
-In contrast, J-ReCoVer can verify all of them very efficiently.
-
-In Table~\ref{tab:svcomp}, the statistics of tools other than J-ReCoVer are taken directly from the SV-Comp~\cite{svcomp} website.
-Although the machines we used are different, the results of J-ReCoVer will not be much different if we run it on other machines.
-The other issue of this experiment is that in J-ReCoVer, we analyze the Java implementations and in SV-Comp they analyze the C implementations of the same functions.
-Since those functions to be analyzed are relatively simple, the syntactical difference between C and Java implementation is very small.
-The difference in the statistics mainly comes from the verification algorithm being used, not the programming language the reducer is written in.
-\begin{table}[t]
-\scalebox{0.95}{
-	\begin{tabular}{|l|l|l|l|l|l|l|}
-\hline
-		& \small CBMC\cite{cbmc2} 	& \small CPA-Seq\cite{cpachecker} & \small  ESBMC-kind\cite{esbmc} & \small  UAutomizer\cite{uautomizer} &\small  VeriAbs\cite{veriabs} &\small J-ReCoVer\\
-\hline
-\hline
-\small \textsf{rangesum}	& 0.96 	   & 30 		 & 2.2 				 &  10				 & 180       &9.9\\
-\hline
-\small \textsf{avg}			 &  TO      &  TO		  &  TO				 &  TO				 &  2          &10.9\\
-\hline
-\small \textsf{max}		    &  TO      &  TO		 &  TO				& TO				 &  7         &9.4\\
-\hline
-\small \textsf{sep}		     &  TO      &  TO		  &  TO				 & TO				 &  TO        &9.9\\
-\hline
-\small \textsf{sum}		    &  TO      &  TO		 &  TO				& TO				&  1.7       &9.9\\
-\hline
-	\end{tabular}
-}
-	\caption{SV-Comp 2018 results on reducer commutativity.
-For space reason, we only list the results of competitive tools in this table, which includes top three tools in the overall ranking and the reachability safety category.}\vspace{-1cm}
-	\label{tab:svcomp}
-\end{table}
-
-\subsection{The performance of J-ReCoVer with and without optimizations}
-
-For the optimization based on data flow analysis (Section~\ref{section:opt1}), we evaluate them based on real-world benchmark sets collected from open repositories (118 examples) and also literature (10 examples).
+For the optimization based on live variable analysis (Section~\ref{section:optimizations}), we evaluate them based on real-world benchmark sets collected from open repositories (118 examples).
 The difference between the version with and without this optimization is very clear.
 The results are presented in table~\ref{tab:opt1}.
-The first column is the result without optimization, i.e., using Equation~(\ref{eq:commu}) and the second column is the result with optimization, i.e., using Equation~(\ref{eq:commu2}).
-The precision of the analysis is improved from $6.8\%$ to $97.5\%$ for examples from open repositories and
-$10\%$ to $100\%$ for examples from literature.
+The first column is the result without optimization and the second column is the result with optimization.
+The precision of the analysis is improved from $6.8\%$ to $97.5\%$.
 There are only three cases that J-ReCoVer with data flow analysis cannot handle.
@@
 The reason is that when Soot converts a Java program to the Jimple format, it always uses a temporary variable to store the value of $\cur$ in the loop body (similar to the example in Figure~\ref{fig:reducer_opt}).
-We tried a simpler heuristics approach that only ignores the temporary variables and the result is not as good as using data flow analysis, because the values of the temporary variables often also propagate to other variables.
+We tried a simpler heuristics approach that only ignores the temporary variables and the result is not as good as using live variable analysis, because the values of the temporary variables often also propagate to other variables.
 \begin{table}[htb]
 	\centering
-	\begin{tabular}{|l|l|l|l|}
+	\begin{tabular}{|l|l|l|}
 		\hline
-		& &W/O optimization	& With optimization\\
+		&W/O optimization	& With optimization\\
 		\hline
 		\hline
-		\multirow{4}{*}{Open repositories}&Commutative& 0&106\\
-		\cline{2-4}
-		&Non-commutative&8&9\\
-		\cline{2-4}
-		&Unknown&110&3\\
-		\cline{2-4}
-		&Precision& 6.8\% & 97.5\%\\
+		Commutative& 0&106\\
 		\hline
+		Non-commutative&8&9\\
 		\hline
-		\multirow{4}{*}{Literatures}&Commutative& 0&9\\
-		\cline{2-4}
-		&Non-commutative&1&1\\
-		\cline{2-4}
-		&Unknown&9&0\\
-		\cline{2-4}
-		&Precision& 10\% & 100\%\\
+		Unknown&110&3\\
 		\hline
+		Precision& 6.8\% & 97.5\%\\
+		\hline
+
 	\end{tabular}
@@
 
-For the optimization based on improving the data structure used in symbolic execution (Section~\ref{section:opt2}), the main focus is on the improvement in scalability.
-So we use a random reducer program generator to produce examples of different sizes for this evaluation.
-For the generator, we can give as a parameter a tuple $(N,B,A)$, where $N$ is the number of variables, $B$ is the number of branch statements, and $A$ is the number of assignment statements.
-All assignments are in the form of $v_1 := v_2\odot v_3,\odot\in\{+,-,\times\}$ and all guards are in the form of $v_1 \circ v_2, \circ\in\{\geq, >,=, \neq, <,\leq \}$.
-The source code of the random generator is available at \url{https://github.com/spencerwuwu/benchmark-generator}.
-In the evaluation, we keep the ratio $N:B:A = 5:1:50$ and produce random reducers from $50$ lines $250$ lines.
-The most difficult cases might have $5$ to $6$ nested branches and $25$ integer variables in a reducer program.
-Those programs will be processed by Soot and translated to the Jimple format.
-In our experience, this will increase the number of lines by $20\%$ and variables by $11$ times.
-The results are presented in Figure~\ref{tab:opt2} in the form of a table and also a scatter plot.
-From there we can see that the optimization is helpful in improving the statistics in particular for larger programs (average, median execution time and the number of cases that cannot be finished within 300 seconds).
-Also from the scatter plot we can see that much more cases are solved with the new optimization.
-
-\begin{figure}[htb]
-
-	\begin{minipage}{0.6\textwidth}
-\begin{tabular}{|l|l|l|l|l|l|l|}
-	\hline
-	& \multicolumn{3}{c|}{\small W/O optimization}	& \multicolumn{3}{c|}{\small With optimization} \\
-	\hline
-	\small Lines & \small Average & \small Median & \small T/O & \small Average & \small Median & \small T/O \\
-	\hline
-	\hline
-	50	&	4.3	    &   3.7	&	0	&	4.7	&	3.6	&	0	\\
-	\hline
-	100	&	35.8	&	5.1&	4	&	37.2	&	4.5	&	6	\\
-	\hline
-	150	&	92.3	&	12.3&	13	&	74.0	&	7.5	&	9	\\
-	\hline
-	200	&	156.6	&	179.7&	25	&	138.1	&	48.2	&	25	\\
-	\hline
-	250	&	196.8	&	300.0&	35	&	175.9	&	274.9	&	30	\\
-	\hline
-\end{tabular}
-	\end{minipage}
-	\begin{minipage}{0.4\textwidth}
-\scalebox{0.6}{
-	\begin{tikzpicture}
-	\begin{axis}[%
-	xmin=-5, xmax=320,
-	ymin=-5, ymax=320,
-	xlabel={\Large with optimization},
-	ylabel={\Large w/o optimization}
-	]
-	\addplot[scatter,only marks,%
-	scatter src=explicit symbolic, mark=x]%
-	file {plot_data/optimize.data};
-	\draw (-100,-100) -- (400, 400);
-	\end{axis}
-	\end{tikzpicture}
-}
-	\end{minipage}
-
-	\caption{The improvement in scalability using a better data structure for symbolic execution.
-Each cell in the table is the summary of 60 randomly generated programs.
-In the table T/O stands for timeout and W/O is without.
-}
-	\label{tab:opt2}
-\end{figure}
-
-\hide{
-% Optimization compare graph
-Bounded model checking (BMC) is another approach to create the $F$ function in Equations~\ref{eq:commu} and \ref{eq:commu2}.
-Although we use symbolic execution in J-ReCoVer, it is interesting to see how good BMC works in checking the commutativity of reducer examples.
-In this evaluation, we use the same random reducer program generator.
-One major different difference is that for the BMC part, we directly generate the corresponding $F$ formula in the BMC-style without going through the Soot framework.
-So the number of variables in the formula is much less than the symbolic execution version.
-The results can be found in Table~\ref{tab:bmc}.
-For symbolic execution, we first use J-ReCoVer to generate the formula for evaluation.
-For BMC, the formula is directly generated by the random generator.
-In this evaluation, we see that the performance of using BMC is in general better, less timeout and lower average execution time, so we plan to also include a BMC engine in the next version.
-However, from the scatter plot we can see there are multiple cases that  can be solved using symbolic execution but are slower or even failed using BMC.
-So the best strategy should be keep the both engine and switch to another if one fails.
-
-\begin{table}[htb]
-
-\begin{minipage}{0.7\textwidth}
-	\begin{tabular}{|l||l|l| l||l|l|}
-\hline
-		Java& \multicolumn{2}{c|}{\small BMC}	& Jimple& \multicolumn{2}{c|}{\small Symbolic Exec.} \\
-\hline
-		\small Lines/Vars & \small Average & \small  \small T/O & Lines/Vars& \small Average & \small  \small T/O \\
-\hline
-\hline
-		50/5	&	0.1		&	0	&	72.9/65.7	&	0.1	&		0	\\
-\hline
-		100/10	&	0.8	&		0	&	130.0/120.9	&	3.1	&	0	\\
-\hline
-		150/15	&	28.5	&		1	&	186.9/175.6	&	36.2	&		1	\\
-\hline
-		200/20	&	76.2	&		2	&	243.8/230.6	&	89.7	&		5	\\
-\hline
-		250/25	&	84.4	&		5	&	300.6/285.9	&	172.5	&		10	\\
-\hline
-	\end{tabular}
-		\end{minipage}
-	\begin{minipage}{0.29\textwidth}
-\scalebox{0.5}{
-\begin{tikzpicture}
-\begin{axis}[%
-xmin=-5, xmax=320,
-ymin=-5, ymax=320,
-xlabel=Symbolic Exec.(s),
-ylabel=BMC(s)
-]
-\addplot[scatter,only marks,%
-scatter src=explicit symbolic, mark=x]%
-file {plot_data/bmc.data};
-\draw (-100,-100) -- (400, 400);
-\end{axis}
-\end{tikzpicture}
-}
-		\end{minipage}
-	\caption{The performance of using BMC and symbolic execution. Each table cell is the result obtained from 20 randomly generated cases.}
-	\label{tab:bmc}
-
-\end{table}
-}
-\section{Concluding Remarks}
-
-The current version of J-ReCoVer shares similar limitation with SMT-based software verification tools.
-We use SMT theory of integer and real number arithmetics as the reasoning tool.
-In this implementation, we do not handle more advanced data-types such as string and floating point.
-The problem of variable overflow is also not handled.
-In fact, if we consider all possible inputs of a reducer, almost all reducer programs will run into the problem of overflow.
-Even the basic example that computes the sum of all input values, overflow can occur when a list [\textsf{MaxInt};\textsf{MaxInt}] is used as the input.
-Nevertheless, such example might not be of the interests of MapReduce programmers, who usually care only about the data set they want to analyze.
-We are planning to build another tool to estimate a safe bound of data size such that overflow will not occur if the data size is within the bound.
-The programmer can then check if their data set fits in the computed bound and switch to use larger data types in the program when needed.
-So overflow will not occur in the data set of interests.
-
-We believe that simpler but more restricted domain specific language/frameworks will be the trend for the development of parallel programs.
-It lowers the barrier for writing correct yet efficient parallel program.
-Complicated issues such as fault tolerance, load balancing, and security are handled by the frameworks automatically.
-Programmers only need to focus on their program logic.
-So experts in other domains such as data science and machine learning can enjoy the power of parallel data processing with much less efforts.
-Many of their applications do not need the full power of message passing programming.
-So they do not need to build their programs on top of traditional means such as MPI or socket programming.
-MapReduce framework is a pioneer in this kind of domain specific language/frameworks for data parallel computation.
-Its successors such as Spark, Flink, Beam, and Google Cloud Dataflow, still share many features of its design.
-We believe the design of J-ReCoVer will lead to significant impacts to the verification/testing of programs under such frameworks.
-
 \bibliographystyle{splncs-sorted}

### 2019-06-18 draft.tex
with fullpage and times on

@@
 \usepackage{times}
+\usepackage{fullpage}
+
 %\usepackage{cancel}
@@
 \begin{figure}[h]
-
+\centering
 	\scalebox{0.9}{
@@
 
-We explain why that the validity of Equation~(\ref{eq:commu}) is sufficient to prove the commutativity of the reducer $s_1;\rloop\{s_2\};s_3$.
+We explain why that the validity of Equation~(\ref{eq:commu}) is sufficient to prove the reducer $s_1;\rloop\{s_2\};s_3$ commutative.
 Notice that $s_1$ does not read from the input (assumed at the beginning of this subsection).
@@
 For the general case, we first rewrite the $s_1$ part of the reducer $s_1;\rloop\{s_2\};s_3$ to the form
-$s'_0;x_{i_1}{:=} \cur;s'_1.\ldots x_{i_{m}}{:=}\cur;s'_m$, where $\cur$ never occur in $s'_0,s'_1,\ldots, s'_m$.
+$$s'_0;x_{i_1}{:=} \cur;s'_1.\ldots x_{i_{m}}{:=}\cur;s'_m$$, where $\cur$ never occur in $s'_0,s'_1,\ldots, s'_m$.
 Then we produce the reducer in Figure~\ref{fig:general_program_transformation}, which is an over-approximation of the original reducer for the same reason: the case that $s=1$ has the same output sequence to the original reducer and when $s\neq 1$, it may produce additional behavior.

### 2019-06-20 draft.tex
with fullpage and times on
Switched off the full page mode
some shorten (unfinished)

@@
 \usepackage{times}
-\usepackage{fullpage}
+% \usepackage{fullpage}
 
@@
 If $R'$ and $R$ are equivalent, using the fact that all permutations of a list can be obtained by swapping consecutive list elements finitely many times\footnote{Here is an example to produce [3;2;5;1;4] from [1;2;3;4;5] by swapping consecutive elements: [\textbf{1};\textbf{2};3;4;5] $\rightarrow$ [2;\textbf{1};\textbf{3};4;5] $\rightarrow$ [2;3;1;\textbf{4};\textbf{5}]$\rightarrow$ [2;3;\textbf{1};\textbf{5};4]$\rightarrow$ [\textbf{2};\textbf{3};5;1;4]$\rightarrow$ [3;2;5;1;4].}, $R$ can be proved to be commutative.
-There is a series of research results on program equivalence checking (or closely related topics such as regression verification and translation validation)~\cite{Pnueli:1998:TV,symdiff,fedyukovich2015automated,sharma2013data,godlin2009regression,fedyukovich2016property,felsing2014automating,KieferKlebanovUlbrich2017,lahiri2013differential,grossman2017verifying,barthe2011relational,KlebanovRuemmerUlbrich2017}.
+There is a series of research results on program equivalence checking (or closely related topics such as regression verification and translation validation), to name a few~\cite{Pnueli:1998:TV,fedyukovich2015automated,barthe2011relational,KlebanovRuemmerUlbrich2017}.
 At a high level, checking equivalence of two programs $P$ and $P'$ can be reduced to a sequential verification problem by executing $P'$ after $P$ and at the end checking if they always have the same outputs.
@@
 One main motivation of commutativity analysis is to reduce the verification problem of a concurrent program to a sequential one.
-There are several pieces of research sharing the similar motivation, e.g., the concept of \emph{robustness} of event-driven asynchronous programs~\cite{ahmed2017:robustness}, the \emph{robustness} of program running under relaxed memory model~\cite{ahmed2013:robustness,AbdullaACLR13,AbdullaACLR12}, and \emph{synchronizability} of communicating finite state machines~\cite{FinkelL17,basu2012synchronizability,basu2011choreography}.
+There are several pieces of research sharing the similar motivation, e.g., the concept of \emph{robustness} of event-driven asynchronous programs~\cite{ahmed2017:robustness} and program running under relaxed memory model~\cite{ahmed2013:robustness,AbdullaACLR13,AbdullaACLR12}.
 However, their computation models are quite different from that of reducers and hence the result cannot be directly applied.
@@
 
+\hide{
 \begin{equation*}
@@
 \end{array}
-\end{equation*}
-
-Here any $v\in \Var$ is a variable and any $c \in \Z$ is a constant integer value.
-An \emph{integer expression} in $\Exp$ can be either a variable, constant value, a call to the $\cur$ function that reads and consumes an input value of the reducer, their combinations over basic arithmetic operations, or a non-deterministically chosen integer value $*$.
-A \emph{guard} in $\Grd$ can be a comparison between two expressions or boolean combinations of several guards.
-A \emph{command} in $\Cmd$ can be an assignment, a branch statement, concatenation of a sequence of commands, or $out(v)$ that outputs the value of $v$.
-A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$, and $s_2$ is assumed to have at most one $\cur$ expression in each \emph{branch}\footnote{We define a \emph{branch} of a command $s$ as a sequence obtained by replacing every branch statement $\ite{g}{s_1}{s_2}$ in $s$ with either $(g); s_1$ or $(not\ g) ;s_2$.
-For example, the loop body of Figure~\ref{fig:reducer_example}(a) has two branches $t:=\cur; (t>0); m:=t$ and $t:=\cur;(not\ t>0)$ }.
-According to our observation over hundreds  of reducer programs in open repositories, reducer programs are almost always in this form.
-The $\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly until the entire input list is consumed.
-A few examples of reducer programs in this model can be found in Figure~\ref{fig:reducer_example}.
-
-Some reducer uses two loops to compute the output.
-For example, for calculating standard deviation, one first computes the average of inputs and then uses it to compute the standard deviation.
-In that case, we can still verify the reducer by first partitioning it into two reducers and then verifying them separately.
-One reducer computes the average (Figure~\ref{fig:reducer_example}(b)) and the other reducer uses a non-deterministic value to over-approximate the computed average ($a := *$) (Figure~\ref{fig:reducer_example}(c)).
-The reducer in Figure~\ref{fig:reducer_example}(c) ``over-approximates''  all possible outputs of the standard deviation computation; it computes an output even if $a$ is not the average of inputs.
-However, the reducer is still commutative and its commutativity verification can still be done.
-
-\begin{figure}
+\end{equation*}}
+\begin{wrapfigure}{r}{3cm}
+	\hide{
 		\begin{minipage}{0.32\textwidth}
@@
 		\hspace{-0.5cm}
+	}
 	\begin{minipage}{0.3\textwidth}
@@
 		\end{algorithm}
-		\caption*{(b) average}
 	\end{minipage}
+	\hide{
 		\begin{minipage}{0.4\textwidth}
@@
 		\end{minipage}
-	\caption{Example of reducer programs}
+	}
+	\caption{Average}
 	\label{fig:reducer_example}
-\end{figure}
+\end{wrapfigure}
+Let $\Var$ be the set of variables and $\Z$ the set of integers.
+An \emph{integer expression} in $\Exp$ can be either a variable, constant value, a call to the $\cur$ function that reads and consumes an input value of the reducer, their combinations over basic arithmetic operations, or a non-deterministically chosen integer value $*$.
 
-In the next section, we give a brief overview of J-ReCoVer,  our tool for reducer commutativity verification.
+A \emph{command} in $\Cmd$ can be an assignment, a branch statement, concatenation of a sequence of commands, or $out(v)$ that outputs the value of $v$.
+A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$, and $s_2$ is assumed to have at most one $\cur$ expression in each \emph{branch}\footnote{We define a \emph{branch} of a command $s$ as a sequence obtained by replacing every branch statement $\ite{g}{s_1}{s_2}$ in $s$ with either $(g); s_1$ or $(not\ g) ;s_2$.
+For example, the loop body of Figure~\ref{fig:reducer_example}(a) has two branches $t:=\cur; (t>0); m:=t$ and $t:=\cur;(not\ t>0)$ }.
+According to our observation over hundreds  of reducer programs in open repositories, reducer programs are almost always in this form.
+The $\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly until the entire input list is consumed.
+One example can be found in Figure~\ref{fig:reducer_example}.
+
+\hide{
+Some reducer uses two loops to compute the output.
+For example, for calculating standard deviation, one first computes the average of inputs and then uses it to compute the standard deviation.
+In that case, we can still verify the reducer by first partitioning it into two reducers and then verifying them separately.
+One reducer computes the average (Figure~\ref{fig:reducer_example}(b)) and the other reducer uses a non-deterministic value to over-approximate the computed average ($a := *$) (Figure~\ref{fig:reducer_example}(c)).
+The reducer in Figure~\ref{fig:reducer_example}(c) ``over-approximates''  all possible outputs of the standard deviation computation; it computes an output even if $a$ is not the average of inputs.
+However, the reducer is still commutative and its commutativity verification can still be done.
+
+In the next section, we give a brief overview of J-ReCoVer,  our tool for reducer commutativity verification.}
 
@@
 
-\begin{figure}[h]
+\textbf{The Preprocessor component} first compiles a reducer program to bytecode and use the tool Soot~\cite{soot} to further convert it to the so-called ``Jimple'' format, which is an intermediate language that is designed to simplify the analysis of Java programs.
+Under the Hadoop MapReduce framework, the permutation of the input is handled by the scheduler/shuffler component and is affected by things like network latency, which is not controllable by programmers.
+In order to deal with this issue, we wrote our own dummy Hadoop environment for the reducer as a part of the Preprocessor component so that the input order of the reducer is now controlled by J-ReCoVer.
+Finally, we perform in the Preprocessor some program transformation tasks to simplify the analysis.
+For example, we convert all output commands $out(e)$ inside loops to a special assignment (will be explained in Section~\ref{sec:program_trans1} and~\ref{sec:program_trans2}).
+
+\begin{wrapfigure}{r}{7cm}
+	\vspace{-0.5cm}
 \centering
-	\scalebox{0.9}{
+	\scalebox{0.7}{
 		\begin{tikzpicture}
@@
 		%J-ReCoVer
-		\node[draw=red!30, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=9cm,fill=red!10,minimum height=8cm] (jrecover) at (5.5,0.8) {};
-		\node at (5.5,0.4) {\textbf{J-ReCoVer}};
+		\node[draw=red!30, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=8cm,fill=red!10,minimum height=8cm] (jrecover) at (5,0.8) {};
+		\node at (5,0.4) {\textbf{J-ReCoVer}};
 
 		%JAVA reducer
-		\node[draw=yellow!80, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=1cm,fill=yellow!20,minimum height=4cm] (reducer) at (0,-1.6) {};
-		\node[rotate=270, align = center] at (0,-3.6) {Java Reducer};
+		\node[draw=yellow!80, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=0.6cm,fill=yellow!20,minimum height=4cm] (reducer) at (0.5,-1.6) {};
+		\node[rotate=270, align = center] at (0.5,-3.6) {Java Reducer};
 
@@
 		%JProver
-		\node[draw=blue!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=3cm,fill=blue!20,minimum height=5.5cm] (prover) at (7,0) {};
-		\node[] at (7,-0.4) {Prover};
+		\node[draw=blue!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=3cm,fill=blue!20,minimum height=5.5cm] (prover) at (6.5,0) {};
+		\node[] at (6.5,-0.4) {Prover};
 
 		%JProver->Technologies
-		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (7,-1) {};
+		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (6.5,-1) {};
 
-		\node at (7,-1.6) {
+		\node at (6.5,-1.6) {
 			\begin{minipage}[t]{0.222\textwidth}
@@
 
-		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (7,-2.5) {};
+		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (6.5,-2.5) {};
 
-		\node at (7,-3.1) {
+		\node at (6.5,-3.1) {
 			\begin{minipage}[t]{0.222\textwidth}
@@
 
-		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (7,-4.) {};
+		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (6.5,-4.) {};
 
-		\node at (7,-4.6) {
+		\node at (6.5,-4.6) {
 			\begin{minipage}[t]{0.222\textwidth}
@@
 		%JBugFinder
-		\node[draw=blue!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=3cm,fill=blue!20,minimum height=1cm] (learner) at (7,-6) {};
-		\node[] at (7,-6.5) {BugFinder};
+		\node[draw=blue!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=3cm,fill=blue!20,minimum height=0.5cm] (learner) at (6.5,-6.2) {};
+		\node[] at (6.5,-6.5) {BugFinder};
 
@@
 
-		\node at (12,-1) {
+		\node[rotate=270, align = center] at (9.5,-1) {
 			Commutative
@@
 
-		\node at (12,-3.5) {
+		\node[rotate=270, align = center] at (9.5,-3.5) {
 			Unknown
@@
 
-		\node at (12,-6.5) {
+		\node[rotate=270, align = center] at (9.6,-6) {
 			\begin{minipage}[t]{0.25\textwidth}
@@
 			Non-Commutative	 \\
-			+\\
-			Counterexample
+			+ Counterexample
 			\end{minipage}
@@
 
-		\draw [->] (8.5,-6.8) -- (10.5,-6.8) ;
-		\draw [->] (8.5,-1) -- (10.5,-1) ;
-		\draw [-] (8.5,-6.2) -- (9.5,-6.2) --(9.5,-3.5);
-		\draw [->] (8.5,-3.5) -- (10.5,-3.5) ;
+		\draw [->] (8,-6.6) -- (9.2,-6.6) ;
+		\draw [->] (8,-1) -- (9.2,-1) ;
+		\draw [-] (8,-6.3) -- (8.5,-6.3) --(8.5,-3.5);
+		\draw [->] (8,-3.5) -- (9.2,-3.5) ;
 
-		\draw [->] (4.5,-3) -- (5.5,-3) ;
-		\draw [->] (4.5,-6.5) -- (5.5,-6.5) ;
+		\draw [->] (4.5,-3) -- (5,-3) ;
+		\draw [->] (4.5,-6.5) -- (5,-6.5) ;
 
-		\draw [->] (0.5,-4) -- (1.5,-4) ;
+		\draw [->] (0.8,-4) -- (1.5,-4) ;
 
@@
 	}
+		\vspace{-1cm}
 	\caption{Overview of the J-ReCoVer Tool. }\label{fig:overview-jrecover}
-\end{figure}
+		\vspace{-0.8cm}
 
-\textbf{The Preprocessor component} first compiles a reducer program to bytecode and use the tool Soot~\cite{soot} to further convert it to the so-called ``Jimple'' format, which is an intermediate language that is designed to simplify the analysis of Java programs.
-Under the Hadoop MapReduce framework, the permutation of the input is handled by the scheduler/shuffler component and is affected by things like network latency, which is not controllable by programmers.
-In order to deal with this issue, we wrote our own dummy Hadoop environment for the reducer as a part of the Preprocessor component so that the input order of the reducer is now controlled by J-ReCoVer.
-Finally, we perform in the Preprocessor some program transformation tasks to simplify the analysis.
-For example, we convert all output commands $out(e)$ inside loops to a special assignment (will be explained in Section~\ref{sec:program_trans1} and~\ref{sec:program_trans2}).
+\end{wrapfigure}
 
@@
 
-\begin{figure}[htb]
+\begin{wrapfigure}{r}{9cm}
 	\centering
@@
 	\label{fig:general_program_transformation}
-\end{figure}
+\end{wrapfigure}
 

### 2019-06-21 draft.tex
emty authors out and different (the math font will be a little more concise then with times)
apply some suggestions from Tomas

@@
 \title{\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier}
-
+\author{}
+\institute{}
 \hide{
@@
 We implement all these heuristics as a tool called J-ReCoVer (Java Reducer Commutativity Verifier), which is available at~\verb|http://jrecover.iis.sinica.edu.tw|.
-
 We collected benchmarks from open repositories such as Github and Bitbucket to evaluate J-ReCoVer.
-With the help of a search engine~\cite{searchcode} over those repositories, we collected 118 examples.
+With the help of a search engine \emph{searchcode.com} over those repositories, we collected 118 examples.
 J-ReCoVer is able to correctly analyze all but 3 of them.
@@
 \begin{wrapfigure}{r}{3cm}
+		\vspace{-0.8cm}
 	\hide{
@@
 	\caption{Average}
+	\vspace{-0.8cm}
 	\label{fig:reducer_example}
@@
 An \emph{integer expression} in $\Exp$ can be either a variable, constant value, a call to the $\cur$ function that reads and consumes an input value of the reducer, their combinations over basic arithmetic operations, or a non-deterministically chosen integer value $*$.
-
 A \emph{command} in $\Cmd$ can be an assignment, a branch statement, concatenation of a sequence of commands, or $out(v)$ that outputs the value of $v$.
@@
 
-\hide{
 Some reducer uses two loops to compute the output.
@@
 In that case, we can still verify the reducer by first partitioning it into two reducers and then verifying them separately.
-One reducer computes the average (Figure~\ref{fig:reducer_example}(b)) and the other reducer uses a non-deterministic value to over-approximate the computed average ($a := *$) (Figure~\ref{fig:reducer_example}(c)).
-The reducer in Figure~\ref{fig:reducer_example}(c) ``over-approximates''  all possible outputs of the standard deviation computation; it computes an output even if $a$ is not the average of inputs.
-However, the reducer is still commutative and its commutativity verification can still be done.
-
-In the next section, we give a brief overview of J-ReCoVer,  our tool for reducer commutativity verification.}
+One reducer computes the average and the other reducer uses a non-deterministic value to over-approximate the computed average ($a := *$) that will be used in standard deivation.
+The second reducer ``over-approximates''  all possible outputs of the standard deviation computation; it computes an output even if $a$ is not the average of inputs.
+However, this reducer is still commutative and its commutativity verification can still be done.
 
@@
 
-\textbf{The Preprocessor component} first compiles a reducer program to bytecode and use the tool Soot~\cite{soot} to further convert it to the so-called ``Jimple'' format, which is an intermediate language that is designed to simplify the analysis of Java programs.
+\textbf{The Preprocessor component} first compiles a reducer program to bytecode and use the tool Soot to further convert it to the so-called ``Jimple'' format, which is an intermediate language that is designed to simplify the analysis of Java programs.
 Under the Hadoop MapReduce framework, the permutation of the input is handled by the scheduler/shuffler component and is affected by things like network latency, which is not controllable by programmers.
@@
 		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1cm] (soot) at (3.2,-2) {};
-		\node at (3.2,-2.6) {Soot~\cite{soot}};
+		\node at (3.2,-2.6) {Soot};
 
@@
 			Z3 SMT \\
-			Solver~\cite{z3}
+			Solver
 			\end{minipage}
@@
 At a high level, we check equivalence between a reducer program and its variant that has two consecutive inputs swapped.
-We show that this can be reduced to an SMT problem and give it to the SMT solver Z3~\cite{z3} for solving.
+We show that this can be reduced to an SMT problem and give it to the SMT solver Z3 for solving.
 In case that Z3 proved the formula unsatisfiable, we know that swapping any two consecutive inputs of the reducer will not change its output.
@@
 \label{sec:program_trans1}
-J-ReCoVer  first generates a new variable $v_{out_k}$ for the $k$-th output command $out(e)$ inside $s_2$ and replace the $out(e)$ command with an assignment $v_{out_k}:=e$.
-Notice that the value of $v_{out_k}$ stays the same from the point it has been assigned a value.
-If the values of $v_{out_k}$ are the same for all permutations of input lists at the end of $s_2$, we know that the reducer is commutative w.r.t.
-to all output values produced inside the loop body $s_2$.
+Recall that the reducer program can perform the ouput command $out(e)$ inside the loop body $s_2$.
+In this case, we remember the output value in a fresh variable $v$ and replace the $out(e)$ command with an assignment $v:=e$.
+Notice that the value of $v$ stays the same from the point it has been assigned a value.
+If the values of $v$ are the same for all permutations of input lists at the end of $s_2$, we know that the reducer is commutative w.r.t. to all output values produced inside the loop body $s_2$.
 
@@
 
+\hide{
+
 In the example of ``average'', the values of $s$ and $c$ are the same no matter the reducer first reads $n_1$ and then $n_2$ or reads the two values in the swapped order.
@@
 Similar to the case of $s_1$, $s_3$ does not read from the input and hence the execution of $s_3$ is deterministic.
-It follows that for all permutations of inputs, the reducer outputs the same sequence of values.
+It follows that for all permutations of inputs, the reducer outputs the same sequence of values.}
 
@@
 
-\section{Optimization: Live Variable Analysis}
+\subsection{Optimization: Live Variable Analysis}
 \label{section:optimizations}
@@
 We find that in many cases, Equation~(\ref{eq:commu}) is a condition that is too strong for the reducer to be commutative.
-For instance, consider the example in Figure~\ref{fig:reducer_opt}.
+For instance, consider a simple example.
 In the loop body, the input is first stored in a variable $t$ and then added to $s$.
-In this case, the $F$ function returns the updated values of both $s$ and $t$ after the execution of the loop body.
-Observe that
+After the loop, output the value of $s$.
+In this case, the $F$ function returns the updated values of both $s$ and $t$ after the execution of the loop body. Observe that
 $F(c_1, F(c_2,s,t)) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t)) = (c_1+c_2, c_2)$.
@@
 
+\hide{
 \begin{figure}[hbt]
@@
 Recall that the first program transformation task uses a set of variables $V_2=\{v_{out_k} \mid k \in [1,l]\}$, where $l$ is the number of output commands occurred in $s_2$, to collect output values occurred in the loop body $s_2$.
-The set $V_2$ is exactly the set of variables that will affect the output inside the loop.
+The set $V_2$ is exactly the set of variables that will affect the output inside the loop.}
 
@@
 After the two executions of $u:=u+u$, the value of $u$ changes to $x_0+y_0+x_0+y_0$ and $x_0+y_0+x_0+y_0+x_0+y_0+x_0+y_0$, respectively.
-One way to alleviate the problem is to apply formula simplification algorithms, e.g., those implemented in Z3~\cite{z3}.
+One way to alleviate the problem is to apply formula simplification algorithms, e.g., those implemented in Z3.
 Here we propose in a very simple alternative solution that works quite well in our reducer benchmarks.
@@
 \label{section:exp}
-J-ReCoVer is implemented in Java and built on top of Soot~\cite{soot} 2.5.0 and Z3~\cite{z3} 4.7.1.
+J-ReCoVer is implemented in Java and built on top of Soot 2.5.0 and Z3 4.7.1.
 We run J-ReCoVer on a virtual machine running on a server with AMD Opteron 6376 CPU.
@@
 In order to properly evaluate the performance of J-ReCoVer, we collect benchmark example from two different sources.
-First, we use the search engine \emph{searchcode.com}~\cite{searchcode} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''.
+First, we use the search engine \emph{searchcode.com} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''.
 Since there is an upper bound on the number of results returned from the search engine, we add different search filters in order to get more data.

### 2019-06-21 draft.tex
apply some suggestions from Tomas

@@
 \usepackage{amssymb}
-\usepackage{times}
+%\usepackage{times}
+
+%here are alternatives for the times package 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\usepackage{times}
+%-------
+%\usepackage{pslatex}
+%-------
+\usepackage{mathptmx}
+\usepackage{mathptm}
+%-------
+%\usepackage{mathtools}
+%\usepackage{newtxmath} 
+%\usepackage{newtxtext}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % \usepackage{fullpage}
@@
 }}
+\author{}
+\institute{}
 
@@
 There are several advantages for a reducer being commutative, e.g., the verification problem of a MapReduce program can be reduced to the problem of verifying a sequential program.
-In this paper, we propose effective heuristics for reducer commutativity analysis and implement them as a tool J-ReCoVer (Java Reducer Commutativity Verifier), which is the first tool that is specialized in checking reducer commutativity.
-Experimental results over 128 benchmark examples collected from literature and open repositories are very positive; J-ReCoVer correctly handles over 97\% of them.
+We present a tool J-ReCoVer (Java Reducer Commutativity Verifier) that implements effective heuristics for reducer commutativity analysis.
+J-ReCoVer is the first tool that is specialized in checking reducer commutativity.
+Experimental results over 118 benchmark examples collected from open repositories are very positive; J-ReCoVer correctly handles over 97\% of them.
 
@@
 
-On the other hand, in many cases, the non-commutative behavior of a reducer is the source of very tricky bugs.
+On the other hand, the non-commutative behavior of a reducer is often the source of very tricky bugs.
 A study conducted by Microsoft investigated the commutativity problem of $508$ reducers running on their MapReduce server~\cite{xiao14mr}.
@@
 \label{section:integer-reducers}
-We use $\Z$ to denote the set of all integers and $[n,m]$ to denote the set of integers $\{k\mid n \leq k\leq m\}$.
-We lift the equality $=$ operation to tuples in the standard way.
-Let $S\subseteq [1,k]$, the equality $(v_1,\ldots,v_k)=_{S} (v'_1,\ldots,v'_k)$ between tuples holds if and only if $\bigwedge_{i\in S} v_i=v'_i$.
-For presentation purpose, we describe a highly simplified model to characterize the essence of reducers. The model allows to describe the computation of reducers and investigate their commutativity.
+We use $[n,m]$ to denote the set of integers $\{k\mid n \leq k\leq m\}$ and lift the equality $=$ operation to tuples in the standard way.
 
@@
 \end{wrapfigure}
-Let $\Var$ be the set of variables and $\Z$ the set of integers.
+For presentation purpose, we describe a highly simplified language to characterize the essence of reducers.
+The model allows to describe the computation of reducers and investigate their commutativity.
+Let $\Var$ be the set of variables.
 An \emph{integer expression} in $\Exp$ can be either a variable, constant value, a call to the $\cur$ function that reads and consumes an input value of the reducer, their combinations over basic arithmetic operations, or a non-deterministically chosen integer value $*$.
@@
 The $\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly until the entire input list is consumed.
-One example can be found in Figure~\ref{fig:reducer_example}.
+An example is in Figure~\ref{fig:reducer_example}.
 
@@
 In that case, we can still verify the reducer by first partitioning it into two reducers and then verifying them separately.
-One reducer computes the average and the other reducer uses a non-deterministic value to over-approximate the computed average ($a := *$) that will be used in standard deivation.
+One reducer computes the average and the other reducer assigns a non-deterministic value to the variable $a$ that is intended to store the computed average ($a := *$).
+The variable $a$ will be used in the computation of standard deivation.
 The second reducer ``over-approximates''  all possible outputs of the standard deviation computation; it computes an output even if $a$ is not the average of inputs.
@@
 			\centering
-			Symbolic \\
-			Execution
+			Equation~\ref{eq:commu}
 			\end{minipage}
@@
 			\centering
-			Data Flow \\
+			Live Variable \\
 			Analysis
@@
 In this case,  J-ReCoVer stops and reports that the reducer is commutative.
-However, if we run the approach in a naive manner, it does not scale to large programs and is very imprecise.
-We will introduce two critical optimizations that enable the proposed approach working for real-world examples in Section~\ref{section:optimizations}: a data flow analysis to extract critical variables and an improved symbolic execution algorithm to generate SMT formulae.
-More details of the algorithms used in the Preprocessor and the Prover components will be explained in Section~\ref{sec:preprocessor_prover} and the optimizations will be introduced in~\ref{section:optimizations}.
 
@@
 Before entering the Prover component, the Preprocessor first performs a few program transformation tasks to simplify the verification task.
-We assume the reducer $s_1;\rloop\{s_2\};s_3$ is given.
-The section begins with an introduction to the first program transformation task (Section~\ref{sec:program_trans1}) that handles the case when $s_2$ contains $out$ commands.
+Assume a reducer $s_1;\rloop\{s_2\};s_3$ is given.
+The section begins with an introduction to the first program transformation task (Section~\ref{sec:program_trans1}) that handles the case when the loop body $s_2$ contains $out$ commands.
 The output of the first transformation task is a commutativity-equivalent reducer program where $out$ does not occur in $s_2$.
@@
 The construction of $F$ from $s_2$ can be done in the standard way.
-We will introduce a more efficient data structure for the construction in Section~\ref{section:optimizations}.
 We check if the formula below is valid for all possible values of $n_1,n_2, x_1,x_2,\ldots,x_k$.
@@
 
-Using the reducer that computes average (Figure~\ref{fig:reducer_example}(b)) as an example.
+Using the reducer that computes average (Figure~\ref{fig:reducer_example}) as an example.
 It has two variables $s$ and $c$.
 It is not difficult to compute that $F_{average}(n,s,c)=(s+n, c+1)$.
-In this case, the corresponding Equation~(\ref{eq:commu}) is valid because $F_{average}(n_1, F_{average}(n_2,s,c)) =F_{average}(n_1, s+n_2, c+1)= (s+n_1+n_2,c+2)=F_{average}(n_2, s+n_1, c+1)=F_{average}(n_2, F_{average}(n_1,s,c))$.
+The corresponding Equation~(\ref{eq:commu}) is valid because $F_{average}(n_1, F_{average}(n_2,s,c)) =F_{average}(n_1, s+n_2, c+1)= (s+n_1+n_2,c+2)=F_{average}(n_2, s+n_1, c+1)=F_{average}(n_2, F_{average}(n_1,s,c))$.
 
@@
 
+\begin{wrapfigure}{r}{3.5cm}
+	\vspace{-1cm}
+	\begin{algorithm}[H]
+	\;\;$m := \cur + 10$; \;
+	\Loop{}{
+		$t:=\cur$\;
+		\uIf{ $t> m$}{
+			$m := t$ \;
+		}
+	};
+	$out(m)$\;\;
+\end{algorithm}
+	\vspace{-0.8cm}
+\caption{Reducer max$^+$}
+	\vspace{-0.8cm}
+	\label{fig:reducer_max1}
+\end{wrapfigure}
+
+\hide{	
 \begin{figure}[t]
@@
 \end{figure}
+}
 
 In real-world examples, it is often that the $s_1$ part of the reducer also reads from the input.
-In the example in Figure~\ref{fig:reducer_max}(a), the reducer program remembers the first input value in the variable $m$, increases its value by 10, and then updates its value to bigger ones if any occurs in the loop.
+In the example in Figure~\ref{fig:reducer_max1}, the reducer program remembers the first input value in the variable $m$, increases its value by 10, and then updates its value to bigger ones if any occurs in the loop.
 The corresponding Equation~(\ref{eq:commu}) is valid in this case.
@@
 
+\begin{wrapfigure}{r}{5.3cm}
+	\vspace{-1cm}
+	\begin{algorithm}[H]
+		$s:=1;$\;
+		\Loop{}{
+			\uIf{$s=1$}{$m := \cur + 10; s:= 2$}
+			\uElse{
+				$t:=\cur$\;
+				\uIf{ $t > m$}{
+					$m := t$ \;
+				}
+			}
+		};
+		$out(m)$
+	\end{algorithm}	
+	\vspace{-0.4cm}
+	\caption{Reducer max$^{+\mathtt{fix}}$}
+	\vspace{-0.4cm}
+	\label{fig:reducer_max2}
+\end{wrapfigure}
 We handle the problem again by program transformation.
-To deal with the example in Figure~\ref{fig:reducer_max}(a), we move the prefix $s_1$ into the loop body and use a new variable $s$ to force that the execution of $s_1$ is always before the original loop body.
-The result after the transformation is demonstrated in Figure~\ref{fig:reducer_max}(b).
+To deal with the example in Figure~\ref{fig:reducer_max1}, we move the prefix $s_1$ into the loop body and use a new variable $s$ to force that the execution of $s_1$ is always before the original loop body.
+The result after the transformation is demonstrated in Figure~\ref{fig:reducer_max2}.
 The new reducer program over-approximates all possible inputs/outputs of the original one.
@@
 
+\hide{
 \begin{wrapfigure}{r}{9cm}
@@
 	\label{fig:general_program_transformation}
-\end{wrapfigure}
+\end{wrapfigure}}
 
-For the general case, we first rewrite the $s_1$ part of the reducer $s_1;\rloop\{s_2\};s_3$ to the form
+This approach can be easily generalize to the situation where $\cur$ occurs multiple times in $s_1$. We first rewrite the $s_1$ part of the reducer $s_1;\rloop\{s_2\};s_3$ to the form
 $$s'_0;x_{i_1}{:=} \cur;s'_1.\ldots x_{i_{m}}{:=}\cur;s'_m$$, where $\cur$ never occur in $s'_0,s'_1,\ldots, s'_m$.
-Then we produce the reducer in Figure~\ref{fig:general_program_transformation}, which is an over-approximation of the original reducer for the same reason: the case that $s=1$ has the same output sequence to the original reducer and when $s\neq 1$, it may produce additional behavior.
-Observe that the reducer in Figure~\ref{fig:general_program_transformation} satisfies all assumptions required for the Prover.
-Hence the Equation~(\ref{eq:commu}) can then be applied to prove its commutativity.
+Then uses a branch statement with garud $s=j$ to handle the case $x_{i_j} := \cur; s'_j; s:=s+1$, for all $j \in [1,m]$.
 

### 2019-06-21 draft.tex
apply some suggestions from Tomas

@@
 The approximation allows a much more efficient yet precise enough commutativity analysis.
+Our approach uses some form of sequentialization which is, however, specialized for the reducer commutativity problem and different from the sequentialisation approaches proposed for verifying common multithreaded programs\cite{XXX}: indeed, in MapReduce programs there is no notion of threads and context switches.
 
@@
 Some reducer uses two loops to compute the output.
-For example, for calculating standard deviation, one first computes the average of inputs and then uses it to compute the standard deviation.
+For example, for calculating standard deviation, one first computes the average of inputs and then uses it to compute the final result.
 In that case, we can still verify the reducer by first partitioning it into two reducers and then verifying them separately.
-One reducer computes the average and the other reducer assigns a non-deterministic value to the variable $a$ that is intended to store the computed average ($a := *$).
-The variable $a$ will be used in the computation of standard deivation.
-The second reducer ``over-approximates''  all possible outputs of the standard deviation computation; it computes an output even if $a$ is not the average of inputs.
+One reducer computes the average and the other reducer performs the rest of the computation.
+The second reducer replaces the average with a non-deterministic value and thus ``over-approximates''  all possible outputs of the standard deviation computation; it computes an output for all possible ``average'' value.
 However, this reducer is still commutative and its commutativity verification can still be done.
@@
 Finally, we perform in the Preprocessor some program transformation tasks to simplify the analysis.
-For example, we convert all output commands $out(e)$ inside loops to a special assignment (will be explained in Section~\ref{sec:program_trans1} and~\ref{sec:program_trans2}).
+For example, we convert all output commands $out(e)$ inside loops to a special assignment (will be explained in Section~\ref{sec:program_trans1}).
 
@@
 
-\textbf{The BugFinder component} randomly generated 1500 pairs of lists.
+\textbf{The BugFinder component} randomly generates pairs of lists.
 The lists in a pair are permutations of each other.
-A concrete counterexample is reported if inputting any pair of lists from the 1500 generated ones to the reducer generates different results.
+A concrete counterexample is reported if inputting any pair of lists from the generated ones to the reducer generates different results.
 Our procedure for generating random pairs is quite naive.
@@
 For each length, we generate 300 lists and pick uniformly at random one of its permutations.
-Although the approach is simple, in practice it finds counterexamples in all of our non-commutative benchmarks.
+Although the approach is simple, in practice it finds counterexamples in all of our non-commutative benchmarks in a few seconds.
 
@@
 
-\subsection{The First Program Transformation Task in the Preprocessor}
+\subsection{The Program Transformation Task in the Preprocessor}
 \label{sec:program_trans1}
-Recall that the reducer program can perform the ouput command $out(e)$ inside the loop body $s_2$.
+\subsubsection{Handling output inside the loop body} Recall that the reducer program can perform the ouput command $out(e)$ inside the loop body $s_2$.
 In this case, we remember the output value in a fresh variable $v$ and replace the $out(e)$ command with an assignment $v:=e$.
-Notice that the value of $v$ stays the same from the point it has been assigned a value.
+Notice that the value of $v$ stays the same from the point it has been assigned a value until the end of the loop body $s_2$.
 If the values of $v$ are the same for all permutations of input lists at the end of $s_2$, we know that the reducer is commutative w.r.t. to all output values produced inside the loop body $s_2$.
 
-\subsection{The Prover: Reduce Commutativity Checking to SMT Solving}
-\label{sec:prover}
-Below we begin with a simple reducer where $s_1$ never calls the $\cur$ function.
-Later we will explain how to handle the general case using program transformation.
-The command $s_2$ can be viewed as a function $F$ that reads the values of all variables and the current input before executing $s_2$ and outputs the values of all variables after $s_2$.
-Formally, the function $F(n,x_1,x_2,\ldots,x_k): \Z^{k+1} \rightarrow \Z^k$ returns a tuple of values $x_1',x_2',\ldots,x_k'$, where $n$ is the current input value of the reducer, $x_i$ and $x_i'$ are the values of variables before and after the execution of $s_2$, respectively, for $i\in[1,k]$.
-The construction of $F$ from $s_2$ can be done in the standard way.
-We check if the formula below is valid for all possible values of $n_1,n_2, x_1,x_2,\ldots,x_k$.
-\begin{equation}
- F(n_1, F(n_2,x_1,x_2,\ldots,x_k)) = F(n_2, F(n_1,x_1,x_2,\ldots,x_k) )
-\label{eq:commu}
-\end{equation}
-
-Using the reducer that computes average (Figure~\ref{fig:reducer_example}) as an example.
-It has two variables $s$ and $c$.
-It is not difficult to compute that $F_{average}(n,s,c)=(s+n, c+1)$.
-The corresponding Equation~(\ref{eq:commu}) is valid because $F_{average}(n_1, F_{average}(n_2,s,c)) =F_{average}(n_1, s+n_2, c+1)= (s+n_1+n_2,c+2)=F_{average}(n_2, s+n_1, c+1)=F_{average}(n_2, F_{average}(n_1,s,c))$.
-
-The validity of Equation~(\ref{eq:commu}) implies that swapping any two consecutive input values will not change the final variable valuation.
-Informally, it says that starting from the same initial valuations of variables and with two different input orders, $[n_1;n_2]$ and $[n_2;n_1]$, the values of all program variables are the same after we execute the loop body twice.
-The first execution reads $n_1$ and then reads $n_2$.
-The other execution reads the two inputs in the reverse order.
-
-\hide{
-
-In the example of ``average'', the values of $s$ and $c$ are the same no matter the reducer first reads $n_1$ and then $n_2$ or reads the two values in the swapped order.
-So it computes the same value for the input [1;2;\textbf{3};\textbf{4};5] and any other input with two consecutive values being swapped, e.g., [1;2;4;3;5].
-The swap operation can be applied arbitrarily many times to produce all possible permutations of the input.
-It follows that that starting from the same variable valuation, the loop ends with the same valuation for any permutation of input values, e.g., the reducer will output the same value for [1;2;3;4;5], [1;2;4;3;5], [1;4;2;3;5], [4;1;2;3;5], etc.
-Recall that the first program transformation task stores all output values in variables that will stay unchanged until the end of the loop.
-The validity of Equation~(\ref{eq:commu}) also implies that the execution of the loop produces the same sequence of outputs.
-
-We explain why that the validity of Equation~(\ref{eq:commu}) is sufficient to prove the reducer $s_1;\rloop\{s_2\};s_3$ commutative.
-Notice that $s_1$ does not read from the input (assumed at the beginning of this subsection).
-The execution of $s_1$ is deterministic in the sense that from the same initial valuation, it outputs the same sequence of values and ends at the same valuation.
-For the execution of $\rloop\{s_2\}$, from the validity of Equation~(\ref{eq:commu}), any permutation of input values leads the reducer to the same final valuation and the same sequence of outputs at the end of the loop.
-Before executing the commands $s_3$, all inputs have been read (the loop exit condition) already.
-Similar to the case of $s_1$, $s_3$ does not read from the input and hence the execution of $s_3$ is deterministic.
-It follows that for all permutations of inputs, the reducer outputs the same sequence of values.}
-
-In the next part, we explain how to generalize our approach to support general reducers (without the restriction on $s_1$) using program transformation.
-
-\subsection{The Second Program Transformation Task in the Preprocessor}
-\label{sec:program_trans2}
-
 \begin{wrapfigure}{r}{3.5cm}
-	\vspace{-1cm}
+	\vspace{-1.5cm}
 	\begin{algorithm}[H]
@@
 
-In real-world examples, it is often that the $s_1$ part of the reducer also reads from the input.
+\subsubsection{Handling the access to $\cur$ before entering the loop} In real-world examples, it is often that the $s_1$ part of the reducer also reads from the input.
 In the example in Figure~\ref{fig:reducer_max1}, the reducer program remembers the first input value in the variable $m$, increases its value by 10, and then updates its value to bigger ones if any occurs in the loop.
@@
 
+\subsection{The Prover: Reduce Commutativity Checking to SMT Solving}
+\label{sec:prover}
+After the transformation, the reducer $s_1;\rloop\{s_2\};s_3$ never calls the $\cur$ function before enthering the loop (the $s_1$ part) and never output values inside the loop body (the $s_2$ part).
+The command $s_2$ can be viewed as a function $F$ that reads the values of all variables and the current input before executing $s_2$ and outputs the values of all variables after $s_2$.
+Formally, the function $F(n,x_1,x_2,\ldots,x_k): \Z^{k+1} \rightarrow \Z^k$ returns a tuple of values $x_1',x_2',\ldots,x_k'$, where $n$ is the current input value of the reducer, $x_i$ and $x_i'$ are the values of variables before and after the execution of $s_2$, respectively, for $i\in[1,k]$.
+The construction of $F$ from $s_2$ can be done in the standard way.
+We check if the formula below is valid for all possible values of $n_1,n_2, x_1,x_2,\ldots,x_k$.
+\begin{equation}
+ F(n_1, F(n_2,x_1,x_2,\ldots,x_k)) = F(n_2, F(n_1,x_1,x_2,\ldots,x_k) )
+\label{eq:commu}
+\end{equation}
+
+Using the reducer that computes average (Figure~\ref{fig:reducer_example}) as an example.
+It has two variables $s$ and $c$.
+It is not difficult to compute that $F_{average}(n,s,c)=(s+n, c+1)$.
+The corresponding Equation~(\ref{eq:commu}) is valid because $F_{average}(n_1, F_{average}(n_2,s,c)) =F_{average}(n_1, s+n_2, c+1)= (s+n_1+n_2,c+2)=F_{average}(n_2, s+n_1, c+1)=F_{average}(n_2, F_{average}(n_1,s,c))$.
+
+The validity of Equation~(\ref{eq:commu}) implies that swapping any two consecutive input values will not change the final variable valuation.
+Informally, it says that starting from the same initial valuations of variables and with two different input orders, $[n_1;n_2]$ and $[n_2;n_1]$, the values of all program variables are the same after we execute the loop body twice.
+The first execution reads $n_1$ and then reads $n_2$.
+The other execution reads the two inputs in the reverse order.
+
+\hide{
+
+In the example of ``average'', the values of $s$ and $c$ are the same no matter the reducer first reads $n_1$ and then $n_2$ or reads the two values in the swapped order.
+So it computes the same value for the input [1;2;\textbf{3};\textbf{4};5] and any other input with two consecutive values being swapped, e.g., [1;2;4;3;5].
+The swap operation can be applied arbitrarily many times to produce all possible permutations of the input.
+It follows that that starting from the same variable valuation, the loop ends with the same valuation for any permutation of input values, e.g., the reducer will output the same value for [1;2;3;4;5], [1;2;4;3;5], [1;4;2;3;5], [4;1;2;3;5], etc.
+Recall that the first program transformation task stores all output values in variables that will stay unchanged until the end of the loop.
+The validity of Equation~(\ref{eq:commu}) also implies that the execution of the loop produces the same sequence of outputs.
+
+We explain why that the validity of Equation~(\ref{eq:commu}) is sufficient to prove the reducer $s_1;\rloop\{s_2\};s_3$ commutative.
+Notice that $s_1$ does not read from the input (assumed at the beginning of this subsection).
+The execution of $s_1$ is deterministic in the sense that from the same initial valuation, it outputs the same sequence of values and ends at the same valuation.
+For the execution of $\rloop\{s_2\}$, from the validity of Equation~(\ref{eq:commu}), any permutation of input values leads the reducer to the same final valuation and the same sequence of outputs at the end of the loop.
+Before executing the commands $s_3$, all inputs have been read (the loop exit condition) already.
+Similar to the case of $s_1$, $s_3$ does not read from the input and hence the execution of $s_3$ is deterministic.
+It follows that for all permutations of inputs, the reducer outputs the same sequence of values.}
+
 \subsection{Optimization: Live Variable Analysis}
 \label{section:optimizations}
-In this section, we explain how data flow analysis is used in J-ReCoVer to improve the precision of commutativity checking and the algorithm we used to construct the $F$ function in Equation~(\ref{eq:commu}).
+Here we explain how live variable analysis is used in J-ReCoVer to improve the precision of commutativity checking.
 
@@
 
-In order to properly evaluate the performance of J-ReCoVer, we collect benchmark example from two different sources.
-First, we use the search engine \emph{searchcode.com} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''.
+In order to properly evaluate the performance of J-ReCoVer, We use the search engine \emph{searchcode.com} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''.
 Since there is an upper bound on the number of results returned from the search engine, we add different search filters in order to get more data.
@@
 
-\hide{The second set of examples are those have been discussed in verification literature~\cite{ChenHSW15,ChenSW16}. This set is relatively small, we have only $10$ examples.
-We also created a program that randomly generates reducer programs in order to test the scalability of J-ReCoVer.
-All benchmark examples can be found on the website of J-ReCoVer.}
+There are only three cases that J-ReCoVer with live variable analysis cannot handle.
+The reason that J-ReCoVer fails is that the three reducers use more complicated structure than what J-ReCoVer currently supports; they use a branch statement before entering the loop, i.e., in the form $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$.
+In theory, such a program can be handled by more sophisticated program transformation tasks.
+For example, we can merge the two loops and push the outer branch condition into the merged loop.
 
+J-ReCoVer is the first tool specialized to the reducer commutativity problem, although the approach is simple, it solves most of the real benchmarks we collected from repositories
+There is no other tool that could handle the reducers as they are.
+Perhaps some other tools could be applied on the transformed programs, but the transformations would still be needed, and our SMT-based backend verifier turned out to work efficiently, and so we did not feel a need to replace it by another verification tool.
+Of course, in the future, this can be done if need be.
+
+\hide{
 For the optimization based on live variable analysis (Section~\ref{section:optimizations}), we evaluate them based on real-world benchmark sets collected from open repositories (118 examples).
@@
 The precision of the analysis is improved from $6.8\%$ to $97.5\%$.
-There are only three cases that J-ReCoVer with data flow analysis cannot handle.
-The reason that J-ReCoVer fails is that the three reducers use more complicated structure than what J-ReCoVer currently supports; they use a branch statement before entering the loop, i.e., in the form $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$.
-In theory, such a program can be handled by more sophisticated program transformation tasks.
-For example, we can merge the two loops and push the outer branch condition into the merged loop.
 However, this new program transformation task is not implemented in J-ReCoVer yet.
@@
 \end{table}
+}
 

### 2019-06-21 draft.tex
apply some suggestions from Tomas

@@
 		%J-ReCoVer
-		\node[draw=red!30, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=8cm,fill=red!10,minimum height=8cm] (jrecover) at (5,0.8) {};
-		\node at (5,0.4) {\textbf{J-ReCoVer}};
+		\node[draw=red!30, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=8cm,fill=red!10,minimum height=7cm] (jrecover) at (5,0) {};
+		\node at (5,-.5) {\textbf{J-ReCoVer}};
 
@@
 		%JProver
-		\node[draw=blue!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=3cm,fill=blue!20,minimum height=5.5cm] (prover) at (6.5,0) {};
-		\node[] at (6.5,-0.4) {Prover};
+		\node[draw=blue!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=3cm,fill=blue!20,minimum height=5cm] (prover) at (6.5,-0.8) {};
+		\node[] at (6.5,-1.2) {Prover};
 
 		%JProver->Technologies
-		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (6.5,-1) {};
+		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (6.5,-2.4) {};
 
-		\node at (6.5,-1.6) {
+		\node at (6.5,-3) {
 			\begin{minipage}[t]{0.222\textwidth}
@@
 			Solver
-			\end{minipage}
-		};
-
-		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (6.5,-2.5) {};
-
-		\node at (6.5,-3.1) {
-			\begin{minipage}[t]{0.222\textwidth}
-			\centering
-			Equation~\ref{eq:commu}
 			\end{minipage}
@@
 		\draw [->] (8,-6.6) -- (9.2,-6.6) ;
-		\draw [->] (8,-1) -- (9.2,-1) ;
+		\draw [->] (8,-1.4) -- (9.2,-1.4) ;
 		\draw [-] (8,-6.3) -- (8.5,-6.3) --(8.5,-3.5);

### 2019-06-21 draft.tex
apply some suggestions from Tomas

@@
 There are several advantages for a reducer being commutative, e.g., the verification problem of a MapReduce program can be reduced to the problem of verifying a sequential program.
-We present a tool J-ReCoVer (Java Reducer Commutativity Verifier) that implements effective heuristics for reducer commutativity analysis.
+We present the tool J-ReCoVer (Java Reducer Commutativity Verifier) that implements effective heuristics for reducer commutativity analysis.
 J-ReCoVer is the first tool that is specialized in checking reducer commutativity.
@@
 
-In this paper, we propose heuristics for the commutativity problem that works very efficiently on a large set of practical integer reducer programs.
-We reduce the commutativity problem to an SMT problem in a sound but incomplete manner.
+In this paper, we present the tool J-ReCoVer (Java Reducer Commutativity Verifier), which is available at~\verb|http://jrecover.iis.sinica.edu.tw|. It implements
+heuristics for the commutativity problem that works very efficiently on a large set of practical integer reducer programs.
+The heuristics reduce the commutativity problem to an SMT problem in a sound but incomplete manner.
 We also propose optimizations to enable the approach that works on real-world examples.
 For the case that the reducer is not proven commutative, we complement the approach by using testing to find concrete counterexamples.
-We implement all these heuristics as a tool called J-ReCoVer (Java Reducer Commutativity Verifier), which is available at~\verb|http://jrecover.iis.sinica.edu.tw|.
 We collected benchmarks from open repositories such as Github and Bitbucket to evaluate J-ReCoVer.
@@
 
-Before entering the Prover component, the Preprocessor first performs a few program transformation tasks to simplify the verification task.
-Assume a reducer $s_1;\rloop\{s_2\};s_3$ is given.
-The section begins with an introduction to the first program transformation task (Section~\ref{sec:program_trans1}) that handles the case when the loop body $s_2$ contains $out$ commands.
-The output of the first transformation task is a commutativity-equivalent reducer program where $out$ does not occur in $s_2$.
+Before entering the Prover component, the Preprocessor first performs a few program transformation tasks to simplify the verification task (Section~\ref{sec:program_trans1}).
+The output of the preprocessor is a commutativity-equivalent reducer program.
 Then the algorithm of the Prover is explained in Section~\ref{sec:prover}.
-This algorithm works only in a special case where no read from input occurs in $s_1$.
-For general reducer programs, we introduce the second program transformation task (Section~\ref{sec:program_trans2}) whose output is a reducer program that falls in the special case required by the Prover and ``over-approximates'' all input/output behaviors of the original reducer.
-The commutativity of the produced reducer implies the commutativity of the original one, but not vice verse.
 

### 2019-06-21 draft.tex
apply some suggestions from Tomas

@@
 A \emph{command} in $\Cmd$ can be an assignment, a branch statement, concatenation of a sequence of commands, or $out(v)$ that outputs the value of $v$.
-A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$, and $s_2$ is assumed to have at most one $\cur$ expression in each \emph{branch}\footnote{We define a \emph{branch} of a command $s$ as a sequence obtained by replacing every branch statement $\ite{g}{s_1}{s_2}$ in $s$ with either $(g); s_1$ or $(not\ g) ;s_2$.
-For example, the loop body of Figure~\ref{fig:reducer_example}(a) has two branches $t:=\cur; (t>0); m:=t$ and $t:=\cur;(not\ t>0)$ }.
+A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$.
 According to our observation over hundreds  of reducer programs in open repositories, reducer programs are almost always in this form.
@@
 
-\begin{wrapfigure}{r}{5.3cm}
+\begin{wrapfigure}{l}{5.3cm}
 	\vspace{-1cm}
@@
 (I) the commands before entering the loop does not have any $\cur$ expression,
-(II) each branch (recall that ``branch'' is formally defined in Section~\ref{section:integer-reducers}) of the loop body has at most one $\cur$, and
-(III) $out(v)$ command does not occur inside the loop body\footnote{We need to apply the first program transformation again to fulfill this assumption.}.
-So we can apply Equation~(\ref{eq:commu}) to prove its commutativity.
+(II) $out(v)$ command does not occur inside the loop body.
 Since the new reducer has all behaviors of the original one, the new reducer being commutative implies that the original one is also commutative.
@@
 We perform a simple backward live variable analysis to collect all variables whose value may propagate to the output command after the loop execution.
+Only these varaibles are required to be equivalent.
 In our evaluation, the ratio of examples that our approach can successfully analyze is significantly increased from $6.8\%$ to $97.5\%$.

### 2019-06-23 appendix.tex
Add appendix of tool usage

% \input{appendix}
\clearpage
\appendix

\section{J-ReCoVer Usages}

\subsection{The User Interface of J-ReCoVer}
\label{appendix:1}

J-ReCoVer is available online at \url{\texttt{http://jrecover.iis.sinica.edu.tw/}}. Fig.~\ref{fig:main_screen} shows the main screen of J-ReCoVer. The alignment of user interface elements are as follows:

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.9\linewidth]{screenshots/main_screen.eps}
% \vspace{-5pt}
\caption{Main Screen of J-ReCoVer}
\label{fig:main_screen}
% \vspace{-15pt}
\end{center}
\end{figure}

\begin{itemize}
\item
Top Menu:
\begin{itemize}
\item
\emph{"Github"} opens a new tab of the repository of J-ReCoVer. The repository also has source code of benchmarks.
\item
\emph{"Benchmark"} leads to the list of benchmarks we collected with their results of commutativity analysis as Fig.~\ref{fig:benchmark_list} shows. Select the filename or "try it" button will select the example and go back to the main screen.
\end{itemize}
\item
Right Menu:
\begin{itemize}
\item
\emph{"Benchmark List"} provides a quick selection to examples in the benchmark (Fig.~\ref{fig:benchmark_list_right})
\item
\emph{"Results"} shows the last analysis result.
\end{itemize}
\item
Upper-Right Menu:
\begin{itemize}
\item
\emph{"Type"} provides types that J-ReCoVer supports. Details are explained in~\ref{appendix:3}.
\item
\emph{"Run"} starts the analysis of the selected example.
\end{itemize}
\item
Upper-Left Menu: See~\ref{appendix:3}.
\end{itemize}

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.8\linewidth]{screenshots/benchmark_list.eps}
% \vspace{-5pt}
\caption{Benchmark list from top menu (part)}
\label{fig:benchmark_list}
% \vspace{-15pt}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.8\linewidth]{screenshots/benchmark_list_right.eps}
% \vspace{-5pt}
\caption{Benchmark list from right menu (part)}
\label{fig:benchmark_list_right}
% \vspace{-15pt}
\end{center}
\end{figure}

\subsection{Run analysis of selected benchmark example}
\label{appendix:2}

To run analysis, you can choose an example from benchmark using either the top menu or the right menu, then click the "Run" button of the upper-right menu to start the commutativity analysis of the selected example. The pull-down menu "Types" of the upper-right menu provides selectable types for input \texttt{(T1,T2)} and output \texttt{(T3,T4)}. Fig.~\ref{fig:type_select_menu} shows the pull-down menu and Fig.~\ref{fig:selectable_types} shows part of the selectable types in J-ReCoVer. If one selects an example from the benchmark, the types will be automatically selected to match the example. The selection will be needed if the user wants to write a reduce function from sketch for analysis (see~\ref{appendix:3}).

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.8\linewidth]{screenshots/type_select_menu.eps}
% \vspace{-5pt}
\caption{Type select menu}
\label{fig:type_select_menu}
% \vspace{-15pt}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.8\linewidth]{screenshots/selectable_types.eps}
% \vspace{-5pt}
\caption{Selectable types (part)}
\label{fig:selectable_types}
% \vspace{-15pt}
\end{center}
\end{figure}

After J-ReCoVer finishes the analysis, the \emph{"Result:"} tab of the right menu will show the result as Fig.~\ref{fig:analysis_result} shows. Fig.~\ref{fig:analysis_result_text} shows the analysis result of the first benchmark \texttt{dis.java} in detail.

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.8\linewidth]{screenshots/analysis_result.eps}
% \vspace{-5pt}
\caption{The analysis result}
\label{fig:analysis_result}
% \vspace{-15pt}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\begin{mdframed}[roundcorner=5pt]
\begin{Verbatim}[fontsize=\tiny]
================================
### Compile ###
================================
Success

================================
### j-ReCoVer ###
================================
RESULT: Proved to be commutative

________________________________

Trying to find a counterexample...

RESULT: Cannot find a counterexample in 500 tests
Testcases were generated randomly.

Following are the first 50 lines of testcases:
Input1: o [5, 4, 5, 2, -1]
Input2: o [-1, 4, 5, 5, 2]
Output1:

Key: [o]
Val: [0.0]
--
Output2:

Key: [o]
Val: [0.0]
--------
Input1: j [1, -1, 0, 3, -2]
Input2: j [0, 3, -2, 1, -1]
Output1:

Key: [j]
Val: [0.0]
--
Output2:

Key: [j]
Val: [0.0]
--------
Input1: e [4, 3, 5, -4, 1]
Input2: e [4, -4, 5, 3, 1]
Output1:

Key: [e]
Val: [0.0]
--
Output2:

Key: [e]
Val: [0.0]
--------
Input1: s [3, 0, 2, -4, -1]
Input2: s [3, -1, 0, -4, 2]
Output1:

Key: [s]
Val: [0.0]
--
Output2:

Key: [s]
Val: [0.0]
--------
Input1: v [-3, -2, 3, 3, -3]
Input2: v [3, -2, -3, -3, 3]
\end{Verbatim}
\end{mdframed}
\caption{The analysis result of \texttt{dis.java}}
\label{fig:analysis_result_text}
\end{center}
\end{figure}

In a commutativity analysis, J-ReCoVer first tries to compile the example then perfrom commutativity analysis. If the analysis says the example is commutative, J-ReCoVer then runs 500 randomly generated test cases to try to find a counterexample. If the test cases all pass, J-ReCoVer concludes that the example is commutative, or the result will be "unknown" since the results of analysis and tests are inconsistent. For the case that the commutativity analysis returns false, J-ReCoVer will also run test cases to find a counterexample. This time, J-ReCoVer will conclude "not commutative" if a counterexample is found, or "unknown" if no counterexample is found.

\subsection{Run Analysis of an example from sketch}
\label{appendix:3}

Besides examples from the benchmark, J-ReCoVer also provides an interactive way to analyze a reduce function starting from a sketch.
The upper-left menu (below the top menu) provides blank templates for two versions of Hadoop. The templates are

\begin{mdframed}[roundcorner=5pt]
\begin{verbatim}
public void reduce(T1 key, Iterator<T2> values,
	OutputCollector<T3,T4> oc1, Reporter reporter)
		throws IOException,InterruptedException {

}
\end{verbatim}
\end{mdframed}

, and

\begin{mdframed}[roundcorner=5pt]
\begin{verbatim}
public void reduce(T1 key, Iterable<T2> values,
	Context context) throws IOException,InterruptedException {

}
\end{verbatim}
\end{mdframed}

In this case, one would have to manually fill the types T1 to T4 and the function body, then selects the types from the pull-down menu, as shown in Fig.~\ref{fig:type_select_menu} and Fig.~\ref{fig:selectable_types}.

For more details, all selectable types are:

\begin{itemize}
\item Long
\item BooleanWritable
\item BytesWritable
\item Text
\item Double
\item DoubleWritable
\item Float
\item FloatWritable
\end{itemize}

### 2019-06-23 draft.tex
Add appendix of tool usage
Abstract and Introduction

@@
 %\usepackage{times}
+
+\usepackage{fancyvrb}
+\usepackage[framemethod=tikZ]{mdframed}
 
@@
 
-MapReduce framework for data-parallel computation was first proposed by Google~\cite{dean04} and later implemented in the Apache Hadoop project~\cite{hadoop}.
-Under the MapReduce framework, a reducer computes output values from a sequence of input values transmitted over the network.
-Due to the non-determinism in data transmission, the order of input values arrives at the reducer is not fixed.
-The \emph{commutativity problem} of reducers asks if the output of a reducer is independent of the order of its inputs.
-There are several advantages for a reducer being commutative, e.g., the verification problem of a MapReduce program can be reduced to the problem of verifying a sequential program.
-We present the tool J-ReCoVer (Java Reducer Commutativity Verifier) that implements effective heuristics for reducer commutativity analysis.
-J-ReCoVer is the first tool that is specialized in checking reducer commutativity.
-Experimental results over 118 benchmark examples collected from open repositories are very positive; J-ReCoVer correctly handles over 97\% of them.
+The MapReduce framework for data-parallel computation was first proposed by
+Google~\cite{dean04} and later implemented in the Apache Hadoop
+project~\cite{hadoop}. Under the MapReduce framework, a reducer computes output
+values from a sequence of input values transmitted over the network. Due to
+non-determinism in data transmission, the order in which input values arrive at
+the reducer is not fixed. In relation to this, the \emph{commutativity problem}
+of reducers asks if the output of a reducer is independent of the order of its
+inputs. Indeed, there are several advantages for a reducer to be commutative,
+e.g., the verification problem of a MapReduce program can be reduced to the
+problem of verifying a sequential program. We present the tool J-ReCoVer (Java
+Reducer Commutativity Verifier) that implements effective heuristics for reducer
+commutativity analysis. J-ReCoVer is the first tool that is specialized in
+checking reducer commutativity. Our experimental results over 118 benchmark
+examples collected from open repositories are very positive; J-ReCoVer correctly
+handles over 97~\% of them.
 
@@
 
-\section{Introduction}
-\label{section:introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction} \label{section:introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-MapReduce is one of the most popular frameworks for data parallel computation.
-A MapReduce~\cite{dean04,hadoop} program consists of several pairs of \emph{mappers} and \emph{reducers} running on a machine cluster for handling big data in parallel.
-Usually, mappers and reducers are the only components in a MapReduce program that involves concurrency.
-Mappers read data from a distributed database and output a sequence of \emph{key-value} pairs.
-The sequence elements (key-value pairs) with the same key will be sent to the same reducer for further processing.
-Due to scheduling policies and network latency, the same inputs may arrive at a reducer in a different order in different executions, which results in the so-called \emph{commutativity problem} of reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}, that is, if the output of a reducer is independent of the order of its inputs.
-If all reducers are commutative, they will have the same external behavior under all possible schedules.
-In such a case, by fixing a schedule, the verification problem of a MapReduce program can be reduced to the verification problem of a sequential program, which is known to be much easier than the verification problem of concurrent programs.
-One needs to consider only a particular interleaving of input values instead of all of them.
+MapReduce belongs among the most popular frameworks for data parallel
+computation. A MapReduce program~\cite{dean04,hadoop} consists of several pairs
+of \emph{mappers} and \emph{reducers} running on a machine cluster for handling
+big data in parallel. Usually, mappers and reducers are the only components in a
+MapReduce program that involve concurrency. Mappers read data from a distributed
+database and output a sequence of \emph{key-value} pairs. The elements of the
+sequence (i.e., key-value pairs) with the same key are sent to the same reducer
+for further processing. Due to scheduling policies and network latency, the same
+inputs may arrive at a reducer in different orders in different executions.
+Therefore, reducers are typically required to be \emph{commutative}, that is,
+the output of a reducer is required to be independent of the order of its
+inputs. The problem of checking whether this is indeed the case is known as the
+\emph{commutativity problem} of
+reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}. If all reducers
+are commutative, they will have the same external behavior under all possible
+schedules. In such a case, by fixing a schedule, the verification problem of a
+MapReduce program can be reduced to the verification problem of a sequential
+program, which is known to be much easier than the verification problem of
+concurrent programs. One then suffices with considering any chosen interleaving
+of input values instead of all of them.
 
-\hide{More concretely, for the verification of a MapReduce program, we propose to do it in two phases.
-First, ensuring if all reducers are commutative.
-If some reducers are non-commutative, modifying them to commutative ones.
-Usually, the modification is not a difficult task~\cite{xiao14mr}, and can be done without affecting their functionality and performance.
-For example, assume that the task of a reducer is to find the name of the person with highest score.
-Such a reducer is non-commutative when the input include two people with the same highest score.
-This reducer can be made commutative, by also comparing the ID number of people with the same score.
-Once all reducers are made commutative, we reduce the verification problem to sequential verification by fixing a scheduler.
-In this two-phase approach, the key enabling technique is an efficient procedure for checking reducer commutativity.}
+\hide{More concretely, for the verification of a MapReduce program, we propose
+to do it in two phases. First, ensuring if all reducers are commutative. If some
+reducers are non-commutative, modifying them to commutative ones. Usually, the
+modification is not a difficult task~\cite{xiao14mr}, and can be done without
+affecting their functionality and performance. For example, assume that the task
+of a reducer is to find the name of the person with highest score. Such a
+reducer is non-commutative when the input include two people with the same
+highest score. This reducer can be made commutative, by also comparing the ID
+number of people with the same score. Once all reducers are made commutative, we
+reduce the verification problem to sequential verification by fixing a
+scheduler. In this two-phase approach, the key enabling technique is an
+efficient procedure for checking reducer commutativity.}
 
-On the other hand, the non-commutative behavior of a reducer is often the source of very tricky bugs.
-A study conducted by Microsoft investigated the commutativity problem of $508$ reducers running on their MapReduce server~\cite{xiao14mr}.
-The reducer programs have been checked carefully using all traditional means such as code review, testing, and experiments with real data for months.
-Still, among them, five programs contain very subtle bugs caused by non-commutativity (confirmed by the programmers).
+On the other hand, the non-commutative behavior of a reducer is often the source
+of very tricky bugs. A study conducted by Microsoft investigated the
+commutativity problem of $508$ reducers running on their MapReduce
+server~\cite{xiao14mr}. These reducers were carefully checked using all
+traditional means such as code review, testing, and experiments with real data
+for months. Still, five of these programs contained very subtle bugs caused by
+non-commutativity (which was confirmed by the programmers).
 
-However, checking reducer commutativity is a difficult problem on its own right~\cite{ChenHSW15,ChenSW16,ChenLTW17}.
-Even for a simple case that all values are mathematical integers, it is proved undecidable in~\cite{ChenHSW15}.
-For the case that all values are machine integer (e.g, 64-bits integer), the problem is decidable, but the only available algorithm that was proposed in the same paper is of very high complexity and hence is only of theoretical interests.
+However, checking reducer commutativity is a difficult problem on its own
+right~\cite{ChenHSW15,ChenSW16,ChenLTW17}. Even for a simple case in which all
+values are mathematical integers, it is proved undecidable in~\cite{ChenHSW15}.
+For the case when all values are machine integers (e.g., 64-bits integers), the
+problem is decidable, but the only available algorithm, which was proposed
+in~\cite{ChenHSW15} too, is of very high complexity and hence of theoretical
+interest only.
 
-In this paper, we present the tool J-ReCoVer (Java Reducer Commutativity Verifier), which is available at~\verb|http://jrecover.iis.sinica.edu.tw|. It implements
-heuristics for the commutativity problem that works very efficiently on a large set of practical integer reducer programs.
-The heuristics reduce the commutativity problem to an SMT problem in a sound but incomplete manner.
-We also propose optimizations to enable the approach that works on real-world examples.
-For the case that the reducer is not proven commutative, we complement the approach by using testing to find concrete counterexamples.
-We collected benchmarks from open repositories such as Github and Bitbucket to evaluate J-ReCoVer.
-With the help of a search engine \emph{searchcode.com} over those repositories, we collected 118 examples.
-J-ReCoVer is able to correctly analyze all but 3 of them.
+In this paper, we present the J-ReCoVer tool (Java Reducer Commutativity
+Verifier), which is available at~\verb|http://jrecover.iis.sinica.edu.tw|. The
+tool implements a heuristic approach for checking the commutativity problem
+that---despite its simplicity---works very efficiently on a large set of
+practical integer reducer programs as shown by our experiments. The main
+ingredient of the approach is a reduction from the commutativity problem to an
+SMT problem. The reduction is incomplete but sound. It is accompanied with
+several heuristics which enable the approach to scale to real-world examples.
+For the case when the reducer is not proven commutative, we complement the
+approach by using testing to find concrete counterexamples.
+
+We collected benchmarks from open repositories such as Github and Bitbucket to
+evaluate J-ReCoVer. With the help of a search engine \emph{searchcode.com} over
+those repositories, we collected 118 programs. We provide this collection of
+programs to other interested researchers as a side contribution of the paper.
+Our tool J-ReCoVer is able to correctly analyze all but three of the programs.
 
@@
 
+\input{appendix}
+
 \end{document}

### 2019-06-23 draft.tex
Related Works

@@
 
+%=============================================================================
 \subsection*{Related Works}
-Reducer commutativity problem can be reduced to a program equivalence problem.
-One creates another program $R'$ that first non-deterministically swaps two consecutive input values and then executes the code of $R$.
-If $R'$ and $R$ are equivalent, using the fact that all permutations of a list can be obtained by swapping consecutive list elements finitely many times\footnote{Here is an example to produce [3;2;5;1;4] from [1;2;3;4;5] by swapping consecutive elements: [\textbf{1};\textbf{2};3;4;5] $\rightarrow$ [2;\textbf{1};\textbf{3};4;5] $\rightarrow$ [2;3;1;\textbf{4};\textbf{5}]$\rightarrow$ [2;3;\textbf{1};\textbf{5};4]$\rightarrow$ [\textbf{2};\textbf{3};5;1;4]$\rightarrow$ [3;2;5;1;4].}, $R$ can be proved to be commutative.
-There is a series of research results on program equivalence checking (or closely related topics such as regression verification and translation validation), to name a few~\cite{Pnueli:1998:TV,fedyukovich2015automated,barthe2011relational,KlebanovRuemmerUlbrich2017}.
-At a high level, checking equivalence of two programs $P$ and $P'$ can be reduced to a sequential verification problem by executing $P'$ after $P$ and at the end checking if they always have the same outputs.
-It can be made more efficient by finding the right~\emph{synchronization points} and combining the code of $P$ and $P'$ in an interleaved manner.
-A lot of research effort in this direction is in finding good synchronization points.
-For the case of commutativity analysis, one can simply use the beginning of the loop as the synchronization point.
-However, in our experience, if we naively reduce the commutativity problem to equivalence problem and check it in a precise manner, many examples cannot be solved.
-In this paper, we propose a good over-approximation (c.f.
-Section~\ref{sec:prover}) of the reducer's behavior.
-The approximation allows a much more efficient yet precise enough commutativity analysis.
-Our approach uses some form of sequentialization which is, however, specialized for the reducer commutativity problem and different from the sequentialisation approaches proposed for verifying common multithreaded programs\cite{XXX}: indeed, in MapReduce programs there is no notion of threads and context switches.
+%=============================================================================
 
-One main motivation of commutativity analysis is to reduce the verification problem of a concurrent program to a sequential one.
-There are several pieces of research sharing the similar motivation, e.g., the concept of \emph{robustness} of event-driven asynchronous programs~\cite{ahmed2017:robustness} and program running under relaxed memory model~\cite{ahmed2013:robustness,AbdullaACLR13,AbdullaACLR12}.
-However, their computation models are quite different from that of reducers and hence the result cannot be directly applied.
-Besides verification, another interesting research direction is the synthesis of MapReduce programs~\cite{SmithA16}.
-Commutativity analysis is used as a component under the synthesis framework.
+The reducer commutativity problem can be reduced to a \emph{program equivalence}
+problem. One creates another program $R'$ that first non-deterministically swaps
+two consecutive input values and then executes the code of $R$. If $R'$ and $R$
+are equivalent, using the fact that all permutations of a list can be obtained
+by swapping consecutive list elements finitely many times\footnote{Here is an
+example to produce [3;2;5;1;4] from [1;2;3;4;5] by swapping consecutive
+elements: [\textbf{1};\textbf{2};3;4;5] $\rightarrow$
+[2;\textbf{1};\textbf{3};4;5] $\rightarrow$
+[2;3;1;\textbf{4};\textbf{5}]$\rightarrow$
+[2;3;\textbf{1};\textbf{5};4]$\rightarrow$
+[\textbf{2};\textbf{3};5;1;4]$\rightarrow$ [3;2;5;1;4].}, $R$ can be proved to
+be commutative. There is a series of research results on program equivalence
+checking (or closely related topics such as regression verification and
+translation validation): see, e.g.,
+\cite{Pnueli:1998:TV,fedyukovich2015automated,barthe2011relational,KlebanovRuemmerUlbrich2017}
+to name a few.
 
-\section{Notations and Definitions}
-\label{section:integer-reducers}
-We use $[n,m]$ to denote the set of integers $\{k\mid n \leq k\leq m\}$ and lift the equality $=$ operation to tuples in the standard way.
+From a high-level view, checking equivalence of two programs $P$ and $P'$ can be
+reduced to a sequential verification problem by executing $P'$ after $P$,
+followed by checking whether the two programs always produce the same outputs.
+The approach can be made more efficient by finding the
+right~\emph{synchronization points} and combining the code of $P$ and $P'$ in an
+interleaved manner. A lot of research effort in this direction is in finding
+good synchronization points. In this work, we propose the \emph{head of the
+top-level reducer loop} as the synchronization point suitable for reducer
+commutativity analysis. According to our experience discussed later on, the
+reducers usually contain just a single such loop. Moreover, for the case when
+there are more top-level loops in a reducer, we propose a way of breaking such a
+reducer into several ones to be checked independently.
+
+However, in our experience, if one naively reduces the commutativity problem to
+an equivalence problem and checks it in a precise manner, many reducers cannot
+be verified. Therefore, J-ReCoVer uses an over-approximation of the reducer's
+behavior. This approximation allows for a much more efficient, yet---according
+to our experiments---precise enough commutativity analysis.
+
+Our approach can be seen as using some form of \emph{sequentialisation} of the
+concurrent behaviour. Sequentialisation is the key approach behind many current
+successful approaches for verifying multithreaded
+programs~\cite{LalReps:Seq:08,LazyCSeq14}. However, our sequentialisation
+approach is specialised for the case of reducers and quite different from what
+is used in sequentialisation of multithreaded programs: indeed, in MapReduce
+programs there is no notion of threads nor context switches.
+
+Various forms of sequentialisation are behind further research works too, such
+as, e.g., works dealing with the concept of \emph{robustness} of event-driven
+asynchronous programs~\cite{ahmed2017:robustness} or those dealing with programs
+running under some \emph{relaxed memory
+models}~\cite{ahmed2013:robustness,AbdullaACLR13,AbdullaACLR12}. However, their
+computation models are again quite different from that of reducers, and hence
+the results cannot be directly applied.
+
+Besides verification, another interesting research direction is the
+\emph{synthesis} of MapReduce programs~\cite{SmithA16}. Commutativity analysis
+is used as a component under the synthesis framework.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Notations and Definitions} \label{section:integer-reducers}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We use $[n,m]$ to denote the set of integers $\{k\mid n \leq k\leq m\}$ and lift
+the equality $=$ operation to tuples in the standard way.
 

### 2019-06-23 draft.tex
Section 2: preliminaries, input language

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\hide{More concretely, for the verification of a MapReduce program, we propose
-to do it in two phases. First, ensuring if all reducers are commutative. If some
-reducers are non-commutative, modifying them to commutative ones. Usually, the
-modification is not a difficult task~\cite{xiao14mr}, and can be done without
-affecting their functionality and performance. For example, assume that the task
-of a reducer is to find the name of the person with highest score. Such a
-reducer is non-commutative when the input include two people with the same
-highest score. This reducer can be made commutative, by also comparing the ID
-number of people with the same score. Once all reducers are made commutative, we
-reduce the verification problem to sequential verification by fixing a
-scheduler. In this two-phase approach, the key enabling technique is an
-efficient procedure for checking reducer commutativity.}
+% More concretely, for the verification of a MapReduce program, we propose to do
+% it in two phases. First, ensuring if all reducers are commutative. If some
+% reducers are non-commutative, modifying them to commutative ones. Usually, the
+% modification is not a difficult task~\cite{xiao14mr}, and can be done without
+% affecting their functionality and performance. For example, assume that the
+% task of a reducer is to find the name of the person with highest score. Such a
+% reducer is non-commutative when the input include two people with the same
+% highest score. This reducer can be made commutative, by also comparing the ID
+% number of people with the same score. Once all reducers are made commutative,
+% we reduce the verification problem to sequential verification by fixing a
+% scheduler. In this two-phase approach, the key enabling technique is an
+% efficient procedure for checking reducer commutativity.
 
@@
 
-\hide{
-\begin{equation*}
-\begin{array}{rclcl}
-\multicolumn{3}{l}{v\in \Var\mbox{, and }c \in \Z}&&\textmd{Variable and Constant}\\
-e \in \Exp    &\ \ \  {\triangleq}\ \ \   & v \mid c \mid \cur \mid e + e \mid e - e \mid e \times e \mid *\mid\ldots & &\textmd{Integer Expression}\\
-g\in \Grd  & {\triangleq}  & e < e \mid not\ g \mid g \wedge g  \mid \ldots& & \textmd{Guard}\\
-s\in \Cmd  & {\triangleq}  & v:= e \mid out(v) \mid \ite{g}{s}{s} \mid s;s && \textmd{Command}\\
-p\in \Prg  & {\triangleq}  & s;\rloop\{s\};s&& \textmd{Reducer Program}\\
-\end{array}
-\end{equation*}}
+% \begin{equation*}
+% \begin{array}{rclcl}
+% \multicolumn{3}{l}{v\in \Var\mbox{, and }c \in \Z}&&\textmd{Variable and 
+%   Constant}\\
+% e \in \Exp    &\ \ \  {\triangleq}\ \ \   & v \mid c \mid \cur \mid e + e \mid
+%   e - e \mid e \times e \mid *\mid\ldots & &\textmd{Integer Expression}\\
+% g\in \Grd  & {\triangleq}  & e < e \mid not\ g \mid g \wedge g  \mid \ldots& & 
+%   \textmd{Guard}\\
+% s\in \Cmd  & {\triangleq}  & v:= e \mid out(v) \mid \ite{g}{s}{s} \mid s;s && 
+%   \textmd{Command}\\
+% p\in \Prg  & {\triangleq}  & s;\rloop\{s\};s&& \textmd{Reducer Program}\\
+% \end{array}
+% \end{equation*}
+
 \begin{wrapfigure}{r}{3cm}
 		\vspace{-0.8cm}
-	\hide{
-		\begin{minipage}{0.32\textwidth}
-			\begin{algorithm}[H]
-				$m := \cur$; \;
-				\Loop{}{
-					$t:=\cur$;\;
-					\uIf{ $t > m$}{
-						$m := t$
-					}
-				};
-				$out(m)$\;
-			\end{algorithm}
-			\caption*{(a) max}
-		\end{minipage}
-		\hspace{-0.5cm}
-	}
+
+%		\begin{minipage}{0.32\textwidth}
+%			\begin{algorithm}[H]
+%				$m := \cur$; \;
+%				\Loop{}{
+%					$t:=\cur$;\;
+%					\uIf{ $t > m$}{
+%						$m := t$
+%					}
+%				};
+%				$out(m)$\;
+%			\end{algorithm}
+%			\caption*{(a) max}
+%		\end{minipage}
+%		\hspace{-0.5cm}
+
 	\begin{minipage}{0.3\textwidth}
@@
 	\end{minipage}
-	\hide{
-		\begin{minipage}{0.4\textwidth}
-			\begin{algorithm}[H]
-				$a:=*;s := 0; c:=0$;\;
-				\Loop{}{
-					$s := s+(\cur-a)^2$; \;
-					$c := c+1$
-				};
-				$o := s/c$;\;
-				$out(o)$
-			\end{algorithm}
-			\caption*{(c) standard deviation}
-		\end{minipage}
-	}
-	\caption{Average}
+
+% 		\begin{minipage}{0.4\textwidth}
+% 			\begin{algorithm}[H]
+% 				$a:=*;s := 0; c:=0$;\;
+% 				\Loop{}{
+% 					$s := s+(\cur-a)^2$; \;
+% 					$c := c+1$
+% 				};
+% 				$o := s/c$;\;
+% 				$out(o)$
+% 			\end{algorithm}
+% 			\caption*{(c) standard deviation}
+% 		\end{minipage}
+
+	\caption{A reducer that computes the average value.}
 	\vspace{-0.8cm}
@@
 \end{wrapfigure}
-For presentation purpose, we describe a highly simplified language to characterize the essence of reducers.
-The model allows to describe the computation of reducers and investigate their commutativity.
-Let $\Var$ be the set of variables.
-An \emph{integer expression} in $\Exp$ can be either a variable, constant value, a call to the $\cur$ function that reads and consumes an input value of the reducer, their combinations over basic arithmetic operations, or a non-deterministically chosen integer value $*$.
-A \emph{command} in $\Cmd$ can be an assignment, a branch statement, concatenation of a sequence of commands, or $out(v)$ that outputs the value of $v$.
-A \emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$, where $s_1,s_2,s_3 \in \Cmd$.
-According to our observation over hundreds  of reducer programs in open repositories, reducer programs are almost always in this form.
-The $\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly until the entire input list is consumed.
-An example is in Figure~\ref{fig:reducer_example}.
 
-Some reducer uses two loops to compute the output.
-For example, for calculating standard deviation, one first computes the average of inputs and then uses it to compute the final result.
-In that case, we can still verify the reducer by first partitioning it into two reducers and then verifying them separately.
-One reducer computes the average and the other reducer performs the rest of the computation.
-The second reducer replaces the average with a non-deterministic value and thus ``over-approximates''  all possible outputs of the standard deviation computation; it computes an output for all possible ``average'' value.
-However, this reducer is still commutative and its commutativity verification can still be done.
+For presentation purposes, we provide a sketch of a highly simplified language
+for describing reducers. The language allows us to give examples of reducers and
+to discuss our approach for checking their commutativity. Let $\Var$ be a set of
+\emph{integer variables}. An \emph{integer expression} in $\Exp$ can either be
+a~variable from $\Var$, a constant value, a call to the $\cur$ function that
+reads and consumes an input value of the reducer, their combinations over basic
+arithmetic operations, or a non-deterministically chosen integer value $*$. A
+\emph{command} in $\Cmd$ can be an assignment, a branch statement, a sequence of
+commands, or an $out(v)$ statement that outputs the value of $v \in \Var$. A
+\emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$ where $s_1,s_2,s_3
+\in \Cmd$. According to our observation over hundreds  of reducer programs in
+open repositories, reducer programs are almost always in this form. The
+$\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly until
+the entire input list is consumed. An example of a reducer is shown in
+Figure~\ref{fig:reducer_example}.
 
-\section{Overview of the J-ReCoVer tool}
-\label{sec:overview}
+Some reducers use two (or more) top-level loops to compute the output, possibly
+interleaved with some non-looping code. {\color{red} These loops are executed
+sequentially, repeatedly iterating over the input list from its beginning.} For
+example, for calculating the standard deviation, one first computes the average
+of inputs and then uses it to compute the final result (using two passes over
+the input list). In that case, we suggest to verify the reducer by first
+partitioning it into two (or more) reducers, each containing a single top-level
+loop, and then verifying these reducers separately.\footnote{\color{red}Nested
+loops can be transformed into branches of the top-level loop.} The top-level
+loops communicate through shared variables.  After the transformation, reducers
+corresponding to the second top-level loop (and possibly further such loops)
+will work with random values of the shared variable, which over-approximates the
+original behaviour.
+
+For instance, for the case of the standard deviation, the first reducer computes
+the average, and the other reducer performs the rest of the computation. The
+second reducer replaces the average with a non-deterministic value and thus
+``over-approximates'' all possible outputs of the standard deviation
+computation. Equivalently, it computes an output for all possible ``average''
+values. However, this reducer is still commutative, and its commutativity can be
+verified.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Overview of the J-ReCoVer tool} \label{sec:overview}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %Hadoop, Java;
+
 The input of J-ReCoVer is a reducer program written in Java, which is the most popular programming language used in the Hadoop~\cite{hadoop} MapReduce framework.
@@
 
-\section{The Preprocessor and the Prover}
-\label{sec:preprocessor_prover}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{The Preprocessor and the Prover} \label{sec:preprocessor_prover}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%=============================================================================
 \subsection{The Program Transformation Task in the Preprocessor}
 \label{sec:program_trans1}
+%=============================================================================
+
 \subsubsection{Handling output inside the loop body} Recall that the reducer program can perform the ouput command $out(e)$ inside the loop body $s_2$.
@@
 
-\hide{	
-	\begin{figure}[t]
-		\begin{minipage}{0.4\textwidth}
-			\begin{algorithm}[H]
-				\;\;$m := \cur + 10$; \;
-				\Loop{}{
-					$t:=\cur$\;
-					\uIf{ $t> m$}{
-						$m := t$ \;
-					}
-				};
-				$out(m)$\;\;
-			\end{algorithm}
-			\caption*{(a) Reducer max$^+$}
-		\end{minipage}
-		\begin{minipage}{0.6\textwidth}
-			\begin{algorithm}[H]
-				$s:=*;$\;
-				\Loop{}{
-					\uIf{$s=1$}{$m := \cur + 10; s:= 2$}
-					\uElse{
-						$t:=\cur$\;
-						\uIf{ $t > m$}{
-							$m := t$ \;
-						}
-					}
-				};
-				$out(m)$
-			\end{algorithm}
-			\caption*{(b) Reducer max$^{+\mathtt{fix}}$}
-		\end{minipage}
-		\caption{Reducer examples}
-		\label{fig:reducer_max}
-	\end{figure}
-}
+%	\begin{figure}[t]
+%		\begin{minipage}{0.4\textwidth}
+%			\begin{algorithm}[H]
+%				\;\;$m := \cur + 10$; \;
+%				\Loop{}{
+%					$t:=\cur$\;
+%					\uIf{ $t> m$}{
+%						$m := t$ \;
+%					}
+%				};
+%				$out(m)$\;\;
+%			\end{algorithm}
+%			\caption*{(a) Reducer max$^+$}
+%		\end{minipage}
+%		\begin{minipage}{0.6\textwidth}
+%			\begin{algorithm}[H]
+%				$s:=*;$\;
+%				\Loop{}{
+%					\uIf{$s=1$}{$m := \cur + 10; s:= 2$}
+%					\uElse{
+%						$t:=\cur$\;
+%						\uIf{ $t > m$}{
+%							$m := t$ \;
+%						}
+%					}
+%				};
+%				$out(m)$
+%			\end{algorithm}
+%			\caption*{(b) Reducer max$^{+\mathtt{fix}}$}
+%		\end{minipage}
+%		\caption{Reducer examples}
+%		\label{fig:reducer_max}
+%	\end{figure}
 
@@
 
-\hide{
-	\begin{wrapfigure}{r}{9cm}
-		\centering
-		\begin{minipage}{0.8\textwidth}
-
-			\begin{algorithm}[H]
-				$s'_0;s:=*;$\;
-				\Loop{}{
-					\lIf{$s=1$}{ $x_{i_1} := \cur; s'_1; s:=2$}
-					\lElseIf{ $s =2$}{ $x_{i_2} := \cur; s'_2; s:=3$}
-					\lElseIf{ $s = 3$}{$\ldots$}
-					\lElseIf{ $s = m$}{$x_{i_m} := \cur; s'_m; s:=m+1$}
-					\lElse{ $s_2$}
-				};$s_3$\;
-			\end{algorithm}
-		\end{minipage}
-		\caption{The second transformation task}
-		\label{fig:general_program_transformation}
-\end{wrapfigure}}
+%	\begin{wrapfigure}{r}{9cm}
+%		\centering
+%		\begin{minipage}{0.8\textwidth}
+%			
+%			\begin{algorithm}[H]
+%				$s'_0;s:=*;$\;
+%				\Loop{}{
+%					\lIf{$s=1$}{ $x_{i_1} := \cur; s'_1; s:=2$}
+%					\lElseIf{ $s =2$}{ $x_{i_2} := \cur; 
+%                                           s'_2; s:=3$}
+%					\lElseIf{ $s = 3$}{$\ldots$}
+%					\lElseIf{ $s = m$}{$x_{i_m} := \cur; 
+%                                          s'_m; s:=m+1$}
+%					\lElse{ $s_2$}
+%				};$s_3$\;
+%			\end{algorithm}
+%		\end{minipage}
+%		\caption{The second transformation task}
+%		\label{fig:general_program_transformation}
+%        \end{wrapfigure}
 
@@
 
+%=============================================================================
 \subsection{The Prover: Reduce Commutativity Checking to SMT Solving}
 \label{sec:prover}
+%=============================================================================
+
 After the transformation, the reducer $s_1;\rloop\{s_2\};s_3$ never calls the $\cur$ function before enthering the loop (the $s_1$ part) and never output values inside the loop body (the $s_2$ part).
@@
 
-\hide{
+% In the example of ``average'', the values of $s$ and $c$ are the same no
+% matter the reducer first reads $n_1$ and then $n_2$ or reads the two values in
+% the swapped order.  So it computes the same value for the input
+% [1;2;\textbf{3};\textbf{4};5] and any other input with two consecutive values
+% being swapped, e.g., [1;2;4;3;5].  The swap operation can be applied
+% arbitrarily many times to produce all possible permutations of the input.  It
+% follows that that starting from the same variable valuation, the loop ends
+% with the same valuation for any permutation of input values, e.g., the reducer
+% will output the same value for [1;2;3;4;5], [1;2;4;3;5], [1;4;2;3;5],
+% [4;1;2;3;5], etc.  Recall that the first program transformation task stores
+% all output values in variables that will stay unchanged until the end of the
+% loop. The validity of Equation~(\ref{eq:commu}) also implies that the
+% execution of the loop produces the same sequence of outputs.
+% 
+% We explain why that the validity of Equation~(\ref{eq:commu}) is sufficient to
+% prove the reducer $s_1;\rloop\{s_2\};s_3$ commutative. Notice that $s_1$ does
+% not read from the input (assumed at the beginning of this subsection). The
+% execution of $s_1$ is deterministic in the sense that from the same initial
+% valuation, it outputs the same sequence of values and ends at the same
+% valuation. For the execution of $\rloop\{s_2\}$, from the validity of
+% Equation~(\ref{eq:commu}), any permutation of input values leads the reducer
+% to the same final valuation and the same sequence of outputs at the end of the
+% loop.  Before executing the commands $s_3$, all inputs have been read (the
+% loop exit condition) already. Similar to the case of $s_1$, $s_3$ does not
+% read from the input and hence the execution of $s_3$ is deterministic. It
+% follows that for all permutations of inputs, the reducer outputs the same
+% sequence of values.
+%
 
-In the example of ``average'', the values of $s$ and $c$ are the same no matter the reducer first reads $n_1$ and then $n_2$ or reads the two values in the swapped order.
-So it computes the same value for the input [1;2;\textbf{3};\textbf{4};5] and any other input with two consecutive values being swapped, e.g., [1;2;4;3;5].
-The swap operation can be applied arbitrarily many times to produce all possible permutations of the input.
-It follows that that starting from the same variable valuation, the loop ends with the same valuation for any permutation of input values, e.g., the reducer will output the same value for [1;2;3;4;5], [1;2;4;3;5], [1;4;2;3;5], [4;1;2;3;5], etc.
-Recall that the first program transformation task stores all output values in variables that will stay unchanged until the end of the loop.
-The validity of Equation~(\ref{eq:commu}) also implies that the execution of the loop produces the same sequence of outputs.
+%=============================================================================
+\subsection{Optimization: Live Variable Analysis} \label{section:optimizations}
+%=============================================================================
 
-We explain why that the validity of Equation~(\ref{eq:commu}) is sufficient to prove the reducer $s_1;\rloop\{s_2\};s_3$ commutative.
-Notice that $s_1$ does not read from the input (assumed at the beginning of this subsection).
-The execution of $s_1$ is deterministic in the sense that from the same initial valuation, it outputs the same sequence of values and ends at the same valuation.
-For the execution of $\rloop\{s_2\}$, from the validity of Equation~(\ref{eq:commu}), any permutation of input values leads the reducer to the same final valuation and the same sequence of outputs at the end of the loop.
-Before executing the commands $s_3$, all inputs have been read (the loop exit condition) already.
-Similar to the case of $s_1$, $s_3$ does not read from the input and hence the execution of $s_3$ is deterministic.
-It follows that for all permutations of inputs, the reducer outputs the same sequence of values.}
-
-\subsection{Optimization: Live Variable Analysis}
-\label{section:optimizations}
 Here we explain how live variable analysis is used in J-ReCoVer to improve the precision of commutativity checking.
@@
 
-\hide{
-\begin{figure}[hbt]
-	\begin{minipage}{0.4\textwidth}
-		\begin{algorithm}[H]
-			$s:= 0$; \;
-			\Loop{}{
-				$t:=\cur$;
-				$s:= s + t$\;
-			};
-			$out(s)$\;\;\;
-		\end{algorithm}
-		\caption{A commutative reducer with an invalid Equation~(\ref{eq:commu}).}
-		\label{fig:reducer_opt}
-	\end{minipage}
-	\ \ \ \ \ \ \ \
-	\begin{minipage}{0.5\textwidth}
-		\LinesNumbered
-		\centering
-		\begin{minipage}{0.75\textwidth}
-		\begin{algorithm}[H]
-			$c_1;c_2;\ldots;c_i$\;
-			\lIf{$g_1$}{$\ldots$}
-			\lElseIf{ $g_2$}{$\ldots$}
-			\lElseIf{ $g_3$}{$\ldots$}
-			\lElseIf{ $g_m$}{$c_{i+1};\ldots ;c_n; out(v);\ldots$}
-			\lElse{ $\ldots$}
-		\end{algorithm}
-	\end{minipage}
-		\caption{The $s_3$ command with an $out(v)$ command in nested branches.}
-		\label{fig:nested_out}
-	\end{minipage}
-\end{figure}
+%\begin{figure}[hbt]
+%	\begin{minipage}{0.4\textwidth}
+%		\begin{algorithm}[H]
+%			$s:= 0$; \;
+%			\Loop{}{
+%				$t:=\cur$;
+%				$s:= s + t$\;
+%			};
+%			$out(s)$\;\;\;
+%		\end{algorithm}
+%		\caption{A commutative reducer with an invalid 
+%                   Equation~(\ref{eq:commu}).}
+%		\label{fig:reducer_opt}
+%	\end{minipage}
+%	\ \ \ \ \ \ \ \
+%	\begin{minipage}{0.5\textwidth}
+%		\LinesNumbered
+%		\centering
+%		\begin{minipage}{0.75\textwidth}
+%		\begin{algorithm}[H]
+%			$c_1;c_2;\ldots;c_i$\;
+%			\lIf{$g_1$}{$\ldots$}
+%			\lElseIf{ $g_2$}{$\ldots$}
+%			\lElseIf{ $g_3$}{$\ldots$}
+%			\lElseIf{ $g_m$}{$c_{i+1};\ldots ;c_n; out(v);\ldots$}
+%			\lElse{ $\ldots$}
+%		\end{algorithm}
+%	\end{minipage}
+%		\caption{The $s_3$ command with an $out(v)$ command in 
+%                   nested branches.}
+%		\label{fig:nested_out}
+%	\end{minipage}
+%\end{figure}
 
-To handle such a situation, we need an algorithm to collect a set of variables whose value may affect the output.
-Recall that the first program transformation task uses a set of variables $V_2=\{v_{out_k} \mid k \in [1,l]\}$, where $l$ is the number of output commands occurred in $s_2$, to collect output values occurred in the loop body $s_2$.
-The set $V_2$ is exactly the set of variables that will affect the output inside the loop.}
+% To handle such a situation, we need an algorithm to collect a set of variables
+% whose value may affect the output.  Recall that the first program
+% transformation task uses a set of variables $V_2=\{v_{out_k} \mid k \in
+% [1,l]\}$, where $l$ is the number of output commands occurred in $s_2$, to
+% collect output values occurred in the loop body $s_2$.  The set $V_2$ is
+% exactly the set of variables that will affect the output inside the loop.
 
@@
 
-\hide{
-Without loss of generality, we assume there is only one output command after the loop.
+% Without loss of generality, we assume there is only one output command after the loop.
 Then the code after the loop (i.e., the $s_3$ part of the reducer) can only be in the form of Figure~\ref{fig:nested_out}.
-We unfold all concatenation of commands, so now the commands $c_1\ldots c_n$ are either assignment commands $w:=e$ or branch command $\ite{g}{c'_1}{c'_2}$, and the only output command stays in the $m$-th layer of the branch command after $c_i$.
+% We unfold all concatenation of commands, so now the commands $c_1\ldots c_n$ are either assignment commands $w:=e$ or branch command $\ite{g}{c'_1}{c'_2}$, and the only output command stays in the $m$-th layer of the branch command after $c_i$.
 For the case that $m=0$, the entire branch command in Lines 2-6 of Figure~\ref{fig:nested_out} is replaced with $out(v)$.
+% 
+% The data flow analysis algorithm works as follows.
+% A set $V_3$ whose value is initially a singleton set $\{v\}$ is used to remember the variables that might flow to the output command $out(v)$ in $s_3$ (in Figure~\ref{fig:nested_out}).
+% The commands and guards will be inspected in the following order $c_{n}$,$\ldots$,$c_{i+1}$, $g_m$, $g_{m-1}$, $\ldots$, $g_1$, $c_i$, $\ldots$, $c_2$, $c_1$.
+For the case that a guard $g_j$ for $j\in [1,m]$ is being processed, we simply add all variables occurred in $g_j$ to $V_3$.
+% For the case that a command $c_j$ for $j\in [1,n]$ is being processed, we need to handle two different cases:
+% \begin{itemize}
+% 	\item $c_j$ is an assignment $w:=e$ and $w\in V_3$: all variables in $e$ are added to $V_3$.
+% 	\item $c_j$ is a branch $\ite{g}{c'_1}{c'_2}$: the algorithm starts from the same set $V_3$ and processes $c'_1$ and $c'_2$ individually and independently (in a similar manner) to obtain $V_3^1$ and $V_3^2$.
+After that, the algorithm takes their union $V_3^1\cup V_3^2$ as the new value of $V_3$.
+% \end{itemize}
+% After the entire $s_3$ is being processed we get the set of important variables that might affect the outputs that happen in $s_3$.
+% Then we modify the Equation~(\ref{eq:commu}) to the one below
+% \begin{equation}
+% F(n_1, F(n_2,x_1,x_2,\ldots,x_k) )=_{PosF(V_2\cup V_3)} F(n_2, F(n_1,x_1,x_2,\ldots,x_k) )
+% \label{eq:commu2}
+% \end{equation}
+% The function $PosF(X)$ returns the corresponding positions of variables in $X$ in the output of $F(n,x_1,\ldots,x_k) $.
+E.g., if $X = \{x_1,x_4,y\}$, where $y\notin \{x_1,\ldots,x_k\}$, then $PosF(X)=\{1,4\}$.
+% The use of Equation~(\ref{eq:commu2}) is critical to the success of our approach.
 
-The data flow analysis algorithm works as follows.
-A set $V_3$ whose value is initially a singleton set $\{v\}$ is used to remember the variables that might flow to the output command $out(v)$ in $s_3$ (in Figure~\ref{fig:nested_out}).
-The commands and guards will be inspected in the following order $c_{n}$,$\ldots$,$c_{i+1}$, $g_m$, $g_{m-1}$, $\ldots$, $g_1$, $c_i$, $\ldots$, $c_2$, $c_1$.
-For the case that a guard $g_j$ for $j\in [1,m]$ is being processed, we simply add all variables occurred in $g_j$ to $V_3$.
-For the case that a command $c_j$ for $j\in [1,n]$ is being processed, we need to handle two different cases:
-\begin{itemize}
-	\item $c_j$ is an assignment $w:=e$ and $w\in V_3$: all variables in $e$ are added to $V_3$.
-	\item $c_j$ is a branch $\ite{g}{c'_1}{c'_2}$: the algorithm starts from the same set $V_3$ and processes $c'_1$ and $c'_2$ individually and independently (in a similar manner) to obtain $V_3^1$ and $V_3^2$.
-After that, the algorithm takes their union $V_3^1\cup V_3^2$ as the new value of $V_3$.
-\end{itemize}
-After the entire $s_3$ is being processed we get the set of important variables that might affect the outputs that happen in $s_3$.
-Then we modify the Equation~(\ref{eq:commu}) to the one below
-\begin{equation}
-F(n_1, F(n_2,x_1,x_2,\ldots,x_k) )=_{PosF(V_2\cup V_3)} F(n_2, F(n_1,x_1,x_2,\ldots,x_k) )
-\label{eq:commu2}
-\end{equation}
-The function $PosF(X)$ returns the corresponding positions of variables in $X$ in the output of $F(n,x_1,\ldots,x_k) $.
-E.g., if $X = \{x_1,x_4,y\}$, where $y\notin \{x_1,\ldots,x_k\}$, then $PosF(X)=\{1,4\}$.
-The use of Equation~(\ref{eq:commu2}) is critical to the success of our approach. }
-\hide{
-\subsection{Computing the $F$ function using symbolic execution with an efficient data structure}
-\label{section:opt2}
-
-The computation of $F$ in Equation~(\ref{eq:commu2}) can be done in several different ways.
+% \subsection{Computing the $F$ function using symbolic execution with an efficient data structure}
+% \label{section:opt2}
+% 
+% The computation of $F$ in Equation~(\ref{eq:commu2}) can be done in several different ways.
 For example, one can construct a formula in the style of bounded model checking.
@@
 Below we first review the standard symbolic execution algorithm and then explain how we use it to construct the formula $F$.
-
-First, we define the set $\Var_0=\{v_0 \mid v \in \Var \}\cup \{c_0\}$ as the set of initial symbolic values of all variables, where $c_0$ is used to denote the symbolic value from the input.
-A \emph{symbolic state} is a triple $\langle pc, val, cmds \rangle$, where the \emph{path condition} $pc$ is a guard in $\Grd$ over $\Var_0$, the \emph{symbolic valuation} is a mapping from variables in $\Var$ to an expression in $\Exp$ over $\Var_0$, and $cmds\in \Cmd$ is the remaining commands to be executed.
+% 
+% 
+% First, we define the set $\Var_0=\{v_0 \mid v \in \Var \}\cup \{c_0\}$ as the set of initial symbolic values of all variables, where $c_0$ is used to denote the symbolic value from the input.
+% A \emph{symbolic state} is a triple $\langle pc, val, cmds \rangle$, where the \emph{path condition} $pc$ is a guard in $\Grd$ over $\Var_0$, the \emph{symbolic valuation} is a mapping from variables in $\Var$ to an expression in $\Exp$ over $\Var_0$, and $cmds\in \Cmd$ is the remaining commands to be executed.
 The \emph{initial symbolic state} is $\langle \true, val_0, s_2\rangle$, where $val_0(v) = v_0$ for all $v\in\Var$ and $s_2$ is the loop body of the reducer.
-One can compute the next symbolic state of $\langle pc, val, c;cmds \rangle$ according to the following transition rules.
+% One can compute the next symbolic state of $\langle pc, val, c;cmds \rangle$ according to the following transition rules.
 Recall that $c$ is either in the form of $v:= e$ or $\ite{g}{c_1}{c_2}$ after the program transformation tasks are performed:
-\begin{enumerate}
-	\item If $c$ is $v:= e$, the next symbolic state is $\langle pc, val[v \rightarrow val(e) ], cmds \rangle$.
-	\item If $c$ is $\ite{g}{c_1}{c_2}$, the next symbolic states are $\langle pc\wedge g, val, c_1.cmds \rangle$ and $\langle pc\wedge not\  g, val, c_2.cmds \rangle$.
-\end{enumerate}
-
-Here we lift the $val$ function from variables to expressions in the standard way and $val[v \rightarrow val(e) ]$ is obtained by reassigning the value of $v$ in $val$ to $val(e)$.
+% \begin{enumerate}
+% 	\item If $c$ is $v:= e$, the next symbolic state is $\langle pc, val[v \rightarrow val(e) ], cmds \rangle$.
+% 	\item If $c$ is $\ite{g}{c_1}{c_2}$, the next symbolic states are $\langle pc\wedge g, val, c_1.cmds \rangle$ and $\langle pc\wedge not\  g, val, c_2.cmds \rangle$.
+% \end{enumerate}
+% 
+% Here we lift the $val$ function from variables to expressions in the standard way and $val[v \rightarrow val(e) ]$ is obtained by reassigning the value of $v$ in $val$ to $val(e)$.
 The execution from a symbolic state terminates when its path condition is conflict or the commands to be executed become empty, i.e., all commands have been processed.
 So far it is standard.
-
-For the loop body $s_2$, symbolic execution is guaranteed to terminate because there exist no commands in $s_2$ that may lead to infinite computations.
-When the execution terminates, we collect all states with empty commands $\langle pc, val, \emptyset \rangle$ as a set $T$ and use them to create the function $F$ in Equation~(\ref{eq:commu2}).
-First, we create for each variable $x\in\Var$ a formula $f_x$ whose value is $\bigvee_{\langle pc, val, \emptyset \rangle \in T} (pc \wedge val(x))$.
-The function $F(n,x_1,x_2,\ldots,x_k)$ simply returns the tuple $(f_{x_1},f_{x_2},\ldots, f_{x_k})$.
-
-However, doing symbolic execution in a naive way can be extremely inefficient.
-The length of the formula $val(v)$ can grow exponentially w.r.t.
+% 
+% For the loop body $s_2$, symbolic execution is guaranteed to terminate because there exist no commands in $s_2$ that may lead to infinite computations.
+% When the execution terminates, we collect all states with empty commands $\langle pc, val, \emptyset \rangle$ as a set $T$ and use them to create the function $F$ in Equation~(\ref{eq:commu2}).
+% First, we create for each variable $x\in\Var$ a formula $f_x$ whose value is $\bigvee_{\langle pc, val, \emptyset \rangle \in T} (pc \wedge val(x))$.
+% The function $F(n,x_1,x_2,\ldots,x_k)$ simply returns the tuple $(f_{x_1},f_{x_2},\ldots, f_{x_k})$.
+% 
+% However, doing symbolic execution in a naive way can be extremely inefficient.
+% The length of the formula $val(v)$ can grow exponentially w.r.t.
 the input commands.
@@
 One way to alleviate the problem is to apply formula simplification algorithms, e.g., those implemented in Z3.
-Here we propose in a very simple alternative solution that works quite well in our reducer benchmarks.
-
-We use a more efficient data structure to store symbolic values.
+% Here we propose in a very simple alternative solution that works quite well in our reducer benchmarks.
+% 
+% We use a more efficient data structure to store symbolic values.
 At a high level, in a symbolic state, we count the number of occurrences of each symbolic values in $\Var_0$ and update the count when operations such as $+$ and $-$ is applied.
 For other operations $x\odot y$, we create a new symbolic expression $val(x) \odot val(y)$ and count its number of occurrence as one.
-More concretely, we use a map $sv_x:\Exp\rightarrow \mathbb{N}$ (symbolic value of $x$) to remember the number of occurrences of each expression in $x$.
+% More concretely, we use a map $sv_x:\Exp\rightarrow \mathbb{N}$ (symbolic value of $x$) to remember the number of occurrences of each expression in $x$.
 We have $val(x)= (\Sigma_{z\in \dom{sv_x}} (z\times sv_x(z)) )$, where $\dom{sv}=\{e\mid sv(e)\neq 0\}$.
-Initially, $sv_x(x_0) = 1$ and $sv_x (e) =0$ for all $e\neq x$.
+% Initially, $sv_x(x_0) = 1$ and $sv_x (e) =0$ for all $e\neq x$.
 Assume that the symbolic value of $x,y$ are $sv_x,sv_y$ in the current symbolic state.
 The symbolic value $sv'_x$ of $x$ after the assignment $x:=p\circ q$ is defined as follows.
+% 
+% \begin{itemize}
+% 	\item For the case that $\circ \in\{+,-\}$, we have $sv'_x(z) = sv_p(z)\circ  sv_q(z)$.
+% 	\item For the case that $\circ \notin\{+,-\}$, we define $sv'_x(val(p) \circ val(q)) =1$ and $sv'_x(e) = 0$ for all $e\neq val(p) \circ val(q)$.
+% \end{itemize}
+% To make the definition complete for our simple reducer program commands, we further define (I) $sv_{\cur}(c_0) =1$ and $sv_{\cur}(e)=0$ for $e\neq \cur$, (II) $sv_{n}(1) =n$ and $sv_{n}(e)=0$ for $e\neq 1 \wedge n\in \Z$.
+% This data structure is efficient for strong symbolic values of reducer programs mainly for reason that the operations $+$ and $-$ are quite heavily used in such programs.
+% Here we give a tiny example. Initially, $sv_x(x_0)=1$. After the commands $x:=x*x;x:=x+x$, we get $sv_x(x_0*x_0)=1$ and $sv_x(x_0*x_0)=2$, respectively.
 
-\begin{itemize}
-	\item For the case that $\circ \in\{+,-\}$, we have $sv'_x(z) = sv_p(z)\circ  sv_q(z)$.
-	\item For the case that $\circ \notin\{+,-\}$, we define $sv'_x(val(p) \circ val(q)) =1$ and $sv'_x(e) = 0$ for all $e\neq val(p) \circ val(q)$.
-\end{itemize}
-To make the definition complete for our simple reducer program commands, we further define (I) $sv_{\cur}(c_0) =1$ and $sv_{\cur}(e)=0$ for $e\neq \cur$, (II) $sv_{n}(1) =n$ and $sv_{n}(e)=0$ for $e\neq 1 \wedge n\in \Z$.
-This data structure is efficient for strong symbolic values of reducer programs mainly for reason that the operations $+$ and $-$ are quite heavily used in such programs.
-Here we give a tiny example. Initially, $sv_x(x_0)=1$. After the commands $x:=x*x;x:=x+x$, we get $sv_x(x_0*x_0)=1$ and $sv_x(x_0*x_0)=2$, respectively.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Evaluation} \label{section:exp}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Evaluation}
-\label{section:exp}
 J-ReCoVer is implemented in Java and built on top of Soot 2.5.0 and Z3 4.7.1.
@@
 
-\hide{
-For the optimization based on live variable analysis (Section~\ref{section:optimizations}), we evaluate them based on real-world benchmark sets collected from open repositories (118 examples).
-The difference between the version with and without this optimization is very clear.
-The results are presented in table~\ref{tab:opt1}.
-The first column is the result without optimization and the second column is the result with optimization.
-The precision of the analysis is improved from $6.8\%$ to $97.5\%$.
-However, this new program transformation task is not implemented in J-ReCoVer yet.
+% For the optimization based on live variable analysis
+% (Section~\ref{section:optimizations}), we evaluate them based on real-world
+% benchmark sets collected from open repositories (118 examples). The difference
+% between the version with and without this optimization is very clear. The
+% results are presented in table~\ref{tab:opt1}. The first column is the result
+% without optimization and the second column is the result with optimization.
+% The precision of the analysis is improved from $6.8\%$ to $97.5\%$.  However,
+% this new program transformation task is not implemented in J-ReCoVer yet.
+%
+% If we look into scrutiny, we failed to verify any example using
+% Equation~(\ref{eq:commu}). The reason is that when Soot converts a Java
+% program to the Jimple format, it always uses a temporary variable to store the
+% value of $\cur$ in the loop body (similar to the example in
+% Figure~\ref{fig:reducer_opt}). We tried a simpler heuristics approach that
+% only ignores the temporary variables and the result is not as good as using
+% live variable analysis, because the values of the temporary variables often
+% also propagate to other variables.
 
-If we look into scrutiny, we failed to verify any example using Equation~(\ref{eq:commu}).
-The reason is that when Soot converts a Java program to the Jimple format, it always uses a temporary variable to store the value of $\cur$ in the loop body (similar to the example in Figure~\ref{fig:reducer_opt}).
-We tried a simpler heuristics approach that only ignores the temporary variables and the result is not as good as using live variable analysis, because the values of the temporary variables often also propagate to other variables.
-\begin{table}[htb]
-	\centering
-	\begin{tabular}{|l|l|l|}
-		\hline
-		&W/O optimization	& With optimization\\
-		\hline
-		\hline
-		Commutative& 0&106\\
-		\hline
-		Non-commutative&8&9\\
-		\hline
-		Unknown&110&3\\
-		\hline
-		Precision& 6.8\% & 97.5\%\\
-		\hline
+%\begin{table}[htb]
+%	\centering
+%	\begin{tabular}{|l|l|l|}
+%		\hline
+%		&W/O optimization	& With optimization\\
+%		\hline
+%		\hline
+%		Commutative& 0&106\\
+%		\hline
+%		Non-commutative&8&9\\
+%		\hline
+%		Unknown&110&3\\
+%		\hline
+%		Precision& 6.8\% & 97.5\%\\
+%		\hline
+%		
+%	\end{tabular}
+%
+%        \caption{The improvement of precision using data flow analysis. The row
+%        ``Precision'' is calculated as the number of examples that J-ReCoVer
+%        returns commutative or non-commutative divided by the total number of
+%        example.}
+%
+%	\label{tab:opt1}
+%\end{table}
 
-	\end{tabular}
-	\caption{The improvement of precision using data flow analysis.
-The row ``Precision'' is calculated as the number of examples that J-ReCoVer returns commutative or non-commutative divided by the total number of example.}
-	\label{tab:opt1}
-\end{table}
-}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-06-23 draft.tex
Section 3: overview of the tool

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Overview of the J-ReCoVer tool} \label{sec:overview}
+\vspace*{-2mm}
+\section{Overview of the J-ReCoVer Tool} \label{sec:overview}
+\vspace*{-1mm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The input of J-ReCoVer is a reducer program written in Java, which is the most popular programming language used in the Hadoop~\cite{hadoop} MapReduce framework.
-The J-ReCoVer tool has three main components, the \emph{Preprocessor}, the \emph{Prover}, and the \emph{BugFinder}.
-As the name suggests, the Preprocessor reads as input a reducer program and performs the required preprocessing.
-The goal of Prover is to show that a given reducer is commutative and the goal of BugFinder is the opposite.
-The architecture of J-ReCoVer can be found in Figure~\ref{fig:overview-jrecover}.
-The user can input a reducer program to J-ReCoVer either through our web-interface or binary application installed on their own machine.
+The input of J-ReCoVer is a reducer program written in Java, which is the most
+popular programming language used in the Hadoop~\cite{hadoop} MapReduce
+framework. The J-ReCoVer tool has three main components, the
+\emph{Preprocessor}, the \emph{Prover}, and the \emph{BugFinder}. As the name
+suggests, the Preprocessor reads as input a reducer program and performs the
+required preprocessing. The goal of Prover is to show that a given reducer is
+commutative, and the goal of BugFinder is the opposite. The architecture of
+J-ReCoVer can be found in Figure~\ref{fig:overview-jrecover}. The user can input
+a reducer program to J-ReCoVer either through our web-interface or use a binary
+application installed on his/her own machine.
 
-\textbf{The Preprocessor component} first compiles a reducer program to bytecode and use the tool Soot to further convert it to the so-called ``Jimple'' format, which is an intermediate language that is designed to simplify the analysis of Java programs.
-Under the Hadoop MapReduce framework, the permutation of the input is handled by the scheduler/shuffler component and is affected by things like network latency, which is not controllable by programmers.
-In order to deal with this issue, we wrote our own dummy Hadoop environment for the reducer as a part of the Preprocessor component so that the input order of the reducer is now controlled by J-ReCoVer.
-Finally, we perform in the Preprocessor some program transformation tasks to simplify the analysis.
-For example, we convert all output commands $out(e)$ inside loops to a special assignment (will be explained in Section~\ref{sec:program_trans1}).
+The \emph{Preprocessor component} first compiles a reducer program to bytecode
+and uses the tool Soot to further convert it to the so-called ``Jimple'' format,
+which is an intermediate language designed to simplify the analysis of Java
+programs. Under the Hadoop MapReduce framework, the permutation of the input is
+handled by the scheduler/shuffler component and is affected by issues like
+network latency, which are not controllable by programmers. In order to deal
+with such issues, we wrote our own dummy Hadoop environment for the reducer as a
+part of the Preprocessor component so that the input order of the reducer is now
+controlled by J-ReCoVer. Finally, the Preprocessor performs some program
+transformation tasks to simplify the analysis. For example, it converts all
+output commands $out(e)$ inside loops to a special assignment (as explained in
+Section~\ref{sec:program_trans1}).
 
 \begin{wrapfigure}{r}{7cm}
-	\vspace{-0.5cm}
+	\vspace{-8mm}
 \centering
@@
 
-\textbf{The BugFinder component} randomly generates pairs of lists.
-The lists in a pair are permutations of each other.
-A concrete counterexample is reported if inputting any pair of lists from the generated ones to the reducer generates different results.
-Our procedure for generating random pairs is quite naive.
-We use five different input list of lengths 5, 7, 9, 11, and 13.
-For each length, we generate 300 lists and pick uniformly at random one of its permutations.
-Although the approach is simple, in practice it finds counterexamples in all of our non-commutative benchmarks in a few seconds.
+%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+\enlargethispage{4mm}
+%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 
-\textbf{The Prover component} reduces the commutativity problem to an SMT formula satisfiability problem.
-At a high level, we check equivalence between a reducer program and its variant that has two consecutive inputs swapped.
-We show that this can be reduced to an SMT problem and give it to the SMT solver Z3 for solving.
-In case that Z3 proved the formula unsatisfiable, we know that swapping any two consecutive inputs of the reducer will not change its output.
-Because all permutations of a list can be obtained by swapping consecutive elements finitely many times, it follows that the reducer outputs the same value for all permutations of the same list of inputs.
-In this case,  J-ReCoVer stops and reports that the reducer is commutative.
+The \emph{BugFinder component} randomly generates pairs of lists. The lists in a
+pair are permutations of each other. A concrete counterexample is reported if
+inputting any pair of lists from the generated ones to the reducer generates
+different results. Our procedure for generating random pairs is quite naive. We
+use five different input list of lengths 5, 7, 9, 11, and 13. For each length,
+we generate 300 lists and pick uniformly at random one of its permutations.
+Although the approach is simple; in practice, it finds counterexamples in all of
+our non-commutative benchmarks in a few seconds.
+
+The \emph{Prover component} reduces the commutativity problem to an SMT
+satisfiability problem. From a high-level point of view, we check equivalence
+between a reducer program and its variant that has two consecutive inputs
+swapped. We show that this can be reduced to a first-order formula and give it
+to the SMT solver Z3 for solving. In case that Z3 proves the formula
+unsatisfiable, we know that swapping any two consecutive inputs of the reducer
+will not change its output. Since all permutations of a list can be obtained by
+swapping consecutive elements finitely many times, it follows that the reducer
+outputs the same value for all permutations of the same list of inputs. In this
+case, J-ReCoVer stops and reports that the reducer is commutative.
 

### 2019-06-24 draft.tex
check the commit by Tomas and some minor modification

@@
 the results cannot be directly applied.
-
 Besides verification, another interesting research direction is the
@@
 Some reducers use two (or more) top-level loops to compute the output, possibly
-interleaved with some non-looping code. {\color{red} These loops are executed
-sequentially, repeatedly iterating over the input list from its beginning.} For
+interleaved with some non-looping code. These loops are executed
+sequentially, repeatedly iterating over the input list from its beginning. For
 example, for calculating the standard deviation, one first computes the average
@@
 partitioning it into two (or more) reducers, each containing a single top-level
-loop, and then verifying these reducers separately.\footnote{\color{red}Nested
-loops can be transformed into branches of the top-level loop.} The top-level
+loop, and then verifying these reducers separately.
+\footnote{Nested
+loops can be removed by adding additional branch statements, since both the inner and outer loop are over the same input list.
+In fact, such program construct never occured in examples we have ever seen.} The top-level
 loops communicate through shared variables.  After the transformation, reducers
 corresponding to the second top-level loop (and possibly further such loops)
-will work with random values of the shared variable, which over-approximates the
-original behaviour.
+will work with random initial values of the shared variable, which over-approximates the original behavior.
+Usually, the second (or further) top-level loop are commutative even with arbitary initial shared variable values and hence J-ReCoVer can be used to prove it.
 
-For instance, for the case of the standard deviation, the first reducer computes
-the average, and the other reducer performs the rest of the computation. The
-second reducer replaces the average with a non-deterministic value and thus
-``over-approximates'' all possible outputs of the standard deviation
-computation. Equivalently, it computes an output for all possible ``average''
-values. However, this reducer is still commutative, and its commutativity can be
-verified.
+%For instance, for the case of the standard deviation, the first reducer computes
+%the average, and the other reducer performs the rest of the computation. The
+%second reducer replaces the average with a non-deterministic value and thus
+%``over-approximates'' all possible outputs of the standard deviation
+%computation. Equivalently, it computes an output for all possible ``average''
+%values. However, this reducer is still commutative, and its commutativity can be verified.
 
@@
 J-ReCoVer is implemented in Java and built on top of Soot 2.5.0 and Z3 4.7.1.
-We run J-ReCoVer on a virtual machine running on a server with AMD Opteron 6376 CPU.
-4GB of memory is allocated to this virtual machine.
-The operation system is Ubuntu 16.04.5 LTS.
+We run J-ReCoVer on a virtual machine with 4GB of memeory running on a server with AMD Opteron 6376 CPU.The operation system is Ubuntu 16.04.5 LTS.
 
@@
 
-There are only three cases that J-ReCoVer with live variable analysis cannot handle.
+There are only three cases that J-ReCoVer cannot handle.
 The reason that J-ReCoVer fails is that the three reducers use more complicated structure than what J-ReCoVer currently supports; they use a branch statement before entering the loop, i.e., in the form $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$.
@@
 
-J-ReCoVer is the first tool specialized to the reducer commutativity problem, although the approach is simple, it solves most of the real benchmarks we collected from repositories
+J-ReCoVer is the first tool specialized to the reducer commutativity problem, although the approach is simple, it solves most of the real benchmarks we collected from repositories.
 There is no other tool that could handle the reducers as they are.

### 2019-06-24 draft.tex
Slight language modifications in Footnote 2 (nested loops)

@@
 Some reducers use two (or more) top-level loops to compute the output, possibly
-interleaved with some non-looping code. These loops are executed
-sequentially, repeatedly iterating over the input list from its beginning. For
-example, for calculating the standard deviation, one first computes the average
-of inputs and then uses it to compute the final result (using two passes over
-the input list). In that case, we suggest to verify the reducer by first
-partitioning it into two (or more) reducers, each containing a single top-level
-loop, and then verifying these reducers separately.
-\footnote{Nested
-loops can be removed by adding additional branch statements, since both the inner and outer loop are over the same input list.
-In fact, such program construct never occured in examples we have ever seen.} The top-level
-loops communicate through shared variables.  After the transformation, reducers
-corresponding to the second top-level loop (and possibly further such loops)
-will work with random initial values of the shared variable, which over-approximates the original behavior.
-Usually, the second (or further) top-level loop are commutative even with arbitary initial shared variable values and hence J-ReCoVer can be used to prove it.
+interleaved with some non-looping code. These loops are executed sequentially,
+repeatedly iterating over the input list from its beginning. For example, for
+calculating the standard deviation, one first computes the average of inputs and
+then uses it to compute the final result (using two passes over the input list).
+In that case, we suggest to verify the reducer by first partitioning it into two
+(or more) reducers, each containing a single top-level loop, and then verifying
+these reducers separately.\footnote{Nested loops can be removed by adding
+additional branch statements since both the inner and outer loop are over the
+same input list. In fact, such a program construct has never occurred in the
+examples we have seen.} The top-level loops communicate through shared
+variables. After the transformation, reducers corresponding to the second
+top-level loop (and possibly further such loops) will work with random initial
+values of the shared variable, which over-approximates the original behavior.
+Usually, the second (or further) top-level loop are commutative even with
+arbitrary initial shared variable values and hence J-ReCoVer can be used to
+prove it.
 

### 2019-06-24 draft.tex
More experimental results

--- 2019-06-24 draft.tex
@@
 J-ReCoVer is implemented in Java and built on top of Soot 2.5.0 and Z3 4.7.1.
-We run J-ReCoVer on a virtual machine with 4GB of memeory running on a server with AMD Opteron 6376 CPU.The operation system is Ubuntu 16.04.5 LTS.
+We run J-ReCoVer on a virtual machine with 4GB of memeory running Ubuntu 16.04.5 LTS on a server with AMD Opteron 6376 CPU.
 
@@
 
+\begin{wrapfigure}{r}{9cm}
+	\begin{tabular}{|c|c|c|c||c|c|c|}
+		\hline
+		&Compile &Prepossesor &Prover & Lines & Variables & If-branches\\
+		\hline
+		Min. &6.22   &2.15        &0.032 & 5 & 4 & 0\\
+		Avg. &6.54   &2.44        &0.046 & 20.5 & 14.7 & 1.2\\
+		Max. &7.28   &3.06        &0.101 & 58 & 37 & 5\\
+		\hline
+	\end{tabular}
+	\caption{Time in each step, size of the reducers}
+\end{wrapfigure}  
+For the $115$ solved cases, $72\%$ of the execution time are spent in compiling JAVA source code to bytecode, which is the input of the Soot tool.
+Another $27\%$ of the execution time are spent in the Propossesor, in which Soot is used to transform JAVA bytecode to Jimple and perform the program transformations.
+The time spent in Solver is quite limited, since the real-world integer reducer programs are usually not that big.
+
 J-ReCoVer is the first tool specialized to the reducer commutativity problem, although the approach is simple, it solves most of the real benchmarks we collected from repositories.
 There is no other tool that could handle the reducers as they are.
-Perhaps some other tools could be applied on the transformed programs, but the transformations would still be needed, and our SMT-based backend verifier turned out to work efficiently, and so we did not feel a need to replace it by another verification tool.
+Perhaps some other tools could be applied on the transformed programs, but the transformations would still be needed, and our SMT-based back-end verifier turned out to work efficiently, and so we did not feel a need to replace it by another verification tool.
 Of course, in the future, this can be done if need be.

### 2019-06-24 draft.tex
Sections 4.1 and 4.2

--- 2019-06-24 draft.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace*{-2mm}
 \section{The Preprocessor and the Prover} \label{sec:preprocessor_prover}
+\vspace*{-1mm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Before entering the Prover component, the Preprocessor first performs a few program transformation tasks to simplify the verification task (Section~\ref{sec:program_trans1}).
-The output of the preprocessor is a commutativity-equivalent reducer program.
-Then the algorithm of the Prover is explained in Section~\ref{sec:prover}.
+Before entering the Prover component, the Preprocessor first performs two
+program transformations to simplify the verification task
+(Section~\ref{sec:program_trans1}). The output of the preprocessor is a
+commutativity-equivalent reducer program. The algorithm of the Prover is then
+explained in Section~\ref{sec:prover}.
 
 %=============================================================================
-\subsection{The Program Transformation Task in the Preprocessor}
+\vspace*{-2mm}
+\subsection{The Program Transformations in the Preprocessor}
 \label{sec:program_trans1}
+\vspace*{-1mm}
 %=============================================================================
 
-\subsubsection{Handling output inside the loop body} Recall that the reducer program can perform the ouput command $out(e)$ inside the loop body $s_2$.
-In this case, we remember the output value in a fresh variable $v$ and replace the $out(e)$ command with an assignment $v:=e$.
-Notice that the value of $v$ stays the same from the point it has been assigned a value until the end of the loop body $s_2$.
-If the values of $v$ are the same for all permutations of input lists at the end of $s_2$, we know that the reducer is commutative w.r.t. to all output values produced inside the loop body $s_2$.
+%-----------------------------------------------------------------------------
+\paragraph*{Handling the access to $\cur$ before entering the loop.}
+%-----------------------------------------------------------------------------
 
-\begin{wrapfigure}{r}{3.5cm}
-	\vspace{-1.5cm}
+\begin{wrapfigure}[11]{r}{3.5cm}
+	\vspace{-17mm}
 	\begin{algorithm}[H]
@@
 	\vspace{-0.8cm}
-	\caption{Reducer max$^+$}
-	\vspace{-0.8cm}
+	\caption{The max$^+$ reducer with input before the main loop.}
+	\vspace{-12mm}
 	\label{fig:reducer_max1}
@@
 
-\subsubsection{Handling the access to $\cur$ before entering the loop} In real-world examples, it is often that the $s_1$ part of the reducer also reads from the input.
-In the example in Figure~\ref{fig:reducer_max1}, the reducer program remembers the first input value in the variable $m$, increases its value by 10, and then updates its value to bigger ones if any occurs in the loop.
-The corresponding Equation~(\ref{eq:commu}) is valid in this case.
-However, the reducer is not commutative.
-A counterexample can be easily found.
-With the list $[1,2,3,4,5]$ and its permutation $[5,4,3,2,1]$ as the inputs, the reducer respectively outputs $11$ and $15$.
+In real-world reducers, it is often the case that the $s_1$ part of the reducer
+reads from the input. Since our reduction of the commutativity problem to SMT
+solving, which is presented in Section~\ref{sec:prover}, concentrates on the
+influence of the input on the loop $s_2$ only, we need to transform the reducer
+such that any input happens in the loop only.
 
-\begin{wrapfigure}{l}{5.3cm}
-	\vspace{-1cm}
+In order to be able to explain the transformation that we perform on an example,
+consider the example in Figure~\ref{fig:reducer_max1}. The reducer presented in
+the figure remembers the first input value in the variable $m$, increases its
+value by 10, and then updates its value to bigger ones if any occur in the loop.
+The main loop of the reducer is commutative in this case, but the reducer is not
+commutative. A counterexample can be easily found. With the list $[1,2,3,4,5]$
+and its permutation $[5,4,3,2,1]$ as the inputs, the reducer outputs $11$ and
+$15$, respectively.
+
+\begin{wrapfigure}[12]{r}{5.3cm}
+	\vspace{-9mm}
 	\begin{algorithm}[H]
@@
 	\end{algorithm}	
-	\vspace{-0.4cm}
-	\caption{Reducer max$^{+\mathtt{fix}}$}
-	\vspace{-0.4cm}
+	\vspace{-2mm}
+	\caption{The max$^{+\mathtt{fix}}$ reducer.}
+	\vspace{-4mm}
 	\label{fig:reducer_max2}
 \end{wrapfigure}
-We handle the problem again by program transformation.
-To deal with the example in Figure~\ref{fig:reducer_max1}, we move the prefix $s_1$ into the loop body and use a new variable $s$ to force that the execution of $s_1$ is always before the original loop body.
-The result after the transformation is demonstrated in Figure~\ref{fig:reducer_max2}.
-The new reducer program over-approximates all possible inputs/outputs of the original one.
-When $s=1$, its output sequence is the same as the original reducer.
-When $s\neq 1$, it may produce outputs that are not possible by the original reducer.
-It also satisfies all assumptions required for the Prover component:
-(I) the commands before entering the loop does not have any $\cur$ expression,
-(II) $out(v)$ command does not occur inside the loop body.
-Since the new reducer has all behaviors of the original one, the new reducer being commutative implies that the original one is also commutative.
+
+To deal with the problem, we use a transformation that we first explain on the
+example from Figure~\ref{fig:reducer_max1}. In particular, we move the prefix
+$s_1$ into the loop body and use a new variable $s$ to force that the execution
+of $s_1$ is always before the original loop body. The result after the
+transformation is demonstrated in Figure~\ref{fig:reducer_max2}. The new reducer
+program over-approximates all possible inputs/outputs of the original one. When
+$s=1$, its output sequence is the same as for the original reducer. When $s\neq
+1$, it may produce outputs that are not possible by the original reducer.
+However, since the new reducer has all behaviors of the original one, if the new
+reducer is commutative, the original one is also commutative.
+
+% TV: The below was removed since the requirements have not even be stated.
+%
+% It also satisfies all assumptions required for the Prover component: (1) the
+% commands before entering the loop do not have any $\cur$ expression, (2) the
+% $out(v)$ command does not occur inside the loop body.
 
@@
 
-This approach can be easily generalize to the situation where $\cur$ occurs multiple times in $s_1$. We first rewrite the $s_1$ part of the reducer $s_1;\rloop\{s_2\};s_3$ to the form
-$$s'_0;x_{i_1}{:=} \cur;s'_1.\ldots x_{i_{m}}{:=}\cur;s'_m$$, where $\cur$ never occur in $s'_0,s'_1,\ldots, s'_m$.
-Then uses a branch statement with garud $s=j$ to handle the case $x_{i_j} := \cur; s'_j; s:=s+1$, for all $j \in [1,m]$.
+In general, the problem with the input before the loop can be handled as follows,
+including the case where $\cur$ occurs multiple times in $s_1$. Assume that the
+$s_1$ part of the reducer $s_1;\rloop\{s_2\};s_3$ has the form
+$$s'_0;x_{i_1}{:=} \cur;s'_1; \ldots; x_{i_{m}}{:=}\cur;s'_m$$ where $\cur$ does
+not occur in $s'_0,s'_1,\ldots, s'_m$. For all $j \in [1,m]$, we replace the
+code $x_{i_j} := \cur; s'_j;$ from $s_1$ by a branch statement with the guard
+$s=j$ and body $x_{i_j} := \cur; s'_j; s:=s+1$ in $s_2$. The original $s_2$ loop
+body becomes the else branch of the newly introduced guard statement.
+
+%-----------------------------------------------------------------------------
+\subsubsection{Handling output inside the loop body} 
+%-----------------------------------------------------------------------------
+
+Another problem for our reduction to SMT is the fact that the reducer program
+can perform the output command $out(e)$ inside the loop body $s_2$. Since our
+SMT-based commutativity checking presented later on will be based on examining
+possible values of the variables that appear in the $s_2$ loop body only (these
+values then determine the output performed in $s_3$), we will replace each such
+$out(e)$ command by the assignment $v:=e$ for a fresh variable $v$. This makes
+the value that will be output visible for our analysis. The fact that we loose
+the output command does not matter since---as already said---we will not track
+the output commands but values of the variables that determine the value of the
+output.  Notice that the value of $v$ stays the same from the point it has been
+assigned a value until the end of the loop body $s_2$. If the value that $v$ can
+have at the end of $s_2$ does not change for any permutation of the input lists,
+we know that the reducer is commutative wrt all output values produced inside
+the loop body $s_2$.
 

### 2019-06-24 draft.tex
Polish the experimental results

--- 2019-06-24 draft.tex
@@
 
-In order to properly evaluate the performance of J-ReCoVer, We use the search engine \emph{searchcode.com} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''.
+\begin{wrapfigure}{r}{4cm}
+	\vspace{-0.7cm}
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		& Line & Variable & Branch\\
+		\hline
+		Min. & 5 & 4 & 0\\
+		Avg. & 20.5 & 14.7 & 1.2\\
+		Max. & 58 & 37 & 5\\
+		\hline
+	\end{tabular}
+	\caption{Size of the reducers}
+	\label{fig:benchmark}
+	\vspace{-0.5cm}
+\end{wrapfigure}
+
+\subsubsection{Benchmark collection} In order to properly evaluate the performance of J-ReCoVer, We use the search engine \emph{searchcode.com} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''.
 Since there is an upper bound on the number of results returned from the search engine, we add different search filters in order to get more data.
@@
 We exclude cases that are not Hadoop MapReduce reducer programs (those do not import the Hadoop library, do not extend or implement the reducer interface) and obtain $1273$ examples.
-We further remove those that cannot be compiled, those that are identical to each other, or those with non-numerical data types (e.g, string) and obtained $118$ programs as the final benchmarks.
+We further remove those that cannot be compiled, those that are identical to each other, or those with non-numerical data types (e.g, string) and obtained $118$ reducers as the final benchmarks.
+Figure~\ref{fig:benchmark} contains the details of extracted reducer functions.
 
-There are only three cases that J-ReCoVer cannot handle.
-The reason that J-ReCoVer fails is that the three reducers use more complicated structure than what J-ReCoVer currently supports; they use a branch statement before entering the loop, i.e., in the form $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$.
+\subsubsection{Results} J-ReCoVer successfully handled $115$ cases ($97.4\%$). The analysis time ranges between $9.8$ to $8.6$ seconds. 
+On average, $72\%$ of the execution time is in compiling JAVA source code to bytecode, which is the input of the Soot tool.
+Another $27\%$ of the execution time is in the Propossesor, in which Soot is used to transform JAVA bytecode to Jimple and perform the program transformations.
+The time spent in Solver is quite limited ($<1\%$), since the real-world integer reducer programs are usually not that big.
+
+There is no other tool that could handle the reducers as they are.
+Perhaps some other tools could be applied on the transformed programs, but the transformations would still be needed, and our SMT-based back-end verifier (the Solver) turned out to work efficiently.
+So we did not feel a need to replace it by another verification tool.
+Of course, in the future, this can be done if need be.
+
+J-ReCoVer fails in three cases because the three reducers use more complicated structure than what J-ReCoVer currently supports; they use a branch statement before entering the loop, i.e., in the form of  $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$.
 In theory, such a program can be handled by more sophisticated program transformation tasks.
@@
 
-\begin{wrapfigure}{r}{9cm}
-	\begin{tabular}{|c|c|c|c||c|c|c|}
-		\hline
-		&Compile &Prepossesor &Prover & Lines & Variables & If-branches\\
-		\hline
-		Min. &6.22   &2.15        &0.032 & 5 & 4 & 0\\
-		Avg. &6.54   &2.44        &0.046 & 20.5 & 14.7 & 1.2\\
-		Max. &7.28   &3.06        &0.101 & 58 & 37 & 5\\
-		\hline
-	\end{tabular}
-	\caption{Time in each step, size of the reducers}
-\end{wrapfigure}  
-For the $115$ solved cases, $72\%$ of the execution time are spent in compiling JAVA source code to bytecode, which is the input of the Soot tool.
-Another $27\%$ of the execution time are spent in the Propossesor, in which Soot is used to transform JAVA bytecode to Jimple and perform the program transformations.
-The time spent in Solver is quite limited, since the real-world integer reducer programs are usually not that big.
-
-J-ReCoVer is the first tool specialized to the reducer commutativity problem, although the approach is simple, it solves most of the real benchmarks we collected from repositories.
-There is no other tool that could handle the reducers as they are.
-Perhaps some other tools could be applied on the transformed programs, but the transformations would still be needed, and our SMT-based back-end verifier turned out to work efficiently, and so we did not feel a need to replace it by another verification tool.
-Of course, in the future, this can be done if need be.
+%\begin{wrapfigure}{r}{9cm}
+%	\begin{tabular}{|c|c|c|c||c|c|c|}
+%		\hline
+%		&Compile &Prepossesor &Prover & Lines & Variables & If-branches\\
+%		\hline
+%		Min. &6.22   &2.15        &0.032 & 5 & 4 & 0\\
+%		Avg. &6.54   &2.44        &0.046 & 20.5 & 14.7 & 1.2\\
+%		Max. &7.28   &3.06        &0.101 & 58 & 37 & 5\\
+%		\hline
+%	\end{tabular}
+%	\caption{Time in each step, size of the reducers}
+%\end{wrapfigure}
 

### 2019-06-24 draft.tex

--- 2019-06-24 draft.tex
@@
 J-ReCoVer is implemented in Java and built on top of Soot 2.5.0 and Z3 4.7.1.
-We run J-ReCoVer on a virtual machine with 4GB of memeory running on a server with AMD Opteron 6376 CPU.The operation system is Ubuntu 16.04.5 LTS.
-
-In order to properly evaluate the performance of J-ReCoVer, We use the search engine \emph{searchcode.com} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''.
+We run J-ReCoVer on a virtual machine with 4GB of memeory running Ubuntu 16.04.5 LTS on a server with AMD Opteron 6376 CPU.
+
+\begin{wrapfigure}{r}{4cm}
+	\vspace{-0.7cm}
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		& Line & Variable & Branch\\
+		\hline
+		Min. & 5 & 4 & 0\\
+		Avg. & 20.5 & 14.7 & 1.2\\
+		Max. & 58 & 37 & 5\\
+		\hline
+	\end{tabular}
+	\caption{Size of the reducers}
+	\label{fig:benchmark}
+	\vspace{-0.5cm}
+\end{wrapfigure}
+
+\subsubsection{Benchmark collection} In order to properly evaluate the performance of J-ReCoVer, We use the search engine \emph{searchcode.com} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''.
 Since there is an upper bound on the number of results returned from the search engine, we add different search filters in order to get more data.
@@
 We exclude cases that are not Hadoop MapReduce reducer programs (those do not import the Hadoop library, do not extend or implement the reducer interface) and obtain $1273$ examples.
-We further remove those that cannot be compiled, those that are identical to each other, or those with non-numerical data types (e.g, string) and obtained $118$ programs as the final benchmarks.
-
-There are only three cases that J-ReCoVer cannot handle.
-The reason that J-ReCoVer fails is that the three reducers use more complicated structure than what J-ReCoVer currently supports; they use a branch statement before entering the loop, i.e., in the form $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$.
+We further remove those that cannot be compiled, those that are identical to each other, or those with non-numerical data types (e.g, string) and obtained $118$ reducers as the final benchmarks.
+Figure~\ref{fig:benchmark} contains the details of extracted reducer functions.
+
+\subsubsection{Results} J-ReCoVer successfully handled $115$ cases ($97.4\%$). The analysis time ranges between $9.8$ to $8.6$ seconds. 
+On average, $72\%$ of the execution time is in compiling JAVA source code to bytecode, which is the input of the Soot tool.
+Another $27\%$ of the execution time is in the Propossesor, in which Soot is used to transform JAVA bytecode to Jimple and perform the program transformations.
+The time spent in Solver is quite limited ($<1\%$), since the real-world integer reducer programs are usually not that big.
+
+There is no other tool that could handle the reducers as they are.
+Perhaps some other tools could be applied on the transformed programs, but the transformations would still be needed, and our SMT-based back-end verifier (the Solver) turned out to work efficiently.
+So we did not feel a need to replace it by another verification tool.
+Of course, in the future, this can be done if need be.
+
+J-ReCoVer fails in three cases because the three reducers use more complicated structure than what J-ReCoVer currently supports; they use a branch statement before entering the loop, i.e., in the form of  $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$.
 In theory, such a program can be handled by more sophisticated program transformation tasks.
@@
 
-J-ReCoVer is the first tool specialized to the reducer commutativity problem, although the approach is simple, it solves most of the real benchmarks we collected from repositories.
-There is no other tool that could handle the reducers as they are.
-Perhaps some other tools could be applied on the transformed programs, but the transformations would still be needed, and our SMT-based backend verifier turned out to work efficiently, and so we did not feel a need to replace it by another verification tool.
-Of course, in the future, this can be done if need be.
+%\begin{wrapfigure}{r}{9cm}
+%	\begin{tabular}{|c|c|c|c||c|c|c|}
+%		\hline
+%		&Compile &Prepossesor &Prover & Lines & Variables & If-branches\\
+%		\hline
+%		Min. &6.22   &2.15        &0.032 & 5 & 4 & 0\\
+%		Avg. &6.54   &2.44        &0.046 & 20.5 & 14.7 & 1.2\\
+%		Max. &7.28   &3.06        &0.101 & 58 & 37 & 5\\
+%		\hline
+%	\end{tabular}
+%	\caption{Time in each step, size of the reducers}
+%\end{wrapfigure}
 

### 2019-06-24 draft.tex
Section 4.2

--- 2019-06-24 draft.tex
@@
 
-After the transformation, the reducer $s_1;\rloop\{s_2\};s_3$ never calls the $\cur$ function before enthering the loop (the $s_1$ part) and never output values inside the loop body (the $s_2$ part).
-The command $s_2$ can be viewed as a function $F$ that reads the values of all variables and the current input before executing $s_2$ and outputs the values of all variables after $s_2$.
-Formally, the function $F(n,x_1,x_2,\ldots,x_k): \Z^{k+1} \rightarrow \Z^k$ returns a tuple of values $x_1',x_2',\ldots,x_k'$, where $n$ is the current input value of the reducer, $x_i$ and $x_i'$ are the values of variables before and after the execution of $s_2$, respectively, for $i\in[1,k]$.
-The construction of $F$ from $s_2$ can be done in the standard way.
-We check if the formula below is valid for all possible values of $n_1,n_2, x_1,x_2,\ldots,x_k$.
-\begin{equation}
- F(n_1, F(n_2,x_1,x_2,\ldots,x_k)) = F(n_2, F(n_1,x_1,x_2,\ldots,x_k) )
-\label{eq:commu}
-\end{equation}
-
-Using the reducer that computes average (Figure~\ref{fig:reducer_example}) as an example.
-It has two variables $s$ and $c$.
-It is not difficult to compute that $F_{average}(n,s,c)=(s+n, c+1)$.
-The corresponding Equation~(\ref{eq:commu}) is valid because $F_{average}(n_1, F_{average}(n_2,s,c)) =F_{average}(n_1, s+n_2, c+1)= (s+n_1+n_2,c+2)=F_{average}(n_2, s+n_1, c+1)=F_{average}(n_2, F_{average}(n_1,s,c))$.
-
-The validity of Equation~(\ref{eq:commu}) implies that swapping any two consecutive input values will not change the final variable valuation.
-Informally, it says that starting from the same initial valuations of variables and with two different input orders, $[n_1;n_2]$ and $[n_2;n_1]$, the values of all program variables are the same after we execute the loop body twice.
-The first execution reads $n_1$ and then reads $n_2$.
-The other execution reads the two inputs in the reverse order.
+After the transformations described above, the reducer $s_1;\rloop\{s_2\};s_3$
+never calls the $\cur$ function in the $s_1$ part before entering the loop and
+never outputs values inside the loop body (the $s_2$ part). The command $s_2$
+can be viewed as a function $F$ that reads the values of all variables and the
+current input before executing $s_2$ and outputs the values of all variables
+after $s_2$. Formally, the function $F(n,x_1,x_2,\ldots,x_k): \Z^{k+1}
+\rightarrow \Z^k$ returns a tuple of values $x_1',x_2',\ldots,x_k'$ where $n$ is
+the current input value of the reducer, $x_i$ and $x_i'$ are the values of the
+variables before and after the execution of $s_2$, respectively, for
+$i\in[1,k]$. The construction of $F$ from $s_2$ can be done in the standard way.
+
+We reduce the reducer commutativity checking to checking validity of the
+following formula for all possible values of $n_1,n_2, x_1,x_2,\ldots,x_k$:
+\begin{equation} F(n_1, F(n_2,x_1,x_2,\ldots,x_k)) = F(n_2,
+F(n_1,x_1,x_2,\ldots,x_k) ). \label{eq:commu} \end{equation} Intuitively, the
+formula says that starting from the same initial valuations of variables and
+with two different input orders, $[n_1;n_2]$ and $[n_2;n_1]$, the values of all
+program variables are the same after we execute the loop body twice. The first
+execution reads $n_1$ and then reads $n_2$. The other execution reads the two
+inputs in the reverse order. Since any permutation of the input can be obtained
+by a sequence of permutations of neighbouring inputs, the validity of
+Formula~\ref{eq:commu} implies that the permutations will not change the final
+variable valuation and hence the output in $s_3$.
+
+Consider the reducer computing the average value
+(Figure~\ref{fig:reducer_example}) as an example. The reducer has two variables
+$s$ and $c$. We get that $F_{average}(n,s,c)=(s+n, c+1)$. In this case,
+Formula~\ref{eq:commu} is valid since $F_{average}(n_1, F_{average}(n_2,s,c))
+=F_{average}(n_1, s+n_2, c+1)= (s+n_1+n_2,c+2)=F_{average}(n_2, s+n_1,
+c+1)=F_{average}(n_2, F_{average}(n_1,s,c))$. This implies that the reducer is
+commutative.
 

### 2019-06-24 draft.tex
Typos in 4.1

--- 2019-06-24 draft.tex
@@
 %-----------------------------------------------------------------------------
-\subsubsection{Handling output inside the loop body} 
+\paragraph*{Handling output inside the loop body} 
 %-----------------------------------------------------------------------------
@@
 
-\subsubsection{Benchmark collection} In order to properly evaluate the performance of J-ReCoVer, We use the search engine \emph{searchcode.com} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''.
+\paragraph*{Benchmark collection} In order to properly evaluate the performance of J-ReCoVer, We use the search engine \emph{searchcode.com} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''.
 Since there is an upper bound on the number of results returned from the search engine, we add different search filters in order to get more data.
@@
 
-\subsubsection{Results} J-ReCoVer successfully handled $115$ cases ($97.4\%$). The analysis time ranges between $9.8$ to $8.6$ seconds. 
+\paragraph*{Results} J-ReCoVer successfully handled $115$ cases ($97.4\%$). The analysis time ranges between $9.8$ to $8.6$ seconds. 
 On average, $72\%$ of the execution time is in compiling JAVA source code to bytecode, which is the input of the Soot tool.

### 2019-06-24 draft.tex
Typos in 4.3

@@
 \newcommand{\dom}[1]{\mathsf{dom}(#1)}
+\newcommand{\IF}[2]{
+	\ifmmode
+	\mathbf{if}\ #1 \ \mathbf{then}\ #2
+	\else
+	\textbf{if}\ #1 \ \textbf{then}\ #2
+	\fi}
 \newcommand{\ite}[3]{
@@
 Google~\cite{dean04} and later implemented in the Apache Hadoop
-project~\cite{hadoop}. Under the MapReduce framework, a reducer computes output
+project. Under the MapReduce framework, a reducer computes output
 values from a sequence of input values transmitted over the network. Due to
@@
 MapReduce belongs among the most popular frameworks for data parallel
-computation. A MapReduce program~\cite{dean04,hadoop} consists of several pairs
+computation. A MapReduce program~\cite{dean04} consists of several pairs
 of \emph{mappers} and \emph{reducers} running on a machine cluster for handling
@@
 %=============================================================================
-\subsection*{Related Works}
+\paragraph*{Related Works}
 %=============================================================================
@@
 checking (or closely related topics such as regression verification and
-translation validation): see, e.g.,
+translation validation): c.f.,
 \cite{Pnueli:1998:TV,fedyukovich2015automated,barthe2011relational,KlebanovRuemmerUlbrich2017}
@@
 The input of J-ReCoVer is a reducer program written in Java, which is the most
-popular programming language used in the Hadoop~\cite{hadoop} MapReduce
+popular programming language used in the Hadoop MapReduce
 framework. The J-ReCoVer tool has three main components, the
@@
 		\vspace{-1cm}
-	\caption{Overview of the J-ReCoVer Tool. }\label{fig:overview-jrecover}
+	\caption{Overview of the J-ReCoVer tool. }\label{fig:overview-jrecover}
 		\vspace{-0.8cm}
@@
 $s_1$ part of the reducer $s_1;\rloop\{s_2\};s_3$ has the form
-$$s'_0;x_{i_1}{:=} \cur;s'_1; \ldots; x_{i_{m}}{:=}\cur;s'_m$$ where $\cur$ does
-not occur in $s'_0,s'_1,\ldots, s'_m$. For all $j \in [1,m]$, we replace the
-code $x_{i_j} := \cur; s'_j;$ from $s_1$ by a branch statement with the guard
-$s=j$ and body $x_{i_j} := \cur; s'_j; s:=s+1$ in $s_2$. The original $s_2$ loop
-body becomes the else branch of the newly introduced guard statement.
+$c_0;x_{1}{:=} \cur;c_1; \ldots; x_{m}{:=}\cur;c_m$, where $\cur$ does
+not occur in $c_0,c_1,\ldots, c_m$. 
+In the transformed reducer, the part before the loop is now $c_0;s:=1$. The loop body contains several branch statements. 
+For all $j \in [1,m]$, we add a branch statement $\IF{s=j}{x_{j}:=\cur; c_j; s:=s+1}$. 
+We also add $\IF{s=m+1}{s_2}$ for the original loop body.
 
@@
 In the loop body, the input is first stored in a variable $t$ and then added to $s$.
+That is $t:=\cur;s:=t$.
 After the loop, output the value of $s$.
@@
 However, in this case, the value of $t$ will not affect the output of this reducer.
-
-%\begin{figure}[hbt]
-%	\begin{minipage}{0.4\textwidth}
-%		\begin{algorithm}[H]
-%			$s:= 0$; \;
-%			\Loop{}{
-%				$t:=\cur$;
-%				$s:= s + t$\;
-%			};
-%			$out(s)$\;\;\;
-%		\end{algorithm}
-%		\caption{A commutative reducer with an invalid 
-%                   Equation~(\ref{eq:commu}).}
-%		\label{fig:reducer_opt}
-%	\end{minipage}
-%	\ \ \ \ \ \ \ \
-%	\begin{minipage}{0.5\textwidth}
-%		\LinesNumbered
-%		\centering
-%		\begin{minipage}{0.75\textwidth}
-%		\begin{algorithm}[H]
-%			$c_1;c_2;\ldots;c_i$\;
-%			\lIf{$g_1$}{$\ldots$}
-%			\lElseIf{ $g_2$}{$\ldots$}
-%			\lElseIf{ $g_3$}{$\ldots$}
-%			\lElseIf{ $g_m$}{$c_{i+1};\ldots ;c_n; out(v);\ldots$}
-%			\lElse{ $\ldots$}
-%		\end{algorithm}
-%	\end{minipage}
-%		\caption{The $s_3$ command with an $out(v)$ command in 
-%                   nested branches.}
-%		\label{fig:nested_out}
-%	\end{minipage}
-%\end{figure}
-
-% To handle such a situation, we need an algorithm to collect a set of variables
-% whose value may affect the output.  Recall that the first program
-% transformation task uses a set of variables $V_2=\{v_{out_k} \mid k \in
-% [1,l]\}$, where $l$ is the number of output commands occurred in $s_2$, to
-% collect output values occurred in the loop body $s_2$.  The set $V_2$ is
-% exactly the set of variables that will affect the output inside the loop.
-
-We perform a simple backward live variable analysis to collect all variables whose value may propagate to the output command after the loop execution.
-Only these varaibles are required to be equivalent.
-In our evaluation, the ratio of examples that our approach can successfully analyze is significantly increased from $6.8\%$ to $97.5\%$.
-The details of the evaluation can be found in Section~\ref{section:exp}.
+To handle this issue, we perform a simple backward live variable analysis to collect all variables whose value may propagate to the output command after the loop execution.
+Only these variables are required to be equivalent.
+In our evaluation, the ratio of examples that our approach can successfully analyze is significantly increased from $6.8\%$ to $97.5\%$ with the help of this optimization.
 
@@
 
-\paragraph*{Results} J-ReCoVer successfully handled $115$ cases ($97.4\%$). The analysis time ranges between $9.8$ to $8.6$ seconds. 
+\paragraph*{Results} J-ReCoVer successfully handled $115$ cases ($97.5\%$). The analysis time ranges between $9.8$ to $8.6$ seconds. 
 On average, $72\%$ of the execution time is in compiling JAVA source code to bytecode, which is the input of the Soot tool.

### 2019-06-24 draft.tex
Section 4.3

@@
 %=============================================================================
-\subsection{Optimization: Live Variable Analysis} \label{section:optimizations}
+\subsection{An Optimisation by Live Variable Analysis}
+\label{section:optimizations}
 %=============================================================================
 
-Here we explain how live variable analysis is used in J-ReCoVer to improve the precision of commutativity checking.
-
-We find that in many cases, Equation~(\ref{eq:commu}) is a condition that is too strong for the reducer to be commutative.
-For instance, consider a simple example.
-In the loop body, the input is first stored in a variable $t$ and then added to $s$.
-That is $t:=\cur;s:=t$.
-After the loop, output the value of $s$.
-In this case, the $F$ function returns the updated values of both $s$ and $t$ after the execution of the loop body. Observe that
-$F(c_1, F(c_2,s,t)) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t)) = (c_1+c_2, c_2)$.
-It follows that the corresponding Equation~(\ref{eq:commu}) is invalid.
-The second component of the returned tuples corresponds to the value of $t$ after executing the loop body twice.
-Their values are $c_1$ and $c_2$, respectively, in $F(c_1, F(c_2,s,t))$ and $F(c_2, F(c_1,s,t))$.
-However, in this case, the value of $t$ will not affect the output of this reducer.
-To handle this issue, we perform a simple backward live variable analysis to collect all variables whose value may propagate to the output command after the loop execution.
-Only these variables are required to be equivalent.
-In our evaluation, the ratio of examples that our approach can successfully analyze is significantly increased from $6.8\%$ to $97.5\%$ with the help of this optimization.
+We now explain how a simple live variable analysis is used in J-ReCoVer to
+significantly improve the precision of commutativity checking.
+
+In our initial experiments, we realised that Formula~\ref{eq:commu} is a
+condition that is too strong for the reducer to be commutative. To illustrate
+the issue, we present a simple example. In the loop body, the input is first
+stored in a variable $t$ and this is then assigned to $s$, i.e., $t:=\cur;s:=t$.
+After the loop, the value of $s$ is output. In this case, the $F$ function
+returns the updated values of both $s$ and $t$ after the execution of the loop
+body. Observe that $F(c_1, F(c_2,s,t)) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t))
+= (c_1+c_2, c_2)$. It follows that Formula~\ref{eq:commu} is invalid. The second
+component of the returned tuples, which causes the invalidity, corresponds to
+the value of $t$ after executing the loop body twice. Their values are $c_1$ and
+$c_2$, respectively, in $F(c_1, F(c_2,s,t))$ and $F(c_2, F(c_1,s,t))$. However,
+in this case, the value of $t$ will not affect the output of the reducer.
+
+To handle the above issue, we perform a simple backward live variable analysis
+to collect all variables whose value may propagate to the output command after
+the loop execution. Only these variables are then required to be equivalent. In
+our evaluation, the ratio of reducers that our approach can successfully analyze
+is significantly increased---in particular, from $6.8~\%$ to $97.5~\%$---by
+using this optimisation.
 

### 2019-06-24 draft.tex
Section 4.3

@@
 
-J-ReCoVer is implemented in Java and built on top of Soot 2.5.0 and Z3 4.7.1.
-We run J-ReCoVer on a virtual machine with 4GB of memeory running Ubuntu 16.04.5 LTS on a server with AMD Opteron 6376 CPU.
-
-\begin{wrapfigure}{r}{4cm}
+J-ReCoVer is implemented in Java and built on top of Soot 2.5.0 and Z3 4.7.1. We
+run J-ReCoVer on a virtual machine with 4GB of memory running Ubuntu 16.04.5 LTS
+on a server with AMD Opteron 6376 CPU.
+
+\begin{wraptable}{r}{4cm}
 	\vspace{-0.7cm}
+	\caption{Size of the reducers.}
 	\begin{tabular}{|c|c|c|c|}
@@
 	\end{tabular}
-	\caption{Size of the reducers}
-	\label{fig:benchmark}
+	\label{tab:benchmark}
 	\vspace{-0.5cm}
-\end{wrapfigure}
-
-\paragraph*{Benchmark collection} In order to properly evaluate the performance of J-ReCoVer, We use the search engine \emph{searchcode.com} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''.
-Since there is an upper bound on the number of results returned from the search engine, we add different search filters in order to get more data.
-We tried all $12$ combinations of six filters on code length $\{<50$, $ 50\sim 250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim 1250\}$
-and two filters for data sources $\{\url{github.com}, \url{bitbuckect.com}\}$.
-In total, we get $11346$ Java programs.
-We exclude cases that are not Hadoop MapReduce reducer programs (those do not import the Hadoop library, do not extend or implement the reducer interface) and obtain $1273$ examples.
-We further remove those that cannot be compiled, those that are identical to each other, or those with non-numerical data types (e.g, string) and obtained $118$ reducers as the final benchmarks.
-Figure~\ref{fig:benchmark} contains the details of extracted reducer functions.
-
-\paragraph*{Results} J-ReCoVer successfully handled $115$ cases ($97.5\%$). The analysis time ranges between $9.8$ to $8.6$ seconds. 
+\end{wraptable}
+
+%-----------------------------------------------------------------------------
+\paragraph*{Benchmark collection} 
+%-----------------------------------------------------------------------------
+
+In order to properly evaluate the performance
+of J-ReCoVer, We use the search engine \emph{searchcode.com} to collect java
+programs containing the key strings ``public void reduce'' or ``protected void
+reduce''. Since there is an upper bound on the number of results returned from
+the search engine, we add different search filters in order to get more data. We
+tried all $12$ combinations of six filters on code length $\{<50$, $ 50\sim
+250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim
+1250\}$ and two filters for data sources $\{\url{github.com},
+\url{bitbuckect.com}\}$. In total, we get $11346$ Java programs. We exclude
+cases that are not Hadoop MapReduce reducer programs (those do not import the
+Hadoop library, do not extend or implement the reducer interface) and obtain
+$1273$ examples. We further remove those that cannot be compiled, those that are
+identical to each other, or those with non-numerical data types (e.g, string)
+and obtained $118$ reducers as the final benchmarks. Figure~\ref{fig:benchmark}
+contains the details of extracted reducer functions.
+
+%-----------------------------------------------------------------------------
+\paragraph*{Results} 
+%-----------------------------------------------------------------------------
+
+J-ReCoVer successfully handled $115$ cases ($97.5\%$). The analysis time ranges between $9.8$ to $8.6$ seconds. 
 On average, $72\%$ of the execution time is in compiling JAVA source code to bytecode, which is the input of the Soot tool.

### 2019-06-24 draft.tex
Section 5

@@
 J-ReCoVer is implemented in Java and built on top of Soot 2.5.0 and Z3 4.7.1. We
-run J-ReCoVer on a virtual machine with 4GB of memory running Ubuntu 16.04.5 LTS
+ran J-ReCoVer on a virtual machine with 4GB of memory running Ubuntu 16.04.5 LTS
 on a server with AMD Opteron 6376 CPU.
 
-\begin{wraptable}{r}{4cm}
-	\vspace{-0.7cm}
+\begin{wraptable}[7]{r}{40mm}
+	\vspace{-8mm}
 	\caption{Size of the reducers.}
@@
 	\label{tab:benchmark}
-	\vspace{-0.5cm}
+	\vspace{-5mm}
 \end{wraptable}
@@
 
-In order to properly evaluate the performance
-of J-ReCoVer, We use the search engine \emph{searchcode.com} to collect java
-programs containing the key strings ``public void reduce'' or ``protected void
-reduce''. Since there is an upper bound on the number of results returned from
-the search engine, we add different search filters in order to get more data. We
-tried all $12$ combinations of six filters on code length $\{<50$, $ 50\sim
-250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim
-1250\}$ and two filters for data sources $\{\url{github.com},
-\url{bitbuckect.com}\}$. In total, we get $11346$ Java programs. We exclude
-cases that are not Hadoop MapReduce reducer programs (those do not import the
-Hadoop library, do not extend or implement the reducer interface) and obtain
-$1273$ examples. We further remove those that cannot be compiled, those that are
-identical to each other, or those with non-numerical data types (e.g, string)
-and obtained $118$ reducers as the final benchmarks. Figure~\ref{fig:benchmark}
-contains the details of extracted reducer functions.
+In order to properly evaluate the performance of J-ReCoVer, we used the search
+engine \emph{searchcode.com} to collect Java programs containing the key strings
+``public void reduce'' or ``protected void reduce''. Since there is an upper
+bound on the number of results returned from the search engine, we added
+different search filters in order to get more data. We tried all $12$
+combinations of six filters on the code length $\{<50$, $ 50\sim 250$, $250\sim
+450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim 1250\}$ and two
+filters for data sources $\{\url{github.com}, \url{bitbuckect.com}\}$. In total,
+we got $11,346$ Java programs. We excluded cases that were not Hadoop MapReduce
+reducer programs (those do not import the Hadoop library, do not extend or
+implement the reducer interface) and obtained $1,273$ examples. We further
+removed those that could not be compiled, those that were identical to each
+other, and those with non-numerical data types (e.g., strings). We obtained
+$118$ reducers as the final benchmarks. Table~\ref{tab:benchmark} contains more
+details of the considered reducer functions.
 
@@
 
-J-ReCoVer successfully handled $115$ cases ($97.5\%$). The analysis time ranges between $9.8$ to $8.6$ seconds. 
-On average, $72\%$ of the execution time is in compiling JAVA source code to bytecode, which is the input of the Soot tool.
-Another $27\%$ of the execution time is in the Propossesor, in which Soot is used to transform JAVA bytecode to Jimple and perform the program transformations.
-The time spent in Solver is quite limited ($<1\%$), since the real-world integer reducer programs are usually not that big.
-
-There is no other tool that could handle the reducers as they are.
-Perhaps some other tools could be applied on the transformed programs, but the transformations would still be needed, and our SMT-based back-end verifier (the Solver) turned out to work efficiently.
-So we did not feel a need to replace it by another verification tool.
-Of course, in the future, this can be done if need be.
-
-J-ReCoVer fails in three cases because the three reducers use more complicated structure than what J-ReCoVer currently supports; they use a branch statement before entering the loop, i.e., in the form of  $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$.
-In theory, such a program can be handled by more sophisticated program transformation tasks.
-For example, we can merge the two loops and push the outer branch condition into the merged loop.
+J-ReCoVer successfully handled $115$ cases ($97.5~\%$) out of the considered
+ones. The analysis time ranged between $9.8$ and $8.6$ seconds. On average,
+$72~\%$ of the execution time was spent in compiling Java source code to
+bytecode, which is the input of the Soot tool. Further, $27~\%$ of the execution
+time was spent in the Preprocessor, in which Soot is used to transform Java
+bytecode to Jimple and perform the program transformations. The time spent in
+Solver is quite limited ($<1~\%$) since the real-world integer reducer programs
+are usually not that big.
+
+There is no other tool that could handle the reducers as they are. Perhaps some
+other tools could be applied on the transformed programs, but the
+transformations would still be needed, and our SMT-based back-end verifier (the
+Solver) turned out to work efficiently. Hence, we did not feel a need to replace
+it by another verification tool. Of course, in the future, this can be done if
+need be.
+
+J-ReCoVer failed in three cases out of the considered ones because the three
+reducers use more complicated control structures than what J-ReCoVer currently
+supports. Namely, they use a branch statement before entering the loop, i.e.,
+they have the form of
+$\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$. In theory, such
+a program can be handled by more sophisticated program transformations. For
+example, we can merge the two loops and push the outer branch condition into the
+merged loop. Extensions of J-ReCoVer to be able to handle such constructions,
+together with a support for more data types, belong among our future works.
 

### 2019-06-24 draft.tex
remove the 2nd tranformations

--- 2019-06-24 draft.tex
@@
 $\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly until
-the entire input list is consumed. An example of a reducer is shown in
+the entire input list is consumed. To simplify presentation, we assume the reducer never output in the loop body $s_2$. An example of a reducer is shown in
 Figure~\ref{fig:reducer_example}.
@@
 part of the Preprocessor component so that the input order of the reducer is now
-controlled by J-ReCoVer. Finally, the Preprocessor performs some program
-transformation tasks to simplify the analysis. For example, it converts all
-output commands $out(e)$ inside loops to a special assignment (as explained in
-Section~\ref{sec:program_trans1}).
+controlled by J-ReCoVer. Finally, the Preprocessor performs  a program transformation to simplify the analysis.
+
+%For example, it converts all output commands $out(e)$ inside loops to a special assignment (as explained in Section~\ref{sec:program_trans1}).
 
@@
 
-Before entering the Prover component, the Preprocessor first performs two
-program transformations to simplify the verification task
+Before entering the Prover component, the Preprocessor first performs a
+program transformation to simplify the verification task
 (Section~\ref{sec:program_trans1}). The output of the preprocessor is a
@@
 \vspace*{-2mm}
-\subsection{The Program Transformations in the Preprocessor}
+\subsection{The Program Transformation in the Preprocessor}
 \label{sec:program_trans1}
@@
 %-----------------------------------------------------------------------------
-\paragraph*{Handling the access to $\cur$ before entering the loop.}
+%\paragraph*{Handling the access to $\cur$ before entering the loop.}
 %-----------------------------------------------------------------------------
@@
 %-----------------------------------------------------------------------------
-\paragraph*{Handling output inside the loop body} 
+%\paragraph*{Handling output inside the loop body} 
 %-----------------------------------------------------------------------------
 
-Another problem for our reduction to SMT is the fact that the reducer program
-can perform the output command $out(e)$ inside the loop body $s_2$. Since our
-SMT-based commutativity checking presented later on will be based on examining
-possible values of the variables that appear in the $s_2$ loop body only (these
-values then determine the output performed in $s_3$), we will replace each such
-$out(e)$ command by the assignment $v:=e$ for a fresh variable $v$. This makes
-the value that will be output visible for our analysis. The fact that we loose
-the output command does not matter since---as already said---we will not track
-the output commands but values of the variables that determine the value of the
-output.  Notice that the value of $v$ stays the same from the point it has been
-assigned a value until the end of the loop body $s_2$. If the value that $v$ can
-have at the end of $s_2$ does not change for any permutation of the input lists,
-we know that the reducer is commutative wrt all output values produced inside
-the loop body $s_2$.
+%Another problem for our reduction to SMT is the fact that the reducer program
+%can perform the output command $out(e)$ inside the loop body $s_2$. Since our
+%SMT-based commutativity checking presented later on will be based on examining
+%possible values of the variables that appear in the $s_2$ loop body only (these
+%values then determine the output performed in $s_3$), we will replace each such
+%$out(e)$ command by the assignment $v:=e$ for a fresh variable $v$. This makes
+%the value that will be output visible for our analysis. The fact that we loose
+%the output command does not matter since---as already said---we will not track
+%the output commands but values of the variables that determine the value of the
+%output.  Notice that the value of $v$ stays the same from the point it has been
+%assigned a value until the end of the loop body $s_2$. If the value that $v$ can
+%have at the end of $s_2$ does not change for any permutation of the input lists,
+%we know that the reducer is commutative wrt all output values produced inside
+%the loop body $s_2$.
 
@@
 
-After the transformations described above, the reducer $s_1;\rloop\{s_2\};s_3$
-never calls the $\cur$ function in the $s_1$ part before entering the loop and
-never outputs values inside the loop body (the $s_2$ part). The command $s_2$
+After the transformation described above, the reducer $s_1;\rloop\{s_2\};s_3$
+never calls the $\cur$ function in the $s_1$ part before entering the loop. W.o.l.g, we assume that the reducer reads one input $\cur$ in one loop iteration.
+For the case that multiple reads from input occur in the loop, we can break the multiple reads to several single reads over multiple loop iterations using auxiliary variables and branch statements. 
+The command $s_2$
 can be viewed as a function $F$ that reads the values of all variables and the
@@
 	\end{tabular}
-	\label{tab:benchmark}
+	\label{fig:benchmark}
 	\vspace{-0.5cm}
@@
 identical to each other, or those with non-numerical data types (e.g, string)
-and obtained $118$ reducers as the final benchmarks. Figure~\ref{fig:benchmark}
+and obtained $118$ reducers as the final benchmarks. Table~\ref{fig:benchmark}
 contains the details of extracted reducer functions.

### 2019-06-24 draft.tex

--- 2019-06-24 draft.tex
@@
 	\end{tabular}
+
 	\label{tab:benchmark}
 	\vspace{-5mm}
+
 \end{wraptable}
@@
 time was spent in the Preprocessor, in which Soot is used to transform Java
-bytecode to Jimple and perform the program transformations. The time spent in
+bytecode to Jimple and perform the program transformation. The time spent in
 Solver is quite limited ($<1~\%$) since the real-world integer reducer programs
@@
 other tools could be applied on the transformed programs, but the
-transformations would still be needed, and our SMT-based back-end verifier (the
+transformation would still be needed, and our SMT-based back-end verifier (the
 Solver) turned out to work efficiently. Hence, we did not feel a need to replace
@@
 $\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$. In theory, such
-a program can be handled by more sophisticated program transformations. For
+a program can be handled by more sophisticated program transformation. For
 example, we can merge the two loops and push the outer branch condition into the

### 2019-06-25 draft.tex
polish 1-4.1

@@
 reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}. If all reducers
-are commutative, they will have the same external behavior under all possible
-schedules. In such a case, by fixing a schedule, the verification problem of a
+are commutative, they will have the same external behaviour under all possible
+schedules. 
+One then suffices with considering any chosen interleaving
+of input values instead of all of them.
+In such a case, by fixing a schedule, the verification problem of a
 MapReduce program can be reduced to the verification problem of a sequential
 program, which is known to be much easier than the verification problem of
-concurrent programs. One then suffices with considering any chosen interleaving
-of input values instead of all of them.
+concurrent~programs.
 
@@
 
-On the other hand, the non-commutative behavior of a reducer is often the source
+On the other hand, the non-commutative behaviour of a reducer is often the source
 of very tricky bugs. A study conducted by Microsoft investigated the
@@
 In this paper, we present the J-ReCoVer tool (Java Reducer Commutativity
-Verifier), which is available at~\verb|http://jrecover.iis.sinica.edu.tw|. The
+Verifier). A link to J-ReCoVer can be found in the supplementary materials. The
 tool implements a heuristic approach for checking the commutativity problem
@@
 
-We collected benchmarks from open repositories such as Github and Bitbucket to
+We collected benchmarks from open repositories such as GitHub and Bitbucket to
 evaluate J-ReCoVer. With the help of a search engine \emph{searchcode.com} over
@@
 programs to other interested researchers as a side contribution of the paper.
-Our tool J-ReCoVer is able to correctly analyze all but three of the programs.
+Our tool J-ReCoVer is able to correctly analyse all but three of the programs.
 
@@
 be verified. Therefore, J-ReCoVer uses an over-approximation of the reducer's
-behavior. This approximation allows for a much more efficient, yet---according
+behaviour. This approximation allows for a much more efficient, yet---according
 to our experiments---precise enough commutativity analysis.
@@
 open repositories, reducer programs are almost always in this form. The
-$\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly until
-the entire input list is consumed. To simplify presentation, we assume the reducer never output in the loop body $s_2$. An example of a reducer is shown in
-Figure~\ref{fig:reducer_example}.
+$\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly for each input element until
+the entire input list is consumed.
+An example of a reducer is shown in Figure~\ref{fig:reducer_example}.
+To simplify presentation, we assume in this paper the reducer never output in the loop body $s_2$.
+In the J-ReCoVer tool, an algorithm to deal with output inside the loop is implemented.
 
@@
 top-level loop (and possibly further such loops) will work with random initial
-values of the shared variable, which over-approximates the original behavior.
+values of the shared variable, which over-approximates the original behaviour.
 Usually, the second (or further) top-level loop are commutative even with
@@
 
-In order to be able to explain the transformation that we perform on an example,
+In order to explain the problem with further details,
 consider the example in Figure~\ref{fig:reducer_max1}. The reducer presented in
@@
 
-To deal with the problem, we use a transformation that we first explain on the
+To deal with the problem, we apply a program transformation on the
 example from Figure~\ref{fig:reducer_max1}. In particular, we move the prefix
@@
 transformation is demonstrated in Figure~\ref{fig:reducer_max2}. The new reducer
-program over-approximates all possible inputs/outputs of the original one. When
-$s=1$, its output sequence is the same as for the original reducer. When $s\neq
-1$, it may produce outputs that are not possible by the original reducer.
-However, since the new reducer has all behaviors of the original one, if the new
-reducer is commutative, the original one is also commutative.
+program has the same inputs/outputs as the original one. Therefore, if the new reducer is commutative, the original one~is~also~commutative.
 
@@
 
-In general, the problem with the input before the loop can be handled as follows,
-including the case where $\cur$ occurs multiple times in $s_1$. Assume that the
-$s_1$ part of the reducer $s_1;\rloop\{s_2\};s_3$ has the form
-$c_0;x_{1}{:=} \cur;c_1; \ldots; x_{m}{:=}\cur;c_m$, where $\cur$ does
+In general, the problem with the multiple inputs before the loop can be handled as follows.
+Given a reducer $c_0;x_{1}{:=} \cur;c_1; \ldots; x_{m}{:=}\cur;c_m;\rloop\{s_2\};s_3$, where $m$ inputs are read before the loop and $\cur$ does
 not occur in $c_0,c_1,\ldots, c_m$. 
@@
 the loop execution. Only these variables are then required to be equivalent. In
-our evaluation, the ratio of reducers that our approach can successfully analyze
+our evaluation, the ratio of reducers that our approach can successfully analyse
 is significantly increased---in particular, from $6.8~\%$ to $97.5~\%$---by

### 2019-06-25 draft.tex
polish 4.2-5

@@
 \begin{wrapfigure}[11]{r}{3.5cm}
-	\vspace{-17mm}
+	\vspace{-18mm}
 	\begin{algorithm}[H]
@@
 	\caption{The max$^+$ reducer with input before the main loop.}
-	\vspace{-12mm}
+	\vspace{-11mm}
 	\label{fig:reducer_max1}
@@
 \begin{wrapfigure}[12]{r}{5.3cm}
-	\vspace{-9mm}
+	\vspace{-10mm}
 	\begin{algorithm}[H]
@@
 After the transformation described above, the reducer $s_1;\rloop\{s_2\};s_3$
-never calls the $\cur$ function in the $s_1$ part before entering the loop. W.o.l.g, we assume that the reducer reads one input $\cur$ in one loop iteration.
+never calls the $\cur$ function in the $s_1$ part before entering the loop. W.o.l.g, we assume that the reducer reads exactly one input in one loop iteration.
 For the case that multiple reads from input occur in the loop, we can break the multiple reads to several single reads over multiple loop iterations using auxiliary variables and branch statements.
+
 The command $s_2$
@@
 
-We reduce the reducer commutativity checking to checking validity of the
+We reduce the reducer commutativity verification to checking validity of the
 following formula for all possible values of $n_1,n_2, x_1,x_2,\ldots,x_k$:
@@
 stored in a variable $t$ and this is then assigned to $s$, i.e., $t:=\cur;s:=t$.
-After the loop, the value of $s$ is output. In this case, the $F$ function
+After the loop, output the value of $s$. In this case, the $F$ function
 returns the updated values of both $s$ and $t$ after the execution of the loop
@@
 implement the reducer interface) and obtained $1,273$ examples. We further
-removed those that could not be compiled, those that were identical to each
-other, and those with non-numerical data types (e.g., strings). We obtained
+removed duplicates, those that could not be compiled, and those with non-numerical data types (e.g., strings). We obtained
 $118$ reducers as the final benchmarks. Table~\ref{tab:benchmark} contains more

### 2019-06-25 appendix.tex
check the commit by Tomas and some minor modification
polish appendix

@@
 
-\section{J-ReCoVer Usages}
+\section{J-ReCoVer Demo}
+
+Our plan is to demo the basic usage of J-ReCoVer over two examples.
+The first example is a reducer that is not commutative, and J-ReCoVer will report a counterexample.
+Based on this counterexample, we will fix the reducer to get the 2nd example, and let J-ReCoVer to check it again.
+Now J-ReCoVer will report the reducer is commutative.
+Below we give a more detailed description of the functionalities of J-ReCoVer.
 
@@
 
-J-ReCoVer is available online at \url{\texttt{http://jrecover.iis.sinica.edu.tw/}}.
-Fig.~\ref{fig:main_screen} shows the main screen of J-ReCoVer.
-The alignment of user interface elements are as follows:
+Figure~\ref{fig:main_screen} shows the main screen of J-ReCoVer. The alignment of user interface elements are as follows:
 
@@
 % \vspace{-10pt}
-\includegraphics[width=.9\linewidth]{screenshots/main_screen.eps}
+\includegraphics[width=.9\linewidth]{screenshots/main_screen}
 % \vspace{-5pt}
@@
 \item
-\emph{"Github"} opens a new tab of the repository of J-ReCoVer. The repository also has source code of benchmarks.
+\emph{``GitHub''} opens a new tab of the repository of J-ReCoVer. The repository also has source code of benchmarks.
 \item
-\emph{"Benchmark"} leads to the list of benchmarks we collected with their results of commutativity analysis as Fig.~\ref{fig:benchmark_list} shows.
+\emph{``Benchmark''} leads to the list of benchmarks we collected with their results of commutativity analysis as Fig.~\ref{fig:benchmark_list} shows.
 Select the filename or "try it" button will select the example and go back to the main screen.
@@
 \item
-\emph{"Benchmark List"} provides a quick selection to examples in the benchmark (Fig.~\ref{fig:benchmark_list_right})
+\emph{``Benchmark List''} provides a quick selection to examples in the benchmark (Fig.~\ref{fig:benchmark_list_right})
 \item
-\emph{"Results"} shows the last analysis result.
+\emph{``Results''} shows the last analysis result.
 \end{itemize}
@@
 \item
-\emph{"Type"} provides types that J-ReCoVer supports. Details are explained in~\ref{appendix:3}.
+\emph{``Type''} provides types that J-ReCoVer supports. Details are explained in~\ref{appendix:3}.
 \item
-\emph{"Run"} starts the analysis of the selected example.
+\emph{``Run''} starts the analysis of the selected example.
 \end{itemize}
@@
 % \vspace{-10pt}
-\includegraphics[width=.8\linewidth]{screenshots/benchmark_list.eps}
+\includegraphics[width=.8\linewidth]{screenshots/benchmark_list}
 % \vspace{-5pt}
@@
 % \vspace{-10pt}
-\includegraphics[width=.8\linewidth]{screenshots/benchmark_list_right.eps}
+\includegraphics[width=.8\linewidth]{screenshots/benchmark_list_right}
 % \vspace{-5pt}
@@
 To run analysis, you can choose an example from benchmark using either the top menu or the right menu, then click the "Run" button of the upper-right menu to start the commutativity analysis of the selected example.
-The pull-down menu "Types" of the upper-right menu provides selectable types for input \texttt{(T1,T2)} and output \texttt{(T3,T4)}.
+The pull-down menu "Types" of the upper-right menu provides selectable types for input \texttt{(T1,T2)} and output \texttt{(T3,T4)} key-value pairs.
 Fig.~\ref{fig:type_select_menu} shows the pull-down menu and Fig.~\ref{fig:selectable_types} shows part of the selectable types in J-ReCoVer.
@@
 % \vspace{-10pt}
-\includegraphics[width=.8\linewidth]{screenshots/type_select_menu.eps}
+\includegraphics[width=.8\linewidth]{screenshots/type_select_menu}
 % \vspace{-5pt}
@@
 % \vspace{-10pt}
-\includegraphics[width=.8\linewidth]{screenshots/selectable_types.eps}
+\includegraphics[width=.8\linewidth]{screenshots/selectable_types}
 % \vspace{-5pt}
@@
 
-After J-ReCoVer finishes the analysis, the \emph{"Result:"} tab of the right menu will show the result as Fig.~\ref{fig:analysis_result} shows.
-Fig.~\ref{fig:analysis_result_text} shows the analysis result of the first benchmark \texttt{dis.java} in detail.
+After J-ReCoVer finishes the analysis, the \emph{"Result:"} tab of the right menu will show the result of the analysis, which can be found in Figure~\ref{fig:analysis_result}.
+Figure~\ref{fig:analysis_result_text} shows the complete analysis report of the benchmark \texttt{dis.java} in Figure~\ref{fig:main_screen}.
 
@@
 % \vspace{-10pt}
-\includegraphics[width=.8\linewidth]{screenshots/analysis_result.eps}
+\includegraphics[width=.8\linewidth]{screenshots/analysis_result}
 % \vspace{-5pt}
@@
 
-RESULT: Cannot find a counterexample in 500 tests
+RESULT: Cannot find a counterexample in 1500 tests
 Testcases were generated randomly.
@@
 
-In a commutativity analysis, J-ReCoVer first tries to compile the example then perfrom commutativity analysis.
-If the analysis says the example is commutative, J-ReCoVer then runs 500 randomly generated test cases to try to find a counterexample.
-If the test cases all pass, J-ReCoVer concludes that the example is commutative, or the result will be "unknown" since the results of analysis and tests are inconsistent.
-For the case that the commutativity analysis returns false, J-ReCoVer will also run test cases to find a counterexample.
-This time, J-ReCoVer will conclude "not commutative" if a counterexample is found, or "unknown" if no counterexample is found.
+In a commutativity analysis, J-ReCoVer first tries to compile the example then perform commutativity analysis.
+If the analysis can not conclude that the example is commutative, J-ReCoVer then runs 1500 randomly generated test cases to try to find a counterexample.
+If the test cases all pass, then the result will be "unknown".
 
-\subsection{Run Analysis of an example from sketch}
+\subsection{Run analysis of an example from sketch}
 \label{appendix:3}
 
-Besides examples from the benchmark, J-ReCoVer also provides an interactive way to analyze a reduce function starting from a sketch.
+Besides examples from the benchmark, J-ReCoVer also provides an interactive way to analyse a user defined reducer function.
 The upper-left menu (below the top menu) provides blank templates for two versions of Hadoop. The templates are

### 2019-06-25 draft.tex
Changes in the Introduction

@@
 MapReduce belongs among the most popular frameworks for data parallel
-computation. A MapReduce program~\cite{dean04} consists of several pairs
-of \emph{mappers} and \emph{reducers} running on a machine cluster for handling
-big data in parallel. Usually, mappers and reducers are the only components in a
+computation. A MapReduce program~\cite{dean04} consists of several pairs of
+\emph{mappers} and \emph{reducers} running on a machine cluster for handling big
+data in parallel. Usually, mappers and reducers are the only components in a
 MapReduce program that involve concurrency. Mappers read data from a distributed
@@
 \emph{commutativity problem} of
-reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}. If all reducers
-are commutative, they will have the same external behaviour under all possible
-schedules. 
-One then suffices with considering any chosen interleaving
-of input values instead of all of them.
-In such a case, by fixing a schedule, the verification problem of a
-MapReduce program can be reduced to the verification problem of a sequential
-program, which is known to be much easier than the verification problem of
+reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}.
+
+If a reducer is commutative, it will have the same external behaviour under all
+possible schedules, and one then suffices with considering any chosen
+interleaving of input values when examining its behaviour instead of having to
+consider all of them. By fixing a schedule, the verification problem of a
+MapReduce program reduces to the verification problem of a sequential program,
+which is known to be much easier than the verification problem of
 concurrent~programs.
@@
 In this paper, we present the J-ReCoVer tool (Java Reducer Commutativity
-Verifier). A link to J-ReCoVer can be found in the supplementary materials. The
-tool implements a heuristic approach for checking the commutativity problem
+Verifier), which is available at~\verb|http://www.jrecover.tk/|.
+%
+% A link to J-ReCoVer can be found in the supplementary materials.
+%
+The tool implements a heuristic approach for checking the commutativity problem
 that---despite its simplicity---works very efficiently on a large set of

### 2019-06-25 draft.tex
Changes in Section 2

@@
 open repositories, reducer programs are almost always in this form. The
-$\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly for each input element until
-the entire input list is consumed.
-An example of a reducer is shown in Figure~\ref{fig:reducer_example}.
-To simplify presentation, we assume in this paper the reducer never output in the loop body $s_2$.
-In the J-ReCoVer tool, an algorithm to deal with output inside the loop is implemented.
+$\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly for
+each input element until the entire input list is consumed. An example of a
+reducer is shown in Figure~\ref{fig:reducer_example}. In the paper, to simplify
+the presentation, we assume that a reducer does never produce output in the loop
+body $s_2$. In the J-ReCoVer tool, an algorithm to deal with output inside the
+loop is implemented.
+
+% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+%
+% Just to remember: the way the output from the main loop is handled currently
+% is wrong: One should either check that there is no flow between the input and
+% output in the loop, or to add a check that the projection of the F function on
+% any value output in the main loop stays the same for any input value.
+%
+% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 
@@
 values of the shared variable, which over-approximates the original behaviour.
-Usually, the second (or further) top-level loop are commutative even with
-arbitrary initial shared variable values and hence J-ReCoVer can be used to
-prove it.
+In our experience, the second (or further) top-level loop are usually
+commutative even with arbitrary initial shared variable values, and so J-ReCoVer
+can be used to handle such reducers.
 

### 2019-06-25 draft.tex
sec 5
Modifications in 4.1

@@
 
-In order to explain the problem with further details,
-consider the example in Figure~\ref{fig:reducer_max1}. The reducer presented in
-the figure remembers the first input value in the variable $m$, increases its
-value by 10, and then updates its value to bigger ones if any occur in the loop.
-The main loop of the reducer is commutative in this case, but the reducer is not
-commutative. A counterexample can be easily found. With the list $[1,2,3,4,5]$
-and its permutation $[5,4,3,2,1]$ as the inputs, the reducer outputs $11$ and
-$15$, respectively.
+To illustrate the issue, we consider the reducer shown in
+Figure~\ref{fig:reducer_max1}.
+%
+The reducer presented in the figure remembers the first input value in the
+variable $m$, increases its value by 10, and then updates its value to bigger
+ones if any occur in the loop.  The main loop of the reducer is commutative in
+this case, but the reducer is not commutative. A counterexample can be easily
+found. With the list $[1,2,3,4,5]$ and its permutation $[5,4,3,2,1]$ as the
+inputs, the reducer outputs $11$ and $15$, respectively.
 
@@
 
-To deal with the problem, we apply a program transformation on the
-example from Figure~\ref{fig:reducer_max1}. In particular, we move the prefix
-$s_1$ into the loop body and use a new variable $s$ to force that the execution
-of $s_1$ is always before the original loop body. The result after the
-transformation is demonstrated in Figure~\ref{fig:reducer_max2}. The new reducer
-program has the same inputs/outputs as the original one. Therefore, if the new reducer is commutative, the original one~is~also~commutative.
+Our transformation will handle the example from Figure~\ref{fig:reducer_max1} as
+follows.
+%
+We move the prefix $s_1$ into the loop body and use a new variable $s$ to force
+that the execution of $s_1$ is always before the original loop body. The result
+after the transformation is demonstrated in Figure~\ref{fig:reducer_max2}. The
+new reducer program has the same inputs/outputs as the original one. Therefore,
+if the new reducer is commutative, the original one~is~also~commutative.
 
@@
 
-In general, the problem with the multiple inputs before the loop can be handled as follows.
-Given a reducer $c_0;x_{1}{:=} \cur;c_1; \ldots; x_{m}{:=}\cur;c_m;\rloop\{s_2\};s_3$, where $m$ inputs are read before the loop and $\cur$ does
-not occur in $c_0,c_1,\ldots, c_m$. 
-In the transformed reducer, the part before the loop is now $c_0;s:=1$. The loop body contains several branch statements. 
-For all $j \in [1,m]$, we add a branch statement $\IF{s=j}{x_{j}:=\cur; c_j; s:=s+1}$. 
-We also add $\IF{s=m+1}{s_2}$ for the original loop body.
+% In general, the problem with the multiple inputs before the loop can be handled
+% as follows. Given a reducer $c_0;x_{1}{:=} \cur;c_1; \ldots;
+% x_{m}{:=}\cur;c_m;\rloop\{s_2\};s_3$, where $m$ inputs are read before the loop
+% and $\cur$ does not occur in $c_0,c_1,\ldots, c_m$.  In the transformed reducer,
+% the part before the loop is now $c_0;s:=1$. The loop body contains several
+% branch statements. For all $j \in [1,m]$, we add a branch statement
+% $\IF{s=j}{x_{j}:=\cur; c_j; s:=s+1}$.  We also add $\IF{s=m+1}{s_2}$ for the
+% original loop body.
+
+In general, the problem with the input before the loop can be handled as
+follows, including the case where $\cur$ occurs multiple times in $s_1$. Assume
+that the $s_1$ part of the reducer $s_1;\rloop\{s_2\};s_3$ has the form
+$c_0;x_{1}{:=} \cur;c_1; \ldots; x_{m}{:=}\cur;c_m$ where $\cur$ does not occur
+in $c_0,c_1,\ldots, c_m$. In the transformed reducer, the part before the loop
+will be $c_0;s:=1$, and the loop body will contain several new branch
+statements. In particular, for all $j \in [1,m]$, we add the branch statement
+$\IF{s=j}{x_{j}:=\cur; c_j; s:=s+1}$. Moreover, we transform the original loop
+body into the branch $\IF{s=m+1}{s_2}$.
 

### 2019-06-25 appendix.tex

@@
 
-RESULT: Cannot find a counterexample in 1500 tests
+RESULT: Cannot find a counterexample in 500 tests
 Testcases were generated randomly.
@@
 In a commutativity analysis, J-ReCoVer first tries to compile the example then perform commutativity analysis.
-If the analysis can not conclude that the example is commutative, J-ReCoVer then runs 1500 randomly generated test cases to try to find a counterexample.
+If the analysis can not conclude that the example is commutative, J-ReCoVer then runs 500 randomly generated test cases to try to find a counterexample.
 If the test cases all pass, then the result will be "unknown".
@@
 
-In this case, one would have to manually fill the types T1 to T4 and the function body, then selects the types from the pull-down menu, as shown in Fig.~\ref{fig:type_select_menu} and Fig.~\ref{fig:selectable_types}.
+In this case, one would have to manually fill the types T1 to T4 and the function body, then selects the types from the pull-down menu, as shown in Figure~\ref{fig:type_select_menu} and Figure~\ref{fig:selectable_types}.
 

### 2019-06-25 appendix.tex
Mark main screen graphic for referencing the UI components

@@
 % \vspace{-10pt}
-\includegraphics[width=.9\linewidth]{screenshots/main_screen}
+\includegraphics[width=.9\linewidth]{screenshots/main_screen_marked}
 % \vspace{-5pt}
@@
 Upper-Left Menu: See~\ref{appendix:3}.
+\item
+Coding Space
 \end{itemize}
@@
 
-\subsection{Run analysis of an example from sketch}
+\clearpage
+\subsection{Run analysis of a user-defined reducer function}
 \label{appendix:3}
 
-Besides examples from the benchmark, J-ReCoVer also provides an interactive way to analyse a user defined reducer function.
+Besides examples from the benchmark, J-ReCoVer also provides an interactive way to analyse a user-defined reducer function. 
+One can directly edit the code of a selected example in the coding space for further analysis, or write a reducer function from a sketch. 
 The upper-left menu (below the top menu) provides blank templates for two versions of Hadoop. The templates are

### 2019-06-25 draft.tex
Modification of teh first paragraph of 4.2

@@
 After the transformation described above, the reducer $s_1;\rloop\{s_2\};s_3$
-never calls the $\cur$ function in the $s_1$ part before entering the loop. W.o.l.g, we assume that the reducer reads exactly one input in one loop iteration.
-For the case that multiple reads from input occur in the loop, we can break the multiple reads to several single reads over multiple loop iterations using auxiliary variables and branch statements.
+never calls the $\cur$ function in the $s_1$ part before entering the loop.
+Further, we assume w.l.o.g. that the reducer reads exactly one input in one loop
+iteration. When multiple reads from the input occur in a single branch of the
+loop, we can use additional variables and break the branch into several
+auxiliary ones, each reading just once.
 
@@
 J-ReCoVer successfully handled $115$ cases ($97.5~\%$) out of the considered
-ones. The analysis time ranged between $9.8$ and $8.6$ seconds. On average,
+ones. Among them, $106$ cases are commutative, while $9$ are not. The analysis time ranged between $9.8$ and $8.6$ seconds. On average,
 $72~\%$ of the execution time was spent in compiling Java source code to

### 2019-06-25 draft.tex
sec 4

@@
 Further, we assume w.l.o.g. that the reducer reads exactly one input in one loop
-iteration. When multiple reads from the input occur in a single branch of the
-loop, we can use additional variables and break the branch into several
+iteration. When multiple reads from the input occur in a single execution path from the begin to the end of
+the loop body, we can use additional variables and branch statements to break the path into several
 auxiliary ones, each reading just once.

### 2019-06-25 draft.tex
Tried to add an explanation on the output in the loop

@@
 
+%-----------------------------------------------------------------------------
+\paragraph{A note on dealing with output in the main loop.} 
+%-----------------------------------------------------------------------------
+
+So far we have assumed that there was no output in the main loop and mentioned
+that this restriction is lifted in J-ReCoVer. Due to space restrictions, a
+proper explanation of the way of handling this issue is beyond the scope of this
+paper, but we give at least a brief sketch of the solution. In particular, the
+Preprocessor performs one more transformation which adds an assignment $v := e$
+for every $out(e)$ statement in the main loop where $v$ is a fresh variable
+assigned just once in the loop body. This makes the output visible for our
+analysis since $v$ appears in Formula~\ref{eq:commu}. The Prover then makes an
+additional check whether the value of $F(n, x_1,x_2,\ldots,x_k)$ projected on
+$v$ stays the same for any input value $n$ and any initial values of the
+variables $x_i$.
+
 %=============================================================================

### 2019-06-25 draft.tex
fixed typos in 4.3
Saved space on Page 1, improved the note on output in the loop in Section 2

@@
 \usepackage{multirow}
-\pagestyle{plain}
+%\pagestyle{plain}
+\pagestyle{empty}
 \usepackage{xcolor}
@@
 
-\begin{abstract}
+\vspace*{-4mm}\begin{abstract}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace*{-4mm}
 \section{Introduction} \label{section:introduction}
+\vspace*{-1mm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 reducer is shown in Figure~\ref{fig:reducer_example}. In the paper, to simplify
-the presentation, we assume that a reducer does never produce output in the loop
-body $s_2$. In the J-ReCoVer tool, an algorithm to deal with output inside the
-loop is implemented.
-
-% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-%
-% Just to remember: the way the output from the main loop is handled currently
-% is wrong: One should either check that there is no flow between the input and
-% output in the loop, or to add a check that the projection of the F function on
-% any value output in the main loop stays the same for any input value.
-%
-% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+the presentation, we assume that a reducer does never produce any output in the
+loop body $s_2$. In the J-ReCoVer tool, an algorithm to deal with the output
+inside the loop is implemented (as briefly mentioned at the end of
+Section~\ref{sec:prover}).
 

### 2019-06-25 draft.tex
Language change in 4.3

@@
 the issue, we present a simple example. In the loop body, the input is first
-stored in a variable $t$ and this is then assigned to $s$, i.e., $t:=\cur;s:=t$.
-After the loop, output the value of $s$. In this case, the $F$ function
+stored in a variable $t$ and this is then assigned to $s$, i.e., $t:=\cur;s:=s+t$.
+After the loop, the value of $s$ is output. In this case, the $F$ function
 returns the updated values of both $s$ and $t$ after the execution of the loop
-body. Observe that $F(c_1, F(c_2,s,t)) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t))
-= (c_1+c_2, c_2)$. It follows that Formula~\ref{eq:commu} is invalid. The second
+body. Observe that $F(c_1, F(c_2,s,t)) = (s+c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t))
+= (s+c_1+c_2, c_2)$. It follows that Formula~\ref{eq:commu} is invalid. The second
 component of the returned tuples, which causes the invalidity, corresponds to

### 2019-06-25 draft.tex
little things in sec 1

--- 2019-06-25 draft.tex
@@
 %=============================================================================
-\paragraph*{Related Works}
+\paragraph*{Related Work.}
 %=============================================================================
@@
 [\textbf{2};\textbf{3};5;1;4]$\rightarrow$ [3;2;5;1;4].}, $R$ can be proved to
-be commutative. There is a series of research results on program equivalence
+be commutative. A series of research works address program equivalence
 checking (or closely related topics such as regression verification and
-translation validation): c.f.,
+translation validation), cf.
 \cite{Pnueli:1998:TV,fedyukovich2015automated,barthe2011relational,KlebanovRuemmerUlbrich2017}
@@
 right~\emph{synchronization points} and combining the code of $P$ and $P'$ in an
-interleaved manner. A lot of research effort in this direction is in finding
+interleaved manner. A lot of research effort have been invested into finding
 good synchronization points. In this work, we propose the \emph{head of the
 top-level reducer loop} as the synchronization point suitable for reducer
-commutativity analysis. According to our experience discussed later on, the
+commutativity analysis. According to our experience, discussed later on, the
 reducers usually contain just a single such loop. Moreover, for the case when
-there are more top-level loops in a reducer, we propose a way of breaking such a
+there are more top-level loops in a reducer, we propose a way of breaking the 
 reducer into several ones to be checked independently.
 
-However, in our experience, if one naively reduces the commutativity problem to
+However, we observe that if one naively reduces the commutativity problem to
 an equivalence problem and checks it in a precise manner, many reducers cannot
@@
 
-Various forms of sequentialisation are behind further research works too, such
-as, e.g., works dealing with the concept of \emph{robustness} of event-driven
-asynchronous programs~\cite{ahmed2017:robustness} or those dealing with programs
+%Various forms of sequentialisation are behind further research works too, 
+Various forms of sequentialisation are also used in works dealing with the concept 
+of \emph{robustness} of event-driven
+asynchronous programs~\cite{ahmed2017:robustness} or works dealing with programs
 running under some \emph{relaxed memory
 models}~\cite{ahmed2013:robustness,AbdullaACLR13,AbdullaACLR12}. However, their
-computation models are again quite different from that of reducers, and hence
-the results cannot be directly applied.
+computation models are again quite different from that of reducers, and
+their results cannot be directly applied.
 Besides verification, another interesting research direction is the
-\emph{synthesis} of MapReduce programs~\cite{SmithA16}. Commutativity analysis
-is used as a component under the synthesis framework.
+\emph{synthesis} of MapReduce programs~\cite{SmithA16}, which uses commutativity analysis
+as a component of its framework.
 
@@
 
-%-----------------------------------------------------------------------------
-\paragraph{A note on dealing with output in the main loop.} 
-%-----------------------------------------------------------------------------
-
-So far we have assumed that there was no output in the main loop and mentioned
-that this restriction is lifted in J-ReCoVer. Due to space restrictions, a
-proper explanation of the way of handling this issue is beyond the scope of this
-paper, but we give at least a brief sketch of the solution. In particular, the
-Preprocessor performs one more transformation which adds an assignment $v := e$
-for every $out(e)$ statement in the main loop where $v$ is a fresh variable
-assigned just once in the loop body. This makes the output visible for our
-analysis since $v$ appears in Formula~\ref{eq:commu}. The Prover then makes an
-additional check whether the value of $F(n, x_1,x_2,\ldots,x_k)$ projected on
-$v$ stays the same for any input value $n$ and any initial values of the
-variables $x_i$.
-
 %=============================================================================

### 2019-06-25 draft.tex
fixed typos in 4.3
in sec 2

@@
 We use $[n,m]$ to denote the set of integers $\{k\mid n \leq k\leq m\}$ and lift
-the equality $=$ operation to tuples in the standard way.
+the equality predicate $=$ to tuples in the standard, component-wise, way.
 
@@
 
-For presentation purposes, we provide a sketch of a highly simplified language
-for describing reducers. The language allows us to give examples of reducers and
-to discuss our approach for checking their commutativity. Let $\Var$ be a set of
+%For presentation purposes, we provide a sketch of a highly simplified language
+%for describing reducers. 
+%%
+%The language allows us to give examples of reducers and
+%to discuss our approach for checking their commutativity. 
+%
+To present our approach, we introduce a highly simplified language
+for describing reducers. 
+%
+Let $\Var$ be a set of
 \emph{integer variables}. An \emph{integer expression} in $\Exp$ can either be
 a~variable from $\Var$, a constant value, a call to the $\cur$ function that
-reads and consumes an input value of the reducer, their combinations over basic
-arithmetic operations, or a non-deterministically chosen integer value $*$. A
+reads and consumes an input value of the reducer, a non-deterministically chosen integer value $*$, or a combination of integer expressions over basic
+arithmetic operations. A
 \emph{command} in $\Cmd$ can be an assignment, a branch statement, a sequence of

### 2019-06-25 appendix.tex
Language changes in the appendix

--- 2019-06-25 appendix.tex
@@
 
-Our plan is to demo the basic usage of J-ReCoVer over two examples.
-The first example is a reducer that is not commutative, and J-ReCoVer will report a counterexample.
-Based on this counterexample, we will fix the reducer to get the 2nd example, and let J-ReCoVer to check it again.
-Now J-ReCoVer will report the reducer is commutative.
-Below we give a more detailed description of the functionalities of J-ReCoVer.
+Our plan is to demonstrate the basic usage of J-ReCoVer on two examples. The
+first example is a reducer that is not commutative, and J-ReCoVer will report a
+counterexample. Based on this counterexample, we will fix the reducer to get the
+second example, and let J-ReCoVer to check it again. Now, J-ReCoVer will report
+that the reducer is commutative. Below, we give a more detailed description of
+the functionalities of J-ReCoVer.
 
@@
 
-Figure~\ref{fig:main_screen} shows the main screen of J-ReCoVer. The alignment of user interface elements are as follows:
+Figure~\ref{fig:main_screen} shows the main screen of J-ReCoVer.
 
@@
 % \vspace{-10pt}
-\includegraphics[width=.9\linewidth]{screenshots/main_screen}
+\includegraphics[width=.9\linewidth]{screenshots/main_screen_marked}
 % \vspace{-5pt}
-\caption{Main Screen of J-ReCoVer}
+\caption{The main screen of J-ReCoVer.}
 \label{fig:main_screen}
@@
 
+The alignment of the user interface elements in the main screen is as follows:
 \begin{itemize}
@@
 \item
-\emph{``GitHub''} opens a new tab of the repository of J-ReCoVer. The repository also has source code of benchmarks.
+\emph{``GitHub''} opens a new tab of the repository of J-ReCoVer. The repository
+does also contain the source code of our benchmarks.
 \item
-\emph{``Benchmark''} leads to the list of benchmarks we collected with their results of commutativity analysis as Fig.~\ref{fig:benchmark_list} shows.
-Select the filename or "try it" button will select the example and go back to the main screen.
+\emph{``Benchmark''} leads to the list of benchmarks we collected with their
+results of commutativity analysis as Fig.~\ref{fig:benchmark_list} shows. Select
+a file name or use the ``try it'' button to select an example and go back to the main screen.
 \end{itemize}
@@
 \item
-\emph{``Benchmark List''} provides a quick selection to examples in the benchmark (Fig.~\ref{fig:benchmark_list_right})
+\emph{``Benchmark List''} provides a quick selection of examples in the
+benchmark (Fig.~\ref{fig:benchmark_list_right}).
 \item
@@
 \item
-\emph{``Type''} provides types that J-ReCoVer supports. Details are explained in~\ref{appendix:3}.
+\emph{``Type''} provides types that J-ReCoVer supports. Details are explained in
+Appendix~\ref{appendix:3}.
 \item
@@
 \item
-Upper-Left Menu: See~\ref{appendix:3}.
+Upper-Left Menu: See Appendix~\ref{appendix:3}.
+\item
+Coding Space.
 \end{itemize}
@@
 % \vspace{-5pt}
-\caption{Benchmark list from top menu (part)}
+\caption{A benchmark list from the top menu (a part).}
 \label{fig:benchmark_list}
@@
 % \vspace{-5pt}
-\caption{Benchmark list from right menu (part)}
+\caption{A benchmark list from the right menu (a part).}
 \label{fig:benchmark_list_right}
@@
 
-\subsection{Run analysis of selected benchmark example}
+\subsection{Run Analysis of a Selected Benchmark Example}
 \label{appendix:2}
 
-To run analysis, you can choose an example from benchmark using either the top menu or the right menu, then click the "Run" button of the upper-right menu to start the commutativity analysis of the selected example.
-The pull-down menu "Types" of the upper-right menu provides selectable types for input \texttt{(T1,T2)} and output \texttt{(T3,T4)} key-value pairs.
-Fig.~\ref{fig:type_select_menu} shows the pull-down menu and Fig.~\ref{fig:selectable_types} shows part of the selectable types in J-ReCoVer.
-If one selects an example from the benchmark, the types will be automatically selected to match the example.
-The selection will be needed if the user wants to write a reduce function from sketch for analysis (see~\ref{appendix:3}).
+To run the analysis, one can choose an example from the benchmark using either
+the top menu or the right menu and then click the ``Run'' button of the
+upper-right menu to start the commutativity analysis of the selected example.
+The pull-down menu ``Types'' of the upper-right menu provides selectable types
+for input \texttt{(T1,T2)} and output \texttt{(T3,T4)} key-value pairs.
+Fig.~\ref{fig:type_select_menu} shows the pull-down menu and
+Fig.~\ref{fig:selectable_types} shows a part of the selectable types in
+J-ReCoVer.  If one selects an example from the benchmark, the types will be
+automatically selected to match the example. The selection will be needed if the
+user wants to write a reduce function for analysis  from scratch (see
+Appendix~\ref{appendix:3}).
 
@@
 % \vspace{-5pt}
-\caption{Type select menu}
+\caption{The type selection menu.}
 \label{fig:type_select_menu}
@@
 % \vspace{-5pt}
-\caption{Selectable types (part)}
+\caption{Selectable types (a part).}
 \label{fig:selectable_types}
@@
 
-After J-ReCoVer finishes the analysis, the \emph{"Result:"} tab of the right menu will show the result of the analysis, which can be found in Figure~\ref{fig:analysis_result}.
-Figure~\ref{fig:analysis_result_text} shows the complete analysis report of the benchmark \texttt{dis.java} in Figure~\ref{fig:main_screen}.
+After J-ReCoVer finishes the analysis, the \emph{``Result:''} tab of the right
+menu will show the result of the analysis, which can be found in
+Figure~\ref{fig:analysis_result}. Figure~\ref{fig:analysis_result_text} shows
+the complete analysis report of the benchmark \texttt{dis.java} in
+Figure~\ref{fig:main_screen}.
 
@@
 % \vspace{-5pt}
-\caption{The analysis result}
+\caption{The analysis result.}
 \label{fig:analysis_result}
@@
 \end{mdframed}
-\caption{The analysis result of \texttt{dis.java}}
+\caption{The analysis result of \texttt{dis.java}.}
 \label{fig:analysis_result_text}
@@
 
-In a commutativity analysis, J-ReCoVer first tries to compile the example then perform commutativity analysis.
-If the analysis can not conclude that the example is commutative, J-ReCoVer then runs 500 randomly generated test cases to try to find a counterexample.
-If the test cases all pass, then the result will be "unknown".
+When an analysis is started, J-ReCoVer first tries to compile the chosen example
+and then performs its commutativity analysis. If the analysis cannot conclude
+that the example is commutative, J-ReCoVer then runs 500 randomly generated test
+cases to try to find a counterexample. If the test cases all pass, then the
+result will be ``unknown''.
 
-\subsection{Run analysis of an example from sketch}
+\clearpage
+\subsection{Run Analysis of a User-defined Reducer Function}
 \label{appendix:3}
 
-Besides examples from the benchmark, J-ReCoVer also provides an interactive way to analyse a user defined reducer function.
-The upper-left menu (below the top menu) provides blank templates for two versions of Hadoop. The templates are
+Besides examples from the benchmark, J-ReCoVer also provides an interactive way
+for analysing a user-defined reducer function.  One can directly edit the code
+of a selected example in the coding space for further analysis, or write a
+reducer function from scratch. The upper-left menu (below the top menu)
+provides blank templates for two versions of Hadoop. The templates are shown
+below:
 
@@
 
-, and
-
 \begin{mdframed}[roundcorner=5pt]
@@
 
-In this case, one would have to manually fill the types T1 to T4 and the function body, then selects the types from the pull-down menu, as shown in Figure~\ref{fig:type_select_menu} and Figure~\ref{fig:selectable_types}.
-
-For more details, all selectable types are:
+In this case, one would have to manually fill the types T1 to T4 and the
+function body, and then select the types from the pull-down menu as shown in
+Figure~\ref{fig:type_select_menu} and Figure~\ref{fig:selectable_types}. All
+selectable types are:
 
 \begin{itemize}
-\item Long
-\item BooleanWritable
-\item BytesWritable
-\item Text
-\item Double
-\item DoubleWritable
-\item Float
-\item FloatWritable
+\item Long,
+\item BooleanWritable,
+\item BytesWritable,
+\item Text,
+\item Double,
+\item DoubleWritable,
+\item Float,
+\item FloatWritable.
 \end{itemize}

### 2019-06-25 draft.tex
save space in sec 4 and 5

@@
 use five different input list of lengths 5, 7, 9, 11, and 13. For each length,
-we generate 300 lists and pick uniformly at random one of its permutations.
+we generate 100 lists and pick uniformly at random one of its permutations.
 Although the approach is simple; in practice, it finds counterexamples in all of
@@
 %=============================================================================
+\vspace{-2mm}
 \subsection{The Prover: Reduce Commutativity Checking to SMT Solving}
+\vspace{-2mm}
 \label{sec:prover}
@@
 %-----------------------------------------------------------------------------
+
 \paragraph{A note on dealing with output in the main loop.} 
@@
 %=============================================================================
+\vspace{-2mm}
 \subsection{An Optimisation by Live Variable Analysis}
+\vspace{-2mm}
 \label{section:optimizations}
@@
 to collect all variables whose value may propagate to the output command after
-the loop execution. Only these variables are then required to be equivalent. In
+the loop execution.
+Only these variables are then required to be equivalent.
+For the example above, the variable $t$ will be ignored in the equivalence checking and hence the program can be proven commutative.
+In
 our evaluation, the ratio of reducers that our approach can successfully analyse
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{-3mm}
 \section{Evaluation} \label{section:exp}
+\vspace{-2mm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %-----------------------------------------------------------------------------
+\vspace{-1mm}
 \paragraph*{Benchmark collection} 
@@
 %-----------------------------------------------------------------------------
+\vspace{-1mm}
 \paragraph*{Results} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\vspace{-2mm}
 \bibliographystyle{splncs-sorted}

### 2019-06-25 draft.tex
2 and 3

--- 2019-06-25 draft.tex
@@
 the presentation, we assume that a reducer does never produce any output in the
-loop body $s_2$. In the J-ReCoVer tool, an algorithm to deal with the output
-inside the loop is implemented (as briefly mentioned at the end of
+loop body $s_2$. J-ReCoVer implements an algorithm to deal with an output
+inside the loop (as briefly mentioned at the end of
 Section~\ref{sec:prover}).
@@
 popular programming language used in the Hadoop MapReduce
-framework. The J-ReCoVer tool has three main components, the
-\emph{Preprocessor}, the \emph{Prover}, and the \emph{BugFinder}. As the name
-suggests, the Preprocessor reads as input a reducer program and performs the
+framework. The J-ReCoVer tool has three main components,
+\emph{Preprocessor}, \emph{Prover}, and \emph{BugFinder}. As the name
+suggests, Preprocessor reads as input a reducer program and performs the
 required preprocessing. The goal of Prover is to show that a given reducer is
@@
 The \emph{Preprocessor component} first compiles a reducer program to bytecode
-and uses the tool Soot to further convert it to the so-called ``Jimple'' format,
+and uses the tool Soot\footnote{\url{https://github.com/Sable/soot}} to further convert it to the so-called ``Jimple'' format,
 which is an intermediate language designed to simplify the analysis of Java
@@
 
-The \emph{BugFinder component} randomly generates pairs of lists. The lists in a
-pair are permutations of each other. A concrete counterexample is reported if
-inputting any pair of lists from the generated ones to the reducer generates
-different results. Our procedure for generating random pairs is quite naive. We
+The \emph{BugFinder component} generates random pairs of lists, 
+with the list of each pair being permutations of each other. 
+A concrete counterexample is reported if
+the reducer outputs different results for the two lists of a generated pair. 
+Our procedure for generating random pairs is quite naive. We
 use five different input list of lengths 5, 7, 9, 11, and 13. For each length,
@@
 Although the approach is simple; in practice, it finds counterexamples in all of
-our non-commutative benchmarks in a few seconds.
+our non-commutative benchmarks in few seconds.
 
 The \emph{Prover component} reduces the commutativity problem to an SMT
-satisfiability problem. From a high-level point of view, we check equivalence
+problem. From a high-level point of view, we are checking equivalence
 between a reducer program and its variant that has two consecutive inputs
-swapped. We show that this can be reduced to a first-order formula and give it
+swapped. We show that this equivalence check can be reduced to a first-order formula and give it
 to the SMT solver Z3 for solving. In case that Z3 proves the formula

### 2019-06-25 draft.tex
little things in 4

@@
 
-In our initial experiments, we realised that Formula~\ref{eq:commu} is a
-condition that is too strong for the reducer to be commutative. To illustrate
+In our initial experiments, we realised that Formula~\ref{eq:commu} is too strong, 
+too often violated by reducers that are commutative.
+%
+To illustrate
 the issue, we present a simple example. In the loop body, the input is first
 stored in a variable $t$ and this is then assigned to $s$, i.e., $t:=\cur;s:=s+t$.
-After the loop, the value of $s$ is output. In this case, the $F$ function
+After the loop, the value of $s$ is output. In this case, the function $F$ 
 returns the updated values of both $s$ and $t$ after the execution of the loop

### 2019-07-29 draft.tex
4
one bloody referrence
Added authors and Czech acknowledgement

@@
 
-\title{\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier}
-\author{}
-\institute{}
-\hide{
+\title{\hspace{-1mm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier\thanks{The
+work was supported by the Czech Science Foundation project
+17-12465S.}\vspace*{-2mm}}
+
 \author{
-Yu-Fang Chen\inst{1}\inst{2}
+Yu-Fang Chen\inst{1,2}
 \and
@@
 \and
+Luk\'{a}\v{s} Hol\'{\i}k\inst{3}
+\and
+Wei-Tsung Kao\inst{1}
+\and
 Hsin-Hung Lin\inst{1}
 \and
-Wei-Tsung Kao\inst{1}
+Tom\'{a}\v{s} Vojnar\inst{3}
 \and
@@
 \and
-Graduate Institute of Information Management, National Taipei University, Taiwan
-}}
-\author{}
-\institute{}
+Graduate Institute of Information Management, National Taipei University,
+Taiwan
+\and
+FIT,  IT4I Centre of Excellence,Brno University of Technology, Czechia
+}
 
@@
 
-\vspace*{-4mm}\begin{abstract}
-
-The MapReduce framework for data-parallel computation was first proposed by
-Google~\cite{dean04} and later implemented in the Apache Hadoop
-project. Under the MapReduce framework, a reducer computes output
-values from a sequence of input values transmitted over the network. Due to
-non-determinism in data transmission, the order in which input values arrive at
-the reducer is not fixed. In relation to this, the \emph{commutativity problem}
-of reducers asks if the output of a reducer is independent of the order of its
-inputs. Indeed, there are several advantages for a reducer to be commutative,
-e.g., the verification problem of a MapReduce program can be reduced to the
-problem of verifying a sequential program. We present the tool J-ReCoVer (Java
-Reducer Commutativity Verifier) that implements effective heuristics for reducer
-commutativity analysis. J-ReCoVer is the first tool that is specialized in
-checking reducer commutativity. Our experimental results over 118 benchmark
-examples collected from open repositories are very positive; J-ReCoVer correctly
-handles over 97~\% of them.
-
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace*{-4mm}
-\section{Introduction} \label{section:introduction}
-\vspace*{-1mm}
+\vspace*{-4mm}\begin{abstract} The MapReduce framework for data-parallel
+computation was first proposed by Google~\cite{dean04} and later implemented in
+the Apache Hadoop project. Under the MapReduce framework, a reducer computes
+output values from a sequence of input values transmitted over the network. Due
+to non-determinism in data transmission, the order in which input values arrive
+at the reducer is not fixed. In relation to this, the \emph{commutativity
+problem} of reducers asks if the output of a reducer is independent of the order
+of its inputs. Indeed, there are several advantages for a reducer to be
+commutative, e.g., the verification problem of a MapReduce program can be
+reduced to the problem of verifying a sequential program. We present the tool
+J-ReCoVer (Java Reducer Commutativity Verifier) that implements effective
+heuristics for reducer commutativity analysis. J-ReCoVer is the first tool that
+is specialized in checking reducer commutativity. Our experimental results over
+118 benchmark examples collected from open repositories are very positive;
+J-ReCoVer correctly handles over 97~\% of them. \end{abstract}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace*{-5mm}\section{Introduction}\label{section:introduction}\vspace*{-2mm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % efficient procedure for checking reducer commutativity.
+
+%!!!!!!!!!!!!!!!!!!!!!!!!
+\enlargethispage{5mm}
+%!!!!!!!!!!!!!!!!!!!!!!!!
 
@@
 
+%!!!!!!!!!!!!!!!!!!!!!!!!
+\enlargethispage{5mm}
+%!!!!!!!!!!!!!!!!!!!!!!!!
+
 However, we observe that if one naively reduces the commutativity problem to
@@
 %Various forms of sequentialisation are behind further research works too, 
-Various forms of sequentialisation are also used in works dealing with the concept 
-of \emph{robustness} of event-driven
-asynchronous programs~\cite{ahmed2017:robustness} or works dealing with programs
-running under some \emph{relaxed memory
+Various forms of sequentialisation are also used in works dealing with the
+concept of \emph{robustness} of event-driven asynchronous
+programs~\cite{ahmed2017:robustness} or works dealing with programs running
+under some \emph{relaxed memory
 models}~\cite{ahmed2013:robustness,AbdullaACLR13,AbdullaACLR12}. However, their
-computation models are again quite different from that of reducers, and
-their results cannot be directly applied.
-Besides verification, another interesting research direction is the
-\emph{synthesis} of MapReduce programs~\cite{SmithA16}, which uses commutativity analysis
-as a component of its framework.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Notations and Definitions} \label{section:integer-reducers}
+computation models are again quite different from that of reducers, and their
+results cannot be directly applied. Besides verification, another interesting
+research direction, using commutativity analysis as a component, is
+\emph{synthesis} of MapReduce programs~\cite{SmithA16}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace*{-2mm} \section{Notations and Definitions}
+\label{section:integer-reducers} \vspace*{-1mm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Section~\ref{sec:prover}).
+
+%!!!!!!!!!!!!!!!!!!!!!!!!
+\enlargethispage{5mm}
+%!!!!!!!!!!!!!!!!!!!!!!!!
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{-3mm}
+%\vspace{-3mm}
 \section{Evaluation} \label{section:exp}
-\vspace{-2mm}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\vspace{-2mm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+\enlargethispage*{4mm}
+%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 
@@
 merged loop. Extensions of J-ReCoVer to be able to handle such constructions,
-together with a support for more data types, belong among our future works.
+together with a support for more data types, is among our future directions.
 
@@
 
+%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+\enlargethispage*{4mm}
+%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-08-26 draft.tex
Added authors and Czech acknowledgement
final version

@@
 \usepackage{graphicx}
-\usepackage{appendix}
 \usepackage{amssymb}
@@
 \title{\hspace{-1mm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier\thanks{The
-work was supported by the Czech Science Foundation project
-17-12465S.}\vspace*{-2mm}}
+work was supported by the Minister of Science and Technology of Taiwan project 106-2221-E-001-009-MY3 and Czech Science Foundation project
+17-12465S.}}
 
@@
 
-\vspace*{-4mm}\begin{abstract} The MapReduce framework for data-parallel
+\begin{abstract} The MapReduce framework for data-parallel
 computation was first proposed by Google~\cite{dean04} and later implemented in
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace*{-5mm}\section{Introduction}\label{section:introduction}\vspace*{-2mm}
+\section{Introduction}\label{section:introduction}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % efficient procedure for checking reducer commutativity.
-
-%!!!!!!!!!!!!!!!!!!!!!!!!
-\enlargethispage{5mm}
-%!!!!!!!!!!!!!!!!!!!!!!!!
 
@@
 
-%!!!!!!!!!!!!!!!!!!!!!!!!
-\enlargethispage{5mm}
-%!!!!!!!!!!!!!!!!!!!!!!!!
-
 However, we observe that if one naively reduces the commutativity problem to
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace*{-2mm} \section{Notations and Definitions}
-\label{section:integer-reducers} \vspace*{-1mm}
+\section{Notations and Definitions}
+\label{section:integer-reducers}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%!!!!!!!!!!!!!!!!!!!!!!!!
-\enlargethispage{5mm}
-%!!!!!!!!!!!!!!!!!!!!!!!!
-
 Some reducers use two (or more) top-level loops to compute the output, possibly
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace*{-2mm}
 \section{Overview of the J-ReCoVer Tool} \label{sec:overview}
-\vspace*{-1mm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%For example, it converts all output commands $out(e)$ inside loops to a special assignment (as explained in Section~\ref{sec:program_trans1}).
+
+\begin{wrapfigure}{r}{7cm}
+	\vspace{-3mm}
+\centering
+	\scalebox{0.7}{
+		\begin{tikzpicture}
+
+		%J-ReCoVer
+		\node[draw=red!30, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=8cm,fill=red!10,minimum height=7cm] (jrecover) at (5,0) {};
+		\node at (5,-.5) {\textbf{J-ReCoVer}};
+
+		%JAVA reducer
+		\node[draw=yellow!80, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=0.6cm,fill=yellow!20,minimum height=4cm] (reducer) at (0.5,-1.6) {};
+		\node[rotate=270, align = center] at (0.5,-3.6) {Java Reducer};
+
+		%JPreprocessor
+		\node[draw=blue!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=3cm,fill=blue!20,minimum height=6.cm] (preprocessor) at (3,-.8) {};
+		\node[] at (3,-1.2) {Preprocessor};
+
+		%JPreprocessor->Interface
+		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=0.3cm,fill=green!10,minimum height=1.5cm] (interface1) at (1.8,-1.6) {};
+		\node[rotate=270, align = center] at (1.8,-2.4) {Web};
+
+		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=0.3cm,fill=green!10,minimum height=3cm] (interace2) at (1.8,-3.6) {};
+		\node[rotate=270, align = center] at (1.8,-5) {Installed app.};
+
+		%JPreprocessor->Technologies
+		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1cm] (soot) at (3.2,-2) {};
+		\node at (3.2,-2.6) {Soot};
+
+		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.4cm] (symex) at (3.2,-3.3) {};
+		\node at (3.2,-4) {
+			\begin{minipage}[t]{0.222\textwidth}
+			\centering
+			Dummy\\
+			Hadoop\\
+			Environment
+			\end{minipage}		
+			};
+
+			\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (prog_trans) at (3.2,-5) {};
+			\node at (3.2,-5.6) {
+				\begin{minipage}[t]{0.222\textwidth}
+				\centering
+				Program\\
+				Transform.
+				\end{minipage}
+			};
+
+		%JProver
+		\node[draw=blue!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=3cm,fill=blue!20,minimum height=5cm] (prover) at (6.5,-0.8) {};
+		\node[] at (6.5,-1.2) {Prover};
+
+		%JProver->Technologies
+		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (6.5,-2.4) {};
+
+		\node at (6.5,-3) {
+			\begin{minipage}[t]{0.222\textwidth}
+			\centering
+			Z3 SMT \\
+			Solver
+			\end{minipage}
+		};
+
+		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (6.5,-4.) {};
+
+		\node at (6.5,-4.6) {
+			\begin{minipage}[t]{0.222\textwidth}
+			\centering
+			Live Variable \\
+			Analysis
+			\end{minipage}
+		};
+
+		%JBugFinder
+		\node[draw=blue!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=3cm,fill=blue!20,minimum height=0.5cm] (learner) at (6.5,-6.2) {};
+		\node[] at (6.5,-6.5) {BugFinder};
+
+		%JResults
+
+		\node[rotate=270, align = center] at (9.5,-1) {
+			Commutative
+		};
+
+		\node[rotate=270, align = center] at (9.5,-3.5) {
+			Unknown
+		};
+
+		\node[rotate=270, align = center] at (9.6,-6) {
+			\begin{minipage}[t]{0.25\textwidth}
+			\centering
+			Non-Commutative	 \\
+			+ Counterexample
+			\end{minipage}
+
+		};
+
+		\draw [->] (8,-6.6) -- (9.2,-6.6) ;
+		\draw [->] (8,-1.4) -- (9.2,-1.4) ;
+		\draw [-] (8,-6.3) -- (8.5,-6.3) --(8.5,-3.5);
+		\draw [->] (8,-3.5) -- (9.2,-3.5) ;
+
+		\draw [->] (4.5,-3) -- (5,-3) ;
+		\draw [->] (4.5,-6.5) -- (5,-6.5) ;
+
+		\draw [->] (0.8,-4) -- (1.5,-4) ;
+
+		\end{tikzpicture}
+	}
+		\vspace{-1cm}
+	\caption{Overview of the J-ReCoVer tool. }\label{fig:overview-jrecover}
+		\vspace{-0.3cm}
+
+\end{wrapfigure}
+
 The \emph{Preprocessor component} first compiles a reducer program to bytecode
@@
 controlled by J-ReCoVer. Finally, the Preprocessor performs  a program transformation to simplify the analysis.
-
-%For example, it converts all output commands $out(e)$ inside loops to a special assignment (as explained in Section~\ref{sec:program_trans1}).
-
-\begin{wrapfigure}{r}{7cm}
-	\vspace{-8mm}
-\centering
-	\scalebox{0.7}{
-		\begin{tikzpicture}
-
-		%J-ReCoVer
-		\node[draw=red!30, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=8cm,fill=red!10,minimum height=7cm] (jrecover) at (5,0) {};
-		\node at (5,-.5) {\textbf{J-ReCoVer}};
-
-		%JAVA reducer
-		\node[draw=yellow!80, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=0.6cm,fill=yellow!20,minimum height=4cm] (reducer) at (0.5,-1.6) {};
-		\node[rotate=270, align = center] at (0.5,-3.6) {Java Reducer};
-
-		%JPreprocessor
-		\node[draw=blue!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=3cm,fill=blue!20,minimum height=6.cm] (preprocessor) at (3,-.8) {};
-		\node[] at (3,-1.2) {Preprocessor};
-
-		%JPreprocessor->Interface
-		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=0.3cm,fill=green!10,minimum height=1.5cm] (interface1) at (1.8,-1.6) {};
-		\node[rotate=270, align = center] at (1.8,-2.4) {Web};
-
-		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=0.3cm,fill=green!10,minimum height=3cm] (interace2) at (1.8,-3.6) {};
-		\node[rotate=270, align = center] at (1.8,-5) {Installed app.};
-
-		%JPreprocessor->Technologies
-		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1cm] (soot) at (3.2,-2) {};
-		\node at (3.2,-2.6) {Soot};
-
-		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.4cm] (symex) at (3.2,-3.3) {};
-		\node at (3.2,-4) {
-			\begin{minipage}[t]{0.222\textwidth}
-			\centering
-			Dummy\\
-			Hadoop\\
-			Environment
-			\end{minipage}		
-			};
-
-			\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (prog_trans) at (3.2,-5) {};
-			\node at (3.2,-5.6) {
-				\begin{minipage}[t]{0.222\textwidth}
-				\centering
-				Program\\
-				Transform.
-				\end{minipage}
-			};
-
-		%JProver
-		\node[draw=blue!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=3cm,fill=blue!20,minimum height=5cm] (prover) at (6.5,-0.8) {};
-		\node[] at (6.5,-1.2) {Prover};
-
-		%JProver->Technologies
-		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (6.5,-2.4) {};
-
-		\node at (6.5,-3) {
-			\begin{minipage}[t]{0.222\textwidth}
-			\centering
-			Z3 SMT \\
-			Solver
-			\end{minipage}
-		};
-
-		\node[draw=green!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=2cm,fill=green!10,minimum height=1.2cm] (z3) at (6.5,-4.) {};
-
-		\node at (6.5,-4.6) {
-			\begin{minipage}[t]{0.222\textwidth}
-			\centering
-			Live Variable \\
-			Analysis
-			\end{minipage}
-		};
-
-		%JBugFinder
-		\node[draw=blue!50, inner sep=0, anchor=north,rounded corners, fill opacity=0.85,text width=3cm,fill=blue!20,minimum height=0.5cm] (learner) at (6.5,-6.2) {};
-		\node[] at (6.5,-6.5) {BugFinder};
-
-		%JResults
-
-		\node[rotate=270, align = center] at (9.5,-1) {
-			Commutative
-		};
-
-		\node[rotate=270, align = center] at (9.5,-3.5) {
-			Unknown
-		};
-
-		\node[rotate=270, align = center] at (9.6,-6) {
-			\begin{minipage}[t]{0.25\textwidth}
-			\centering
-			Non-Commutative	 \\
-			+ Counterexample
-			\end{minipage}
-
-		};
-
-		\draw [->] (8,-6.6) -- (9.2,-6.6) ;
-		\draw [->] (8,-1.4) -- (9.2,-1.4) ;
-		\draw [-] (8,-6.3) -- (8.5,-6.3) --(8.5,-3.5);
-		\draw [->] (8,-3.5) -- (9.2,-3.5) ;
-
-		\draw [->] (4.5,-3) -- (5,-3) ;
-		\draw [->] (4.5,-6.5) -- (5,-6.5) ;
-
-		\draw [->] (0.8,-4) -- (1.5,-4) ;
-
-		\end{tikzpicture}
-	}
-		\vspace{-1cm}
-	\caption{Overview of the J-ReCoVer tool. }\label{fig:overview-jrecover}
-		\vspace{-0.8cm}
-
-\end{wrapfigure}
-
-%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-\enlargethispage{4mm}
-%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace*{-2mm}
 \section{The Preprocessor and the Prover} \label{sec:preprocessor_prover}
-\vspace*{-1mm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %=============================================================================
-\vspace*{-2mm}
 \subsection{The Program Transformation in the Preprocessor}
 \label{sec:program_trans1}
-\vspace*{-1mm}
 %=============================================================================
 
-%-----------------------------------------------------------------------------
-%\paragraph*{Handling the access to $\cur$ before entering the loop.}
-%-----------------------------------------------------------------------------
-
-\begin{wrapfigure}[11]{r}{3.5cm}
-	\vspace{-18mm}
+In real-world reducers, it is often the case that the $s_1$ part of the reducer
+reads from the input. Since our reduction of the commutativity problem to SMT
+solving, which is presented in Section~\ref{sec:prover}, concentrates on the
+influence of the input on the loop $s_2$ only, we need to transform the reducer
+such that any input happens in the loop only.
+
+\begin{wrapfigure}{r}{3.5cm}
+	\vspace{-13mm}
 	\begin{algorithm}[H]
@@
 	\end{algorithm}
-	\vspace{-0.8cm}
+
 	\caption{The max$^+$ reducer with input before the main loop.}
-	\vspace{-11mm}
+
 	\label{fig:reducer_max1}
 \end{wrapfigure}
-
-%	\begin{figure}[t]
-%		\begin{minipage}{0.4\textwidth}
-%			\begin{algorithm}[H]
-%				\;\;$m := \cur + 10$; \;
-%				\Loop{}{
-%					$t:=\cur$\;
-%					\uIf{ $t> m$}{
-%						$m := t$ \;
-%					}
-%				};
-%				$out(m)$\;\;
-%			\end{algorithm}
-%			\caption*{(a) Reducer max$^+$}
-%		\end{minipage}
-%		\begin{minipage}{0.6\textwidth}
-%			\begin{algorithm}[H]
-%				$s:=*;$\;
-%				\Loop{}{
-%					\uIf{$s=1$}{$m := \cur + 10; s:= 2$}
-%					\uElse{
-%						$t:=\cur$\;
-%						\uIf{ $t > m$}{
-%							$m := t$ \;
-%						}
-%					}
-%				};
-%				$out(m)$
-%			\end{algorithm}
-%			\caption*{(b) Reducer max$^{+\mathtt{fix}}$}
-%		\end{minipage}
-%		\caption{Reducer examples}
-%		\label{fig:reducer_max}
-%	\end{figure}
-
-In real-world reducers, it is often the case that the $s_1$ part of the reducer
-reads from the input. Since our reduction of the commutativity problem to SMT
-solving, which is presented in Section~\ref{sec:prover}, concentrates on the
-influence of the input on the loop $s_2$ only, we need to transform the reducer
-such that any input happens in the loop only.
 
@@
 
-\begin{wrapfigure}[12]{r}{5.3cm}
-	\vspace{-10mm}
+\begin{wrapfigure}{r}{5.3cm}
+
 	\begin{algorithm}[H]
@@
 %=============================================================================
-\vspace{-2mm}
 \subsection{The Prover: Reduce Commutativity Checking to SMT Solving}
-\vspace{-2mm}
 \label{sec:prover}
@@
 Further, we assume w.l.o.g. that the reducer reads exactly one input in one loop
-iteration. When multiple reads from the input occur in a single execution path from the begin to the end of
-the loop body, we can use additional variables and branch statements to break the path into several
-auxiliary ones, each reading just once.
-
-The command $s_2$
-can be viewed as a function $F$ that reads the values of all variables and the
-current input before executing $s_2$ and outputs the values of all variables
-after $s_2$. Formally, the function $F(n,x_1,x_2,\ldots,x_k): \Z^{k+1}
+iteration.
+When multiple reads from the input occur in a single execution path from the begin to the end of the loop body, we can use additional variables and branch statements to break the path into several auxiliary ones, each reading just once.
+
+The command $s_2$ can be viewed as a function $F$ that reads the values of all variables and the current input before executing $s_2$ and outputs the values of all variables after $s_2$.
+The loop body $s_2$ contains no nested loop structure.
+Hence, a bounded summary in quantifier-free linear integer arithmetic is sufficient~for~describing~$F$.
+
+Formally, the function $F(n,x_1,x_2,\ldots,x_k): \Z^{k+1}
 \rightarrow \Z^k$ returns a tuple of values $x_1',x_2',\ldots,x_k'$ where $n$ is
@@
 %=============================================================================
-\vspace{-2mm}
 \subsection{An Optimisation by Live Variable Analysis}
-\vspace{-2mm}
 \label{section:optimizations}
@@
 
-%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-\enlargethispage*{4mm}
-%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-
 J-ReCoVer is implemented in Java and built on top of Soot 2.5.0 and Z3 4.7.1. We
@@
 \begin{wraptable}[7]{r}{40mm}
-	\vspace{-8mm}
+
 	\caption{Size of the reducers.}
@@
 %-----------------------------------------------------------------------------
-\vspace{-1mm}
 \paragraph*{Benchmark collection} 
@@
 %-----------------------------------------------------------------------------
-\vspace{-1mm}
 \paragraph*{Results} 
@@
 
-%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-\enlargethispage*{4mm}
-%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{-2mm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{splncs-sorted}
@@
 
-\input{appendix}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-08-26 draft.tex
final version
Minor change of language in the acknowledgement

@@
 \title{\hspace{-1mm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier\thanks{The
-work was supported by the Minister of Science and Technology of Taiwan project 106-2221-E-001-009-MY3 and Czech Science Foundation project
+work was supported by the Minister of Science and Technology of Taiwan project
+106-2221-E-001-009-MY3 and the Czech Science Foundation project
 17-12465S.}}
@@
 The command $s_2$ can be viewed as a function $F$ that reads the values of all variables and the current input before executing $s_2$ and outputs the values of all variables after $s_2$.
-The loop body $s_2$ contains no nested loop structure.
+Note that $s_2$ contains no nested loop structure.
 Hence, a bounded summary in quantifier-free linear integer arithmetic is sufficient~for~describing~$F$.
